\footnotetext[1]{1703 sets/2458 disks}

%%   1289  1 disk sets = 1289
%%    324  2 disk sets =  648
%%     39  3 disk sets =  117
%%     16  4 disk sets =   64
%%     11  5 disk sets =   55
%%     10  6 disk sets =   60
%%      2  7 disk sets =   14
%%      2  8 disk sets =   16
%%      4  9 disk sets =   36
%%      2 10 disk sets =   20
%%      1 12 disk set  =   12
%%      1 13 disk set  =   13
%%      1 16 disk set  =   16
%%      1 98 disk set  =   98

\begin{enumerate}

\cd*\relax
\artist{Abrahamsen, Hans}.
\cdtitle{Sonata for Solo Cello}.
\see{1700}.

\cd\relax
\artist{Accardo, Salvatore}.
\cdtitle{\track \C{Edward Elgar} Concerto for Violin and Orchestra
  Op.~61 in B~minor \; \track \C{William Walton} Concerto for Violin and
  Orchestra}.
The London Symphony Orchestra.
Richard Hickox, cond.
Collins Classics, 1990 \cdnum{13382}.

\cd\relax
\artist{Adams, Douglas}.
\cdtitle{The Hitch Hiker's Guide to the Galaxy}.
Time Warner AudioBooks, 1994 \cdnum[6]{2-521269}.

\cd\relax
\artist{Adelphi Saxophone Quartet}.
\cdtitle{Simply Four Saxophones}.
EMI Classics, 1998 \cdnum{7243 5 72527 2~0}.

\cd\relax
\artist{Aeolian Winds}.
\cdtitle{The Devil's Dictionary \: \track \C{Gy\"orgy Ligeti} Six
  Bagatelles \; \track \C{Carl Nielsen} Wind Quintet, Op.~43 \; \track
  \C{Gary Kulesha} Bagatelles from ``The Devil's Dictionary'' \; \track
  \C{Jean Fran\c{c}aix} Wind Quintet No.~1 \(1948\)}.
Fiona Wilkinson (flute), Ian Franklin (oboe), Peter Shackleton
  (clarinet), David Haward (bassoon) and Derek Conrod (horn).
CBC Records, 2001 \cdnum{MVCD~1142}.

\cd\relax
\artist{Aeschylus}.
\cdtitle{Oresteia, The}.
The Hollywood Theatre for the Ear.
Blackstone Audio, 2007 (0-7861-5934-0).

\cd*\relax
\artist{Ahle, Johann Rudolf}.
\cdtitle{Missa \`a~10: Kyrie}.
\see{73}.

\cd\relax
\artist{Aho, Kalevi}.
\cdtitle{\track Kiinalaisia lauluja \(Chinese Songs\) \; \track Symphony
  No.~4}.
Tiina Vahevaara (soprano).
Lahti Symphony Orchestra.
Osmo V\"ansk\"a, cond.
BIS, 2000 \cdnum{BIS-CD-1066}.

\cd\relax
\artist{Aho, Kalevi}.
\cdtitle{\track Quintet for Bassoon and String Quartet \(1977\) \;
  \track Quintet for Alto Saxophone, Bassoon, Viola, Cello and Double
  Base \(1994\)}.
Harri Ahmas (bassoon), Jyrki Lasonpalo (violin~I), Ulla-Maija Hallantie
  (violin~II), Anu Airas (viola), Ilkka P\"alli (cello), Hannu Lehtonen
  (alto saxophone) and Eero Munter (double bass).
BIS, 1997 \cdnum{BIS-CD-866}.

\cd\relax
\artist{Aho, Kalevi}.
\cdtitle{Symphony No.~10 \and Rejoicing of the Deep Waters}.
Lahti Symphony Orchestra.
Osmo V\"anska\"a, cond.
BIS, 1997 \cdnum{BIS-CD-856}.

\cd\relax
\artist{Aho, Kalevi}.
\cdtitle{\track Symphony No.~2 \(1970/1995\) \; \track Symphony No.~7
  ``Insect Symphony'' \(1988\)}.
Lahti Symphony Orchestra.
Osmo V\"ansk\"a, cond.
BIS, 1998 \cdnum{BIS-CD-936}.

\cd\relax
\artist{Akademie f\"ur Alte Musik Berlin}.
\cdtitle{Ouvert\"uren: Music for the Hamburg Opera \: \track \C{Georg
  Caspar Sch\"urmann} Suite ``Ludovicus Pius'' \; \track \C{Philipp
  Heinrich Erlebach} Ouverture No.~4 \; \track \C{Reinhard Keiser} Le
  Ridicule Prince Jodelet \; \track \C{Georg Friedrich Haendel} Almira
  \; \track \C{Johann Christian Schieferdecker} Concerts musicaux
  \(1713\): Premier concert}.
Harmonia Mundi, 2005 \cdnum{HMC 901852}.

\cd\relax
\artist{Alban Berg Quartet}.
\cdtitle{\track \C{Joseph Haydn} Streichquartette Op.~77, Nos.~1 and~2
  \; \track \C{Luciano Berio} Notturno \(Quartetto~III\)}.
EMI Records, 1995 \cdnum{7243 5~55191 2~2}.

\cd*\relax
\artist{Alb\'eniz, Isaac}.
\cdtitle{Evocaci\'on \(\from Iberia, Book~1\)}.
\see{877}.

\cd\relax
\artist{Alb\'eniz, Isaac}.
\cdtitle{\track Iberia \; \track Navarra \; \track \C{Enrique Granados}
  Goyescas}.
Alicia de Larrocha.
The Decca Record Company, 1996 \cdnum[2]{448 191-2}.

\cd*\relax
\artist{Alb\'eniz, Isaac}.
\cdtitle{Iberia \and Navarra}.
\see{477}.

\cd*\relax
\artist{Alb\'eniz, Isaac}.
\cdtitle{Iberia \(Book~1\)}.
\see{43}.

\cd*\relax
\artist{Alb\'eniz, Isaac}.
\cdtitle{Tango, Op.~165, No.~2}.
\see{1604}.

\cd*\relax
\artist{Alb\'eniz, Mateo}.
\cdtitle{Piano Sonata in~D}.
\see{477}.

\cd*\relax
\artist{Albert, Stephen}.
\cdtitle{Concerto for Cello and Orchestra}.
\see{1019}.

\cd\relax
\artist{Albinoni, Tomaso}.
\cdtitle{Wind Concertos \: \track Concerto in G~major for two oboes,
  op~9 no~6 \and Concerto in C~major for trumpet, three oboes, basson
  and continuo \and Concerto in D~minor for solo oboe, op~9 no~2 \and
  Concerto in C~major for two oboes, op~9, no~9 \; \track \C{Antonio
  Vivaldi} Concerto in C~major for two oboes, two clarinets and strings,
  RV560 \and Concerto in F~major for solo oboe, RV455 \and Concerto in
  C~major for two oboes, two clarinets and strings, RV559}.
Paul Goodwin (solo oboe).
The King's Consort.
Robert King, cond.
Hyperion, 1990 \cdnum{CDA66383}.

\cd*\relax
\artist{Albrechtsberger, Johann Georg}.
\cdtitle{Concerto in B~flat major for Alto Trombone}.
\see{963}.

\cd\relax
\artist{Alfv\'en, Hugo}.
\cdtitle{Orchestral Works, Volume~1 \: \track Festspel, Op.~25 \; \track
  Suite from Bergakungen \; \track Uppsalarapsodi, Op.~24 \(Svensk
  rapsodi nr.~2\) \; \track Symphony No.~1 in F~minor, Op.~7}.
Royal Scottish National Orchestra.
Niklas Will\'en, cond.
Naxos, 1998 \cdnum{8.553962}.

\cd\relax
\artist{Alfv\'en, Hugo}.
\cdtitle{Orchestral Works, Volume~2 \: \track Dalarapsodi, Op.~47
  \(Svensk rapsodi nr.~3\) \; \track En sk\"arg{\aa}rdss\"agen, Op.~20
  \(Legend of the Skerries\) \; \track Symphony No.~3 in E~major,
  Op.~23}.
Royal Scottish National Orchestra.
Niklas Will\'en, cond.
Naxos, 1999 \cdnum{8.553729}.

\cd*\relax
\artist{Aliabiev, Alexander}.
\cdtitle{The Nightingale \arr{Franz Liszt}}.
\see{645}.

\cd\relax
\artist{Ali-Zadeh, Franghiz}.
\cdtitle{Mugam Sayagi \: \track Oasis \; \track Apsheron Quintet \;
  \track Music for Piano \; \track Mugam Sayagi}.
Kronos Quartet and Franghiz Ali-Zadeh (piano).
Nonesuch, 2005 \cdnum{79804-2}.

\cd*\relax
\artist{Alkan, Charles-Valentin}.
\cdtitle{Concerto da Camera in C~sharp minor op~10 no~2 \and Concerto da
  Camera in A~minor op~10 no~1}.
\see{722}.

\cd\relax
\artist{Alkan, Charles-Valentin}.
\cdtitle{\track Grande Sonate ``Les Quatre Ages'' op.~33 \; \track
  Sonatine op.~61 \; \track Barcarolle op.~65 no.~6 \; \track Le Festin
  D'Esope op.~39 no~12}.
Marc-Andr\'e Hamelin.
Hyperion, 1994 \cdnum{CDA66794}.

\cd*\relax
\artist{Alkan, Charles-Valentin}.
\cdtitle{Haydn Adante from Symphony No~94 \(transcription\) \and
  Esquisses Op~63, Nos.~46 and~47}.
\see{726}.

\cd*\relax
\artist{Alkan, Charles-Valentin}.
\cdtitle{Trois Grandes \'Etudes, Op~76}.
\see{725}.

\cd*\relax
\artist{Alkan, Valentin}.
\cdtitle{Concerto pour piano seul \from 12 \'Etudes dans les tons
  mineurs, Op.~39}.
\see{1177}.

\cd\relax
\artist{Allen, Woody}.
\cdtitle{The Nightclub Years 1964--1968}.
EMI Records, 1990 \cdnum[2]{0777 7 93968~2~5}.

\cd\relax
\artist{Alliage Quartett}.
\cdtitle{Una voce poca fa: Opera Paraphrases for 4 Saxophones and Piano
  \: \track \C{Jun Nagao} Rhapsody on \emph{Carmen} de Georges Bizet \;
  \track \C{Gioacchino Rossini} Overture from \emph{Il barbiere di
  Siviglia} \arr{Sebastian Pottmeier for saxophone quartet} \; \track
  \C{Andreas Hilner} Fantasy after \emph{Tosca} for saxophone quartet \;
  \track \C{Sylvain Dedenon} Suite after themes of \emph{Porgy and Bess}
  for saxophone quartet \; \track \C{Chikade Imai} Seductive Realm,
  after \emph{Die Zauberfl\"ote} for saxophone quartet and piano}.
MDG, 2004 \cdnum{MDG 603 1272-2}.

\cd\relax
\artist{Allman Brothers Band, The}.
\cdtitle{A Decade of Hits: 1969--1979}.
PolyGram Records, 1991 \cdnum{314 511 156-2}.

\cd*\relax
\artist{Alm, Jon}.
\cdtitle{Quartet for Four Double Basses \(1984\)}.
\see{619}.

\cd\relax
\artist{Altan}.
\cdtitle{Horse with a Heart}.
Green Linnet, 1989 \cdnum{GLCD 1095}.

\cd\relax
\artist{Altman, Sean}.
\cdtitle{SeanDemonium}.
Big Sean Music, 1997 \cdnum{BSM1-2}.

\cd\relax
\cdtitle{America's Millennium Tribute to Adolphe Sax, Volume~IX \:
  \track \C{Lars-Erik Larsson} Concerto for Alto Saxophone and String
  Orchestra, Op.~14 \; \track \C{Lawrence Moss} Rivermusic for Saxophone
  Quartet \; \track \C{Edward Green} Concerto for Alto Saxophone and
  Strings \; \track \C{David Bennett Thomas} Rondo Capricioso for Alto
  Saxophone and Piano \; \track \C{Edward Green} Sextet for Alto
  Saxophone and Brass Quintet \; \track \C{Hye Kyung Lee} Sonatina for
  Soprano Saxophone and Piano, movement~II \; \track \C{Arthur
  Gottschalk} Shall We Gather \(In memoriam Arnett Cobb\) for Alto
  Saxophone and Electroacoustic Sounds \; \track \C{H. Benne Hento}
  Nadine for Alto Saxophone and Band}.
Kenneth Tse and others.
Arizona University Recordings, 2000 \cdnum{AUR CD~3122}.

\cd\relax
\artist{Amram, David}.
\cdtitle{At Home/Around the Word}.
Rounder Records, 1996 \cdnum{Flying Fish~094}.

\cd\relax
\artist{Anda, G\'eza}.
\cdtitle{Bart\'ok/Chopin/Mozart \: \track \C{Bela Bart\'ok} Piano
  Concerto No.~1 \and Piano Concerto No.~2 \and Piano Concerto No.~3 \;
  \track \C{Fr\'ed\'eric Chopin} Waltzes \; \track \C{Wolfgang Amadeus
  Mozart} Piano Concerto No.~21 in~C, KV~467}.
Volume~1 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 772-2}.

\cd\relax
\artist{Andersson, Benny, Tim Rice and Bj\"orn Ulvaeus}.
\cdtitle{Chess}.
RCA, 1984 \cdnum[2]{PCD2-5340}.

\cd\relax
\artist{Andrews, Michael}.
\cdtitle{Donnie Darko}.
Everloving Records, 2001 \cdnum{ENJOY003}.

\cd*\relax
\artist{Andriessen, Louis}.
\cdtitle{Facing Death}.
\see{51}.

\cd*\relax
\artist{Andriessen, Louis}.
\cdtitle{`Vergeet me niet'}.
\see{1344}.

\cd\relax
\artist{Andsnes, Leif Ove}.
\cdtitle{The long, long winter night \: \track \C{Edvard Grieg}
  Norwegian Folk Songs, Op.~66 \and Peasant Dances, Op.~72 \; \track
  \C{Geirr Tveitt} Fifty Folk Tunes from Hardanger, Op.~150 \; \track
  \C{David Monrad Johansen} Pictures from Nordland, Suite No.~1, Op.~5
  \; \track \C{Fartein Valen} Variations for piano, Op.~23 \; \track
  \C{Harald S{\ae}verud} Tunes and Dances from ``Siljust{\o}l'',
  Opp.~22, 24, and~25 \and Peer Gynt: Hymn against the Boyg, Op.~28}.
EMI Classics, 1998 \cdnum{7243 5~56541 2~0}.

\cd\relax
\artist{Andy Biskin Quintet}.
\cdtitle{Dogmental}.
GM Recordings, 2000 \cdnum{GM3044CD}.

\cd\relax
\artist{Anonymous~4}.
\cdtitle{A Lammas Ladymass: 13th and 14th Century English Chant and
  Polyphony}.
Harmonia Mundi, 1998 \cdnum{HMU 907222}.

\cd\relax
\artist{Anonymous~4}.
\cdtitle{Legends of St~Nicholas: Medieval Chant and Polyphony}.
Harmonia Mundi, 1999 \cdnum{HMU 907232}.

\cd\relax
\artist{An\'una}.
\cdtitle{An\'una}.
Celtic Heartbeat/Universal Records, 1993 \cdnum{UD-53085}.

\cd\relax
\artist{An\'una}.
\cdtitle{Invocation}.
Celtic Heartbeat/Universal Records, 1995 \cdnum{UD-53089}.

\cd\relax
\artist{An\'una}.
\cdtitle{Omnis}.
Celtic Heartbeat/Universal Records, 1997 \cdnum{UD-53098}.

\cd\relax
\artist{Apollo Saxophone Quartet}.
\cdtitle{First and Foremost \: \track \C{Chick Corea} Children's Songs
  \; \track \C{Michael Nyman} Songs for Tony \; \track \C{David Bedford}
  Fridiof Kennings \; \track \C{Will Gregory} Hoe down \; \track \C{roy
  Powell} Bow out}.
Argo/The Decca Record Company, 1994 \cdnum{443 903-2}.

\cd\relax
\artist{Applebaum, Jody Karin and Marc-Andr\'e Hamelin}.
\cdtitle{Farewell to Boh\`eme}.
Helicon Records, 2000 \cdnum{KL~5108}.

\cd\relax
\artist{Applebaum, Jody Karin and Marc-Andr\'e Hamelin}.
\cdtitle{Masterpieces of Cabaret \: \track \C{Benjamin Britten} Cabaret
  Songs \(1937\) \; \track \C{Arnold Sch\"onberg} Brettl-Lieder \(1901\)
  \; \track \C{William Bolcom} Twelve Cabaret Songs \(1977--83\)}.
Music and Arts, 1992 \cdnum{CD-729}.

\cd*\relax
\artist{Arensky, Anton}.
\cdtitle{Suite No.~1 for Two Pianos, Op.~15 \and Suite No.~2 for Two
  Pianos, Op.~23 ``Silhouettes''}.
\see{380}.

\cd\relax
\artist{Argerich, Martha}.
\cdtitle{Bach/Liszt/Ravel/Prokofiev/Rachmaninoff \: \track \C{Johann
  Sebastian Bach} Partita No.~2 in C~minor, BWV~826 \; \track \C{Franz
  Liszt} Piano Concerto No.~1 in E~flat, S.~124 \; \track \C{Sergei
  Prokofiev} Piano Concerto No.~3 in~C, Op.~26 \; \track \C{Sergei
  Rachmaninoff} Piano Concerto No.~3 in D~minor, Op.~30 \; \track
  \C{Maurice Ravel} Piano Concerto in~G \and Sonatine \and Gaspard de la
  nuit}.
Volume~2 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 700-2}.

\cd\relax
\artist{Argerich, Martha}.
\cdtitle{Chopin/Liszt/Schumann \: \track \C{Fr\'ed\'eric Chopin} Prelude
  in C~sharp minor, Op.~45 \and Polonaise in A~flat, Op.~61
  ``Polonaise-Fantaisie'' \and Mazurka in A~minor, Op.~59 No.~1 \and
  Mazurka in A~flat, Op.~59 No.~2 \and Mazurka in F~sharp minor, Op.~59
  No.~3 \and Scherzo No.~3 in C~sharp minor, Op.~39 \and Preludes,
  Op.~28 \and Scherzo No.~2 in B~flat minor, Op.~31 \and Polonaise in
  A~flat, Op.~53 ``Heroic'' \and Piano Sonata No.~3 in B~minor, Op.~58
  \; \track \C{Franz Liszt} Piano Sonata in B~minor \and Hungarian
  Rhapsody No.~6 in D~flat \; \track \C{Robert Schumann} Piano Sonata
  No.~2 in G~minor, Op.~22}.
Volume~3 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 703-2}.

\cd\relax
\artist{Argerich, Martha}.
\cdtitle{\track \C{Serge Prokofiev} Konzert f\"ur Klavier und Orchester
  Nr.~3 C-dur op.~26 \; \track \C{Maurice Ravel} Konzert f\"ur Klavier
  unde Orchester G-dur \and Gaspard de la nuit}.
Berliner Philharmoniker.
Claudio Abbado, cond.
Deutsche Grammophon, 1967/1975 \cdnum{447 438-2}.

\cd*\relax
\artist{Arnold, Malcolm}.
\cdtitle{Fantasy for Cello}.
\see{983}.

\cd\relax
\artist{Arnold, Sir Malcolm}.
\cdtitle{Chamber Music \: \track Trio for Violin, Cello and Piano,
  Op.~54 \; \track Violin Sonata No.~2, Op.~43 \; \track Fantasy for
  Cello, Op.~130 \; \track Violin Sonata No.~1, Op.~15 \; \track Five
  Pieces for Violin and Piano, Op.~84}.
English Piano Trio.
Naxos, 1998 \cdnum{8.554237}.

\cd\relax
\artist{Arnold, Sir Malcolm}.
\cdtitle{Symphony No.~9}.
National Symphony Orchestra of Ireland.
Andrew Penny, cond.
Naxos, 1996 \cdnum{8.553540}.

\cd\relax
\artist{Arrau, Claudio}.
\cdtitle{Alb\'eniz/Bach/Balakirev/Brahms/Liszt \: \track \C{Isaac
  Alb\'eniz} Iberia \(Book~1\) \; \track \C{Johann Sebastian Bach}
  Chromatic Fantasy and Fugue \; \track \C{Mili Balakirev} Islamey \;
  \track \C{Johannes Brahms} Variations on a Theme by Paganini, Op.~35
  \and Piano Concerto No.~1 in D~minor, Op.~15 \; \track \C{Franz Liszt}
  Spanish Rhapsody \and B\'en\'ediction de Dieu dans la solitude \and
  Les jeux d'eaux \`a la Villa d'Este \and Chasse-neige \(\'Etude
  d'execution transcendante No.~12\)}.
Volume~4 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 706-2}.

\cd\relax
\artist{Arrau, Claudio}.
\cdtitle{Beethoven/Chopin/Liszt/Schumann \: \track \C{Ludwig van
  Beethoven} Piano Sonata No.~21 in~C, Op.~53 ``Waldstein'' \and Adanti
  Favori in~F, WoO~57 \and Piano Concerto No.~5 in E~flat, Op.~73
  ``Emperor'' \; \track \C{Fr\'ed\'eric Chopin} Fantaisie in F~minor,
  Op.~49 \; \track \C{Franz Liszt} Piano Sonata in B~minor, S.~178 \;
  \track \C{Robert Schumann} Fantasie in~C, Op.~17}.
Volume~5 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 709-2}.

\cd\relax
\artist{Arrau, Claudio}.
\cdtitle{Chopin/Debussy/Granados/Liszt/Mozart/Schubert \: \track
  \C{Fr\'ed\'eric Chopin} Preludes, Op.~28 \and Prelude in C~sharp
  minor, Op.~45 \and Prelude in A~flat, Op.~posth. \and Nocturnes,
  Op.~48 \; \track \C{Debussy} Images, Book~2 \; \track \C{Enrique
  Granados} Quejas \'o la maja y el ruis\~nor \; \track \C{Franz Liszt}
  Aida: Danza sacra e duetto final \and Vall\'ee d'Obermann \; \track
  \C{Wolfgang Amadeus Mozart} Fantasie in C~minor, KV~475 \; \track
  \C{Schubert} Moments musicaux, D.~780}.
Volume~6 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 712-2}.

\cd\relax
\artist{Arriaga, Juan Cris\'ostomo de}.
\cdtitle{Symphony in D minor \: \track Overture to ``Los esclavos
  felices'' \; \track \C{Jan V\'aclav Vo\v{r}{\'\i}\v{s}ek} Symphony in
  D major}.
Scottish Chamber Orchestra.
Sir Charles Mackerras, cond.
Hyperion, 1995 \cdnum{CDA66800}.

\cd\relax
\artist{Arriaga, Juan Cris\'ostomo de}.
\cdtitle{The String Quartets}.
The Guarneri Quartet.
Philips, 1996 \cdnum{446 092-2}.

\cd*\relax
\artist{Arutiunian, Alexander}.
\cdtitle{Concerto for Trumpet and Orchestra}.
\see{1143}.

\cd\relax
\artist{Ashkenazy, Vladimir}.
\cdtitle{Chopin/Liszt/Ravel/Rachmaninoff/Schumann \: \track \C{Alexander
  Borodin} Scherzo in A~flat \; \track \C{Fr\'ed\'eric Chopin} Scherzo
  No.~4 in~E, Op.~54 \and Nocturne in~B, Op.~62 No.~1 \and Mazurka in
  A~flat, Op.~59 No.~2 \and Trois nouvelles \'etudes, Op. posth. \and
  Barcarolle in F~sharp, Op.~60 \; \track \C{Franz Liszt} \'Etudes
  d'ex\'ecution transcendante \(excerpts\) \and Mephisto Waltz No.~1 \;
  \track \C{Sergei Prokofiev} ``Romeo and Juliet before parting'' \;
  \track \C{Maurice Ravel} Gaspard de la nuit \; \track \C{Robert
  Schumann} Humoreske, Op.~20 \; \track \C{Serge Rachmaninoff}
  Variations on a theme by Corelli, Op.~42}.
Volume~7 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 715-2}.

\cd\relax
\artist{Atterberg, Kurt Magnus}.
\cdtitle{\track Cello Concerto, Op.~21 \; \track Cello Sonata, Op.~27}.
Werner Thomas-Mifune (cello) and Carmen Piazzini (piano).
Runfunk-Sinfonieorchester Berlin.
Karl Anton Rickenbacher, cond.
Koch/Schwann, 1997 \cdnum{3-1585-2}.

\cd\relax
\artist{Aurelia Saxophone Quartet}.
\cdtitle{Blow! Saxophone Music from America \: \track \C{George
  Gershwin} Rhapsody in Blue \; \track \C{Samuel Barber} Adagio for
  Strings, Op.~11 \; \track \C{John Cage} Four$^5$ \; \track \C{Elliott
  Carter} Canonic Suite for Quartet of Alto Saxophones \; \track
  \C{Michael Torke} July \; \track \C{Perry Goldstein} Blow! \; \track
  \C{David Dramm} Come True \and Master Bob Blaster}.
Challenge Classics, 1998 \cdnum{72005}.

\cd\relax
\artist{Aurella Saxophone Quartet}.
\cdtitle{Saxophone Quartets \: \track \C{Theo Verbey} Passamezzo \;
  \track \C{Tristan Keuris} Music for Saxophones \; \track \C{Peter van
  Onna} The Gravity of~D \; \track \C{Martijn Padding} Ritorno \; \track
  \C{Louis Andriessen} Facing Death \; \track \C{Geert van Keulen}
  Kwartet}.
NM Classics, 1995 \cdnum{92053}.

\cd\relax
\artist{Austin Lounge Lizards, The}.
\cdtitle{Creatures from the Black Saloon}.
Watermelon Records, 1984 \cdnum{1000-CD}.

\cd\relax
\artist{Austin Lounge Lizards, The}.
\cdtitle{Employee of the Month}.
Sugar Hill Records, 1998 \cdnum{SHCD-3874}.

\cd\relax
\artist{Austin Lounge Lizards, The}.
\cdtitle{Live Bait}.
Watermelon Records, 1996 \cdnum{CD~0034}.

\cd\relax
\artist{Austin Lounge Lizards, The}.
\cdtitle{Lizard Vision}.
Flying Fish Records, 1996 \cdnum{FF~70569}.

\cd\relax
\artist{Austin Lounge Lizards, The}.
\cdtitle{Never an Adult Moment}.
Sugar Hill Records, 2000 \cdnum{SUG-CD-3918}.

\cd\relax
\artist{Austin Lounge Lizards, The}.
\cdtitle{Paint Me on Velvet}.
Flying Fish Records, 1993 \cdnum{FF 70618}.

\cd\relax
\artist{Austin Lounge Lizards, The}.
\cdtitle{Small Minds}.
Watermelon Records, 1995 \cdnum{1034}.

\cd\relax
\artist{Austin Lounge Lizards, The}.
\cdtitle{Strange Noises in the Dark}.
Blue Corn Music, 20003 \cdnum{BCM0303}.

\cd\relax
\artist{Austin Lounge Lizards, The}.
\cdtitle{The Highway Caf\'e of the Damned}.
Watermelon Records, 1988 \cdnum{1001-CD}.

\cd*\relax
\artist{Bach, Carl Philipp Emanuel}.
\cdtitle{Concerto No.~2 in B~flat major, Wq~171 \(H~436\)}.
\see{1314}.

\cd\relax
\artist{Bach, Carl Philipp Emanuel}.
\cdtitle{The Three Cello Concertos \: \track Cello Concerto in A~minor,
  Wq.~170/H.~432 \; \track Cello Concerto in B~flat major,
  Wq.~171/H.~436 \; \track Cello Concerto in A~major, Wq.~172.~439}.
Hidemi Suzuki (cello and direction).
Bach Collegium Japan.
BIS, 1997 \cdnum{BIS-CD-807}.

\cd*\relax
\artist{Bach, J. C.}
\cdtitle{Quartet in B-flat major for Oboe, Violin, Viola and
  Violoncello}.
\see{784}.

\cd\relax
\artist{Bach, J. S.}
\cdtitle{Morimur \: \track Partita D~Minor BWV~1004 for solo violin \;
  \track Christ lag in Todesbanden \; \track Dein Will' gescheh' \;
  \track Befiehl Du Deine WEge \; \track Jesu meine Freude \; \track Auf
  meinen lieben Gott \; \track Jesu Deine Passion \; \track In meines
  Herzens Grunde \; \track Nun lob', mein Sell', den Herren \; \track
  Ciaccona for solo violin and four voices}.
Christoph Poppen and the Hilliard Ensemble.
ECM Records, 2001 \cdnum{ECM~1765}.

\cd*\relax
\artist{Bach, J. S.}
\cdtitle{Ricercare a~6 from ``Musikalisches Opfer'', BVW1079}.
\see{784}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{15 Two-Part Inventions, BWV~772--786 \and 15 Three-Part
  Inventions \(Sinfoniae\), BWV~787--801 \and Chromatic Fantasy and
  Fugue, BWV~903 \and English Suite No.~2 in A~minor, BWV~807}.
\see{1340}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{6 Favorite Cantatas \: \track Herz und Mund und Tat und Leben,
  BWV~147 \; \track Ein feste Burg ist under Gott, BWV~80 \; \track
  Liebster Gott, wann werd ich sterben, BWV~8 \; \track Wachtet auf,
  ruft uns die Stimme, BWV~140 \; \track Jauchzet Gott in allen Landen,
  BWV~51 \; \track Jesu, der du meine Seele, BWV~78}.
The Bach Ensemble.
Joshua Rifkin, cond.
The Decca Record Company, 1997 \cdnum[2]{455 706-2}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Agnus Dei from Mass in B~minor arr.\ for flugelhorn}.
\see{1139}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Air from Suite No.~3 in~D, BWV~1068}.
\see{902}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Bach and Bassoon \: \track Partita for flute in a minor,
  BWV~1013 \; \track Partita No.~2 for violin in d~minor, BWV~1004 \;
  \track Suite No.~2 for violoncello in d~minor, BWV~1008 \; \track
  Suite No.~3 for violoncello in~C, BWV~1009}.
Arthur Weisberg.
Crystal Records, 1987/1998 \cdnum{CD345}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Brandenburg Concerto No.~3 in G~major, BWV~1048}.
\see{628}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Brandenburg Concertos and Violin Concertos \(BMV~1041, 1042\)
  and Concerto for 2 Violins \op{BMV~1043}}.
Scottish Ensemble.
Jonathan Rees, cond.
Virgin Classics, 1998 \cdnum[2]{7243 5 61403 2 5}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Brandenburgische Konzerte~1, 2,~3}.
The English Concert.
Trevor Pinnock, cond.
Polygram Records, 1982 \cdnum{410 500-2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Brandenburgische Konzerte~4, 5,~6}.
The English Concert.
Trevor Pinnock, cond.
Polygram Records, 1982 \cdnum{410 501-2}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Brandenburgisches Konzert Nr.~2 F-dur BWV~1047 f\"ur Trompete,
  Fl\"ote, Oboe, Violine, Streicher und Basso continuo}.
\see{1523}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Cantatas and Arias}.
Ian Bostridge (tenor).
Europa Galante.
Fabio Bondi, cond.
EMI Records, 2000 \cdnum{7243 5~45420~2~2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Cantatas BWV~208, 211 and~212 \: \track \C{Alessandro
  Scarlatti} Infirmata vulnerata \; \track \C{Georg Philipp Telemann}
  Die Hoffnung ist mein Leben \; \track \C{Fran\c{c}ois Couperin}
  Le\c{c}ons des t\'en\`ebres `Pour le Mercredy'---Premi\`ere
  Le\c{c}on}.
Dietrich Fischer-Dieskau.
Berliner Philharmoniker.
Karl Forster, cond.
EMI Records, 1998 \cdnum[2]{7243 5 72634 2~9}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Cantatas \: \track ``Ich habe genug'', BWV~82 \; \track ``Geist
  und Seele wird verwirret'', BWV~35, I and~V \; \track ``Der Friede sei
  mit dir'', BWV~158 \; \track ``Ich will den Kreuzstab gerne tragen'',
  BWV~56}.
Matthias Goerne (baritone), Albrecht Mayer (oboe), Johannes Strobl
  (organ) and Rainer Schmidt (violin).
Salzburger Bachchor and Camerata Academica Salzburg.
Sir Roger Norrington, cond.
The Decca Record Company, 1999 \cdnum{289 466 570-2}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Cello Suite No.~1 in~G, BWV1007 \and Cello Suite No.~2 in
  D~minor, BWV1008}.
\see{500}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Cello Suites Nos.~1--6}.
Pablo Casals.
Naxos, 2000 \cdnum[2]{8.110915--16}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Cello-Suiten}.
Mstislav Rostropovich.
EMI Records, 1995 \cdnum[2]{5~55363~2}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Chaconne}.
\see{504}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Chaconne \(\from Partita No.~2, BWV~1004\)}.
\see{766}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{\track Christ lag in Todesbanden, BWV~4 \; \track Nach dir,
  Herr, verlanget mich, BWV~150 \; \track Der Herr denket an uns,
  BWV~196 \; \track Gott ist mein K\"onig, BWV~71 \(I.~Chorus\) \;
  \track Weinen, klagen, sorgen, zagen, BWV~12 \(II.~Chorus\) \; \track
  Nur jedem das Seine, BWV~163 \(III.~Bass aria\) \; \track Lobe den
  Herrn, meine Seele, BWV~143 \(IV.~Tenor aria\) \; \track Ich hatte
  viel Bek\"ummernis, BWV~21 \(VI.~Chorus\) \; \track \C{Georg Friedrich
  H\"andel} Messiah, Part the Second: Chorus ``Hallelujah!'' \; \track
  \C{Johann Rudolf Ahle} Missa \`a~10: Kyrie \; \track \C{Heinrich
  Sch\"utz} Geistliche Chormusik No.~28: Auf dem Gebirge hat man ein
  Geschrei geh\"ort}.
Yumiko Kurisu (soprano), Akira Tachikawa (counter-tenor), Koki Katano
  (tenor) and Peter Kooij (bass).
Bach Collegium Japan.
Masaaki Suzuki, cond.
BIS, 1998 \cdnum{BIS-CD-751}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Chromatic Fantasy and Fugue}.
\see{43}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Complete Violin Sonatas, BWV 1014--1023}.
Arthur Grumiaux (violin), Christiane Jaccottet (harpsichord) and
  Philippe Mermoud (cello).
Philips Classics, 1996 \cdnum[2]{454 011-2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{\track Concerto in D~minor for Two Violins and Orchestra,
  BWV~1044 \; \track Violin Concerto in A~minor, BWV~1041 \; \track
  Violin Concerto in E~major, BWV~1042 \; \track Trio Sonata in G~major,
  BWV~1038}.
Isaac Stern (violin), Itzhak Perlman (violin), Jean-Pierre Rampal
  (flute), Leslie Parnas (cello) and John Steele Ritter (harpsichord).
Sony Music, 2004 \cdnum{SK~92732}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Concertos for Piano and Orchestra, Nos.~1--5,~7}.
Glenn Gould.
Sony, 1992 \cdnum[2]{SM2K 52591}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Contrapunctus~III}.
\see{1231}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Das Wohltemperirte Clavier, Buch~1}.
Angela Hewitt.
Hyperion Records, 1998 \cdnum[2]{CDA67301/2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Das Wohltemperirte Clavier, Buch~2}.
Angela Hewitt.
Hyperion Records, 1999 \cdnum[2]{CDA67303/4}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Die Kunst der Fuge}.
Berliner Saxophon Quartett.
CPO, 1991 \cdnum[2]{999 058-2}.
Arranged for saxophone quartet by Friedemann Graef.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Die Kunst der Fuge}.
The Juilliard String Quartet.
Sony, 1992 \cdnum[2]{S2K~45~937}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Die Kunst der Fuge}.
The Keller Quartett.
ECM Records, 1998 \cdnum{457 849-2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{English Suites \(BMV 806--11\)}.
Andras Schiff.
The Decca Record Company, 1988 \cdnum[2]{421 640-2}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{French Suite No.~2 in C~minor, BWV~813}.
\see{1201}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{French Suite No.~5 in~G, BWV~816}.
\see{632}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{French Suite No.~6 in~E, BWV~817}.
\see{407}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{French Suite No.~6 in~E, BWV~817}.
\see{720}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Goldberg Variations}.
Glenn Gould.
CBS Records, 1956/1983 \cdnum{MYK~38479}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Goldberg Variations: Aria with Thirty Variations, BWV~988,
  Clavier\"ubung, Part~IV}.
Rosalyn Tureck.
VAI Audio, 1988 \cdnum{VAIA~1029}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{``Goldberg'' Variations, BWV~988}.
\see{1698}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Goldberg Variations, BWV~988}.
Pierre Hanta{\"\i} (harpsichord).
Mirare \cdnum{MIR~9945}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Goldberg Variations, BWV~988}.
Angela Hewitt.
Hyperion Records, 2000 \cdnum{CDA67305}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Goldberg Variations \(BWV~988\), arranged by Arthur
  Frackenpohl}.
The Canadian Brass.
RCA Victor, 1999 \cdnum{09026-63610-2}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Italian Concerto in~F, BWV~971 \and Liebster Jesu, wir sind
  hier, BWV~731 \and Ert\"ot uns durch dein G\"ute \and French Suite
  No.~6 in~E, BWV~817}.
\see{478}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Jesu, Joy of Man's Desiring \arr{Myra Hess}}.
\see{770}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Kantaten 170, 82, and~159}.
Janet Baker (contralto), Robert Tear (tenor) and John Shirley-Quirk
  (bass).
Academy of St~Martin-in-the-Fields.
Sir Neville Marriner, cond.
The Decca Record Company, 1991 \cdnum{430 260-2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Magnificat en R\'e majeur, BWV~243 \and Cantate BWV~80, ``Ein
  feste Burg ist unser Gott''}.
Barbara Schlick (soprano), Agnes Mellon (soprano), G\'erard Lesne
  (alto), Howard Crook (tenor) and Peter Kooy (bass).
La Chapelle Royale, Collegium Vocale.
Philippe Herreweghe, cond.
Harmonia Mundi, 1997 \cdnum{HMX 2901326}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Mass in B~Minor \(BWV~232\)}.
The Monteverdi Choir and the English Baroque Soloists.
John Eliot Gardiner, cond.
Archiv Produktion, 1985 \cdnum[2]{415 514-2}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Nun komm' der Heiden Heiland, BWV~659 \and Jesus bleibet meine
  Freude \(\from BWV~147\) \and Wachtet auf! ruft uns die Stimme \(\from
  BWV~140\)}.
\see{886}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Orchestral Suites 1\&2 \(BMV~1066-1067\) \and Concerto for 2
  Harpsichords, BWV~1060}.
The Academy of Ancient Music.
Christopher Hogwood, cond.
The Decca Record Company, 1988/1994 \cdnum{443 181-2}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Partita BWV~1004 \(with ``Ciaccona''\)}.
\see{1540}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Partita in a~minor}.
\see{881}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Partita in B~flat, BWV~825 \and ``Jesu, Joy of Man's Desiring''
  \T{Myra Hess}}.
\see{967}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Partita No.~2 in C~minor, BWV~826}.
\see{38}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Partita No.~4 in~D, BWV~828}.
\see{877}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Partita No.~4 in~D, BWV~828 \and Prelude and Fugue in A~minor,
  BWV~543 \and Prelude in B~minor}.
\see{1683}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Partitas BWV 825--830, Preludes and Fugues}.
Glenn Gould.
Sony Music, 1993 \cdnum[2]{SM2K 52 597}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Prelude and Fugue in A~minor, BWV~543}.
\see{844}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Prelude and Fugue in A~minor, BWV~543}.
\see{1485}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Prelude and Fugue in~D, BWV~532 \arr{Ferriccio Busoni} \and
  French Suite No.~5 in~G, BWV~816}.
\see{642}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Prelude in B~minor}.
\see{644}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Preludio and Fuga~XVI}.
\see{830}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Preludio, Gavotte and Gigue from Violin Partita No.~3 in~E,
  BWV~1006}.
\see{1233}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Sechs Suiten f\"ur Violoncello solo, BWV 1007--1012}.
Pierre Fournier.
Archiv Produktion, 1961 \cdnum[2]{449 711-2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Sechs Suiten f\"ur Violoncello solo, BWV 1007--1012}.
Hidemi Suzuki.
BMG Classics, 1996 \cdnum[2]{05472 77387~2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Seven Harpsichord Concertos \: Triple Concerto BWV~1044}.
director Andrew Manze (violin), Richard Egarr (harpsichord) and Rachel
  Brown (flute).
The Academy of Ancient Music.
Harmonia Mundi, 2002 \cdnum[2]{HMU 907283.84}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Six Solo Suites}.
Richard Hartshorne (double bass).
Centaur Records, 1997 \cdnum[3]{CRC 2348/49/50}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Six Suites for Unaccompanied Cello}.
Yo-Yo Ma.
Sony Classical, 1997 \cdnum[2]{S2K~63203}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Six Suites per violoncello solo senza basso}.
Peter Wispelwey (baroque cello and violoncello piccolo).
Channel Classics, 1998 \cdnum[2]{CCS~12298}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Solo and Double Violin Concertos \: \track Concerto in D~Minor
  for Two Violins \(BWV~1043\) \; \track Concerto in A~Minor for Violins
  \(BWV~1041\) \; \track Concerto in E~Major for Violins \(BWV~1042\) \;
  \track Concerto in D~Minor for Two Violins \(BWV~1060\)}.
Andrew Manze and Rachel Podger.
The Academy of Ancient Music.
Andrew Manze, cond.
Harmonia Mundi, 1997 \cdnum{HMU 907155}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Sonata in E~major, BWV~1035}.
\see{1602}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Sonatas and Partitas for Solo Violin \(BWV~1001--1006\)}.
Yehudi Menuhin.
EMI Classics, 1999 \cdnum[2]{7243 5~67197~2 9}.
Recorded Paris, 1934--1936.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Sonatas and Partitas for Solo Violin, Volume~1 \: \track Sonata
  No.~1 in G~Minor, BWV~1001 \; \track Partita No.~1 in B~Minor,
  BWV~1002 \; \track Partita No.~2 in D~Minor, BWV~1004}.
Rachel Podger.
Channel Classics, 1999 \cdnum{CCS~12198}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Sonatas and Partitas for Solo Violin, Volume~1 \: \track Sonata
  No.~1 in G~Minor, BWV~1001 \; \track Partita No.~1 in B~Minor,
  BWV~1002 \; \track Sonata No.~2 in A~Minor, BWV~1003}.
Christiane Edinger.
Naxos, 1991 \cdnum{8.550569}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Sonatas and Partitas for Solo Violin, Volume~1 \: \track Sonata
  No.~1 in G~Minor, BWV~1001 \; \track Partita No.~1 in B~Minor,
  BWV~1002 \; \track Sonata No.~2 in A~Minor, BWV~1003}.
Lucy van Dael.
Naxos, 1999 \cdnum{8.554422}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Sonatas and Partitas for Solo Violin, Volume~2 \: \track
  Partita No.~2 in D~Minor, BWV~1004 \; \track Sonata No.~3 in C~major,
  BWV~1005 \; \track Partita No.~3 in E~Major, BWV~1006}.
Christiane Edinger.
Naxos, 1992 \cdnum{8.550570}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Sonatas and Partitas for Solo Violin, Volume~2 \: \track
  Partita No.~2 in D~Minor, BWV~1004 \; \track Sonata No.~3 in C~Major,
  BWV~1005 \; \track Partita No.~3 in E~Major, BWV~1006}.
Lucy van Dael.
Naxos, 1999 \cdnum{8.554423}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Sonatas and Partitas for Solo Violin, Volume~2 \: \track
  Partita No.~3 in E~Major, BWV~1006 \; \track Sonata No.~2 in A~Minor,
  BWV~1003 \; \track Sonata No.~3 in C~major, BWV~1005}.
Rachel Podger.
Channel Classics, 1999 \cdnum{CCS~14498}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Sonatas for Viola da Gamba and Harpsichord \(BMV 1027--1029\)}.
Yo-Yo Ma and Kenneth Cooper.
CBS Records, 1983 \cdnum{MK~37794}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Sonaten und Partiten \(BWV 1001--1006\)}.
Itzhak Perlman.
EMI Records, 1988 \cdnum[2]{CDC 7 49483~2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{St. Matthew Passion \(BWV~244\)}.
The Monteverdi Choir, the London Oratory Junior Choir and the English
  Baroque Soloists.
John Eliot Gardiner, cond.
Archiv Produktion, 1989 \cdnum[3]{427 648-2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{St~John Passion, BWV~245}.
Peter Pears (Evangelist), Gwynne Howell (Jesus), John Shirley-Quirk
  (Pilate and bass arias), Heather Harper (soprano arias), Alfreda
  Hodgson (alto arias) and Robert Tear (tenor arias).
English Chamber Orchestra and the Wandsworth School Boys' Choir.
Russell Burgess and Benjamin Britten, cond.
The Decca Record Company, 1995 \cdnum[2]{443 859-2}.
English translation by Peter Pears and Imogen Holst.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Suites for Cello \(BWV 1007--1012\)}.
Jaap ter Linden (baroque violoncello).
Harmonia Mundi, 1997 \cdnum[2]{HMU 907216.7}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Suites for Cello, Volume~1}.
Pablo Casals.
EMI Classics, 1988 \cdnum{CDH-7 61028~2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Suites for Cello, Volume~2}.
Pablo Casals.
EMI Classics, 1988 \cdnum{CDH-7 61029~2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{\track Suites for Solo Cello \(BWV 1007--1012\) \; \track
  Sonata in G~major, BWV~1027 \; \track Sonata in D~major, BWV~1028}.
Janos Starker (cello) and Gyorgy Sebok (piano).
Philips Classics, 1991 \cdnum[2]{432 756-2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The 6 Unaccompanied Cellos Suites \(S.~1007--1012\)}.
Yo-Yo Ma.
CBS Records, 1983 \cdnum[2]{M2K~37867}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The Art of Fugue \and Musical Offering}.
Academy of St~Martin in the Fields.
Sir Neville Marriner, cond.
Philips Classics, 1994 \cdnum[2]{442 556-2}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The Art of the Fugue}.
Trio~335, Amy Goeser (oboe), Heike Storm (accordian) and Steve Vacchi
  (bassoon).
Equilibrium, 2001 \cdnum{EQ~48}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The Brandenburg Concertos, Volume~1 \: \track Concerto No.~1 in
  F~Major, BWV~1046 \; \track Concerto No.~2 in F~Major, BWV~1047 \;
  \track Concerto No.~3 in G~Major, BWV~1048}.
Frans Br\"uggen (recorder), Wieland Kuijken (baroque violoncello) and
  Anner Bylsma (baroque violoncello).
Gustav Leonhardt, cond.
Sony Classical, 1977/1999 \cdnum{SBK~61814}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The Brandenburg Concertos, Volume~2 \: \track Concerto No.~4 in
  G~Major, BWV~1049 \; \track Concerto No.~5 in D~Major, BWV~1050 \;
  \track Concerto No.~6 in B-flat Major, BWV~1051}.
Frans Br\"uggen (recorder), Wieland Kuijken (baroque violoncello) and
  Anner Bylsma (baroque violoncello).
Gustav Leonhardt, cond.
Sony Classical, 1977/1999 \cdnum{SBK~61815}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The Complete Organ Music}.
Christopher Herrick.
Hyperion, 2002 \cdnum[16]{CDS44121/36}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The Complete Sonatas for Violin and Obbligato Harpsichord \(BWV
  1014--1019, 1021, 1023\)}.
Rachel Podger (violin), Trevor Pinnock (harpsichord) and Jonathan Manson
  (viola da gamba).
Channel Classics, 2001 \cdnum[2]{CCS~144798}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The Organ Toccatas and Passacaglia \: \track Toccata and Fugue
  in D~minor, BWV~565 \; \track Toccata, Adagio, and Fugue in C~major,
  BWV~564 \; \track Toccata and Fugue in F~major, BWV~540 \; \track
  `Dorian' Toccata and Fugue in D~minor, BWV~538 \; \track Passacaglia
  in C~minor, BWV~582}.
Christopher Herrick.
Hyperion, 1990 \cdnum{CDA66434}.
Recorded on 6, 7, 8~May, 1990, on the Metzler organ of the Stadkirche,
  Zofingen, Switzerland.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The Sonatas and Partitas for Solo Violin \: \track Sonata No.~1
  in G~Minor, BWV~1001 \; \track Partita No.~1 in B~Minor, BWV~1002 \;
  \track Sonata No.~2 in A~Minor, BWV~1003 \; \track Partita No.~2 in
  D~Minor, BWV~1004 \; \track Sonata No.~3 in C~major, BWV~1005 \;
  \track Partita No.~3 in E~Major, BWV~1006}.
Henryk Szeryng.
Sony Classical \cdnum[2]{SB2K87947}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The Well-Tempered Clavier, Book~I}.
Jen\H{o} Jand\'o.
Naxos, 1997 \cdnum[2]{8.553796--7}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The Well-Tempered Clavier, Book~II}.
Jen\H{o} Jand\'o.
Naxos, 1994 \cdnum[2]{8.550970--1}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The Well-Tempered Clavier \(excerpts\) \and Chromatic Fantasy
  and Fugue in D~minor, BWV~903 \and Prelude \(Fantasy\) in A~minor,
  BWV~922 \and Fantasy and Fugue in A~minor, BWV~904 \and Concerto in
  D~minor, BWV~1052 \and Concerto in~A, BWV~1055 \and Concerto in
  F~minor, BWV~1056 \and Ich ruf zu dir, Herr Jesu Christ, BWV~639}.
\see{588}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The Well-Tempered Clavier~I}.
Glenn Gould.
Sony Music, 1993 \cdnum[2]{SM2K 52 600}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{The Well-Tempered Clavier~II}.
Glenn Gould.
Sony Music, 1993 \cdnum[2]{SM2K 52 603}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Three Oboe Concertos \: \track Concert in~F \(BWV~1053\) \;
  \track Concerto in D~minor \(BWV~1059\) \; \track Concerto in~A
  \(BWV~1055\)}.
Heinz Holliger.
Academy of St~Martin-in-the-Fields.
Iona Brown, cond.
Philips Classics, 1983 \cdnum{412 851-2}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Toccata, Adagio and Fugue in~C, BWV~564 \arr{Ferruccio
  Busoni}}.
\see{617}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Toccatas, BWV 910--916}.
Glenn Gould.
Sony Music, 1994 \cdnum[2]{SM2K 52 612}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Two- and Three-Part Inventions, BWV~772--801}.
Glenn Gould.
Sony, 1966/1992 \cdnum{SMK~52 596}.

\cd*\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Two-Part Inventions~1, 3, 6, 7, 9, 10, and~13}.
\see{486}.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{\track Violin Concerto No.~1 in A~minor \(BWV~1041\) \; \track
  Violin Concerto No.~2 in E~major \(BWV~1042\) \; \track Double
  Concerto in D~minor \(BWV~1043\) \; \track Partita No.~2 in D~minor
  \(BWV~1004\)}.
Yehudi Menuhin and George Enescu.
Orchestre Symphonique de Paris.
George Enescu and Pierre Monteux, cond.
EMI Classics, 1999 \cdnum{7243 5~67201~2 1}.
Recorded Paris, 1932--1936.

\cd\relax
\artist{Bach, Johann Sebastian}.
\cdtitle{Violin Sonatas \: \track Sonata in B~minor, BWV~1014 \; \track
  Sonata in A~major, BWV~1015 \; \track Sonata in E~major, BWV~1016 \;
  \track Sonata in C~minor, BWV~1017 \; \track Sonata in F~minor,
  BWV~1018 \; \track Sonata in G~major, BWV~1019 \; \track Sonata in
  G~major, BWV~1019/alt \; \track Sonata in G~major, BWV~1021 \; \track
  Sonata in E~minor, BWV~1023 \; \track Sonata in C~minor, BWV~1024 \;
  \track Toccata and Fugue in D~minor, BWV~565, for solo violin}.
Andrew Manze, Richard Egarr (harpsichord) and Jaap ter Linden
  (gamba/cello).
Harmonia Mundi, 2000 \cdnum[2]{HMU 907250.51}.

\cd\relax
\artist{Bach, P. D. Q.}
\cdtitle{Liebeslieder Polkas and Twelve Quite Heavenly Songs}.
Vanguard, 1980 \cdnum{VMD~79438}.

\cd\relax
\artist{Bach, P. D. Q.}
\cdtitle{Music for an Awful Lot of Winds and Percussion}.
Telarc, 1992 \cdnum{CD-80307}.

\cd\relax
\artist{Bach, P. D. Q.}
\cdtitle{The Dread P.~D.~Q. Bach Collection: The Complete Vanguard
  Recordings, Volume~I \: \track An Evening with P.~D.~Q. Bach \; \track
  An Hysteric Return \; \track P.~D.~Q. Back on the Air \; \track The
  Stoned Guest \; \track The Intimate P.~D.~Q. Bach}.
Vanguard, 1996 \cdnum[4]{159/62-2}.

\cd\relax
\artist{Bach, P. D. Q.}
\cdtitle{The Short-Tempered Clavier and other dysfunctional works for
  keyboard}.
Telarc, 1995 \cdnum{CD-80390}.

\cd\relax
\artist{Bach, P. D. Q.}
\cdtitle{The Stoned Guest}.
Vanguard, 1970 \cdnum{VMD~6536}.

\cd\relax
\artist{Bach, P. D. Q.}
\cdtitle{Two Pianos Are Better Than One \: \track Concerto for Two
  Pianos vs.\ Orchestra \(S.~2 are better than one\) \; \track Trio
  \(sic\) Sonata \(S.~3\(4\)\) \; \track Chaconne \`a son Go\^ut \;
  \track The Musical Sacrifice \(S.~50\% off\)}.
Telarc, 1994 \cdnum{CD-80376}.

\cd\relax
\artist{Bach, P. D. Q.}
\cdtitle{WTWP Classical Talkity-Talk Radio}.
Telarc, 1991 \cdnum{CD-80295}.

\cd*\relax
\artist{Bach, W. F.}
\cdtitle{Duet for Flute and Oboe, No.~4 in F~major}.
\see{1664}.

\cd\relax
\artist{Backhaus, Wilhelm}.
\cdtitle{Beethoven/Brahms/Chopin/Schubert \: \track \C{Ludwig van
  Beethoven} Piano Sonata in C~minor, Op.~13 ``Path\'etique'' \and Piano
  Sonata in D~minor, Op.~31 No.~2 ``Tempest'' \and Piano Sonata in
  E~flat, Op.~81a ``Les adieux'' \and Piano Sonata in C~minor, Op.~111
  \and Piano Sonata in~G, Op.~79 \; \track \C{Johannes Brahms}
  Klavierst\"ucke, Op.~119, No.~3: Intermezzo in~C \and Piano Concerto
  No.~2 in B~flat, Op.~83 \; \track \C{Fr\'ed\'eric Chopin} Etude in
  F~minor, Op.~25 No.~2 \; \track \C{Franz Liszt} Soir\'ees de Vienne:
  Valse-Caprice No.~6, S.~427 \(after Schubert\) \; \track \C{Franz
  Schubert} Impromptu in E~flat, D.~899 No.~2 \; \track \C{Robert
  Schumann} Fantasiest\"ucke, Op.~12, No.~3: Warum?}
Volume~8 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 718-2}.

\cd*\relax
\artist{Baden, Conrad}.
\cdtitle{Sonata, Op.~116}.
\see{504}.

\cd\relax
\artist{Baez, Joan}.
\cdtitle{Any Day Now}.
Vanguard Records, 1968/1987 \cdnum{79306/7-2}.

\cd\relax
\artist{Baez, Joan}.
\cdtitle{Blowin' Away}.
CBS Records, 1977 \cdnum{EK~34697}.

\cd\relax
\artist{Baez, Joan}.
\cdtitle{David's Album}.
Vanguard Records, 1969 \cdnum{79308-2}.

\cd\relax
\artist{Baez, Joan}.
\cdtitle{Diamonds and Rust}.
A\&M Records, 1975 \cdnum{CD 3233}.

\cd\relax
\artist{Baez, Joan}.
\cdtitle{Honest Lullaby}.
CBS Records, 1979 \cdnum{EK 35766}.

\cd\relax
\artist{Baez, Joan}.
\cdtitle{Joan}.
Vanguard Records, 1967 \cdnum{CMD 79240}.

\cd\relax
\artist{Baez, Joan}.
\cdtitle{Live at Newport}.
Vanguard Records, 1996 \cdnum{77015-2}.

\cd\relax
\artist{Baez, Joan}.
\cdtitle{Play Me Backwards}.
Virgin Records, 1992 \cdnum{V2-86458}.

\cd\relax
\artist{Bagratuni, Suren}.
\cdtitle{Cello \: \track \C{Adam Khudoyan} Sonata No.~1 for Cello Solo
  \and Sonata No.~2 for Cello Solo \and Sonata No.~3 for Cello Solo \;
  \track \C{George Crumb} Sonata for Solo Violoncello \and Sonata for
  Two Cellos \and Nostalgia \; \track \C{Paul Hindemith} Sonata for
  Cello Solo}.
Natalia Khoma (second cello).
Ongaku Records, 1995 \cdnum{024-104}.

\cd*\relax
\artist{Balakirev, Mili}.
\cdtitle{Islamey}.
\see{43}.

\cd*\relax
\artist{Balakirev, Mili}.
\cdtitle{Islamey}.
\see{1178}.

\cd*\relax
\artist{Balakirev, Mili}.
\cdtitle{Islamey}.
\see{882}.

\cd*\relax
\artist{Balakirev, Mily}.
\cdtitle{Islamey}.
\see{632}.

\cd\relax
\artist{Band, The}.
\cdtitle{The Last Walz}.
Warner Brothers, 1978 \cdnum{3146-2}.

\cd\relax
\artist{Baraglioli, Jean-Pierre}.
\cdtitle{Concertos pour saxophone alto et orchestre \`a cordes \: \track
  \C{Alexandre Glazounov} Concerto en Mi b\'emol, Op.~109 \; \track
  \C{Eug\'ene Bozza} Aria \; \track \C{Gustavo Beytelmann} Pi\`ece
  concertante \; \track \C{Carleton Macy} Faust}.
Daph\'en\'eo, 1997 \cdnum{9709}.

\cd*\relax
\artist{Barbella, Francesco}.
\cdtitle{Sonata in C~major}.
\see{1653}.

\cd\relax
\artist{Barber, Samuel}.
\cdtitle{\track Adagio for Strings \; \track \C{Charles Ives} Symphony
  No.~3 \; \track \C{Aaron Copland} Quiet City for cor anglais, trumpet
  and strings \; \track \C{Henry Cowell} Hymn and Fuguing tune No.~10
  for oboe and strings \; \track \C{Paul Creston} A Rumor}.
Celia Nicklin (oboe and cor anglais) and Michael Laird (trumpet).
Academy of St~Martin-in-the-Fields.
Sir Neville Marriner, cond.
The Decca Record Company, 1987 \cdnum{417 818-2}.

\cd*\relax
\artist{Barber, Samuel}.
\cdtitle{Adagio for Strings, Op.~11}.
\see{50}.

\cd*\relax
\artist{Barber, Samuel}.
\cdtitle{Concerto for Cello and Orchestra, Op.~22}.
\see{1013}.

\cd*\relax
\artist{Barber, Samuel}.
\cdtitle{Souvenirs}.
\see{1602}.

\cd\relax
\artist{Barbieri, Gato}.
\cdtitle{The Best of Gato Barbieri}.
Universal Music, 2004 \cdnum{B0003098-02}.

\cd*\relax
\artist{Barchet, Siegfried}.
\cdtitle{Boulevard de Garavan}.
\see{902}.

\cd\relax
\artist{Barenaked Ladies}.
\cdtitle{Born on a Pirate Ship}.
Reprise Records, 1996 \cdnum{9 46128-2}.

\cd\relax
\artist{Barenaked Ladies}.
\cdtitle{Maroon}.
Warner Records, 2000 \cdnum{9 47814-2}.

\cd\relax
\artist{Barenaked Ladies}.
\cdtitle{Maybe You Should Drive}.
Sire Records, 1994 \cdnum{9 45709-2}.

\cd\relax
\artist{Barenaked Ladies}.
\cdtitle{Stunt}.
Reprise Records, 1998 \cdnum{9 46963-2}.

\cd\relax
\artist{Barenboim, Daniel}.
\cdtitle{Beethoven/Brahms/Mozart/Liszt \: \track \C{Beethoven, Ludwig
  van} Piano Concerto No.~1 in~C, Op.~15 \; \track \C{Brahms, Johannes}
  Piano Concerto No.~1 in D~minor, Op.~15 \; \track \C{Liszt, Franz}
  Ann\'ees de p\`elerinage: Deuxi\`eme ann\'ee: Italie \; \track
  \C{Mozart, Wolfgang Amadeus} Piano Concerto No.~25 in~C, Op.~15 \;
  \track \C{Wagner, Richard and Franz Liszt} Isoldens Liebestod}.
Volume~9 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 721-2}.

\cd*\relax
\artist{B\"armann, Heinrich Joseph}.
\cdtitle{Quintet No.~3 in E-Flat Major, Op.~23}.
\see{438}.

\cd*\relax
\artist{Bartholdy, Felix Mendelssohn}.
\cdtitle{``Hunting Song'' \(\from Lieder ohne Worte, Op.~19\) \and
  ``Spring Song'' \(\from Lieder ohne Worte, Op.~62\) \and The Bee's
  Wedding \(\from Lieder ohne Worte, Op.~67`\) \and Rondo capriccioso,
  Op.~14 \(abridged\)}.
\see{775}.

\cd*\relax
\artist{Bartholdy, Felix Mendelssohn}.
\cdtitle{Lieder ohne Worte, Op.~102 No.~5}.
\see{770}.

\cd*\relax
\artist{Bartholdy, Felix Mendelssohn}.
\cdtitle{Lieder ohne Worte \(selections\) \and Scherzo in E~minor,
  Op.~16, No.~2}.
\see{625}.

\cd*\relax
\artist{Bartholdy, Felix Mendelssohn}.
\cdtitle{Prelude and Fugue in E~minor, Op.~35 No.~1 \and Rondo
  capriccioso in~E, Op.~14}.
\see{882}.

\cd*\relax
\artist{Bartholdy, Felix Mendelssohn}.
\cdtitle{Scherzo from ``A Midsummer Night's Dream''}.
\see{1076}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Bart\'ok plays Bart\'ok}.
Pearl, 1995 \cdnum{GEMM CD~9166}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Bart\'ok plays Bart\'ok \: \track Mikrocosmos \; \track Sonata
  for Two Pianos and Percussion}.
B\'ela Bart\'ok (piano), Ditta Pasztory-Bart\'ok (piano), Harry J. Baker
  (percussion) and Edward J. Rubsan (percussion).
Pearl, 2003 \cdnum{GEM~0179}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Concerto for Orchestra \and Music for Strings, Percussion and
  Celesta \and Hungarian Sketches}.
The Chicago Symphony Orchestra.
Fritz Reiner, cond.
BMG Classics, 1993 \cdnum{09026-61504-2}.

\cd*\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Concerto for Viola and Orchestra}.
\see{1019}.

\cd*\relax
\artist{Bart\'ok, Bela}.
\cdtitle{H\'arom Csikmegyei N\'epdal \(Three folksongs from the country
  of Csik\) \and Este a sz\'ekelyekn\'el \(An evening in the village\)}.
\see{1344}.

\cd*\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Improvisations on Hungarian Peasant Songs, Op.~20}.
\see{1196}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Microcosmos}.
Claude Helffer.
Harmonia Mundi, 1973/1991 \cdnum[2]{HMA 190968.69}.

\cd*\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Out of Doors, BB~89, Sz.~81 \and Sonatina, BB~69, Sz.~55 \and
  Piano Concerto No.~2, BB~101, Sz.~95}.
\see{930}.

\cd*\relax
\artist{Bart\'ok, Bela}.
\cdtitle{Piano Concerto No.~1 \and Piano Concerto No.~2 \and Piano
  Concerto No.~3}.
\see{25}.

\cd*\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Piano Concerto No.~3, Sz.~119}.
\see{1224}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Pi\`eces pour piano \: \track Danses populaires roumaines
  \(1915\) \; \track Suite op.~14 \(1916\) \; \track Improvisations sur
  des chants paysans hongrois, op.~20 \(1920\) \; \track En plein air
  \(1926\) \; \track Sonate \(1926\)}.
Claude Helffer.
Harmonia Mundi, 1982/1993 \cdnum{HMA 1901094}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{\track Rhapsody No.~1 \(Folk Dances\) \; \track Rhapsody No.~2
  \(Folk Dances\) \; \track Andante \; \track Piano Quintet}.
Gy\"org Pauk (violin), Jen\H{o} Jand\'o (piano) and Kod\'aly Quartet.
Naxos, 1995 \cdnum{8.550886}.

\cd*\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Roumanian Folk Dances, Sz.~56}.
\see{911}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{The Miraculous Mandarin, \op{BB~82} \and Hungarian Peasant
  Songs, \op{BB~107} \and Hungarian Sketches, \op{BB~103} \and Roumanian
  Folk Dances, \op{BB~76} \and Dances of Transylvania, \op{BB~102b} \and
  Roumanian Dance, \op{BB~61}}.
Budapest Radio Orchestra and the Hungarian Radio Chorus.
Iv\'an Fischer, cond.
Philips, 1997 \cdnum{454 430-2}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{The Piano Concertos \and Violin Concerto No.~2 \and Concerto
  for Orchestra}.
Stephen Kovacevich (piano) and Henryk Szeryng (violin).
London Symphony Orchestra, BBC Symphony Orchestra, and Royal
  Concertgebouw Orchestra.
Sir Colin Davis and Bernard Haitink, cond.
Philips Classics, 1993 \cdnum[2]{438 812-2}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{The Piano Concertos \(BB~91, 101, and~127\)}.
Zolt\'an Kocsis.
Budapest Festival Orchestra.
Iv\'an Fischer, cond.
Philips Classics, 1995 \cdnum{446 366-2}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{The Six String Quartets}.
The Juilliard String Quartet.
Sony, 1997 \cdnum[2]{SB2K 63234}.
(1981 Digital Cycle).

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{\track Violin Concerto No.~1 Sz.~36 \; \track Violin Concerto
  No.~2 Sz.~112}.
Gy\"org Pauk (violin).
Polish National Radio Symphony Orchestra (Katowice).
Antoni Wit, cond.
Naxos, 1999 \cdnum{8.554321}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Works for Piano Solo~1}.
Zolt\'an Kocsis.
Philips Classics, 1992 \cdnum{434 104-2}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Works for Piano Solo~2}.
Zolt\'an Kocsis.
Philips Classics, 1994 \cdnum{442 016-2}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Works for Piano Solo~3: For Children}.
Zolt\'an Kocsis.
Philips Classics, 1995 \cdnum{442 146-2}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Works for Piano Solo~4}.
Zolt\'an Kocsis.
Philips Classics, 1997 \cdnum{446 369-2}.

\cd\relax
\artist{Bart\'ok, B\'ela}.
\cdtitle{Works for Violin \: \track Sonata for Solo Violin SZ~117 \;
  \track 44 Duos for Two Violins}.
Gy\"orgy Pauk and Kazuki Sawa.
Naxos, 1995 \cdnum{8.550868}.

\cd\relax
\artist{Bart\'ok, B\'ela and Zolt\'an Kod\'aly}.
\cdtitle{Hungarian Folk Music}.
B\'ela Bart\'ok (piano), M\'aria Basilides, Vilma Medgyaszay and Ferenc
  Sz\'ekelyhidy.
Pearl, 1997 \cdnum{GEMM CD~9266}.

\cd\relax
\artist{Barton, Rachel}.
\cdtitle{Instrument of the Devil}.
Patrick Sinozich (piano).
Cedille Records, 1998 \cdnum{CDR 90000 041}.

\cd\relax
\artist{Basrak, Cathy}.
\cdtitle{American Viola Works \: \track \C{George Rochberg} Sonata for
  Viola and Piano \(1979\) \; \track \C{Frederick Jacobi} Fantasy for
  Viola and Piano \(1941\) \; \track \C{Alan Shulman} Theme and
  Variations \(1940\) \; \track \C{Quincy Porter} Speed Etude \(1948\)
  \; \track \C{Lowell Liebermann} Sonata for Violin and Piano \(1984\)}.
William Koehler (piano) and Robert Koenig (piano).
Cedille Records, 2000 \cdnum{CDR 90000 053}.

\cd\relax
\artist{Beamish, Sally}.
\cdtitle{\track Viola Concerto \(1995\) \; \track Cello Concerto
  ``River'' \(1997\) \; \track Tam Lin \(1993\) for oboe and orchestra}.
Philip Dukes (viola), Robert Cohen (cello) and Gordon Hunt (oboe).
Swedish Chamber Orchestra.
Ola Rudner, cond.
BIS, 1999 \cdnum{BIS-CD-971}.

\cd\relax
\artist{Beatles, The}.
\cdtitle{Abbey Road}.
EMI Records, 1969/1987 \cdnum{CDP 7 46446~2}.

\cd\relax
\artist{Beatles, The}.
\cdtitle{Let It Be}.
EMI Records, 1970/1987 \cdnum{CDP 7 46447~2}.

\cd\relax
\artist{Beatles, The}.
\cdtitle{Magical Mystery Tour}.
EMI Records, 1967/1987 \cdnum{CDP 7 48062~2}.

\cd\relax
\artist{Beatles, The}.
\cdtitle{Past Masters, Volume~One}.
EMI Records, 1988 \cdnum{CDP~7 90043~2}.

\cd\relax
\artist{Beatles, The}.
\cdtitle{Past Masters, Volume~Two}.
EMI Records, 1988 \cdnum{CDP~7 90044~2}.

\cd\relax
\artist{Beatles, The}.
\cdtitle{Revolver}.
EMI Records, 1966 \cdnum{CDP 7 46441~2}.

\cd\relax
\artist{Beatles, The}.
\cdtitle{Rubber Soul}.
EMI Records, 1965 \cdnum{CDP 7 46440~2}.

\cd\relax
\artist{Beatles, The}.
\cdtitle{Sgt. Pepper's Lonely Hearts Club Band}.
EMI Records, 1967/1987 \cdnum{CDP 7 46442~2}.

\cd\relax
\artist{Beatles, The}.
\cdtitle{The White Album}.
Capitol Records, 1968 \cdnum[2]{CDP~7 46443~2}.

\cd*\relax
\artist{B\'edard, Denis}.
\cdtitle{Fantaisie}.
\see{1604}.

\cd*\relax
\artist{Bedford, David}.
\cdtitle{Fridiof Kennings}.
\see{35}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{32 Variations in C~minor, WoO~80}.
\see{1684}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{32 Variations in C~minor, WoO~80 \and Piano Sonata in C~sharp
  minor, Op.~27 No.~2 ``Moonlight''}.
\see{988}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Bagatellen \: \track 7 Bagatelles for Piano, Op.~33 \; \track
  11 Bagatelles for Piano, Op.~119 \; \track 6 Bagatelles for Piano,
  Op.~126}.
Stephen Bishop Kovacevich.
Philips Classics, 1990 \cdnum{426 976-2}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Bagatelles \: \track Seven Bagatelles, Op.~33 \; \track Eleven
  New Bagatelles, Op.~119 \; \track Six Bagatelles, Op.~126}.
Jen\H{o} Jand\'o.
Naxos, 1991 \cdnum{8.550474}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{08}}.
\cdtitle{Cellosonaten}.
Volume~8 of \emph{The Complete Beethoven Edition}.
Mischa Maisky (cello) and Martha Argerich (piano).
Deutsche Grammophon, 1997 \cdnum[2]{453~748-2}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Clarinet Trio Op.~38 \(after the Septet Op.~20\) \:
  \C{Ferdinand Ries} Clarinet Trio Op.~28}.
J\"urgen Demmler (clarinet), Markus Tillier (cello) and Peter Grabinger
  (piano).
Naxos, 1998 \cdnum{8.553389}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Complete Cello Music \: \track Sonata in F~major Op~5 No~1 \;
  \track Twelve Variations in G~major WoO45 \; \track Sonata in G~major
  Op~5 No~2 \; \track Twelve Variations in F~major Op~66 \; \track Seven
  Variations in E~flat major WoO46 \; \track Sonata in A~major Op~69 \;
  \track Sonata in C~major Op~102 No~1 \; \track Sonata in D~major
  Op~102 No~2}.
Anthony Pleeth (cello) and Melvyn Tan (fortepiano).
Hyperion, 1996 \cdnum[2]{CDD22004}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Complete Music for Cello and Piano \: \track Sonata No.~1 in
  F~major Op.~5, No.~1 \; \track Sonata No.~2 in G~major Op.~5, No.~2 \;
  \track Sonata No.~3 in A~major Op.~69 \; \track Sonata No.~4 in
  C~major Op.~102, No.~1 \; \track Sonata No.~5 in D~major Op.~102,
  No.~2 \; \track Twelve Variations in F~major Op.~66 \; \track Seven
  Variations in E~flat major WoO~46 \; \track Twelve Variations in
  G~major WoO~45}.
Mstislav Rostropovich (cello), Sviatoslav Richter (piano), Maurice
  Gendron (cello) and Jean Fran\c{c}aix (piano).
Philips Classics, 1994 \cdnum[2]{442 565-2}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Concerto No.~1 for Piano and Orchestra in C~major, op.~15 \and
  Concerto No.~2 for Piano and Orchestra in B~flat major, op.~19 \and
  Sonata No.~30 in E~major, op.~109 \and Sonata No.~31 in A~flat major,
  op.~110 \and Sonata No.~32 in C~minor, op.~111}.
\see{659}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{``Diabelli'' Variations, Op.~120 \and ``Eroica'' Variations,
  Op.~35}.
\see{1698}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{12}}.
\cdtitle{Die Mittleren Streichquartette}.
Volume~12 of \emph{The Complete Beethoven Edition}.
The Emerson String Quartet.
Deutsche Grammophon, 1997 \cdnum[2]{453~764-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{13}}.
\cdtitle{Die Sp\"aten Streichquartette}.
Volume~13 of \emph{The Complete Beethoven Edition}.
The LaSalle Quartet.
Deutsche Grammophon, 1997 \cdnum[3]{453~768-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{10}}.
\cdtitle{Die Werke f\"ur Streichtrio}.
Volume~10 of \emph{The Complete Beethoven Edition}.
Anne-Sophie Mutter (violin), Bruno Giuranna (viola) and Mstislav
  Rostropovich (cello).
Deutsche Grammophon, 1997 \cdnum[2]{453~757-2}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Ecossaises}.
\see{952}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Egmont-Overture, op.~84}.
\see{628}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{First movement from Piano Concerto No~3 in C~minor, Op~37,
  transcribed and with cadenza by Charles-Valentin Alkan}.
\see{725}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{11}}.
\cdtitle{Fr\"uhe Werke f\"ur Streichquartette}.
Volume~11 of \emph{The Complete Beethoven Edition}.
The Amadeus Quartet, the Hagen Quartett and the Mendelssohn Quartett.
Deutsche Grammophon, 1997 \cdnum[3]{453~760-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{19}}.
\cdtitle{Grosse Chorwerke}.
Volume~19 of \emph{The Complete Beethoven Edition}.
Deutsche Grammophon, 1997 \cdnum[5]{453~798-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{20}}.
\cdtitle{Historische Aufnahmen}.
Volume~20 of \emph{The Complete Beethoven Edition}.
Deutsche Grammophon, 1989 \cdnum[6]{453~804-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{14}}.
\cdtitle{Kammermusik}.
Volume~14 of \emph{The Complete Beethoven Edition}.
Deutsche Grammophon, 1997 \cdnum[6]{453~772-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{05}}.
\cdtitle{Klaviersonaten}.
Volume~5 of \emph{The Complete Beethoven Edition}.
Wilhelm Kempff.
Deutsche Grammophon, 1997 \cdnum[8]{453 724-2}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Konzert f\"ur Klavier, Violine, Violoncello und
  Orchester C-dur, Op.~56 ``Tripelkonzert'' \; \track Fantasie f\"ur
  Klavier, Chor und Orchester, Op~80 ``Chorfantasie''}.
Itzhak Perlman (violin), Yo-Yo Ma (violoncello) and Daniel Baremboim
  (piano and conductor).
Berliner Philharmoniker and Chor der Deutschen Staatsoper.
EMI Classics, 1995 \cdnum{7243 5~55516 2~7}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{02}}.
\cdtitle{Konzerte}.
Volume~2 of \emph{The Complete Beethoven Edition}.
Deutsche Grammophon, 1997 \cdnum[5]{453 707-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{04}}.
\cdtitle{Leonore and Fidelio}.
Volume~4 of \emph{The Complete Beethoven Edition}.
Deutsche Grammophon, 1997 \cdnum[4]{453 719-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{16}}.
\cdtitle{Lieder}.
Volume~16 of \emph{The Complete Beethoven Edition}.
Deutsche Grammophon, 1997 \cdnum[3]{453~782-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{15}}.
\cdtitle{Musik f\"ur Bl\"aser}.
Volume~15 of \emph{The Complete Beethoven Edition}.
Deutsche Grammophon, 1997 \cdnum[2]{453~779-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{03}}.
\cdtitle{Orchesterwerke und B\"uhnenmusik}.
Volume~3 of \emph{The Complete Beethoven Edition}.
Deutsche Grammophon, 1997 \cdnum[5]{713-2}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Concerto No.~1 in C~major, op.~15}.
\see{629}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Concerto No.~1 in~C, Op.~15}.
\see{158}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Concerto No.~1 in~C, Op.~15}.
\see{579}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Concerto No.~1 in~C, Op.~15}.
\see{716}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Concerto No.~4 in~G, Op.~58}.
\see{642}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Concerto No.~4 in~G, Op.~58 \and Piano Concerto No.~5 in
  E~flat, Op.~73 ``Emperor''}.
\see{637}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Concerto No.~5 in E~flat, Op.~73 ``Emperor''}.
\see{796}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Concerto No.~5 in E~flat, Op.~73 ``Emperor'' \and Piano
  Sonata No.~23 in F~minor, Op.~57 ``Appassionata'' \and Piano Sonata
  No.~31 in A~flat, Op.~110}.
\see{589}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata in B~flat, Op.~106 ``Hammerklavier''}.
\see{1485}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata in B~flat, Op.~106 ``Hammerklavier'' \and 6
  Bagatelles, Op.~126 \and 10 Variations on ``La stessa, la
  stessissima,'' WoO~73 from Salieri's ``Falstaff'' \and 33 Variations
  on a Waltz by Anton Diabelli in~C, Op.~120 \and Piano Sonata in
  C~minor, Op.~111}.
\see{335}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata in C~minor, Op.~10 No.~1}.
\see{930}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata in C~minor, Op.~13 ``Path\'etique'' \and Piano
  Sonata in D~minor, Op.~31 No.~2 ``Tempest'' \and Piano Sonata in
  E~flat, Op.~31 No.~3 ``Hunt'' \and Piano Sonata in~A, Op.~101 \and
  Piano Sonata in~E, Op.~109 \and Piano Sonata in~A~flat, Op.~110 \and
  Piano Sonata in~C~minor, Op.~111}.
\see{931}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata in C~minor, Op.~13 ``Path\'etique'' \and Piano
  Sonata in D~minor, Op.~31 No.~2 ``Tempest'' \and Piano Sonata in
  E~flat, Op.~81a ``Les adieux'' \and Piano Sonata in C~minor, Op.~111
  \and Piano Sonata in~G, Op.~79}.
\see{140}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata in C~sharp minor, Op.~27, No.~2 ``Moonlight''}.
\see{625}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata in E~flat, Op.~81a ``Les adieux''}.
\see{650}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata in E~minor, Op.~90}.
\see{886}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata in F~minor, Op.~57 ``Appassionata''}.
\see{1428}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata in~C, Op.~53 ``Waldstein'' \and Piano Sonata in
  F~minor, Op.~57 ``Apassionata''}.
\see{638}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata in~E, Op.~109 \and Piano Sonata in A~flat,
  Op.~110}.
\see{770}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata No.~11 in B~flat, Op.~22 \and Rondo in~C, Op.~51
  No.~1 \and Piano Sonata No.~2 in~A, Op.~2 No.~2}.
\see{887}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata No.~17 in D~minor, Op.~31, No.~2 ``Tempest''}.
\see{844}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata No.~17 in D~minor, Op.~31 No.~2 ``Tempest'' \and
  Piano Sonata No.~18 in E~flat, Op.~31 No.~3 ``La Chasse''}.
\see{747}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata No.~17 in D~minor, Op.~31, No.~2 ``The Tempest''}.
\see{734}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata No.~18 in E~flat, Op.~31 No.~3 ``Hunt''}.
\see{1320}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata No.~21 in~C, Op.~53 ``Waldstein'' \and 33
  Variations on a Waltz by Anton Diabelli in~C, Op.~120 \and Piano
  Sonata No.~30 in~E, Op.~109 \and Piano Sonata No.~32 in~C~minor,
  Op.~111 \and Piano Concerto No.~4 in~G, Op.~58}.
\see{1343}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonata No.~21 in~C, Op.~53 ``Waldstein'' \and Adanti
  Favori in~F, WoO~57 \and Piano Concerto No.~5 in E~flat, Op.~73
  ``Emperor''}.
\see{44}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Piano Sonata No.~23 in F~minor, Op.~57 ``Appassionata''
  \; \track Piano Sonata No.~22 in~E, Op.~54 \; \track Piano Sonata
  No.~25 in~G, Op.~79 \; \track Piano Sonata No.~4 in E~flat, Op.~7}.
Stephen Kovacevich.
EMI Classics, 2000 \cdnum{7243 5~56965~2~6}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Piano Sonata No.~5 in C~minor, Op.~10 No.~1 \; \track
  Piano Sonata No.~6 in~E, Op.~10 No.~2 \; \track Piano Sonata No.~7
  in~D, Op.~10 No.~3}.
Stephen Kovacevich.
EMI Classics, 1999 \cdnum{7243 5~56761 2~2}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Piano Sonata No.~8 in C~minor, Op.~13 ``Grande Sonata
  Path\'etique'' \; \track Piano Sonata No.~9 in~E, Op.~14 No.~1 \;
  \track Piano Sonata No.~10 in~G, Op.~14 No.~2 \; \track Piano Sonata
  No.~11 in B~flat, Op.~22}.
Stephen Kovacevich.
EMI Classics, 1998 \cdnum{7243 5~56586 2~3}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonatas \: \track Sonata No.~14 in C~Sharp Minor `quasi
  una fantasia,' Op.~27, No.~2 ``Moonlight'' \; \track Sonata No.~23 in
  F~Minor, Op.~57 ``Appassionata'' \; \track Sonata No.~21 in C~Major,
  Op.~53 ``Waldstein''}.
Jen\"o Jand\'o (piano).
Naxos, 1989 \cdnum{8.550294}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonatas, Volume~I}.
Glenn Gould.
CBS Records, 1990 \cdnum[3]{MM3K~45821}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Piano Sonatas, Volume~II}.
Glenn Gould.
CBS Records, 1990 \cdnum[3]{MB3K~45822}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Rondo for Piano and Orchestra in B~flat, WoO~6}.
\see{883}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Rondo, Op.~51 No.~2 \and Rondo a capriccio, Op.~129 ``Rage over
  a Lost Penny''}.
\see{899}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Seven Variations on Bei M\"annern welche Liebe f\"uhlen from
  Mozart's Die Zauberfl\"ote, WoO~46}.
\see{1156}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Sonata for piano and violin No.~9 in A~major, Op.~47
  ``Kreutzer'' \: \C{C\'esar Franck} Violin Sonata in A~major}.
Itzhak Perlman (violin) and Argerich (piano).
EMI Classics, 1999 \cdnum{7243 5~56815~2~2}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Sonata in A~flat ``Funeral March'' \and Sonata in D~minor
  ``Tempest'' \and Sonata in F~minor ``Appassionata'' \and Sonata in~E,
  Op.~109 \and Sonata in A~flat, Op.~110 \and Sonata in C~minor, Op.~111
  \and Rondo in B~flat for Piano and Orchestra, WoO~6 \and Andante
  favori in~F, WoO~57}.
\see{1269}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Sonata in D~major, Op.~12 No.~1}.
\see{1540}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Sonata No.~1 in F~major Op.~5, No.~1 \; \track Sonata
  No.~2 in G~major Op.~5, No.~2}.
Yo-Yo Ma (cello) and Emanuel Ax (piano).
CBS Records, 1982 \cdnum{MK~37251}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Sonata No.~2 in~A, Op.~2 No.~2}.
\see{407}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Sonata No.~3 in A~major Op.~69 \; \track Sonata No.~4 in
  C~major Op.~102, No.~1 \; \track Sonata No.~5 in D~major Op.~102,
  No.~2}.
Pablo Casals (cello) and Rudolf Serkin (piano).
Sony \cdnum{MPK~45682}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Sonata No.~3 in A~major Op.~69 \; \track Sonata No.~5 in
  D~major Op.~102, No.~2}.
Yo-Yo Ma (cello) and Emanuel Ax (piano).
CBS Records, 1984 \cdnum{MK~39024}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Sonata No.~4 in C~major Op.~102, No.~1 \; \track Seven
  Variations in E~flat major WoO~46 \; \track Twelve Variations in
  G~major WoO~45 \; \track Twelve Variations in F~major Op.~66}.
Yo-Yo Ma (cello) and Emanuel Ax (piano).
CBS Records, 1986 \cdnum{MK~42121}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{01}}.
\cdtitle{Symphonien}.
Volume~1 of \emph{The Complete Beethoven Edition}.
The Berliner Philharmoniker.
Herbert von Karajan, cond.
Deutsche Grammophon, 1997 \cdnum[5]{453 701-2}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Symphonies 1--9}.
Amadis/Naxos, 1997 \cdnum{18501}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Symphony No.~1 in C~Major, Op.~21 \; \track Symphony
  No.~6 in F~Major, Op.~68 ``Pastoral''}.
Nicolaus Esterh\'azy Sinfonia.
B\'ela Drahos, cond.
Naxos, 1996 \cdnum{8.553474}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Symphony No.~2 in D~Major, Op.~36 \; \track Symphony
  No.~5 in C~Minor, Op.~67}.
Nicolaus Esterh\'azy Sinfonia.
B\'ela Drahos, cond.
Naxos, 1997 \cdnum{8.553477}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Symphony No.~3 in E~flat Major, Op.~55 ``Eroica'' \;
  \track Symphony No.~8 in F~Major, Op.~93}.
Nicolaus Esterh\'azy Sinfonia.
B\'ela Drahos, cond.
Naxos, 1996 \cdnum{8.553475}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Symphony No.~4 in B~flat Major, Op.~60 \; \track
  Symphony No.~7 in A~Major, Op.~92}.
Nicolaus Esterh\'azy Sinfonia.
B\'ela Drahos, cond.
Naxos, 1997 \cdnum{8.553477}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Symphony No.~5 in C~Minor, Op.~67 \; \track Symphony
  No.~6 in F~Major, Op.~68 ``Pastoral''}.
Nicolaus Esterh\'azy Sinfonia.
B\'ela Drahos, cond.
Naxos, 1997 \cdnum{8.554061}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Symphony No.~5 in C~minor, op.~67 \and Symphony No.~6 in
  F~major, op.~68 ``Pastorale'' \and Violin Concerto in D~major, op.~61
  \and Leonore~III, Overture, op.~138 \and Coriolan-Overture, op.~62}.
\see{630}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Symphony No~7 \(Fragment transcribed by the composer\)}.
\see{978}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Symphony No.~9 in D minor, Op.~125 ``Choral''}.
Elisabeth Schwarzkopf (soprano), Elisabeth H\"ongen (contralto), Hans
  Hopf (tenor) and Otto Edelmann (bass).
Chor und Orchester der Bayreuther Festspiele.
Wilhelm Furtw\"angler, cond.
EMI, 1955/1997 \cdnum{7243 5~66953~2~0}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Symphony No.~9 in D-minor, op.~125}.
Tilla Briem (soprano), Elisabeth H\"ongen (contralto), Peter Anders
  (tenor) and Rudolf Watzke (bass).
Berlin Philharmonic Orchestra and the Bruno Kittel Choir.
Wilhelm Furtw\"angler, cond.
Music and Arts, 1990 \cdnum{CD-653}.
Recorded March 1942.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Symphony No.~9 in D~Minor, Op.~125 ``Choral''}.
Hasmik Papian (soprano), Ruxandra Donose (mezzo-soprano), Manfred Fink
  (tenor) and Claudio Otelli (bass-baritone).
Nicolaus Esterh\'azy Sinfonia and Chorus.
B\'ela Drahos, cond.
Naxos, 1997 \cdnum{8.553478}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Symphony No.~9 in D~Minor, Op.~125 ``Choral'' \; \track
  Fidelio Overture, Op.~72b}.
Adele Addison (soprano), Jane Hobson (mezzo-soprano), Richard Lewis
  (tenor) and Donald Bell (baritone).
The Cleveland Orchestra.
George Szell, cond.
Sony Classical, 1991 \cdnum{SBK~46533}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{The 5 Piano Concertos}.
Glenn Gould.
Sony Music, 1992 \cdnum[3]{SM3K 52~632}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{The Complete Piano Sonatas}.
Seymour Lipkin.
Newport Classic, 2004 \cdnum{NRM59001}.
MP3 files and PDF scores.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{The Complete Piano Sonatas on Period Instruments}.
Malcolm Bilson, Tom Beghin, David Breitman, Ursula D\"utschler, Zvi
  Meniker, Bart van Oort and Andrew Willis.
Claves, 1997 \cdnum[10]{50-8707/10}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{The Early String Quartets, Op.~18}.
The Guarneri Quartet.
BMG Classics, 1990 \cdnum[3]{60456-2-RG}.
Recorded 1969.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{The Late String Quartets, Opp.~127, 130, 131, 132, 135}.
The Guarneri Quartet.
BMG Classics, 1990 \cdnum[3]{60458-2-RG}.
Recorded 1968--1969.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{The Middle String Quartets, Opp.~59, 74, 95}.
The Guarneri Quartet.
BMG Classics, 1990 \cdnum[3]{60457-2-RG}.
Recorded 1966--1968.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Trio for Piano, Clarinet and Cello, Op.~11}.
\see{1005}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{09}}.
\cdtitle{Trios f\"ur Klavier, Violine und Violoncello}.
Volume~9 of \emph{The Complete Beethoven Edition}.
Deutsche Grammophon, 1997 \cdnum[5]{453 751-2}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Triple Concerto for Violin, Cello and Piano in~C, Op.~56 \:
  \C{Johannes Brahms} Double Concerto for Violin and Cello in A~minor,
  Op.~102}.
David Oistrakh (violin), Mstislav Rostropovich (violoncello) and
  Sviaoslav Richter (piano).
Berliner Philharmoniker.
Herbert von Karajan, cond.
EMI Classics, 1970/1998 \cdnum{7243 5~66954~2 9}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Triple Concerto, Op.~56}.
\see{1315}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Turkish March from ``Die Ruinen von Athen''}.
\see{775}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Turkish March from ``Die Ruinen von Athen'' \arr{Anton
  Rubinstein} \and Rondo a capriccio in~G, Op.~129 ``Rage Over a Lost
  Penny''}.
\see{645}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Variations in C~minor, WoO~80}.
\see{1196}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Variations in C~minor, WoO~80 \(Excerpts\)}.
\see{1233}.

\cd*\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{Violin Sonata in A~major, Op.~12, No.~2}.
\see{875}.

\cd\relax
\artist{Beethoven, Ludwig van}.
\cdtitle{\track Violin Sonata No.~9 in A~major, op.~47 ``Kreutzer'' \;
  \track Violin Sonata No.~5 in F~major, op.~24 ``Spring''}.
Itzhak Perlman (violin) and Vladimir Ashkenazy (piano).
The Decca Record Company, 1999 \cdnum{289 458 618-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{07}}.
\cdtitle{Violinsonaten}.
Volume~7 of \emph{The Complete Beethoven Edition}.
Deutsche Grammophon, 1997 \cdnum[4]{453~743-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{17}}.
\cdtitle{Volkslied-Bearbeitungen}.
Volume~17 of \emph{The Complete Beethoven Edition}.
Deutsche Grammophon, 1997 \cdnum[7]{453~786-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{18}}.
\cdtitle{Weltliche Vokalwerke}.
Volume~18 of \emph{The Complete Beethoven Edition}.
Deutsche Grammophon, 1997 \cdnum[2]{453~794-2}.

\cd\relax
\artist{Beethoven, Ludwig van\noop{06} and Norman Shetler}.
\cdtitle{Klavierwerke: Verschiedene Klaverwerke \and Werke f\"ur Klavier
  zu Vier H\"anden \and Werke f\"ur Orgel}.
Volume~6 of \emph{The Complete Beethoven Edition}.
Daniel Barenboim, Gianluca Cascioli, J\"org Demus, Emil Gilels, Wilhelm
  Kempff, Olli Mustonen, Walter Olbertz, Mikhail Pletnev, Anatol Ugorski
  and Simon Preston (organ).
Deutsche Grammophon, 1997 \cdnum[8]{453 733-2}.

\cd*\relax
\artist{Beethoven, Ludwin van}.
\cdtitle{Piano Sonata in E~flat, Op.~7}.
\see{1066}.

\cd*\relax
\artist{Behr, Franz}.
\cdtitle{Polka de~W.R. \T{Sergei Rachmaninov}}.
\see{724}.

\cd*\relax
\artist{Belcke, Friedrich August}.
\cdtitle{Fantasia, Op.~58}.
\see{1599}.

\cd\relax
\artist{Bell, Joshua}.
\cdtitle{Bruch, Mendelssohn, Mozart \: \track \C{Max Bruch} Violin
  Concerto No.~1 in G minor, op.~26 \; \track \C{Felix Mendelssohn}
  Violin Concerto in E minor, op.~64 \; \track \C{Wolfgang Amadeus
  Mozart} Violin Concerto No.~3 in G major, K216 \and Adagio in E major
  for violin and orchestra, K261 \and Violin Concerto No.~5 in A major,
  K219 \and Rondo in C major for violin and orchestra, K373}.
Academy of St Martin in the Fields and English Chamber Orchestra.
Neville Marriner and Peter Maag, cond.
Decca, 2005 \cdnum[2]{B0004203-02}.

\cd\relax
\artist{Bell, Joshua}.
\cdtitle{French Chamber Works \: \track \C{Gabriel Faur\'e} Violin
  Sonata No.~1 in A~major, op.~13 \; \track \C{Claude Debussy} Violin
  Sonata \; \track \C{C\'esar Franck} Violin Sonata in A~major \; \track
  \C{Ernest Chausson} Concert for piano, violin and string quartet,
  op.~21 \; \track \C{Maurice Ravel} Trio for piano, violin and cello}.
Jean-Yves Thibaudet (piano), Tak\'acs Quartet and Stephen Isserlis
  (cello).
Decca, 2005 \cdnum[2]{B0004447-02}.

\cd\relax
\artist{Bell, Joshua}.
\cdtitle{Kreisler, Brahms, Paganini, Sarasate, Wieniawski, etc.: Violin
  Favorites and Virtuoso Showpieces \: \track \C{Henry Wieniawski}
  Th\`eme original vari\'e, op.~15 \and Scherzo-tarantelle, op.~16 \;
  \track \C{Jean Sibelius} Romance, op.~78, no.~2 \and Mazurka, op.~81,
  no.~1 \; \track \C{Johannes Brahms} Hungarian Dance No.~1 \; \track
  \C{Ernet Bloch} Nigun \; \track \C{Ottokar Nov\'a\v{c}ek} Perpetuum
  mobile \; \track \C{Robert Schumann} Vogel als Prophet \; \track
  \C{Manuel de Falla} Spanish Dance \; \track \C{Edwin Grasse}
  Wellenspiel \; \track \C{Pablo de Sarasate} Carmen Fantasy, op.~25 \;
  \track \C{Fritz Kreisler} Praeludium and Allegro \and Sch\"on Rosmarin
  \and Tamburin chinois \and La Pr\'ecieuse \and Liebesfreud \and
  Liebesleid \and La gitana \and Berceuse romantique \and Polichinelle
  \and Rondino \(on a theme by Beethoven\) \and Tempo di minuetto \and
  Toy-Soldier's March \and Allegretto \and Marche miniature viennoise
  \and Aucassin and Nicollete \and Menuett \and Sicilienne and Rigaudon
  \and Syncopation}.
Samuel Sanders (piano) and Paul Coker (piano).
Decca, 2005 \cdnum[2]{B0004205-02}.

\cd\relax
\artist{Bell, Joshua}.
\cdtitle{Tchaikovsky, Wieniawski, Brahms, Schumann \: \track \C{Pyotr
  Ilyich Tchaikovsky} Violin Concerto in D major, op.~35 \; \track
  \C{Henri Wieniawski} Violin Concerto No.~2 in D minor, op.~22 \;
  \track \C{Johannes Brahms} Violin Concerto in D major, op.~77 \;
  \track \C{Robert Schumann} Violin Concerto in D minor}.
The Cleveland Orchestra.
Vladimir Ashkenazy and Christoph von Dohn\'anyi, cond.
Decca, 2005 \cdnum[2]{B0004204-02}.

\cd\relax
\artist{Bell, Joshua}.
\cdtitle{Violin Concertos and Virtuoso Showpieces \: \track \C{Camille
  Saint-Sa\"ens} Violin Concerto No.~3 in B minor, op.~61 \and
  Introduction et Rondo capriccioso, op.~21 \; \track \C{\'Edouard Lalo}
  Symphonie espagnole, op.~21 \; \track \C{Jules Massenet} M\'editation
  \from Tha{\"\i}s \; \track \C{Pablo de Sarasate} Zigeunerweisen,
  op.~20 \; \track \C{Ernest Chausson} Po\`eme, op.~25 \; \track
  \C{Eug\`ene Ysaye} Caprice d'apr\`es l'\'Etude en forme de valse de
  Saint-Sa\"ens \; \track \C{Maurice Ravel} Tzigane}.
Orchestra symphonique de Montr\'eal and Royal Philharmonic Orchestra.
Charles Dutoit and Andrew Litton, cond.
Decca, 2005 \cdnum[2]{B0004448-02}.

\cd\relax
\artist{Bell, Joshua and Egar Meyer}.
\cdtitle{Short Trip Home}.
Sam Bush (mandolin and violin) and mandola and violin Mike Marshall
  (guitar).
Sony Classical, 1999 \cdnum{SK~60864}.

\cd*\relax
\artist{Bellini, Vincenzo}.
\cdtitle{Concerto in E~flat major for oboe and strings}.
\see{1313}.

\cd\relax
\artist{Ben Folds Five}.
\cdtitle{Ben Folds Five}.
Caroline Records, 1995 \cdnum{PSR 9501-2}.

\cd\relax
\artist{Ben Folds Five}.
\cdtitle{Naked Baby Photos}.
Caroline Recordings, 1998 \cdnum{CAR~7554}.

\cd\relax
\artist{Ben Folds Five}.
\cdtitle{Whatever and Ever Amen}.
Sony, 1997 \cdnum{BK 67762}.

\cd*\relax
\artist{Bennet, Richard Rodney}.
\cdtitle{Concerto for alto saxophone and string orchestra}.
\see{744}.

\cd*\relax
\artist{Bennett, Richard Rodney}.
\cdtitle{Piano Concerto No.~1}.
\see{930}.

\cd\relax
\artist{Bensmann, Detlef and Michael Rische}.
\cdtitle{Saxophone and Piano \: \track \C{Darius Milhaud} Scaramouche \;
  \track \C{Maurice Ravel} Five-o'clock Foxtrot \and Pi\`ece en forme de
  Habanera \; \track \C{Isao Matsushita} Atoll~II \; \track \C{Dietrich
  Erdmann} Akzente \; \track \C{Paul Dessau} Suite f\"ur Altsaxophon und
  Klavier \; \track \C{Erwin Schulhoff} Hot-Sonate}.
Koch/Schwann, 1990 \cdnum{310 071}.

\cd\relax
\artist{Bensmann, Detlef and Michael Rische}.
\cdtitle{Saxophone and Piano, Volume~2 \: \track \C{Pierre Max Dubois}
  Dix Figures \`a danser \; \track \C{Andr\'e Jolivet}
  Fantaisie-Impromptu \; \track \C{Erwin Schulhoff} Susi \(Fox-Song\) \;
  \track \C{Otmar M\'acha} Plac saxophone/The wailing of the saxophone
  \; \track \C{Bernhard Heiden} Solo for Alto Saxophone and Piano \;
  \track \C{Michael Rische} permanent isolation \; \track \C{G\"unter
  Raphael} R\'ecitatif pour Saxophone alto et piano \; \track \C{Edison
  Denissov} Deux pi\`eces pour Saxophone alto and Piano \; \track
  \C{Alojzy Thomys} Ten Miniatures in different styles}.
Koch/Schwann, 1997 \cdnum{3-6430-2}.

\cd*\relax
\artist{Benson, Warren}.
\cdtitle{Aeolian Song}.
\see{1603}.

\cd\relax
\artist{Berg, Alban}.
\cdtitle{\track Concerto for Violin and Orchestra \; \track Chamber
  Concerto for Piano and Violin with Thirteen Winds}.
Isaac Stern (violin) and Peter Serkin.
New York Philharmonic.
Leonard Bernstein, cond.
Sony, 1995 \cdnum{SMK 64 504}.

\cd*\relax
\artist{Berg, Alban}.
\cdtitle{Piano Sonata, Op.~1}.
\see{658}.

\cd\relax
\artist{Berg, Alban}.
\cdtitle{\track Three Fragments from ``Wozzeck'' \; \track Drei
  Orchesterst\"ucke op.~6 \; \track Symphonic Pieces from the Opera
  ``Lulu''}.
Ren\'ee Fleming (soprano).
The MET Orchestra.
James Levine, cond.
Sony Classical, 1995 \cdnum{SK~53~959}.

\cd\relax
\artist{Berg, Alban}.
\cdtitle{Wozzeck \: \track \C{Arnold Schoenberg} Erwartung, Op.~17 \;
  \track \C{Ernst Krenek} Symphonic Elegy for String Orchestra}.
New York Philharmonic.
Dimitri Mitropoulos, cond.
Sony Classical \cdnum[2]{MH2K 62759}.

\cd*\relax
\artist{Berg, Olav}.
\cdtitle{Vertigo for Bassoon Solo \and Sonatine for Basson and Piano}.
\see{847}.

\cd*\relax
\artist{Berio, Luciano}.
\cdtitle{Notturno \(Quartetto~III\)}.
\see{11}.

\cd*\relax
\artist{Berio, Luciano}.
\cdtitle{Opus Number Zoo}.
\see{1687}.

\cd*\relax
\artist{Berio, Luciano}.
\cdtitle{Sequenza~V per trombone solo}.
\see{964}.

\cd\relax
\artist{Berlioz, Hector}.
\cdtitle{Great Orchestral Works \: \track Symphonie fantastique, Op.~14
  \; \track Le carnaval romain, Op.~9 \; \track Le corsaire, Op.~21 \;
  \track Harold en Italie, Op.~16 \; \track Symphonie fun\`ebre et
  triomphale, Op.~15}.
The London Symphony Orchestra.
Sir Colin Davis, cond.
Philips Classics, 1994 \cdnum[2]{442 290-2}.

\cd*\relax
\artist{Berlioz, Hector}.
\cdtitle{Les Nuits d'\'et\'e}.
\see{461}.

\cd*\relax
\artist{Bernstein, Leonard}.
\cdtitle{Clarinet Sonata \(transcribed for cello and piano by Yo-Yo
  Ma\)}.
\see{1007}.

\cd*\relax
\artist{Bernstein, Leonard}.
\cdtitle{West Side Story Medley}.
\see{1603}.

\cd*\relax
\artist{Berwald, Franz}.
\cdtitle{Concert Piece in~F for bassoon and orchestra}.
\see{1589}.

\cd\relax
\artist{Berwald, Franz}.
\cdtitle{\track Septet in B~flat major \; \track Serenade \; \track
  Piano Quartet in E~flat major}.
Arion Wind Quintet, Schein String Quartet, Mikael Bj\"ork (double bass),
  Joakim Kallhed (piano) and Thomas Annmo (tenor).
Naxos, 1997 \cdnum{8.553714}.

\cd*\relax
\artist{Beurden, Bernard van}.
\cdtitle{Pas de trois}.
\see{1606}.

\cd*\relax
\artist{Beytelmann, Gustavo}.
\cdtitle{Pi\`ece concertante}.
\see{151}.

\cd\relax
\artist{Biber, Heinrich Ignaz Franz von}.
\cdtitle{Der T\"urken Anmarsch \: \track Sonata ``Victori der Christen''
  in A minor \; \track Sonata~I in A~major from Sonatae Violino solo \;
  \track Sonata~II in D~dorian from Sonatae Violino solo \; \track
  Sonata~V in E~minor from Sonatae Violino solo \; \track Sonata~VIII in
  A~major from Sonatae Violino solo \; \track \C{Georg Muffat} Sonata
  Violino Solo in D~major}.
John Holloway (violin), Alyosia Assenbaum (organ) and Lars Ulrik
  Mortensen.
ECM Records, 2004 \cdnum{ECM~1837}.

\cd\relax
\artist{Biber, Heinrich Ignaz Franz von}.
\cdtitle{Missa Christi resurgentis and other works \: \track Fanfare
  No.~4 \`a due \; \track Sonata~XI \from \emph{Fidicinium
  sacro-profanum} \; \track Fanfare No.~1 \`a due \; \track Sonata~I
  \from \emph{Fidicinium sacro-profanum} \; \track Sonata~V \from
  \emph{Fidicinium sacro-profanum} \; \track Sonata~III \from
  \emph{Fidicinium sacro-profanum} \; \track Sonata~VII \from
  \emph{Fidicinium sacro-profanum} \; \track Sonata \`a~6 for trumpet, 2
  violins, 2 violas and bass \; \track \C{Johann Heinrich Schmelzer}
  Sonata~XII \from \emph{Sacro-profanus concentus musicus}}.
The English Concert and the Choir of The English Concert.
Andrew Manze, cond.
Harmonia Mundi, 2005 \cdnum{HMU 907397}.

\cd\relax
\artist{Biber, Heinrich Ignaz Franz von}.
\cdtitle{\track Sonata III F~major from Sonatae Violino solo~1681 \;
  \track Sonata IV D~major from Sonatae Violino solo~1681 \; \track
  Sonata No.~81 A major (unpublished) \; \track Sonata VI C~minor from
  Sonatae Violino solo~1681 \; \track Sonata VII G~major from Sonatae
  Violino solo~1681 \; \track Sonata No.~84 E~major (unpublished)}.
Unam Ceylum, John Holloway (violin), Aloysia Assenbaum (organ) and Lars
  Ulrik Mortensen (harpsichord).
ECM Records, 2002 \cdnum{289 472 084-2}.

\cd\relax
\artist{Biber, Heinrich Ignaz Franz von}.
\cdtitle{The Mystery Sonatas \: \track The Five Joyful Mysteries \;
  \track The Five Sorrowful Mysteries \; \track The Five Glorious
  Mysteries \; \track Passagalia}.
John Holloway (violin), harpsichord Davitt Moroney (chamber organ),
  chitarrone Stephen Stubbs (baroque lute), lirone Erin Headley (viola
  da gamba) and regal Andrew Lawrence-King (double harp).
Veritas/EMI, 1990 \cdnum[2]{7243 5 62062 2 9}.

\cd\relax
\artist{Biber, Heinrich Ignaz Franz von}.
\cdtitle{The Rosary Sonatas}.
Andrew Manze (violin), Richard Egarr (organ and harpsichord) and Alison
  McGillivray (cello).
Harmonia Mundi, 2004 \cdnum[2]{HMX 907321.22}.

\cd\relax
\artist{Biber, Heinrich Ignaz Franz von}.
\cdtitle{Violin Sonatas \: \track 8 Sonatae a Violino Solo,
  Salzburg~1681 \; \track Sonata representativa \; \track Sonata ``La
  Pastorella'' \; \track Passacaglia for solo lute \; \track Passacaglia
  for solo violin}.
Romanesca, Andrew Manze (violin), Nigel North (lute theorbo) and John
  Toll (harpsichord and organ).
Harmonia Mundi, 1994 \cdnum[2]{HMX 907134.35}.

\cd\relax
\artist{Biber, Heinrich Ignaz Franz von}.
\cdtitle{Violin Sonatas: Sonata~I \and Sonata~III \and Sonata~V \and
  Sonata~VI \and Sonata Representativa \and Passagalia for solo violin}.
Romanesca, Andrew Manze (violin), Nigel North (lute theorbo) and John
  Toll (harpsichord and organ).
Harmonia Mundi, 1997 \cdnum{HMX 2907225}.

\cd\relax
\artist{Biber, Heinrich von}.
\cdtitle{Harmonia artificiosa-ariosa \: \track Partita~I in D~minor \;
  \track Partita~II in B~minor \; \track Partita~III in A~major \;
  \track Partita~IV in E~flat major \; \track Partita~V in G~minor \;
  \track Partita~VI in D~major \; \track Partita~VII in C~minor}.
The Purcell Quartet.
Chandos, 1994 \cdnum[2]{CHAN 0575/6}.

\cd*\relax
\artist{Biggs, John}.
\cdtitle{Dance Suite for Oboe, Violin, Viola and Cello}.
\see{432}.

\cd\relax
\cdtitle{Billy Elliot}.
Interscope Records/Polydor, 2000 \cdnum{314549360-2}.

\cd*\relax
\artist{Birtwistle, Harrison}.
\cdtitle{Pulse Sampler}.
\see{1344}.

\cd*\relax
\artist{Bittov\'a, Iva}.
\cdtitle{Hoboj \and Divn\'a slecinka \(A strange young lady\) \and V
  zemi Neoran\'e \(On unploughed land\)}.
\see{1344}.

\cd\relax
\artist{Bizet, Georges}.
\cdtitle{Carmen}.
Agnes Baltsa, Jos\'e Carreras, Jos\'e van Dam, Katia Ricciarelli,
  Christine Barbaux, Jane Berbi\'e, Alexander Malta, Mikael Melbye, Gino
  Quilico and Heinz Zednik.
Berliner Philharmoniker.
Herbert von Karajan, cond.
Deutsche Grammophon, 1983 \cdnum[3]{410 088-2}.

\cd\relax
\artist{Bizet, Georges}.
\cdtitle{Songs by Georges Bizet}.
Anne Murray (mezzo soprano) and Graham Johnson (piano).
Hyperion, 1998 \cdnum{CDA66976}.

\cd*\relax
\artist{Bizet, Georges}.
\cdtitle{Variations chromatiques \(de concert\)}.
\see{658}.

\cd*\relax
\artist{Blanchet, Emile-Robert}.
\cdtitle{Au jardin du vieux s\'erail \(Andrianople\), Op.~18, No.~3}.
\see{724}.

\cd\relax
\artist{Blenders, The}.
\cdtitle{From the Mouth}.
Cowtown Records, 1994 \cdnum{PAC 2421}.

\cd\relax
\artist{Blenders, The}.
\cdtitle{Totally Whipped}.
Cowtown Records, 1992 \cdnum{PAC 2420}.

\cd*\relax
\artist{Bliss, Arthur}.
\cdtitle{Pastoral}.
\see{894}.

\cd\relax
\artist{Bliss, Sir Arthur}.
\cdtitle{Orchestral Works \: \track Music for Strings, Op.~54 \; \track
  Cello Concerto, Op.~120 \; \track Two Studies, Op.~16, No.~2--3}.
Tim Hugh (cello).
English Northern Philharmonia.
David Lloyd-Jones, cond.
Naxos, 1996 \cdnum{8.553383}.

\cd*\relax
\artist{Bloch, Ernest}.
\cdtitle{Schelomo: Hebraic Rhapsody for Cello and Orchestra}.
\see{1019}.

\cd*\relax
\artist{Bloch, Ernet}.
\cdtitle{Nigun}.
\see{245}.

\cd\relax
\artist{Blues Traveler}.
\cdtitle{Blues Traveler}.
A\&M Records, 1990 \cdnum{75021 5308-2}.

\cd\relax
\artist{Blues Traveler}.
\cdtitle{Four}.
A\&M Records, 1994 \cdnum{31454 0265~2}.

\cd\relax
\artist{Blues Traveler}.
\cdtitle{Save His Soul}.
A\&M Records, 1993 \cdnum{31454 0080~2}.

\cd\relax
\artist{Blues Traveler}.
\cdtitle{Straight on till Morning}.
A\&M Records, 1997 \cdnum{31454 0750~2}.

\cd\relax
\artist{Blues Traveler}.
\cdtitle{Travelers and Thieves}.
A\&M Records, 1991 \cdnum{75021 5373~2}.

\cd*\relax
\artist{Blumenfeld, Felix}.
\cdtitle{Etude pour la main gauche seule, Op.~36}.
\see{724}.

\cd\relax
\artist{Bobs, The}.
\cdtitle{Coaster}.
Primarily A Cappella Records, 2000 \cdnum{PAC~2900}.

\cd\relax
\artist{Bobs, The}.
\cdtitle{i brow club}.
Rounder Records, 1997 \cdnum{CD~9062}.

\cd\relax
\artist{Bobs, The}.
\cdtitle{My, I'm Large}.
Rhino Records, 1987 \cdnum{RS 71465}.

\cd\relax
\artist{Bobs, The}.
\cdtitle{Plugged}.
Rounder Records, 1995 \cdnum{CD~9059}.

\cd\relax
\artist{Bobs, The}.
\cdtitle{Shut Up and Sing!}
Rounder Records, 1993 \cdnum{CD~9039}.

\cd\relax
\artist{Bobs, The}.
\cdtitle{Songs for Tomorrow Morning}.
Rhino Records, 1988 \cdnum{RS 71466}.

\cd\relax
\artist{Bobs, The}.
\cdtitle{The Bobs}.
Rhino Records, 1983/1987 \cdnum{R2~71464}.

\cd\relax
\artist{Bobs, The}.
\cdtitle{The Bobs Cover the Songs of\dots}.
Rounder Records, 1994 \cdnum{CD~9049}.

\cd\relax
\artist{Bobs, The}.
\cdtitle{The Bobs Sing the Songs of\dots}.
Rhino Records, 1991 \cdnum{R2~71467}.

\cd\relax
\artist{Bobs, The}.
\cdtitle{Too Many Santas!}
Rounder Records, 1996 \cdnum{CD~9060}.

\cd\relax
\artist{Boccherini, Luigi}.
\cdtitle{Cello Sonatas \: \track Sonata for Violoncello and Basso
  continuo in B-flat major, G.~8 \; \track Fugue for Two Violoncellos in
  F~major, G.~72 No.~2 \; \track Sonata for Violoncello and Basso
  continuo in E-flat major, G.~10 \; \track Sonata for Violoncello and
  Basso continuo in F~major, G.~9 \; \track Fugue for Two Violoncellos
  in B-flat major, G.~73 No.~3 \; \track Sonata for Violoncello and
  Basso continuo in C~minor, G.~2 \; \track Fugue for Two Violoncellos
  in A~major, G.~73 No.~5 \; \track Sonata for Violoncello and Basso
  continuo in G~major, G.~15}.
Anner Bylsma (solo violoncello), Kenneth Slowik (violoncello) and Bob
  van Asperen (fortepiano).
Sony Classical, 1993 \cdnum{SK~53362}.

\cd*\relax
\artist{Boccherini, Luigi}.
\cdtitle{Concerto in B~flat major for Cello and String Orchestra, G.~482
  \and Concerto in D~major for Cello and Orchestra, G.~476}.
\see{1016}.

\cd*\relax
\artist{Boccherini, Luigi}.
\cdtitle{Concerto in G~major for Cello and String Orchestra, G.~480 \and
  Concerto in D~major for Cello and Orchestra, G.~479}.
\see{1015}.

\cd*\relax
\artist{Boccherini, Luigi}.
\cdtitle{Minuet \from\ String Quintet in E~Major, Op.~13, No.~5}.
\see{1619}.

\cd*\relax
\artist{Boccherini, Luigi}.
\cdtitle{Quintet for Two Violins, Viola, and Two Cellos in E~Major,
  Op..~13, No.~5}.
\see{1400}.

\cd\relax
\artist{Boismortier, Joseph Bodin de}.
\cdtitle{S\'er\'enades fran\c{c}aises \: \track Daphnis et Chlo\'e:
  Chaconne \; \track Fragments m\'elodiques \; \track Bassoon Concerto
  \; \track Deuxi\`eme s\'er\'enade ou simphonie fran\c{c}oise \; \track
  Concerto pour Zampogna \; \track Les Voyages de l'Amour: Entr\'ee des
  g\'enies \'el\'ementaires}.
Laurent Le Chenadec (bassoon).
Le Concert Spirituel.
Herv\'e Niquet, cond.
Naxos, 1999 \cdnum{8.554456}.

\cd\relax
\artist{Boismortier, Joseph Bodin de}.
\cdtitle{Six Concertos for Five Flutes; Works for One, Two and Three
  Flutes}.
Barthold Kuijken, Marc Hanta{\"\i}, Frank Theuns, S. Sa{\"\i}tta and D.
  Etienne.
Accent, 1995 \cdnum{ACC 24161}.

\cd\relax
\artist{Boismortier, Joseph Bodin de}.
\cdtitle{Sonatas for Flute and Harpsichord, Op.~91}.
Stephen Schultz (baroque flute) and Byron Schenkman (harpsichord).
Naxos, 1995 \cdnum{8.553414}.

\cd\relax
\artist{Boismortier, Joseph Bodin de}.
\cdtitle{Sonates pour basses \: \track Suite pour la viole, Op.~31 \;
  \track Sonate vi \`a quatre parties \'egalement travaill\'ees, Op.~34
  \; \track Sonata III pour le basson, Op. 26 \; \track Sonata II pour
  violoncelle, Op.~50 \; \track Sonata III \`a deux parties, Op.~14 \;
  \track Suite de pi\`eces que l'on peut jouer seul, Op.~40}.
Le Concert Spirituel.
Herv\'e Niquet, cond.
Glossa Music, 2004 \cdnum{GCD 921609}.

\cd\relax
\artist{Bok, Henri}.
\cdtitle{Music for Bass Clarinet and Piano \: \track \C{Paul Hindemith}
  Sonata \; \track \C{Othmar Schoeck} Sonata, Op.~41 \; \track \C{Lubos
  Sluka} Sonata \; \track \C{V\'aclav Rehak} Sonnet~III \; \track
  \C{Stefan Heucke} Sonate, Op.~23 \; \track \C{Burkhardt S\"oll}
  Lumen}.
Rainer Klaas (piano).
Clarinet Classics, 1999 \cdnum{CC0026}.

\cd*\relax
\artist{Bolcom, William}.
\cdtitle{Lilith}.
\see{505}.

\cd*\relax
\artist{Bolcom, William}.
\cdtitle{Twelve Cabaret Songs \(1977--83\)}.
\see{37}.

\cd\relax
\artist{Bolet, Jorge}.
\cdtitle{Bolet at Carnegie Hall Live}.
Volume~10 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 724-2}.

\cd\relax
\artist{Bolet, Jorge}.
\cdtitle{Liszt \: \track ``Mephisto'' Waltz No.~1 \; \track Venezia e
  Napoli \; \track Fun\'erailles \; \track Liebestraum No.~3 in A~flat
  \; \track La leggierezza \; \track La campanella \; \track
  R\'eminiscences de ``Norma'' \(Bellini\) \; \track ``Rigoletto''
  Paraphrase \(Verdi\) \; \track Sonetto 104 del Petrarca \; \track
  Harmonies du soir \; \track Gnomenreigen \; \track Au bord d'une
  source \; \track Consolation No.~3 in D~flat \; \track Hungarian
  Rhapsody No.~12 in C~sharp minor \; \track Ricordanza \; \track
  R\'eminiscences de ``Don Juan'' \(Mozart\)}.
Volume~11 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 814-2}.

\cd\relax
\artist{Bolling, Claude}.
\cdtitle{Suite for Cello and Jazz Piano Trio}.
Yo-Yo Ma (cello), Claude Bolling (piano), Marc Michel (bass) and
  Jean-Luc Dayan (drums).
CBS Records, 1984 \cdnum{MK~39059}.

\cd*\relax
\artist{Boone, Benjamin}.
\cdtitle{Alley Dance \(1996\)}.
\see{1146}.

\cd\relax
\artist{Borge, Victor}.
\cdtitle{Live (!)}.
Sony, 1992 \cdnum{MDK 48482}.

\cd*\relax
\artist{Borgo, Elliot Del}.
\cdtitle{Quartet for Saxophone \(1982\)}.
\see{1147}.

\cd\relax
\artist{Bornkamp, Arno and Ivo Janssen}.
\cdtitle{Saxophone Sonatas \: \track \C{Paul Creston} Sonata, op.~19 \;
  \track \C{Florent Schmitt} L\'egende, op.~66 \; \track \C{Paul
  Hindemith} Sonata \(1943\) \; \track \C{Alfred Desenclos} Pr\'elude,
  cadence et finale \(1956\) \; \track \C{Jacques Charpentier}
  Gavambodi~2 \; \track \C{Edison Denisov} Sonata \(1970\)}.
Globe/Klaas Posthuma Productions, 1990 \cdnum{GLO~5032}.

\cd\relax
\artist{Borodin, Alexander}.
\cdtitle{Polovetsian Dances from \emph{Prince Igor} \: \track \C{Modest
  P. Mussorgsky} A Night on Bald Mountain \; \track \C{Peter I.
  Tschaikowsky} Overture 1812, Op.~36 \; \track \C{Nicolai
  Rimsky-Korsakov} Russian Easter Overture, Op.~36}.
Vienna Symphonic Orchestra.
Heinrich Hollreiser, cond.
Tuxedo Music, 1989 \cdnum{TUXCD 1009}.
Recorded 1960.

\cd*\relax
\artist{Borodin, Alexander}.
\cdtitle{Polovtsian Dances \(Prince Igor, Act~II\)}.
\see{1272}.

\cd*\relax
\artist{Borodin, Alexander}.
\cdtitle{Prince Igor: Polovtsian March}.
\see{1137}.

\cd*\relax
\artist{Borodin, Alexander}.
\cdtitle{Scherzo in A~flat}.
\see{48}.

\cd\relax
\artist{Borodin, Alexander Porfiryevich}.
\cdtitle{Prince Igor}.
Sofia Festival Orchestra and Sofia National Opera Chorus.
Emil Tchakarov, cond.
Sony, 1990 \cdnum[3]{S3K 44878}.

\cd\relax
\artist{Borodin, Alexander Porfiryevich}.
\cdtitle{\track Symphony No.~1 in E-Flat Major \; \track Symphony No.~2
  in B~Minor \; \track Symphony No.~3 in A~Minor}.
CSR Symphony Orchestra \(Bratislava\).
Stephen Gunzenhauser, cond.
Naxos, 1989 \cdnum{8.550238}.

\cd\relax
\artist{Bostridge, Ian}.
\cdtitle{\track \C{Claude Debussy} F\^etes galantes \; \track \C{Gabriel
  Faur\'e} Fleur jet\'ee \and Le berceaux \and Au bord de l'eau \and
  Prison \and Clair de lune \and Nell \and La bonne chanson \; \track
  \C{Francis Poulenc} Montparnasse \and Deux po\`emes de uillaume
  Apollinaire \and Deux po\`emes de Louis Aragon \and Tel jour telle
  nuit}.
Julius Drake (piano), Corina Belcea (violin), Laura Samuel (violin),
  Krzysztof Chorzelski (viola), Alasdair Tait (cello) and Leon Bosch
  (double bass).
EMI Classics, 2004 \cdnum{7243~5 57609 2~0}.

\cd\relax
\artist{Bostridge, Ian}.
\cdtitle{The English Songbook}.
Julius Drake (piano).
EMI Classics, 1999 \cdnum{7243~5 56830 2~1}.

\cd*\relax
\artist{Bottermund-Starker}.
\cdtitle{Variations on a Theme by Paganini}.
\see{920}.

\cd*\relax
\artist{Bottesini, Giovanni}.
\cdtitle{Concerto No.~2 in B~Minor for Double Bass and Orchestra \and
  Gran Duo Concertante}.
\see{1065}.

\cd\relax
\artist{Bottesini, Giovanni}.
\cdtitle{Music for Double Bass and Piano, Volume~1}.
Joel Quarrington (double bass) and Andrew Burashko (piano).
Naxos, 1997 \cdnum{8.554002}.

\cd\relax
\artist{Boublil, Alain, Claude-Michel Sch\"onberg and Herbert Kretzmer}.
\cdtitle{Les Mis\'erables}.
Relativity/First Night Records, 1985 \cdnum[2]{88561-8140-2}.
Original London cast recording.

\cd\relax
\artist{Boulez, Pierre}.
\cdtitle{Piano Sonatas Nos.~1--3}.
Idil Biret.
Naxos, 1995 \cdnum{8.553353}.

\cd*\relax
\artist{Boutry, Roger}.
\cdtitle{``Interferences'' for Bassoon and Piano}.
\see{661}.

\cd\relax
\artist{Bowie, David}.
\cdtitle{Let's Dance}.
Virgin Records, 1983 \cdnum{7243 8 40982 2~3}.

\cd*\relax
\artist{Bozza, Eug\'ene}.
\cdtitle{Aria}.
\see{151}.

\cd*\relax
\artist{Bozza, Eug\`ene}.
\cdtitle{Aria}.
\see{1602}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{4 Ballades, Op.~10 \and 2 Rhapsodies, Op.~78 \and 10
  Intermezzi}.
Glenn Gould.
Sony, 1992 \cdnum[2]{SM2K 52~651}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{4 Piano Pieces, Op.~119}.
\see{930}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Ballades, Op.~10 \and Fantasias, Op.~116 \and Intermezzi,
  Op.~117 \and Klavierst\"ucke, Op.~118 \and Klavierst\"ucke, Op.~119
  \and Klavierst\"ucke, Op.~76}.
\see{888}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Cello Sonata No.~2 in~F, Op.~99}.
\see{500}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{Concerto for Piano and Orchestra No.~1}.
Glenn Gould.
New York Philharmonic.
Leonard Bernstein, cond.
Sony, 1998 \cdnum{SK~60675}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Double Concerto for Violin and Cello in A~minor, Op.~102}.
\see{237}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{Ein Deutsches Requiem}.
Elisabeth Schwarzkopf (soprano), Dietrich Fischer-Dieskau (baritone) and
  Ralph Downes (organ).
Philharmonia Orchestra and Chorus.
Otto Klemperer, cond.
EMI Records, 1997 \cdnum{7243 5 56218 2~5}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{Four Hand Piano Music, Volume~1 \: \track Variations in E~Flat
  Major on a Theme by Schumann, Op.~23 \; \track 16 Waltzes, Op.~39 \;
  \track Souvenir de la Russie, Anh.~IV/6 \; \track 15 Neue Liebeslieder
  Waltzes, Op.~65a}.
Silke-Thora Matthies and Christian K\"ohn.
Naxos, 1997 \cdnum{8.553139}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Gavotte in~A \(\from Paride ed Elena\)}.
\see{775}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{Geistliche Chormusik}.
RIAS-Kammerchor.
Marcus Creed, cond.
Harmonia Mundi, 1996 \cdnum{HMC 901591}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Hungarian Dance No.~1}.
\see{245}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Hungarian Dances}.
\see{1575}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{Hungarian Dances Nos.~1--21}.
Budapest Symphony Orchestra.
Istv\'an Bog\'ar, cond.
Naxos, 1988 \cdnum{8.550110}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Intermezzi, Op.~117 \and Theme and Variations in D~minor
  \(transcribed from String Sextet, Op.~18\)}.
\see{988}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Klavierst\"ucke, Op.~119, No.~3: Intermezzo in~C \and Piano
  Concerto No.~2 in B~flat, Op.~83}.
\see{140}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{Lieder}.
Dietrich Fischer-Dieskau (bariton) and Daniel Barenboim (piano).
Deutsche Grammophon, 1983 \cdnum[6]{437 501-2}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{Lieder und Ges\"ange \(opp.~17, 42, 62, 104\) \and In stiller
  Nacht}.
RIAS-Kammerchor.
Marcus Creed, cond.
Harmonia Mundi, 1996 \cdnum{HMC 901592}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{Orchesterwerke \: \track Symphonie Nr.~1 c-moll, op.~68 \;
  \track Symphonie Nr.~2 D-dur, op.~73 \; \track Symphonie Nr.~3 F-dur,
  op.~90 \; \track Symphonie Nr.~4 e-moll, op.~98 \; \track Serenade
  Nr.~1 D-dur, op.~11 \; \track Serenade Nr.~2 A-dur, op.~16 \; \track
  Tragische Ouvert\"ure, op.~81 \; \track Variationen f\"ur Orchester
  B-dur \"uber ein Thema von Joseph Haydn, op.~56a \; \track Akademische
  Festouvert\"ure, op.~80 \; \track Ungarische T\"anze, WoO~1}.
Berliner Philharmoniker and Wiener Philharmoniker.
Herbert von Karajan and Claudio Abbado, cond.
Deutsche Grammophon, 1989 \cdnum[5]{449 601-2}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Piano Concerto No.~1 in D~minor, Op.~15}.
\see{158}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Piano Concerto No.~1 in D~minor, Op.~15}.
\see{336}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{\track Piano Concerto No.~1 in D~minor, Op.~15 \; \track Three
  Intermezzi, Op.~117}.
Leif Ove Andsnes.
City of Birmingham Symphony Orchestra.
Sir Simon Rattle, cond.
EMI Classics, 1998 \cdnum{7243 5 56583 2~6}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Piano Concerto No.~2 in B~flat, Op.~83}.
\see{643}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{Piano Quartets \: \track Piano Quartet in G~minor, Op.~25 \;
  \track Piano Quartet in C~minor, Op.~60 \; \track Piano Quartet in
  A~major, Op.~26}.
Emanuel Ax (piano), Isaac Stern (violin), Jaime Laredo (viola) and Yo-Yo
  Ma (cello).
Sony Classical, 1990 \cdnum[2]{S2K~45846}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Piano Sonata in F~minor, Op.~5 \and Variations on an Original
  Theme, Op.~21 No.~1 \and Hungarian Dances, Vol.~1}.
\see{882}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Piano Sonata No.~3 in F~minor, Op.~5}.
\see{623}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Piano Sonata No.~3 in F~minor, Op.~5 \and Romance in~F, Op.~118
  No.~5 \and Intermezzo in~E, Op.~116 No.~6 \and Ballade in~B, Op.~10
  No.~4}.
\see{1320}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Rhapsody in B~minor, Op.~79 No.~1}.
\see{1196}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Rhapsody in B~minor, Op.~79 No.~1 \and Rhapsody in G~minor,
  Op.~79 No.~2}.
\see{887}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Scherzo in E~flat minor, Op.~4 \and Piano Concerto No.~2 in
  B~flat, Op.~83}.
\see{1702}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Sonata in E-flat Major, Op.~120, No.~2}.
\see{439}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Sonata in F~Minor, Op.~120, No.~1}.
\see{438}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Sonata in G~major, Op.~78}.
\see{1540}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{Sonatas for Cello and Piano \: \track Sonata No.~1 for Cello
  and Piano, Op.~38 \; \track Sonata No.~2 for Cello and Piano, Op.~99}.
Yo-Yo Ma and Emanuel Ax.
BMG Classics, 1998 \cdnum{09026-63267-2}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Symphony No.~1 in C~minor, op.~68 \and Haydn Variations,
  op.~56}.
\see{629}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{The Four Quintets, Volume~I \: \track Clarinet Quintet in
  B~minor, Op.~115 \; \track Piano Quintet in F~minor, Op.~34}.
Thomas Friedli (clarinet), Philippe Bianconi (piano) and Quartet Sine
  Nomine.
Claves, 1997 \cdnum{CD 50-9608}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{The Four Quintets, Volume~II \: \track String Quintet No.~1 in
  F~major, Op.~88 \; \track String Quintet No.~2 in G~major, Op.~111}.
Rapha\"el Oleg and Quartet Sine Nomine.
Claves, 1997 \cdnum{CD 50-9609}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Trio for Piano, Clarinet and Cello in A~minor, Op.~114}.
\see{1005}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Variations and Fugue on a Theme by Handel, Op.~24 \and
  Intermezzo in B~flat minor, Op.~117 No.~2}.
\see{1485}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Variations on a Theme by Paganini, Op.~35 \and Ballades,
  Op.~10}.
\see{1066}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Variations on a Theme by Paganini, Op.~35 \and Piano Concerto
  No.~1 in D~minor, Op.~15}.
\see{43}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Violin Concerto in D major, op.~77}.
\see{246}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{Violin Concerto in~D, Op.~77 \and Concerto in A minor, Op.~102
  for violin and cello, with orchestra}.
Henryk Szeryng (violin) and J\'anos Starker (cello).
The Royal Concertgebouw Orchestra.
Bernard Haitink, cond.
Philips Classics, 1995 \cdnum{446 194-2}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Violin Concerto, Op.~77}.
\see{766}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{Vokal-Ensembles \: \track Drei Duette op.~20 \; \track Vier
  Duette op.~28 \; \track Vier Duette op.~61 \; \track F\"unf Duette
  op.~66 \; \track Balladen und Romanzen op.~75 \; \track Drei Quartette
  op.~31 \; \track Drei Quartette op.~64 \; \track Liebeslieder op.~52
  \; \track Neue Liebeslieder op.~65 \; \track Vier Quartette op.~92 \;
  \track Drei Quartette aus ``Zigeunerlieder'' op.~103 \; \track Sechs
  Quartette op.~112 \; \track 49 Deutsche Volkslieder WoO~33 \; \track
  14 Volks-Kinderlieder WoO~31}.
Edith Mathis (sopran), Brigitte Fassbaender (alt/contralto), Peter
  Schreier (tenor), Dietrich Fischer-Dieskau (bariton), Karl Engel
  (piano), Wolfgang Sawallisch (piano) and Gernot Kahl (piano).
North German Radio Chorus.
Deutsche Grammophon, 1983 \cdnum[4]{449 641-2}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Waltz in A~flat, Op.~39 No.~15 \and Intermezzo in~C, Op.~119
  No.~3}.
\see{770}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Waltzes, Op.~39 \(Excerpts\) \(with Nadia Boulanger\)}.
\see{967}.

\cd*\relax
\artist{Brahms, Johannes}.
\cdtitle{Walzes, Op.~39, Nos.~1, 2, 6, and~15}.
\see{844}.

\cd\relax
\artist{Brahms, Johannes}.
\cdtitle{Zigeunerlieder \(opp.~103, 112b\) und Quartette \(opp.~31, 64,
  92, 112a\)}.
RIAS-Kammerchor.
Marcus Creed, cond.
Harmonia Mundi, 1997 \cdnum{HMC 901593}.

\cd\relax
\artist{Brandl, Johann Evangelist}.
\cdtitle{Bassoon Quintets \: \track Quintet Op.~14 \; \track Quintet
  Op.~52/1 \; \track Quintet Op.~52/2}.
Rainer Schottst\"adt (bassoon), Torsten Janicke (violin), Mile Kosi
  (viola), Urara Seo (viola) and Johannes Nauber (violoncello).
MDG, 2002 \cdnum{MDG 603 1133-2}.

\cd*\relax
\artist{Brassin, Louis}.
\cdtitle{Magic Fire Music \(\from Die Walk\"ure\)}.
\see{775}.

\cd\relax
\artist{Brave Combo}.
\cdtitle{A Night on Earth}.
Rounder Records, 1990 \cdnum{CD 9029}.

\cd\relax
\artist{Brave Combo}.
\cdtitle{Humansville}.
Rounder Records, 1988 \cdnum{CD 9019}.

\cd\relax
\artist{Brave Combo}.
\cdtitle{It's Christmas, Man!}
Rounder Records, 1992 \cdnum{CD 9033}.

\cd\relax
\artist{Brave Combo}.
\cdtitle{Mood Swing Music}.
Rounder Records, 1996 \cdnum{CD 11574}.

\cd\relax
\artist{Brave Combo}.
\cdtitle{Musical Varieties}.
Rounder Records, 1987 \cdnum{CD 11546}.

\cd\relax
\artist{Brave Combo}.
\cdtitle{No, No, Cha Cha Cha}.
Rounder Records, 1993 \cdnum{CD 9035}.

\cd\relax
\artist{Brave Combo}.
\cdtitle{Polkas for a Gloomy World}.
Rounder Records, 1995 \cdnum{CD 9045}.

\cd\relax
\artist{Brave Combo}.
\cdtitle{Polkatharsis}.
Rounder Records, 1987 \cdnum{CD 9009}.

\cd\relax
\artist{Brave Combo and Lauren Agnelli}.
\cdtitle{Kiss of Fire}.
Watermelon Records, 1996 \cdnum{CD 1058}.

\cd\relax
\artist{Brendel, Alfred}.
\cdtitle{Beethoven \: \C{Ludwig van Beethoven} Piano Sonata in B~flat,
  Op.~106 ``Hammerklavier'' \and 6 Bagatelles, Op.~126 \and 10
  Variations on ``La stessa, la stessissima,'' WoO~73 from Salieri's
  ``Falstaff'' \and 33 Variations on a Waltz by Anton Diabelli in~C,
  Op.~120 \and Piano Sonata in C~minor, Op.~111}.
Volume~13 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 730-2}.

\cd\relax
\artist{Brendel, Alfred}.
\cdtitle{Brahms/Busoni/Chopin/Liszt/Mendelssohn/Weber \: \track \C{Felix
  Mendelssohn Mendelssohn} Variations S\'erieuses, Op.~54 \; \track
  \C{Carl Maria von Weber} Konzertst\"uck in F~minor, Op.~79 \; \track
  \C{Johannes Brahms} Piano Concerto No.~1 in D~minor, Op.~15 \; \track
  \C{Fr\'ed\'eric Chopin} Polonaise in F~sharp minor, Op.~44 \; \track
  \C{Franz Liszt} Valle\'e d'Obermann \and Orage \and Totentanz \and
  Sposalizio \and Bagatelle sans Tonalit\'e \and Hungarian Rhapsody
  No.~15 in A~minor ``R\'ak\'oczy March'' \; \track \C{Ferruccio Busoni}
  Toccata}.
Volume~14 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 733-2}.

\cd\relax
\artist{Brendel, Alfred}.
\cdtitle{Haydn/Mozart/Schubert/Schumann \: \track \C{Joseph Haydn} Piano
  Sonata in E~minor, Hob.~XVI:34 \and Piano Sonata in~G, Hob.~XVI:40
  \and Piano Sonata in~D, Hob.~XVI:42 \and Piano Sonata in E~flat,
  Hob.~XVI:52 \; \track \C{Wolfgang Amadeus Mozart} Fantasia in C~minor,
  KV~475 \; \track \C{Franz Schubert} Impromptus, D.~899 \and
  Impromptus, D.~935 \; \track \C{Robert Schumann} Fantasiest\"ucke,
  Op.~12}.
Volume~12 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 727-2}.

\cd*\relax
\artist{Bridge, Frank}.
\cdtitle{Elegy for Cello and Piano \and Scherzetto for Cello and Piano}.
\see{984}.

\cd\relax
\artist{Bridge, Frank}.
\cdtitle{Works for String Orchestra \: \track Phantasie Quartet \;
  \track Novelletten \; \track Three Idylls \; \track An Irish Melody:
  Londonderry Air \; \track Sir Roger de Coverly \; \track Cherry Ripe
  \; \track Three Pieces}.
Maggini Quartet.
Naxos, 1995 \cdnum{8.553718}.

\cd\relax
\artist{Britten, Benjamin}.
\cdtitle{Billy Budd}.
Thomas Hampson, Anthony Rolfe Johnson and Eric Halfvarson.
Manchester Boys Choir and the Hall\'e Orchestra and Choir.
Kent Nagano, cond.
Erato, 1998 \cdnum[2]{3984-21631-2}.
Libretto by E. M. Forster and Eric Crozier.

\cd*\relax
\artist{Britten, Benjamin}.
\cdtitle{Cabaret Songs \(1937\)}.
\see{37}.

\cd*\relax
\artist{Britten, Benjamin}.
\cdtitle{Cello Sonata in~C, Op.~65 \(Scherzo and Marcia\)}.
\see{500}.

\cd\relax
\artist{Britten, Benjamin}.
\cdtitle{Cello Suite No.~1, op.~72 \and Cello Suite No.~2, op.~80 \and
  Sonata for Cello and Piano, op.~65}.
Mstislav Rostropovich (cello) and Benjamin Britten (piano).
The Decca Record Company, 1989 \cdnum{421 859-2}.

\cd\relax
\artist{Britten, Benjamin}.
\cdtitle{Foklsong from Somerset \and Quatre Chansons Fran\c{c}aises
  \(1928\) \and French Folksongs \and Sinfonietta, Op.~1 \and Our
  Hunting Fathers, Op.~8 \and Nursery Rhyme from Suffolk}.
Ian Bostridge (tenor).
Britten Sinfonia.
Daniel Harding, cond.
EMI Classics, 1998 \cdnum{7243 5 56534~2~0}.

\cd\relax
\artist{Britten, Benjamin}.
\cdtitle{Peter Grimes}.
Peter Pears, Claire Watson, James Pease, David Kelly and Owen Brannigan.
Orchestra and Chorus of the Royal Opera House, Covent Garden.
Benjamin Britten, cond.
The Decca Record Company, 1959/1985 \cdnum[3]{414 577-2}.

\cd\relax
\artist{Britten, Benjamin}.
\cdtitle{\track Serenade for Tenor, Horn and Strings, Op.~31 \; \track O
  Waly, Waly \; \track Our Hunting Fathers, Op.~8 \; \track Oliver
  Cromwell}.
Ian Bostridge (tenor) and Marie Luise Neunecker (horn).
Bamberger Symphoniker and Britten Sinfonia.
Ingo Metzmacher and Daniel Harding, cond.
EMI Classics, 1999 \cdnum{7243 5 56871 2~8}.

\cd*\relax
\artist{Britten, Benjamin}.
\cdtitle{Six Metamorphoses after Ovid for Oboe Solo, Op. 49}.
\see{1664}.

\cd\relax
\artist{Britten, Benjamin}.
\cdtitle{String Quartets, Volume~1 \: \track String Quartet No.~1 in
  D~major, Op.~25 \; \track String Quartet No.~2 in C~major, Op.~36 \;
  \track Thre Divertimenti}.
Maggini String Quartet.
Naxos, 1998 \cdnum{8.553883}.

\cd\relax
\artist{Britten, Benjamin}.
\cdtitle{String Quartets, Volume~2 \: \track Simple Symphony \; \track
  Quartettino \; \track Alla Marcia \; \track String Quartet No.~3,
  Op.~94}.
Maggini String Quartet.
Naxos, 1999 \cdnum{8.554360}.

\cd*\relax
\artist{Britten, Benjamin}.
\cdtitle{Suite for solo cello, Op.~72 \and Second suite for solo cello,
  Op.~80 \and Symphony for cello and orchestra, Op.~68}.
\see{1315}.

\cd*\relax
\artist{Britten, Benjamin}.
\cdtitle{Symphony for Cello and Orchestra, Op.~68}.
\see{1013}.

\cd*\relax
\artist{Britten, Benjamin}.
\cdtitle{Tema ``Sacher'' \and Third Suite for Cello, Op.~87}.
\see{983}.

\cd\relax
\artist{Britten, Benjamin}.
\cdtitle{The Red Cockatoo, The Holy Sonnets of John Donne, and other
  songs}.
Ian Bostridge (tenor) and Graham Johnson (piano).
Hyperion, 1995 \cdnum{CDA66823}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{44 \& 66}.
Red House Records, 1980 \cdnum{RHR CD~02}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{Bath Tub Blues}.
Red House Records, 1993 \cdnum{RHR CD~42}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{Covenant}.
Red House Records, 2000 \cdnum{RHR CD~148}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{Down in There}.
Red House Records, 1990 \cdnum{RHR~35}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{Dream Caf\'e}.
Red House Records, 1992 \cdnum{RHR CD~47}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{Further In}.
Red House Records, 1996 \cdnum{RHR CD~88}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{Honey in the Lions Head}.
Trailer Records, 2004 \cdnum{TR0035}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{If I Had Known: Essential Recordings, 1980--1996}.
Red House Records, 2003 \cdnum[2]{RHR CD~171}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{In the Dark With You}.
Red House Records \cdnum{RHR CD~08}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{In the Hills of California: Live from the Kate Wolf Music
  Festival 1997--2003}.
Red House Records, 2004 \cdnum[2]{RHR CD~180}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{Milk of the Moon}.
Red House Records, 2002 \cdnum{RHR CD~168}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{One Big Town}.
Red House Records, 1989 \cdnum{RHR CD~28}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{One More Goodnight Kiss}.
Red House Records, 1988 \cdnum{RHR CD~23}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{One Night}.
Red House Records, 1982/1999 \cdnum{RHR CD~128}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{Over and Under}.
Trailer Records/Rubric Records, 2002 \cdnum{TRUB~33}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{Slant 6 Mind}.
Red House Records, 1997 \cdnum{RHR CD~98}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{Songs of Innocence and Experience}.
Angust Foster (bass), Michael Doucet (violin), mandolin Peter Ostroushko
  (violion) and harmonica, pan pipes Dave Moore (button accordion).
Red House Records, 1986 \cdnum{RHR CD~14}.
Settings of poems by William Blake.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{The Iowa Waltz}.
Red House Records, 1981 \cdnum{RHR CD~01}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{The Live One}.
Red House Records, 1995 \cdnum{RHR CD~78}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{The Poet Game}.
Red House Records, 1994 \cdnum{RHR CD~68}.

\cd\relax
\artist{Brown, Greg}.
\cdtitle{Yellow Dog}.
Earthwork Music Archives, 2007 \cdnum{EWA001}.

\cd\relax
\artist{Browne, Jackson}.
\cdtitle{Lawyers in Love}.
Elektra/Asylum Records, 1983 \cdnum{9~60268-2}.

\cd\relax
\artist{Browne, Jackson}.
\cdtitle{Lives in the Balance}.
Elektra/Asylum Records, 1986 \cdnum{9 60457-2}.

\cd*\relax
\artist{Bruch, Max}.
\cdtitle{Canzone}.
\see{1144}.

\cd\relax
\artist{Bruch, Max}.
\cdtitle{Gesamtwerk f\"ur Violoncello und Orchester \: \track Kol
  Nidrei, Adagio nach Hebr\"aischen Melodien f\"ur Violoncello und
  Orchester, op.~47 \; \track Cancona f\"ur Violoncello und Orchester
  B-dur, op.~55 \; \track Adagio nach keltischen Motiven f\"ur
  Violoncello und Orchester e-moll, op.~56 \; \track Ave Maria f\"ur
  Violoncello und Orchester, op.~61}.
Julius Berger.
Nationales Rundfunk-Sinfonieorchester Polen.
Antoni Wit, cond.
EBS Records, 1991 \cdnum{ebs~6060}.

\cd*\relax
\artist{Bruch, Max}.
\cdtitle{Schottische Fantasie, Op.~46}.
\see{766}.

\cd\relax
\artist{Bruch, Max}.
\cdtitle{The Complete Violin Concertos \: \track Violin Concerto No.~1
  in G~minor, op.~26 \; \track Violin Concerto No.~2 in D~minor, op.~44
  \; \track Serenade for Violin and Orchestra, op.~75 \; \track Violin
  Concerto No.~3 in D~minor, op.~58 \; \track Scottish Fantasy, op.~46}.
Salvatore Accardo (violin).
Gewandhausorchester Leipzig.
Kurt Masur, cond.
Philips Classics, 1998 \cdnum[2]{289 462 167-2}.

\cd*\relax
\artist{Bruch, Max}.
\cdtitle{Violin Concerto No.~1 in G minor, op.~26}.
\see{243}.

\cd\relax
\artist{Bruckner, Anton}.
\cdtitle{Symphony No.~2 in C~minor \(1872 version, ed.~Carragan\)}.
National Symphony Orchestra of Ireland.
Georg Tintner, cond.
Naxos, 1997 \cdnum{8.554006}.

\cd\relax
\artist{Bruckner, Anton}.
\cdtitle{Symphony No.~3 in D~minor \(1873 version, ed.~Nowak\)}.
National Symphony Orchestra of Ireland.
Georg Tintner, cond.
Naxos, 2000 \cdnum{8.553454}.

\cd\relax
\artist{Bruckner, Anton}.
\cdtitle{Symphony No.~4 in E~flat major ``Romantic'' \(1878/80 version,
  ed.~Haas\)}.
Royal Scottish National Orchestra.
Georg Tintner, cond.
Naxos, 1998 \cdnum{8.554128}.

\cd\relax
\artist{Bruckner, Anton}.
\cdtitle{Symphony No.~5 in B~flat major}.
Royal Scottish National Orchestra.
Georg Tintner, cond.
Naxos, 1997 \cdnum{8.553452}.

\cd\relax
\artist{Bruckner, Anton}.
\cdtitle{Symphony No.~6 in A~major}.
New Zealand Symphony Orchestra.
Georg Tintner, cond.
Naxos, 1997 \cdnum{8.553453}.

\cd\relax
\artist{Bruckner, Anton}.
\cdtitle{Symphony No.~7 in E~major \(ed. Haas\)}.
Royal Scottish National Orchestra.
Georg Tintner, cond.
Naxos, 1999 \cdnum{8.554269}.

\cd\relax
\artist{Bruckner, Anton}.
\cdtitle{\track Symphony No.~8 in C~minor \(1887 version, ed.~Nowak\) \;
  \track Symphony No.~0 in D~minor ``Die Nullte''}.
National Symphony Orchestra of Ireland.
Georg Tintner, cond.
Naxos, 1998 \cdnum[2]{8.554215-6}.

\cd\relax
\artist{Bruckner, Anton}.
\cdtitle{Symphony No.~9 in D~minor \(ed. Nowak\)}.
Royal Scottish National Orchestra.
Georg Tintner, cond.
Naxos, 1999 \cdnum{8.554268}.

\cd\relax
\artist{Bruk, Lyubov and Mark Taimanov}.
\cdtitle{Arensky/Busoni/Mozart/Poulenc/Rachmaninoff \: \track \C{Anton
  Arensky} Suite No.~1 for Two Pianos, Op.~15 \and Suite No.~2 for Two
  Pianos, Op.~23 ``Silhouettes'' \; \track \C{Ferruccio Busoni} Duettino
  concertante \; \track \C{Fr\'ed\'eric Chopin} Rondo for Two Pianos
  in~C, Op.~73 \; \track \C{Darius Milhaud} Scaramouche, Suite for Two
  Pianos, Op.~165b \; \track \C{Wolfgang Amadeus Mozart} Concerto for
  Two Pianos in E~flat, KV~365 \; \track \C{Francis Poulenc} Concerto
  for Two Pianos in D~minor \and Sonata for Two Pianos \; \track
  \C{Sergei Rachmaninoff} Suite No.~1 for Two Pianos in G~minor, Op.~5
  \and Suite No.~2 for Two Pianos, Op.~17}.
Volume~15 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 736-2}.

\cd*\relax
\artist{Brumby, Colin}.
\cdtitle{Suite for Four Double Basses \(1975\)}.
\see{619}.

\cd*\relax
\artist{Bryars, Gavin}.
\cdtitle{The Green Ray}.
\see{745}.

\cd*\relax
\artist{Buckley, John}.
\cdtitle{Saxophone Quartet}.
\see{1231}.

\cd\relax
\artist{Buffett, Jimmy}.
\cdtitle{Changes in Lattitudes, Changes in Attitudes}.
MCA Records, 1977 \cdnum{MCAD-31070}.

\cd\relax
\artist{Buffett, Jimmy}.
\cdtitle{One Particular Harbour}.
MCA Records, 1983 \cdnum{MCAD-31094}.

\cd\relax
\artist{Buffett, Jimmy}.
\cdtitle{Riddles in the Sand}.
MCA Records, 1984 \cdnum{MCAD-31095}.

\cd\relax
\artist{Buffett, Jimmy}.
\cdtitle{Songs You Know by Heart}.
MCA Records, 1985 \cdnum{MCAD-5633}.

\cd\relax
\artist{Buffett, Jimmy}.
\cdtitle{Volcano}.
MCA Records, 1979 \cdnum{MCAD-1657}.

\cd*\relax
\artist{Buonamente, Giovanni Battista}.
\cdtitle{Sonata a tre violini from \emph{Book~6}}.
\see{1184}.

\cd*\relax
\artist{Burgers, Simon}.
\cdtitle{`Pastiche'}.
\see{1344}.

\cd*\relax
\artist{Busoni, Ferruccio}.
\cdtitle{Chaconne in D~minor \(arr.\ from J.~S. Bach's Partita No.~2 for
  Violi, BWV~1004\)}.
\see{899}.

\cd*\relax
\artist{Busoni, Ferruccio}.
\cdtitle{Duettino concertante}.
\see{380}.

\cd*\relax
\artist{Busoni, Ferruccio}.
\cdtitle{Fantasia nach J~S Bach}.
\see{726}.

\cd*\relax
\artist{Busoni, Ferruccio}.
\cdtitle{Fantasia on 2 themes from ``Le nozze di Figaro''}.
\see{644}.

\cd*\relax
\artist{Busoni, Ferruccio}.
\cdtitle{Ich ruf zu dir, Herr Jesu Christ, BWV~639}.
\see{588}.

\cd\relax
\artist{Busoni, Ferruccio}.
\cdtitle{Piano Concerto in C~major, Op.~39}.
Marc-Andr\'e Hamelin.
The City of Birmingham Symphony Orchestra.
Mark Elder, cond.
Hyperion, 1999 \cdnum{CDA67143}.

\cd*\relax
\artist{Busoni, Ferruccio}.
\cdtitle{Sonatina No~6: Kammer-Fantasie \"uber Carmen, BV284}.
\see{725}.

\cd*\relax
\artist{Busoni, Ferruccio}.
\cdtitle{Toccata}.
\see{336}.

\cd*\relax
\artist{Busoni, Ferruccio}.
\cdtitle{Variations and Fugue on Prelude in C~minor by Fr\'ed\'eric
  Chopin \and Piano Concerto, Op.~39}.
\see{1177}.

\cd*\relax
\artist{Busoni, Ferrucio}.
\cdtitle{Ecossaises}.
\see{952}.

\cd\relax
\artist{Buttons and Bows}.
\cdtitle{Grace Notes---N\'ota{\'\i} Maise}.
Gael-Linn, 1991 \cdnum{CEFCD 151}.

\cd\relax
\artist{Buttons and Bows}.
\cdtitle{The First Month of Summer}.
Green Linnet, 1987 \cdnum{GLCD 1079}.

\cd*\relax
\artist{Byrd, William}.
\cdtitle{First Pavan and Galliard \and Hughe Ashton's Ground \and Sixth
  Pavan and Galliard \and A Voluntary \and Sellinger's Round}.
\see{658}.

\cd\relax
\artist{Byrd, William}.
\cdtitle{Sacred Choral Music \: \track Mass for 3 voices \and Mass for 4
  voices \and Mass for 5 voices \and Magnificat \and Nunc dimittis \and
  Ave verum corpus \; \track \C{John Taverner} Kyrie ``Le Roy'' \and
  Mass ``The Western Wind'' \and Dum transisset sabbatum \and Christe
  Jesu pastor bone \and Mater Christi}.
Cambridge The Choir of King's College.
Sir David Willcocks, cond.
The Decca Record Company, 1996 \cdnum[2]{452 170-2}.

\cd\relax
\artist{Byrd, William}.
\cdtitle{The Complete Keyboard Music}.
Davitt Moroney.
Hyperion, 1999 \cdnum[7]{CDA66551/7}.

\cd\relax
\artist{Byrds, The}.
\cdtitle{Mr. Tambourine Man}.
Columbia, 1965/1996 \cdnum{CK~64845}.

\cd\relax
\artist{Cafiso, Francesco}.
\cdtitle{Very Early!}
Philology, 2001 \cdnum{W~225}.

\cd\relax
\artist{Cafiso, Francesco and Franco D'Andrea}.
\cdtitle{Standing Ovation at Pescara Jazz Festival 2002}.
Philology, 2002 \cdnum{W~410.2}.

\cd*\relax
\artist{Cage, John}.
\cdtitle{Five$^4$ \and Four$^5$}.
\see{1686}.

\cd*\relax
\artist{Cage, John}.
\cdtitle{Four$^5$}.
\see{50}.

\cd*\relax
\artist{Cage, John}.
\cdtitle{Solo for Sliding Trombone}.
\see{964}.

\cd\relax
\artist{Cale, J. J.}
\cdtitle{To Tulsa and Back}.
Sanctuary Records, 2004 \cdnum{06076-84687-2}.

\cd\relax
\artist{Canadian Brass, The}.
\cdtitle{All You Need Is Love}.
RCA Victor, 1998 \cdnum{09026-68970-2}.

\cd*\relax
\artist{Canfield, David DeBoor}.
\cdtitle{Sonata for Alto Saxophone and Piano \(2000\)}.
\see{1601}.

\cd*\relax
\artist{Canteloube, Joseph}.
\cdtitle{Chants d'Auvergne}.
\see{1602}.

\cd\relax
\artist{Canteloube, Joseph}.
\cdtitle{\track Chants d'Auvergne \; \track \C{Heitor Villa-Lobos}
  Bachianas brasileiras No.~5}.
Kiri Te Kanawa.
English Chamber Orchestra/Lynn Harrell and Instrumental Ensemble~(2).
Jeffrey Tate, cond.
The Decca Record Company, 1995 \cdnum[2]{444 995-2}.

\cd\relax
\artist{Canteloube, Joseph}.
\cdtitle{Songs of the Auvergne}.
Netania Davrath (soprano).
Pierre de la Roche, cond.
Vanguard Classics, 1996 \cdnum[2]{SVC-38/39}.

\cd\relax
\artist{Capercaillie}.
\cdtitle{Crosswinds}.
Green Linnet, 1987 \cdnum{GLCD 1077}.

\cd\relax
\artist{Capercaillie}.
\cdtitle{Delirium}.
Green Linnet, 1991 \cdnum{GLCD~3108}.

\cd\relax
\artist{Capercaillie}.
\cdtitle{Get out}.
Green Linnet, 1992 \cdnum{GLCD~3110}.

\cd\relax
\artist{Capercaillie}.
\cdtitle{Secret People}.
Arista, 1993 \cdnum{74321 16274-2}.

\cd\relax
\artist{Capercaillie}.
\cdtitle{Sidewaulk}.
Green Linnet, 1989 \cdnum{GLCD~1094}.

\cd\relax
\artist{Capercaillie}.
\cdtitle{To the Moon}.
Green Linnet, 1997 \cdnum{GLCD~3117}.

\cd*\relax
\artist{Caplet, Andr\'e}.
\cdtitle{L\'egende}.
\see{631}.

\cd\relax
\cdtitle{Carmina Burana, Volume~I}.
Catherine Bott (soprano) and Michael George (baritone).
The New London Consort.
Pickett, Philip, cond.
The Decca Record Company, 1987 \cdnum{417 373-2}.

\cd\relax
\cdtitle{Carmina Burana, Volume~II}.
Catherine Bott (soprano) and Michael George (baritone).
The New London Consort.
Pickett, Philip, cond.
The Decca Record Company, 1988 \cdnum{421 062-2}.

\cd\relax
\cdtitle{Carmina Burana, Volumes~III and~IV}.
Catherine Bott (soprano) and Michael George (baritone).
The New London Consort.
Pickett, Philip, cond.
The Decca Record Company, 1989 \cdnum[2]{425 117-2}.

\cd*\relax
\artist{Carpenter, Gary}.
\cdtitle{Une Semaine de Bont\'e}.
\see{1231}.

\cd*\relax
\artist{Carter, Elliott}.
\cdtitle{Canonic Suite for Quartet of Alto Saxophones}.
\see{50}.

\cd*\relax
\artist{Carter, Elliott}.
\cdtitle{Inner Song}.
\see{1686}.

\cd\relax
\artist{Casadesus, Robert}.
\cdtitle{Bach/Beethoven/Debussy/Faur\'e/Rameau/Scarlatti \: \track
  \C{Jean-Philippe Rameau} Gavotte \and Le rappel des oiseaux \and Les
  sauvages \and Les nials de Sologne \; \track \C{Johann Sebastian Bach}
  French Suite No.~6 in~E, BWV~817 \; \track \C{Domenico Scarlatti}
  Sonata in~E, K.~380 \and Sonata in~A, K.~533 \and Sonata in~D, K.~23
  \and Sonata in~G, K.~14 \and Sonata in B~minor, K.~27 \and Sonata
  in~D, K.~430 \; \track \C{Ludwig van Beethoven} Sonata No.~2 in~A,
  Op.~2 No.~2 \; \track \C{Claude Debussy} En blanc et noir \(for 2
  pianos\) \; \track \C{Claude Faur\'e} Dolly, Op.~56 \(Piano duet\)
  \and Pr\'elude in D~flat, Op.~103 No.~1 \and Pr\'elude in G~minor,
  Op.~103 No.~3 \and Pr\'elude in D~minor, Op.~103 No.~5 \and Nocturne
  No.~7 in C~sharp minor, Op.~74 \and Barcarolle No.~5 in F~sharp minor,
  Op.~66 \and Impromptu No.~5 in F~sharp minor, Op.~102 \; \track
  \C{Maurice Ravel} Piano Concerto in~D ``for the left hand''}.
Volume~16 of \emph{Great Pianists of the 20th Century}.
Gaby Casadesus (piano).
Philadelphia Orchestra.
Eugene Ormandy, cond.
Philips Classics, 1999 \cdnum[2]{456 739-2}.

\cd*\relax
\artist{Cascarino, Romeo}.
\cdtitle{Sonata for Bassoon and Piano}.
\see{661}.

\cd*\relax
\artist{Casella, Alfredo}.
\cdtitle{Deux Contrastes}.
\see{724}.

\cd*\relax
\artist{Cassad\'o, Gaspar}.
\cdtitle{Dance of the Green Devil}.
\see{902}.

\cd*\relax
\artist{Castello, Dario}.
\cdtitle{Sonata~I \and Sonata~II \from ``Sonate concertate in stil
  moderno,'' Lib.~II}.
\see{1308}.

\cd\relax
\artist{Catoire, Georgy}.
\cdtitle{Piano Music \: \track Caprice, Op.~3 \; \track Intermezzo,
  Op.~6 No.~5 \; \track Trois morceaux, Op.~2 \; \track Pr\'elude, Op.~6
  No.~2 \; \track Scherzo, Op.~6 No.~3 \; \track Vision \(\'Etude\),
  Op.~8 \; \track Cinq morceaux, Op.~10 \; \track Quatre morceaux,
  Op.~12 \; \track Quatre pr\'eludes, Op.~17 \; \track Chants du
  cr\'epuscule, Op.~24 \; \track Po\`eme, Op.~34, No.~2 \; \track
  Pr\'elude, Op.~34, No.~3 \; \track Valse, Op.~36}.
Marc-Andr\'e Hamelin.
Hyperion, 1999 \cdnum{CDA67090}.

\cd*\relax
\artist{Celis, Frits}.
\cdtitle{Da Uno a Cinque for Bass Clarinet and String Quartet, Op.~27}.
\see{1321}.

\cd\relax
\artist{Cellists of the Berlin Philharmonic, The 12}.
\cdtitle{Cello Submarine}.
Teldec Classics, 1983 \cdnum{10012-2}.

\cd*\relax
\artist{Cervetto, Giacomo}.
\cdtitle{Sicilienne}.
\see{881}.

\cd*\relax
\artist{Chaikovsky, Boris}.
\cdtitle{Suite for solo cello \and Partita for cello, piano,
  harpsichord, electric guitar and percussion \and Cello Concerto}.
\see{1315}.

\cd\relax
\artist{Charles, Ray}.
\cdtitle{Blues and Jazz}.
Rhino, 1991 \cdnum[2]{R2~71607}.

\cd\relax
\artist{Charles, Ray}.
\cdtitle{The Birth of Soul, Volume One: 1952--1954}.
Atlantic, 1991 \cdnum{7 82310-2}.

\cd\relax
\artist{Charles, Ray}.
\cdtitle{The Birth of Soul, Volume Three: 1957--1959}.
Atlantic, 1991 \cdnum{7 82310-2}.

\cd\relax
\artist{Charles, Ray}.
\cdtitle{The Birth of Soul, Volume Two: 1954--1957}.
Atlantic, 1991 \cdnum{7 82310-2}.

\cd\relax
\artist{Charles, Ray}.
\cdtitle{The Complete Country and Western Recordings, 1959--1986}.
Rhino, 1998 \cdnum[4]{R2 75328}.

\cd*\relax
\artist{Charpentier, Jacques}.
\cdtitle{Gavambodi~2}.
\see{298}.

\cd*\relax
\artist{Chausson, Ernest}.
\cdtitle{Concert for piano, violin and string quartet, op.~21}.
\see{244}.

\cd*\relax
\artist{Chausson, Ernest}.
\cdtitle{Po\`eme, op.~25}.
\see{247}.

\cd*\relax
\artist{Chausson, Ernest}.
\cdtitle{String Quartet in C~minor, Op.~35}.
\see{616}.

\cd*\relax
\artist{Ch\'avez, Carlos}.
\cdtitle{Concerto para tromb\'on y orquesta}.
\see{962}.

\cd\relax
\artist{Cheallaigh, \'Aine U{\'\i}}.
\cdtitle{In Two Minds}.
Gael-Linn, 1992 \cdnum{CEFCD~158}.

\cd*\relax
\artist{Cheetham, John}.
\cdtitle{Sonata for Alto Saxophone and Piano \(2001\)}.
\see{1601}.

\cd\relax
\artist{Chen, Gang and Zhanhao He}.
\cdtitle{The Butterfly Lovers \and Street Musician \(arr. Huichang Yan\)
  \and \C{Xiaogu Zhu} Love in Spring \and \C{Xiaogu Zhu and Xiaofeng
  Zhang} Parting of the Newly Wedded}.
Takako Nishizaki (violin).
Shanghai Conservatory Symphony Orchestra.
Fan Chengwu, cond.
Naxos, 1998 \cdnum{8.554334}.

\cd\relax
\artist{Cherkassky, Shura}.
\cdtitle{Chopin \: \C{Fr\'ed\'eric Chopin} Etudes, Op.~10 \and Etudes,
  Op.~25 \and Trois nouvelles \'etudes \and Fantasy in F~minor, Op.~49
  \and Mazurka in~D, Op.~33 No.~2 \and Barcarolle in F~sharp, Op.~60
  \and Nocturne in F~minor, Op.~55 No.~1 \and Pr\'eludes, Op.~28 \and
  Piano Sonata No.~3 in B~minor, Op.~58}.
Volume~17 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 742-2}.

\cd\relax
\artist{Cherkassky, Shura}.
\cdtitle{Litolff/Tchaikovsky/Schumann/Strauss \: \track \C{Henry
  Litolff} Scherzo from Concerto Symphonique, Op.~102 \; \track
  \C{Robert Schumann} Symphonische Et\"uden, Op.~13 \and Kreisleriana,
  Op.~16 \; \track \C{Johann Strauss} Arabesques on ``An der sch\"onen,
  blauen Donau'' \and Wein, Weib und Gesang, Op.~333 \; \track \C{Peter
  Ilyich Tchaikovsky} Piano Concerto No.~1 in B~flat minor, Op.~23 \and
  Piano Concerto No.~2 in~G, Op.~44}.
Volume~18 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 745-2}.

\cd*\relax
\artist{Cherubini, Luigi}.
\cdtitle{\'Etude No.~2 for French Horn and strings}.
\see{1313}.

\cd\relax
\artist{Chicago}.
\cdtitle{The Very Best of: Only the Beginning}.
Rhino, 2002 \cdnum[2]{R2 76170}.

\cd\relax
\cdtitle{Chinese Bamboo Flute Music \: \track Capriccio for Chinese
  Flute \; \track The Flower of Hsin-Jang \; \track A Tayal Folk Song \;
  \track The Imperial Officer on Horseback Galloping By \; \track Go
  Dating with My Love \; \track The Maidens of the Tea Mountain \;
  \track Chatting with an Old Friend by the Window \; \track The Song of
  the Four Seasons \; \track The Crab and the Egret}.
Laserlight, 1993 \cdnum{12~183}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Andante spianato and Grande Polonaise brillante, Op.~22 \and
  Nocturne in C~minor, Op.~48, No.~1 \and Nocturne in F~sharp minor,
  Op.~48, No.~2 \and Polonaise in~A, Op.~40 No.~1 ``Military'' \and
  Waltz in C~sharm minor, Op.~64 No.~2 \and Nocturne in C~sharm minor,
  Op.~27 No.~1 \and Nocturne in D~flat, Op.~27 No.~2 \and Waltz in
  D~flat, Op.~64 No.~1 ``Minute'' \and Berceuse in D~flat, Op.~57 \and
  Impromptu No.~1 in A~flat, Op.~29 \and Impromptu No.~2 in F~sharp,
  Op.~36 \and Impromptu No.~3 in G~flat, Op.~51 \and Scherzo No.~3 in
  C~sharp minor, Op.~39 \and Ballade No.~3 in A~flat, Op.~47 \and Trois
  nouvelles \'etudes, Op.~posth. \and Fantaisie-Impromptu in C~sharp
  minor, Op.~66 \and Waltz in A~flat, Op.~34, No.~1 \and Waltz in
  A~flat, Op.~42 ``Two-Four Waltz'' \and Mazurkas, Op.~68 \and Piano
  Sonata No.~2 in B~flat minor, Op.~35 ``Funeral March'' \and Ballade
  No.~4 in F~minor, Op.~52 \and Polonaise No.~6 in A~flat ``Heroic''}.
\see{1318}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Ballade No.~1 in G~minor, Op.~23}.
\see{1196}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Ballade No.~1 in G~minor, Op.~23 \and Impromptu No.~1 in
  A~flat, Op.~29 \and Waltz in E~minor, Op.~posth.\ \and Waltz in
  A~minor, Op.~34 No.~2 \and Mazurka in A~minor, Op.~67 No.~4 \and Etude
  in~E, Op.~10 No.~3 ``Tristesse'' \and Etude in~F, Op.~25 No.~3 \and
  Etude in G~flat, Op.~10 No.~5 ``Black Keys'' \and Etude in~F, Op.~10
  No.~8 \and Piano Sonata No.~2 in B~flat minor, Op.~35 ``Funeral
  March'' \and Scherzo No.~3 in C~sharp minor, Op.~39}.
\see{844}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Ballade No.~2 in~F, Op.~38}.
\see{632}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Ballade No.~3 in A~flat, Op.~47 \and Ballade No.~4 in F~minor,
  Op.~52 \and Barcarolle in F~sharp, Op.~60 \and Fantaisie-Impromptu in
  C~sharp minor, Op.~66 \and Nocturne in~E, Op.~62 No.~2 \and Nocturne
  in~G, Op.~37 No.~2 \and Scherzo No.~2 in B~flat minor, Op.~31 \and
  Scherzo No.~4 in~E, Op.~54}.
\see{1076}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Ballade No.~3 in A~flat, Op.~47 \and Fantasy in F~minor,
  Op.~49}.
\see{882}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Ballade No.~3 in A~flat, Op.~47 \and Impromptu No.~2 in
  F~sharp, Op.~36 \and Polonaise No.~6 in A~flat, Op.~53 ``Heroic'' \and
  Polonaise No.~9 in B~flat, Op.~71, No.~2 \and Prelude in D~flat,
  Op.~28, No.~15 ``Raindrop'' \and Prelude in E~flat, Op.~28, No.~19
  \and Nocturne No.~16 in E~flat, Op.~55, No.~2 \and Mazurka in B~flat,
  Op.~7, No.~1 \and Mazurka in A~minor, Op.~7, No.~2 \and Mazurka in
  F~minor, Op.~7, No.~3 \and Mazurka in~D, Op.~33, No.~2 \and Mazurka in
  B~flat minor, Op.~24, No.~4 \and Mazurka in B~minor, Op.~33, No.~4
  \and Mazurka in C~sharp minor, Op.~41, No.~1 \and Mazurka in A~flat,
  Op.~50, No.~2 \and Mazurka in C~sharp minor, Op.~63, No.~3 \and
  Mazurka in~C, Op.~67, No.~3 \and Mazurka in A~minor, Op.~67, No.~4
  \and Mazurka in A~minor, Op.~68, No.~2 \and Berceuse in D~flat, Op.~57
  \and Waltz in A~minor, Op.~34, No.~2 \and Piano Sonata No.~2 in B~flat
  minor, Op.~35 \(Marche fun\`ebre and Finale\) \and Waltz in D~flat,
  Op.~64, No.~1 ``Minute'' \and Etude in G~sharp minor, Op.~25, No.~6
  \and Etude in G~flat, Op.~10, No.~5 ``Black Keys'' \and Etude in
  G~flat, Op.~25, No.~9 ``Butterfly'' \and Etude in~C, Op.~10, No.~7
  \and Etude in C~minor, Op.~10, No.~12 ``Revolutionary''}.
\see{625}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Ballade No.~3 in A~flat, Op.~47 \and Scherzo No.~3 in C~sharp
  minor, Op.~39 Waltz No.~7 in C~sharp minor, Op.~64 No.~2 Waltz No.~8
  in A~flat, Op.~64 No.~3 Piano Sonata No.~2 in B~flat minor, Op.~35
  ``Funeral March'' \and Chants polonais de Fr\'ed\'eric Chopin,
  S.~480}.
\see{1233}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Ballade No.~4 in F~minor, Op.~52 \and Fantaisie in F~minor,
  Op.~49}.
\see{1702}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Berceuse in D~flat, Op.~57}.
\see{637}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Berceuse in D~flat, Op.~57 \and Ballade No.~4 in F~minor,
  Op.~52 \and Fantaise in F~minor, Op.~49 \and Polonaise in A~flat,
  Op.~53 ``Heroic''}.
\see{1485}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Cello Sonata, Op.~65}.
\see{1315}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Etude in C~minor, Op.~10 No.~12 ``Revolutionary'' \and Etude
  in~E, Op.~10 No.~3 ``Tristesse'' \and Etude in G~flat, Op.~10 No.~5
  ``Black Keys'' \and Etude in~C, Op.~10 No.~7 \and Nocturne in~F,
  Op.~15 No.~1 \and Nocturne in F~sharp, Op.~15 No.~2 \and Nocturne in
  E~flat, Op.!9 No.~2 \and Waltz in E~flat, Op.~18 ``Grande valse
  brillante'' \and Mazurka in A~minor, Op.~17 No.~4 \and Etude in
  A~flat, Op.~25 No.~1 ``Aeolian Harp'' \and Etude in F~minor, Op.~25
  No.~2 \and Etude in G~sharp minor, Op.~24 No.~6 \and Etude in C~sharp
  minor, Op.~25 No.~7 \and Etude in G~flat, Op.~25 No.~9 ``Butterfly''
  \and Etude in A~minor, Op.~25 No.~11 ``Winter Wind'' \and Polonaise in
  E~flat minor, Op.~26 No.~2 \and Prelude in D~flat, Op.~28 No.~15
  ``Raindrop'' \and Prelude in A~flat, Op.~28 No.~17 \and Mazurka in~D,
  Op.~33 No.~2 \and Waltz in A~flat, Op.~34 No.~1 ``Valse brillante''
  \and Marche fun\`ebre from Piano Sonata No.~2 in B~flat minor, Op.~35
  \and Polonaise in~A, Op.~40 No.~1 ``Military'' \and Waltz in A~flat,
  Op.~42 ``Grande valse'' \and Berceuse in D~flat, Op.~57 \and Mazurka
  in A~flat, Op.~59 No.~2 \and Mazurka in F~sharp minor, Op.~59 No.~3
  \and Mazurka in C~sharp minor, Op.~63 No.~3 \and}.
\see{1187}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Etude in E~flat, Op.~10 No.~11 \and Etude in G~sharp minor,
  Op.~25 No.~6 \and Etude in B~minor, Op.~25 No.~10 \and Etude in
  A~minor, Op.~25 No.~11 \and Prelude in B~flat minor, Op.~28 No.~16
  \and Prelude in A~flat, Op.~28 No.~17 \and Polonaise in A~flat, Op.~53
  \and Piano Concert No.~1 in E~minor, Op.~11}.
\see{952}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Etude in F~minor, Op.~25 No.~2}.
\see{140}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Etude in~C, Op.~10 No.~1 \and Etude in C~sharp minor, Op.~25
  No.~7 \and Etude in C~minor, Op.~25 No.~12}.
\see{1684}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Etude in~E, Op.~10 No.~3 ``Tristesse''}.
\see{1270}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{\'Etude Op.~25, No.~7}.
\see{929}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Etudes, Op.~10 \and Etudes, Op.~25}.
\see{449}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{\'Etudes, Op.~10 \and \'Etudes, Op.~25 \and Polonaise No.~6 in
  A~flat, Op.~53 ``Heroic''}.
\see{472}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Etudes, Op.~10 \and Etudes, Op.~25 \and Trois nouvelles
  \'etudes \and Fantasy in F~minor, Op.~49 \and Mazurka in~D, Op.~33
  No.~2 \and Barcarolle in F~sharp, Op.~60 \and Nocturne in F~minor,
  Op.~55 No.~1 \and Pr\'eludes, Op.~28 \and Piano Sonata No.~3 in
  B~minor, Op.~58}.
\see{417}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Fantaisie in F~minor, Op.~49}.
\see{44}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Fantasy in F~minor, Op.~49 \and Polonais-Fantaisie in A~flat,
  Op.~61}.
\see{797}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Impromptu No.~1 in A~flat, Op.~29 \and Impromptu No.~2 in
  F~sharp, Op.~36 \and Impromptu No.~3 in G~flat, Op.~51 \and Impromptu
  No.~4 in C~sharp minor, Op.~66 \and Piano Sonata No.~2 in B~flat
  minor, Op.~35 \and Waltz in G~flat, Op.~70 No.~1 \and Waltz in E~flat,
  Op.~18 ``Grande Valse brillante'' \and Waltz in C~flat, Op.~70 No.~3
  \and Waltz in C~sharp minor, Op.~64 No.~2 \and Ballade No.~1 in
  G~minor, Op.~23 \and Ballade No.~2 in~F, Op.~38 \and Ballade No.~3 in
  A~flat, Op.~47 \and Ballade No.~4 in F~minor, Op.~52}.
\see{617}.

\cd\relax
\artist{Chopin, Frederic}.
\cdtitle{Konzert f\"ur Klavier und Orchester Nr.~1 e-moll op.~11 \and
  Konzert f\"ur Klavier und Orchester Nr.~2 f-moll op.~21}.
Krystian Zimerman.
Los Angeles Philharmonic Orchestra.
Carlo Maria Giulini, cond.
Deutsche Grammophon, 1979/1980 \cdnum{415 970-2}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Mazurka in G~minor, Op.~67 No.~2 \and Mazurka in~C, Op.~56
  No.~2 \and Mazurka in A~minor, Op.~67 No.~4 \and Mazurka in A~minor,
  Op.~68 No.~2 \and Mazurka in~C, Op.~68 No.~1 \and Mazurka in G~sharp
  minor, Op.~33 No.~1 \and Mazurka in D~flat, Op.~30 No.~3 \and Mazurka
  in B~minor, Op.~30 No.~2 \and Mazurka in B~minor, Op.~33 No.~4 \and
  Mazurka in F~minor, Op.~68 No.~4}.
\see{1066}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Nocturne in B~flat minor, Op.~9 No.~1 \and Nocturne in E~flat,
  Op.~9 No.~2 \and Nocturne in~B, Op.~9 No.~3 \and Bol\'ero in~C, Op.~19
  \and Piano Sonata No.~1 in C~minor, Op.~4 \and Tarantelle in A~flat,
  Op.~43 \and Mazurka in B~flat, Op.~17 No.~1 \and Mazurka in E~minor,
  Op.~17 No.~2 \and Mazurka in A~flat, Op.~17 No.~3 \and Mazurka in
  A~minor, Op.~17 No.~4 \and Rondo \`a la Mazur in~F, Op.~5 \and
  Variations brillantes, Op.~12 \and Allegro de concert in~A, Op.~46
  \and Ecossaise No.~1 in~D, Op.~72 No.~3 \and Ecossaise No.~2 in~G,
  Op.~72 No.~4 \and Ecossaise No.~3 in D~flat, Op.~72 No.~5}.
\see{1032}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Nocturne in C~minor, Op.~48, No.~1 \and Nocturne in F~sharp
  minor, Op.~48, No.~2 \and Nocturne in~E, Op.~62, No.~2}.
\see{1201}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Nocturne in~B, Op.~62 No.~1 \and Nocturne in~E, Op.~62 No.~2
  \and}.
\see{1683}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Nocturne No.~17 in~B, Op.~62, No.~1 \and Nocturne No.~18 in~E,
  Op.~62, No.~2 Impromptu No.~3 in G|flat, Op.~51}.
\see{930}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Nocturne No.~19 in E~minor, Op.~72, No.~1 \and Nocturne No.~1
  in B~flat minor, Op.~9, No.~1 \and Nocturne No.~2 in E~flat, Op.~9,
  No.~2 \and Nocturne No.~4 in~F, Op.~15, No.~1 \and Nocturne No.~5 in
  F~sharp, Op.~15, No.~2 \and Nocturne No.~7 in C~sharp minor, Op.~27,
  No.~1 \and Nocturne No.~8 in D~flat, Op.~27, No.~2 \and Nocturne No.~9
  in~B, Op.~32, No.~1 \and Nocturne No.~11 in G~minor, Op.~37, No.~1
  \and Nocturne No.~12 in~G, Op.~37, No.~2 \and Nocturne No.~14 in
  F~sharp minor, Op.~48, No.~2 \and Nocturne No.~15 in F~minor, Op.~55,
  No.~1 \and Etude in G~flat, Op.~10, No.~5 ``Black Keys'' \and Etude in
  G~flat, Op.~25, No.~9 ``Butterfly'' \and Scherzo No.~4 in~E, Op.~54
  \and Piano Sonata No.~2 in B~flat minor, Op.~35}.
\see{650}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Piano Concerto No.~1 in E~minor, Op.~11 \and Ballade No.~1 in
  G~minor, Op.~23 \and Ballade No.~2 in~F, Op.~38 \and Ballade No.~3 in
  A~flat, Op.~47 \and Ballade No.~4 in F~minor, Op.~52}.
\see{716}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Piano Concerto No.~2 in F~minor, Op.~21}.
\see{1319}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Piano Sonata in B~minor, Op.~58 \and Barcarolle in F~sharp,
  Op.~60 \and Nocturne in D~flat, Op.~27, No.~2}.
\see{967}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Piano Sonata No.~2 in B~flat minor, Op.~35 ``Funeral March''
  \and Piano Sonata No.~3 in B~minor, Op.~58 \and Etude in F~minor,
  Op.~25 No.~2}.
\see{643}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Piano Sonata No.~3 in B~minor, Op.~48}.
\see{877}.

\cd\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{\track Piano Sonata No.~3 in B~minor, op.~58 \; \track Grand
  Polonaise brillante in E~flat major with preceding Andante spianato in
  G~major, op.~22 \; \track Etude in A~minor, op.~10 no.~2 \; \track
  Etude in G~flat major, op.~10 no.~5 \; \track Etude in A~minor, op.~25
  no.~11 \; \track Nocturne in B~flat minor, op.~9 no.~1 \; \track
  Nocturne in E~flat major, op.~9 no.~2 \; \track Nocturne in F~sharp
  major, op.~15 no.~2 \; \track Impromptu No.~4 in C~sharp minor, op.
  posth.}
Yundi Li.
Deutsche Grammophon, 2001 \cdnum{471 479-2}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Polonaise in A~flat, Op.~61 ``Polonaise-Fantasie'' \and Mazurka
  in F~minor, Op.~63 No.~2 \and Mazurka in A~minor, Op.~68 No.~2 \and
  Mazurka in C~sharp minor, Op.~50 No.~3 \and Mazurka in C~sharp minor,
  Op.~63 No.~3 \and Mazurka in F~minor, Op.~68 No.~4 \and Mazurka in~C,
  Op.~56 No.~2 \and Mazurka in E~minor, Op.~41 No.~2 \and Scherzo No.~2
  in B~flat minor, Op.~31 \and Nocturne No.~17 in~B, Op.~62 No.~1 \and
  Nocturne No.~18 in~E, Op.~62, No.~2 \and Barcarolle in F~sharp, Op.~60
  \and Ballade No.~4 in F~minor, Op.~52}.
\see{1092}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Polonaise in C~sharp minor, Op.~26, No.~1 \and Waltz in A~flat,
  Op.~69, No.~1 ``Farewell'' \and Waltz in F~minor/A~flat, Op.~70, No.~2
  \and Waltz in D~flat, Op.~70, No.~3 \and Impromptu No.~3 in G~flat,
  Op.~51 \and Barcarolle in F~sharp, Op.~60 \and Nocturne in C~sharp
  minor, Op.~27, No.~1 \and Nocturne in D~flat, Op.~27, No.~2 \and
  Mazurka in C~sharp minor, Op.~41, No.~1 \and Mazurka in E~minor,
  Op.~41, No.~2 \and Mazurka in F~minor, Op.~63, No.~2 \and Mazurka
  in~C, Op.~33, No.~3 \and Mazurka in B~minor, Op.~33, No.~4 \and
  Mazurka in F~minor, Op.~68, No.~4 \and Mazurka in B~minor, Op.~30,
  No.~2 \and Mazurka in D~flat, Op.~30, No.~3 \and Mazurka in C~sharp
  minor, Op.~30, No.~4 \and Mazurka in C~sharp minor, Op.~50, No.~3}.
\see{1484}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Polonaise in F~sharp minor, Op.~44}.
\see{336}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Polonaise in~A, Op.~40 No.~1 ``Military'' \and Waltz in
  E~minor, Op.~posth. \and Waltz in A~flat, Op.~34 No.~1 ``Valse
  brillante'' \and Berceuse in D~flat, Op.~57 \and Polonaise No.~3 in~A
  Op.~40 No.~1 ``Military'' \and Waltz in C~sharp minor, Op.~64 No.~2
  \and Nocturne in F~sharp, Op.~15 No.~2 \and Scherzo in B~minor, Op.~20
  \(abridged\)}.
\see{775}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Prelude in C~sharp minor, Op.~45 \and Polonaise in A~flat,
  Op.~61 ``Polonaise-Fantaisie'' \and Mazurka in A~minor, Op.~59 No.~1
  \and Mazurka in A~flat, Op.~59 No.~2 \and Mazurka in F~sharp minor,
  Op.~59 No.~3 \and Scherzo No.~3 in C~sharp minor, Op.~39 \and
  Preludes, Op.~28 \and Scherzo No.~2 in B~flat minor, Op.~31 \and
  Polonaise in A~flat, Op.~53 ``Heroic'' \and Piano Sonata No.~3 in
  B~minor, Op.~58}.
\see{39}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Preludes, Op.~28}.
\see{448}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Preludes, Op.~28 \and Prelude in C~sharp minor, Op.~45 \and
  Prelude in A~flat, Op.~posth. \and Nocturnes, Op.~48}.
\see{45}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Romanza from Piano Concerto No~1 in E~minor, Op~11, transcribed
  by Mily Alexeyevich Balakirev}.
\see{725}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Rondo for Two Pianos in~C, Op.~73}.
\see{380}.

\cd\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Scherzi/Impromptus \: \track Scherzo No.~1 in B~minor, Op.~20
  \; \track Scherzo No.~2 in B~flat minor, Op.~31 \; \track Scherzo
  No.~3 in C~sharp minor, Op.~39 \; \track Scherzo No.~4 in E~major,
  Op.~54 \; \track Impromptu No.~1 in A~flat minor, Op.~29 \; \track
  Impromptu No.~2 in F~sharp major, Op.~36 \; \track Impromptu No.~3 in
  G~flat major, Op.~51}.
Yundi Li.
Deutsche Grammophon, 2004 \cdnum{B0003887-02}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Scherzo No.~ in B~minor, Op.~20}.
\see{1207}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Scherzo No.~1 in B~minor, Op.~20 \and Impromptu No.~2 in
  F~sharp, Op.~36 \and Mazurka in C~sharp minor, Op.~41 No.~1 \and
  Mazurka in B~flat minor, Op.~24 No.~4 \and Piano Sonata No.~3 in
  B~minor, Op.~58}.
\see{623}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Scherzo No.~4 in~E, Op.~54 \and Nocturne in~B, Op.~62 No.~1
  \and Mazurka in A~flat, Op.~59 No.~2 \and Trois nouvelles \'etudes,
  Op. posth. \and Barcarolle in F~sharp, Op.~60}.
\see{48}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Various}.
\see{796}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Waltz in E~flat, Op.~18 ``Grande Valse brillante''}.
\see{720}.

\cd*\relax
\artist{Chopin, Fr\'ed\'eric}.
\cdtitle{Waltzes}.
\see{25}.

\cd\relax
\artist{Chopin, Fr\'ed\'eric Fran\c{c}ois}.
\cdtitle{Sonatas No.~2 and~3 and Fantaisie in F~minor}.
Artur Rubinstein.
RCA, 1961/1985 \cdnum{5616-2-RC}.

\cd\relax
\artist{Chopin, Fr\'ed\'eric Fran\c{c}ois}.
\cdtitle{The Nocturnes}.
Artur Rubinstein.
RCA, 1967/1984 \cdnum[2]{5613-2-RC}.

\cd\relax
\artist{Chopin, Frederick}.
\cdtitle{51 Mazurkas}.
Andrzej Wasowski.
Concord Concerto, 1996 \cdnum[2]{CCD-42036}.

\cd\relax
\artist{Chopin, Frederick}.
\cdtitle{Impromptu, Op.~29 \and Impromptu, Op.~36 \and Impromptu, Op.~51
  \and Fantaisie-Impromptu, Op.~66 \and Barcarolle, Op.~60 \and
  Berceuse, Op.~57 \and Berceuse, Op.~57}.
Murray Perahia.
CBS, 1985 \cdnum{MK~39708}.

\cd\relax
\artist{Chopin, Frederick}.
\cdtitle{Mazurkas}.
Vladimir Ashkenazy.
The Decca Record Company, 1996 \cdnum[2]{448 086-2}.

\cd\relax
\artist{Chopin, Frederick}.
\cdtitle{Nocturnes and Ballades}.
Vladimir Ashkenazy.
The Decca Record Company, 1997 \cdnum[2]{452 579-2}.

\cd\relax
\artist{Chopin, Frederick}.
\cdtitle{Polonaises \(opp.~26, 40, 44, 53, 61, 71, and posth.\) \and
  Allegro de concert, op.~46 \and Trois Nouvelles \'Etudes \and
  Tarentelle in A~flat major, op.~43 \and Fugue in A~minor \and
  Albumblatt in E~major \and Wiosna \and 2 Bourr\'ees \and Galop marquis
  \and Berceuse in D~flat major, op.~57 \and Barcarolle in F~sharp
  major, op.~60}.
Vladimir Ashkenazy.
The Decca Record Company, 1996 \cdnum[2]{452 167-2}.

\cd\relax
\artist{Chopin, Frederick}.
\cdtitle{\track Sonata for Cello and Piano in G~Minor, Op.~65 \; \track
  Polonaise brillante in C~Major, Op.~3 \; \track Grand Duo Concertant
  in E~Major on Themes from ``Robert le Diable'' \; \track Nocturne in
  C~Sharp Minor, B.~I.~49 \; \track Etude in E~Minor, Op.~25, No.~7 \;
  \track Waltz in A~Minor, Op.~34, No.~2 \; \track Etude in D~Minor,
  Op.~10, No.~6}.
Maria Kliegel (cello) and Bernd Glemser (piano).
Naxos, 1996 \cdnum{8.553159}.

\cd\relax
\artist{Christ, Peter}.
\cdtitle{Rendezvous and Dreams \: \track \C{Vazgen Muradian} Concerto
  for Oboe and String Quartet, Opus~25 \; \track \C{Martin Scot Kosins}
  Rendezvous and Dreams: A Romance for Oboe and Piano \; \track \C{John
  Biggs} Dance Suite for Oboe, Violin, Viola and Cello \; \track
  \C{Gregory La Traille} Quintet for Oboe and String Quartet}.
Daniel Rouslin (violin), Debbie Dare (violin), Michael Grossman
  (violin), Joseph Gold (viola), Charles Noble (viola), Abigail
  Stoughton (viola), Bruce McIntosh (cello) and Lisa Bergman (piano).
Crystal Records, 2001 \cdnum{CD723}.

\cd\relax
\artist{Chung, Kyung Wha}.
\cdtitle{\track \C{Sergei Prokofiev} Violin Concerto No.~1 in D~major,
  op.~19 \and Violin Concerto No.~2 in G~minor, op.~63 \; \track \C{Igor
  Stravinsky} Violin Concerto in D~major}.
The London Symphony Orchestra.
Andr\'e Previn, cond.
The Decca Record Company, 1990 \cdnum{425 003-2}.

\cd*\relax
\artist{Cima, Giovanni Paolo}.
\cdtitle{Sonata per il Violino \and Sonata \from ``Concerti
  ecclesiastici''}.
\see{1308}.

\cd\relax
\artist{Clannad}.
\cdtitle{An D{\'\i}olaim}.
Music Collection International, 1998 \cdnum{50063}.

\cd*\relax
\artist{Clementi, Muzio}.
\cdtitle{Piano Sonata in~C, Op.~34 No.~1}.
\see{643}.

\cd\relax
\artist{Cliburn, Van}.
\cdtitle{Rachmaninoff/Tchaikovsky \: \track \C{Rachmaninoff, Sergei}
  Piano Concerto No.~3 in D~minor, Op.~30 \and Piano Sonata No.~2 in
  B~flat minor, Op.~36 \and Prelude in D, Op.~23 No.~4 \and Prelude in
  G~minor, Op.~23 No.~5 \and Prelude in E~flat, Op.~23 No.~6 \and
  Prelude in C~minor, Op.~23 No.~7 \and Etude-Tableau in E~flat minor,
  Op.~39 No.~5 \and Prelude in C~sharp minor, Op.~3 No.~2 \and Prelude
  in~G, Op.~32 No.~5 \and Prelude in G~sharp minor, Op.~32 No.~12 \;
  \track \C{Peter Ilyich Tchaikovsky} Piano Concerto No.~1 in B~flat
  inor, Op.~23 \and Juin: Barcarolle \(\from ``Les Saisons,'' Op.~37b\)
  \and Mars: Chant de l'alouette \(\from ``Les saisons,'' Op.~37b\)}.
Volume~19 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 748-2}.

\cd\relax
\artist{Cocker, Joe}.
\cdtitle{With a Little Help from My Friends}.
A\&M Records, 1969 \cdnum{CD~3106}.

\cd\relax
\artist{Cohen, Leonard}.
\cdtitle{Songs from a Room}.
Columbia Records, 1969 \cdnum{CK~9767}.

\cd\relax
\artist{Cohler, Jonathan}.
\cdtitle{Cohler on Clarinet \: \track \C{Johannes Brahms} Sonata in
  F~Minor, Op.~120, No.~1 \; \track \C{Carl Maria von Weber} Grand Duo
  Concertant, Op.~48 \; \track \C{Heinrich Joseph B\"armann} Quintet
  No.~3 in E-Flat Major, Op.~23 \; \track \C{Simon A. Sargon} Deep Ellum
  Nights: Three Sketches}.
Judith Gordon (piano).
Ongaku, 1993 \cdnum{024-101}.

\cd\relax
\artist{Cohler, Jonathan}.
\cdtitle{More Cohler on Clarinet \: \track \C{Johannes Brahms} Sonata in
  E-flat Major, Op.~120, No.~2 \; \track \C{Francis Poulenc} Sonata \;
  \track \C{Robert Schumann} Fantasy Pieces, Op.~73 \; \track \C{Darius
  Milhaud} Sonatina, Op.~100 \; \track \C{Igor Stravinsky} Three Pieces
  for Clarinet Solo}.
Randall Hodkinson (piano).
Ongaku, 1994 \cdnum{024-102}.

\cd\relax
\artist{Connick Jr., Harry}.
\cdtitle{Come by Me}.
Columbia, 1999 \cdnum{CK 69618}.

\cd*\relax
\artist{Constant, Marius}.
\cdtitle{Musique de Concert}.
\see{631}.

\cd*\relax
\artist{Constantin, Louis}.
\cdtitle{``Pavan'' from \emph{'t Uitnemend Kabinet}}.
\see{1184}.

\cd\relax
\artist{Cooder, Ry}, ed.
\cdtitle{Buena Vista Social Club}.
World Circuit/Nonesuch, 1999 \cdnum{79478-2}.

\cd*\relax
\artist{Cooke, Arnold}.
\cdtitle{Sonata in B~flat for clarinet and piano}.
\see{894}.

\cd\relax
\artist{Cooke, Sam}.
\cdtitle{Portrait of a Legend: 1951--1964}.
ABKCO Records, 2003 \cdnum{92642}.

\cd\relax
\artist{Copland, Aaron}.
\cdtitle{Appalachian Spring \and Rodeo \and Billy the Kid \and Fanfare
  for the Common Man}.
The New York Philharmonic.
Leonard Bernstein, cond.
Sony, 1997 \cdnum{SMK 63082}.

\cd*\relax
\artist{Copland, Aaron}.
\cdtitle{Quiet City for cor anglais, trumpet and strings}.
\see{152}.

\cd*\relax
\artist{Copland, Aaron}.
\cdtitle{Sonata}.
\see{604}.

\cd*\relax
\artist{Corea, Chick}.
\cdtitle{Children's Songs}.
\see{35}.

\cd*\relax
\artist{Corelli, Arcangelo}.
\cdtitle{Sonata for Violin and Cello, Op.~5 No.~9 in an ornamented
  version by Geminiani}.
\see{634}.

\cd\relax
\artist{Corelli, Arcangelo}.
\cdtitle{The Complete Concerti grossi, Op.~6}.
I~Musici.
Philips Classics, 1997 \cdnum[2]{456 326-2}.

\cd\relax
\artist{Corelli, Arcangelo}.
\cdtitle{Trio Sonatas}.
Simon Standage (violin), Micaela Comberti (violin), Anthony Pleeth
  (cello), Nigel North (archlute and theorbo) and Trevor Pinnock (organ
  and harpsichord).
Archiv Produktion, 1987 \cdnum{419 614-2}.

\cd\relax
\artist{Corelli, Arcangelo}.
\cdtitle{Violin Sonatas, Op.~5}.
Andrew Manze (violin) and Richard Egarr (harpsichord).
Harmonia Mundi, 2002 \cdnum[2]{HMU 907298.99}.

\cd\relax
\artist{Corigliano, John}.
\cdtitle{Phantasmagoria \: \track Fancy on a Bach Air \; \track Fantasia
  on an Ostinato \; \track \'Etude Fantasy \; \track Phantasmagoria}.
Emanuel Ax (piano), Yo-Yo Ma (cello) and James Tocco (piano).
Sony Classical, 2000 \cdnum{SK~60747}.

\cd*\relax
\artist{Corradini, Nicol\`o}.
\cdtitle{Sonata ``La Sfondrata'' \from ``Il primo libro de canzoni
  francese''}.
\see{1308}.

\cd\relax
\artist{Cortot, Alfred}.
\cdtitle{Chopin/Debussy/Franck/Ravel/Saint-Sa\"ens \: \track \C{Cesar
  Franck} Pr\'elude, choral et fugue \and Pr\'elude, aria et final \and
  Variations symphoniques \; \track \C{Camille Saint-Sa\"ens} Piano
  Concerto No.~4 in C~minor, Op.~44 \; \track \C{Fr\'ed\'eric Chopin}
  Preludes, Op.~28 \; \track \C{Maurice Ravel} Sonatine \; \track
  \C{Claude Debussy} Pr\'eludes, Book~I}.
Volume~21 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 754-2}.

\cd\relax
\artist{Cortot, Alfred}.
\cdtitle{Chopin/Liszt/Ravel/Schumann \: \track \C{Fr\'ed\'eric Chopin}
  Etudes, Op.~10 \and Etudes, Op.~25 \; \track \C{Franz Liszt} Hungarian
  Rhapsody No.~2 in C~sharp minor \and Hungarian Rhapsody No.~11 in
  A~minor \and ``Rigoletto'' Paraphrase \; \track \C{Maurice Ravel} Jeux
  d'eau \; \track \C{Robert Schumann} Symphonische Et\"uden, Op.~13 \and
  Carnaval, Op.~9 \and Kreisleriana, Op.~18}.
Volume~20 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 751-2}.

\cd\relax
\artist{Cougar, John}.
\cdtitle{American Fool}.
Riva Records, 1982 \cdnum{814 993-2}.

\cd*\relax
\artist{Couperin, Fran\c{c}ois}.
\cdtitle{Le\c{c}ons des t\'en\`ebres `Pour le Mercredy'---Premi\`ere
  Le\c{c}on}.
\see{69}.

\cd*\relax
\artist{Couperin, Fran\c{c}ois}.
\cdtitle{Trelzi\`e Concert \`a 2 instruments \`a l'unisson \(`Les
  To\^uts-r\'eunis', 1724\)}.
\see{500}.

\cd\relax
\artist{Cowboy Junkies}.
\cdtitle{Black Eyed Man}.
BMG Music, 1992 \cdnum{61049-2}.

\cd\relax
\artist{Cowboy Junkies}.
\cdtitle{Miles from Our Home}.
Geffen Records, 1998 \cdnum{GEFD-25201}.

\cd\relax
\artist{Cowboy Junkies}.
\cdtitle{One Soul Now}.
Latent Recordings, 2004 \cdnum{Zo\"e 01143 1036-2}.

\cd\relax
\artist{Cowboy Junkies}.
\cdtitle{Pale Sun, Crescent Moon}.
BMG Music, 1993 \cdnum{66344-2}.

\cd\relax
\artist{Cowboy Junkies}.
\cdtitle{The Caution Horses}.
BMG Music, 1999 \cdnum{2058-2-R}.

\cd\relax
\artist{Cowboy Junkies}.
\cdtitle{The Trinity Session}.
BMG Music, 1988 \cdnum{8568-2-R}.

\cd*\relax
\artist{Cowell, Henry}.
\cdtitle{Hymn and Fuguing tune No.~10 for oboe and strings}.
\see{152}.

\cd\relax
\artist{Cream}.
\cdtitle{Disraeli Gears}.
Polygram, 1967 \cdnum{31453 1811-2}.

\cd\relax
\artist{Credence Clearwater Revival}.
\cdtitle{Chronicle, Volume Two}.
Fantasy Records, 1986/1991 \cdnum{FCD-CCR3-2}.

\cd\relax
\artist{Credence Clearwater Revival}.
\cdtitle{Credence Gold}.
Fantasy Records, 1972/1991 \cdnum{FCD-9418-2}.

\cd\relax
\artist{Credence Clearwater Revival}.
\cdtitle{More Credence Gold}.
Fantasy Records, 1973/1991 \cdnum{FCD-9430-2}.

\cd\relax
\artist{Crespin, R\'egine}.
\cdtitle{\track \C{Hector Berlioz} Les Nuits d'\'et\'e \; \track
  \C{Maurice Ravel} Sh\'eh\'erazade \; \track \C{Claude Debussy} Trois
  Chansons de Bilitis \; \track \C{Francis Poulenc} Chanson d'Orkenise
  \and H\^otel \and Le Carafon \and ``C'' \and F\^etes galantes}.
John Wustman (piano).
L'Orchestre de la Suisse Romande.
Ernest Ansermet, cond.
The Decca Record Company, 1999 \cdnum{289 460 973-2}.

\cd*\relax
\artist{Creston, Paul}.
\cdtitle{A Rumor}.
\see{152}.

\cd*\relax
\artist{Creston, Paul}.
\cdtitle{Fantasy for Trombone and Orchestra, Op.~42}.
\see{961}.

\cd*\relax
\artist{Creston, Paul}.
\cdtitle{Sonata, op.~19}.
\see{298}.

\cd\relax
\artist{Crosby, Stills and Nash}.
\cdtitle{Crosby, Stills and Nash}.
Atlantic, 1969 \cdnum{82651-2}.

\cd\relax
\artist{Crosby, Stills and Nash}.
\cdtitle{CSN}.
Atlantic, 1977 \cdnum{82650-2}.

\cd\relax
\artist{Crosby, Stills and Nash}.
\cdtitle{Daylight Again}.
Atlantic, 1982 \cdnum{82672-2}.

\cd\relax
\artist{Crosby, Stills, Nash and Young}.
\cdtitle{D\'ej\`a Vu}.
Atlantic, 1970 \cdnum{82649-2}.

\cd*\relax
\artist{Crumb, George}.
\cdtitle{Sonata for Solo Violoncello \and Sonata for Two Cellos \and
  Nostalgia}.
\see{149}.

\cd*\relax
\artist{Crusell, Bernhard}.
\cdtitle{Concertino in B~flat for bassoon and orchestra}.
\see{1589}.

\cd\relax
\artist{Crusell, Bernhard Henrik}.
\cdtitle{Clarinet Quartets \: \track Clarinet Quartet No~1 in E~flat
  major Op~2 \; \track Clarinet Quartet No~2 in C~minor Op~4 \; \track
  Clarinet Quartet No~3 in D~major Op.~7}.
Thea King (clarinet), Peter Carter (violin), Prudence Pacey (viola) and
  Bruno Schrecker (cello).
Helios, 1999 \cdnum{CDH55031}.

\cd\relax
\artist{Cui Jian}.
\cdtitle{Rock in the Road}.
1999 (7-88481-650-4).
China Version.

\cd\relax
\artist{Cui Jian}.
\cdtitle{The Power of the Powerless}.
1998 (7-88498-290-0).
China Version.

\cd\relax
\artist{Cui Jian}.
\cdtitle{Tsui Chien 1986-1996}.
 (7-88045-036-X)China Version.

\cd\relax
\artist{Cui Jian}.
\cdtitle{Yi Wu Suo You}.
 (7-88491-314-3)China Version.

\cd*\relax
\artist{Cummings, Barton}.
\cdtitle{Concertino for Contrabassoon \and Arioso}.
\see{1161}.

\cd*\relax
\artist{Curtis, Michael}.
\cdtitle{The Impish Imp}.
\see{1164}.

\cd\relax
\artist{Curzon, Clifford}.
\cdtitle{Mozart/Schubert \: \track \C{Franz Schubert} Impromptus, D.~935
  \and Fantasie in~C, D.~760 ``Wanderer-Fantasie'' \and Impromptus,
  D.~899 \; \track \C{Wolfgang Amadeus Mozart} Piano Concerto No.~26
  in~D, KV~537 ``Coronation'' \and Piano Concerto No.~27 in B~flat,
  KV~595}.
Volume~22 of \emph{Great Pianists of the 20th Century}.
London Symphony Orchestra.
Istv\'an Kert\'esz, cond.
Philips Classics, 1998 \cdnum[2]{456 757-2}.

\cd*\relax
\artist{Czerny, Carl}.
\cdtitle{Variations on ``La Ricordanza''}.
\see{1683}.

\cd\relax
\artist{Cziffra, Gy\"orgy}.
\cdtitle{Chopin/Liszt \: \track \C{Fr\'ed\'eric Chopin} \'Etudes, Op.~10
  \and \'Etudes, Op.~25 \and Polonaise No.~6 in A~flat, Op.~53
  ``Heroic'' \; \track \C{Franz Liszt} Polonaise No.~2 in~E \and Sonetto
  123 del Petrarca \and Fantasy and Fugue on the Name B-A-C-H \and Etude
  de concert No.~3 in D~flat ``Un sospiro'' \and Tarantella \(Supplement
  to ``Ann\'ees de p\`elerinage'', Deuxi\`eme ann\'ee: Italie\)\and
  Etude de concert No.~2 in F~minor ``La leggierezza'' \and L\'egende
  No.~2 ``St. Fran\c{c}ois de Paule marchant sur les flots'' \and
  Chasse-neige \(Etude d'ex\'ecution transcedante No.~12\) \and
  Tarantella di bravura \and Mephisto Waltz No.~1}.
Volume~23 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 760-2}.

\cd*\relax
\artist{Dahn, Luke}.
\cdtitle{Prolepsis \emph{for alto sax}}.
\see{1429}.

\cd*\relax
\artist{Danielpour, Richard}.
\cdtitle{Concerto for Cello and Orchestra \(1994\)}.
\see{1012}.

\cd*\relax
\artist{Dankner, Stephen}.
\cdtitle{Sonata for Alto Saxophone and Piano}.
\see{719}.

\cd\relax
\artist{Danzi, Franz}.
\cdtitle{Basson Concertos \: \track Concerto in G~minor \; \track
  Concerto No.~1 in F~major \; \track Concerto in C~major \; \track
  Concerto No.~2 in f~major}.
Albrecht Holder (bassoon).
Neubrandenburger Philharmonie.
Nicol\'as Pasquet, cond.
Naxos, 1999 \cdnum{8.554273}.

\cd\relax
\artist{Danzi, Franz}.
\cdtitle{Wind Quintets Op.~56, Nos.~1--3 \and Sextet in E~Flat Major}.
Michael Thompson Wind Quintet.
Naxos, 1995 \cdnum{8.553076}.

\cd\relax
\artist{Danzi, Franz}.
\cdtitle{Wind Quintets Op.~67, Nos.~1--3 \and Sonata for Horn and
  Piano}.
Michael Thompson Wind Quintet and Philip Fowke (piano).
Naxos, 1999 \cdnum{8.553570}.

\cd*\relax
\artist{David, Ferdinand}.
\cdtitle{Concertino in B~flat, Op.~12 for bassoon and orchestra}.
\see{1589}.

\cd\relax
\artist{Davis, Miles}.
\cdtitle{Kind of Blue}.
Columbia, 1997 \cdnum{CK~64935}.

\cd\relax
\artist{De Larroacha, Alicia}.
\cdtitle{Alb\'eniz/Granados/Halffter/Mompou/Soler \: \track \C{Isaac
  Alb\'eniz} Iberia \and Navarra \; \track \C{Mateo Alb\'eniz} Piano
  Sonata in~D \; \track \C{Enrique Granados} Spanish Dance, Op.~37 No.~5
  ``Andaluza'' \and Goyescus \; \track \C{Ernesto Halffter} ``Sonatina''
  \(Ballet\) \; \track \C{Federico Mompou} Can\c{c}ons i dansas
  \(Excerpts\) \; \track \C{Antonio Soler} Piano Sonata in C~sharp minor
  \and Piano Sonata in~F \and Piano Sonata in~D}.
Volume~62 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 883-2}.

\cd\relax
\artist{De Larroacha, Alicia}.
\cdtitle{Bach/Handel/Haydn/Mozart/Scarlatti \: \track \C{Johann
  Sebastian Bach} Italian Concerto in~F, BWV~971 \and Liebster Jesu, wir
  sind hier, BWV~731 \and Ert\"ot uns durch dein G\"ute \and French
  Suite No.~6 in~E, BWV~817 \; \track \C{Domenico Scarlatti} Sonata in
  D~minor, K.~9 ``Pastorale'' \and Sonata in~F, K.~6 \and Sonata in~G,
  K.~13 \and Sonata in C~minor, K.~11 \and Sonata in~E, K.~28 \; \track
  \C{George Frideric Handel} Suite No.~5 in~E, HWV 430 ``The Harmonious
  Blacksmith'' \; \track \C{Joseph Haydn} Andante con variazioni in
  F~minor, Hob.~XVII:6 \; \track \C{Wolfgang Amadeus Mozart} Rondo in~D,
  KV~485 \and Piano Sonata in~C, KV~330 \and Piano Sonata in~A, KV~331
  ``Alla Turca'' \and Piano Sonata in~D, KV~576}.
Volume~63 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 886-2}.

\cd*\relax
\artist{Debussy}.
\cdtitle{Images, Book~2}.
\see{45}.

\cd\relax
\artist{Debussy, Claude}.
\cdtitle{12 Etudes}.
Mitsuko Uchida.
Philips, 1990 \cdnum{422 412-2}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Children's Corner}.
\see{1684}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Clair de lune \(\from ``Suite bergamasque''\) \and L'isle
  joyeuse \and Pour le piano. Suite}.
\see{617}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Clair de lune \from Suite Bergamasque \and Nocturne et
  scherzo}.
\see{1315}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Deux Arabesques \and D'un cahier d'esquisses \and Suite
  bergamasque \and L'isle joyeuse \and Estampes \and Fantasy for Piano
  and Orchestra}.
\see{911}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Douz Etudes pour le piano \(Excerpts\)}.
\see{1207}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Douz Etudes pour piano}.
\see{1610}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{En blanc et noir \(for 2 pianos\)}.
\see{407}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Estampes}.
\see{1683}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{F\^etes \(for two pianos\)}.
\see{952}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{F\^etes galantes}.
\see{302}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Images \(Book~1\)}.
\see{642}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Images \(Book~1\) \and Images \(Book~2\) \and Pour le piano.
  Suite}.
\see{1092}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Images, Book~1 \and Images, Book~2 \and Pr\'eludes, Book~1
  \(Excerpts\) \and Pr\'eludes, Book~2 \(Excerpts\)}.
\see{1067}.

\cd\relax
\artist{Debussy, Claude}.
\cdtitle{Orchestral Music \: \track Berceuse h\'ero{\"\i}que \; \track
  Images \; \track Jeux \; \track Marche \'ecossaise \; \track Pr\'elude
  \`a l'Apr\`es-midi d'un faune \; \track Nocturnes \; \track La Mer \;
  \track Rhapsodie pour orchestre et clarinette principale \; \track
  Danses pour harpe et orchestre \`a cordes}.
Bernard Haitink and Eduard van Beinum.
The Royal Concertgebouw Orchestra.
Philips, 1993 \cdnum[2]{438 742-2}.

\cd\relax
\artist{Debussy, Claude}.
\cdtitle{Pr\'eludes}.
Krystian Zimerman.
Deutsche Grammophon, 1994 \cdnum{435 773-2}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Pr\'eludes, Book~1, Nos.~1, 5, 10--12 \and Pr\'eludes, Book~2,
  Nos.~5 and~9}.
\see{1702}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Pr\'eludes, Book~I}.
\see{448}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Pr\'eludes, Book~I \and Pr\'eludes, Book~II \and Estampes}.
\see{638}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Pr\'eludes, Book~I \and Pr\'eludes, Book~II \and L'isle joyeuse
  \and Reflets dans l'eau \(\from ``Images,'' Book~I\) \and Soiree dans
  Grenade \(\from ``Estampes''\) \and Suite bergamasque \and Pour le
  piano, Suite}.
\see{717}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Rapsodie for alto saxophone and orchestra}.
\see{744}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Sonata for cello and piano}.
\see{1316}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{String Quartet in G~minor op.~10}.
\see{576}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{The Girl with the Flaxen Hair}.
\see{902}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Trois Chansons de Bilitis}.
\see{461}.

\cd*\relax
\artist{Debussy, Claude}.
\cdtitle{Violin Sonata}.
\see{244}.

\cd*\relax
\artist{Dedenon, Sylvain}.
\cdtitle{Suite after themes of \emph{Porgy and Bess} for saxophone
  quartet}.
\see{19}.

\cd\relax
\artist{Deep Purple}.
\cdtitle{Smoke on the Water and Other Hits}.
Warner Brothers, 2001 \cdnum{R2 76755}.

\cd*\relax
\artist{Defaye, Jean-Michele}.
\cdtitle{Six Pi\`eces D'Audition}.
\see{1598}.

\cd\relax
\artist{Delangle, Claude}.
\cdtitle{The Japanese Saxophone \: \track \C{Masakazu Natsuda} West, or
  Evening Song in Autumn \; \track \C{Ichiro Noda{\"\i}ra} Arabesque~III
  \; \track \C{Fuminori Tanada} Mysterious Morning~III \; \track
  \C{Hoshio Hosokawa} Vertical Time Study~II \; \track \C{T\=oru
  Takemitsu} Distance \; \track \C{Yoshihisa Ta{\"\i}ra} P\'enombres~VI
  \; \track \C{Joji Yuasa} Not I, but the Wind\dots \; \track \C{Karen
  Tanaka} Night Bird}.
BIS, 1998 \cdnum{BIS-CD-890}.

\cd\relax
\artist{Delangle, Claude}.
\cdtitle{The Russian Saxophone \: \track \C{Edison Denisov} Sonata for
  Alto Saxophone and Piano \(1970\) \; \track \C{Alexander Raskatov} Pas
  de deux \(1994\) \; \track \C{Sofia Gubaidulina} Duo-Sonata for two
  baritone saxophones \(1977\) \; \track \C{Vadim Karasikov} Casus in
  terminus \(1995\) \; \track \C{Edison Denisov} Sonata for Alto
  Saxophone and Cello \(1994\) \; \track \C{Alexander Vustin} Musique
  pour l'ange \(1995\)}.
BIS, 1996 \cdnum{BIS-CD-765}.

\cd\relax
\artist{Delibes, L\'eo}.
\cdtitle{\track Copp\'elia \; \track La Source}.
Slovak Radio Symphony Orchestra \(Bratislava\).
Andrew Mogrelia, cond.
Naxos, 1995 \cdnum[2]{8.553356-7}.

\cd\relax
\artist{Delmoni, Arturo and Nathaniel Rosen}.
\cdtitle{Music for a Glass Bead Game \: \track \C{Johann Sebastian Bach}
  Two-Part Inventions~1, 3, 6, 7, 9, 10, and~13 \; \track \C{Zolt\'an
  Kod\'aly} Duo for Violin and Violoncello \; \track \C{Tommaso
  Giordani} Duetto~II \; \track \C{Bohuslav Martin\r{u}} Duo for Violin
  and Violoncello \; \track \C{George Frideric Handel} Passacaglia}.
John Marks Records, 1997 \cdnum{JMR~15}.

\cd*\relax
\artist{Demersseman, Jules}.
\cdtitle{Serenade, Op.~33}.
\see{1334}.

\cd*\relax
\artist{Denissov, Edison}.
\cdtitle{Deux pi\`eces pour Saxophone alto and Piano}.
\see{253}.

\cd*\relax
\artist{Denisov, Edison}.
\cdtitle{Sonata \(1970\)}.
\see{298}.

\cd*\relax
\artist{Denisov, Edison}.
\cdtitle{Sonata for Alto Saxophone and Piano \(1970\) \and Sonata for
  Alto Saxophone and Cello \(1994\)}.
\see{484}.

\cd*\relax
\artist{Desenclos, Alfred}.
\cdtitle{Pr\'elude, cadence et finale \(1956\)}.
\see{298}.

\cd*\relax
\artist{Desenglos, Alfred}.
\cdtitle{Quatuor \(1962\)}.
\see{1147}.

\cd*\relax
\artist{Dessau, Paul}.
\cdtitle{Suite f\"ur Altsaxophon und Klavier}.
\see{252}.

\cd*\relax
\artist{Dillon, Fannie Charles}.
\cdtitle{Birds at Dawn, Op.~20 No.~2}.
\see{775}.

\cd*\relax
\artist{D'Indy, Vincent}.
\cdtitle{Symphonie sur un chant montagnard fran\c{c}ais, Op.~25}.
\see{503}.

\cd\relax
\artist{Dire Straits}.
\cdtitle{Brothers in Arms}.
Warner Brothers, 1985 \cdnum{9 25264-2}.

\cd\relax
\artist{Dire Straits}.
\cdtitle{Dire Straits}.
Warner Brothers, 1978 \cdnum{3266-2}.

\cd\relax
\artist{Dire Straits}.
\cdtitle{Love Over Gold}.
Warner Brothers, 1982 \cdnum{9 23728-2}.

\cd\relax
\artist{Dire Straits}.
\cdtitle{Making Movies}.
Warner Brothers, 1980 \cdnum{3480-2}.

\cd\relax
\artist{Dittersdorf, Carl Ditters von}.
\cdtitle{Sinfonias \: \track Sinfonia in A~minor, `Il delirio delli
  compositori, ossia Il gusto d'oggid{\` \i}' \(Grave~a2\) \; \track
  Sinfonia in D~major, `Il Combattimento delle passioni umani'
  \(Grave~D16\) \; \track Sinfonia in A~major, `Sinfonia nazionale nel
  gusto di cinque nazioni' \(Grave~A10\)}.
Failoni Orchestra.
Uwe Grodd, cond.
Naxos, 1998 \cdnum{8.553975}.

\cd\relax
\artist{Dohn\'anyi, Ernst von}.
\cdtitle{Sonata for Cello and Piano in B~flat major, Op.~8 \:
  \C{L\'aszl\'o Lajtha} Sonata for Cello and Piano, Op.~17 \and Concerto
  for Cello and Piano, Op.~31}.
P\'eter Szab\'o (cello) and D\'enes V\'arjon (piano).
Hungaroton, 1993 \cdnum{HCD~31552}.

\cd*\relax
\artist{Dohn\'anyi, Ernst von}.
\cdtitle{Variations on a Nursery Song, Op.~25}.
\see{911}.

\cd*\relax
\artist{Dohn\'anyi, Ernst von}.
\cdtitle{Variations on a Nursery Tune, Op.~25}.
\see{883}.

\cd\relax
\artist{Donizetti, Gaetano}.
\cdtitle{Lucia di Lammermoor}.
Orchestra e coro dell'Accademia di Santa Cecilia, Roma.
Sir John Pritchard, cond.
The Decca Record Company, 1961/1989 \cdnum[2]{411 622-2}.

\cd\relax
\artist{Donizetti, Gaetano}.
\cdtitle{Lucia di Lammermoor}.
Vicente Sardinero, Montserat Caball\'e, Jos\'e Carreras, Claes H.
  Ahnsj\"o, Samuel Ramey, Ann Murray, Vincenzo Bello and Ambrosian Opera
  Chorus.
New Philharmonia Orchestra.
Jes\'us L\'opez-Cobos, cond.
The Decca Record Company, 1977/2002 \cdnum[2]{289 470 421-2}.

\cd*\relax
\artist{Donizetti, Gaetano}.
\cdtitle{String Quartet in~D \(arranged for String Orchestra\)}.
\see{1313}.

\cd*\relax
\artist{Doran, Matt}.
\cdtitle{Four Movements}.
\see{1163}.

\cd*\relax
\artist{Dorff, Daniel}.
\cdtitle{Sonatina d'Amore}.
\see{1164}.

\cd*\relax
\artist{D{\o}rge, Pierre}.
\cdtitle{The Big Bird}.
\see{960}.

\cd\relax
\artist{Dowland, John}.
\cdtitle{Complete Lute Works, Volume~1}.
Paul O'Dette.
Harmonia Mundi, 1995 \cdnum{HMU~907160}.

\cd\relax
\artist{Dowland, John}.
\cdtitle{Complete Lute Works, Volume~2}.
Paul O'Dette.
Harmonia Mundi, 1996 \cdnum{HMU~907161}.

\cd\relax
\artist{Dowland, John}.
\cdtitle{Complete Lute Works, Volume~3}.
Paul O'Dette.
Harmonia Mundi, 1996 \cdnum{HMU~907162}.

\cd\relax
\artist{Dowland, John}.
\cdtitle{Complete Lute Works, Volume~4}.
Paul O'Dette.
Harmonia Mundi, 1996 \cdnum{HMU~907163}.

\cd\relax
\artist{Dowland, John}.
\cdtitle{Complete Lute Works, Volume~5}.
Paul O'Dette.
Harmonia Mundi, 1997 \cdnum{HMU~907164}.

\cd*\relax
\artist{Draganski, Donald}.
\cdtitle{Heart's Desire}.
\see{1163}.

\cd*\relax
\artist{Dragonetti, Domenico}.
\cdtitle{Konzert A-dur f\"ur Kontraba{\ss} und Orchester}.
\see{880}.

\cd*\relax
\artist{Dramm, David}.
\cdtitle{Come True \and Master Bob Blaster}.
\see{50}.

\cd\relax
\artist{du Pr\'e, Jacqueline}.
\cdtitle{The Early BBC Recordings, 1961--1965 \: \track \C{Johann
  Sebastian Bach} Cello Suite No.~1 in~G, BWV1007 \and Cello Suite No.~2
  in D~minor, BWV1008 \; \track \C{Benjamin Britten} Cello Sonata in~C,
  Op.~65 \(Scherzo and Marcia\) \; \track \C{Manuel de Falla} Suite
  populaire espagnole \; \track \C{Johannes Brahms} Cello Sonata No.~2
  in~F, Op.~99 \; \track \C{Fran\c{c}ois Couperin} Trelzi\`e Concert \`a
  2 instruments \`a l'unisson \(`Les To\^uts-r\'eunis', 1724\) \; \track
  \C{George Friderick Handel} Sonata in G~minor}.
Ernest Lush (piano) and William Pleeth (cello).
EMI Classics \cdnum[2]{7243 5~73377~2 4}.

\cd\relax
\artist{Dubliners, The}.
\cdtitle{Ireland's Finest}.
Sanctuary Records, 2002 \cdnum{06076 81215-2}.

\cd\relax
\artist{Dubliners, The}.
\cdtitle{Irish Pub Songs}.
ARC Music, 2001 \cdnum[2]{EUCD 1642}.

\cd*\relax
\artist{Dubois, Pierre Max}.
\cdtitle{Dix Figures \`a danser}.
\see{253}.

\cd\relax
\artist{Dukas, Paul}.
\cdtitle{\track Fanfare to ``La P\'eri'' \; \track La P\'eri \; \track
  L'apprenti sorcier \; \track Polyeucte \; \track \C{Vincent D'Indy}
  Symphonie sur un chant montagnard fran\c{c}ais, Op.~25}.
Marie-Fran\c{c}oise Bucquet (piano).
Rotterdam Philharmonic Orchestra and Orchestre National de l'Op\'era de
  Monte-Carlo.
David Zinman and Paul Capolongo, cond.
Philips Classics, 1996 \cdnum{454 127-2}.

\cd*\relax
\artist{Dunhill, Thomas}.
\cdtitle{Lyric Suite}.
\see{881}.

\cd\relax
\artist{Duo Alea}.
\cdtitle{Chaconne: Recital for Bass Clarinet and Piano \: \track \C{Paul
  Hindemith} Sonata \; \track \C{Carl Nielsen} Canto Serioso \; \track
  \C{Conrad Baden} Sonata, Op.~116 \; \track \C{Johann Sebastian Bach}
  Chaconne \; \track \C{Sergei Rachmaninov} Vocalise, Op. 34, no.~14 \;
  \track \C{Wolfgang Gabriel} Ballade, Op.~23 \; \track \C{Franz
  Schubert} L'Abeille \(``The Bee''\), Op. 13, no.~9}.
Michael Davenport (bass clarinet) and Kimberly Davenport (piano).
Alea Recording, 2002.

\cd\relax
\artist{Duo Nuova}.
\cdtitle{Visions \: \track \C{Maurice Ravel} Pi\`ece en forme de
  Habanera \; \track \C{Rodney Rogers} Lessons of the Sky \; \track
  \C{William Bolcom} Lilith \; \track \C{Sergei Prokofiev} Visions
  Fugitives, Op.~22 \; \track \C{John Anthony Lennon} Distances Within
  Me \; \track \C{Giovanni Platti} Sonata in G~major}.
Timothy McAllister (saxophone) and Kevin Class (piano).
Centaur Records, 1995 \cdnum{CRC~2280}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Complete Piano Trios including Trio ``Dumky''}.
Philips Classics, 1996 \cdnum[2]{454 259-2}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{\track Concerto for Cello and Orchestra in B~minor, Op.~104 \;
  \track Klid/Silent Woods, Op.~68, No.~5 \; \track Rondo for Cello and
  Orchestra in G~minor, Op.~94}.
Yo-Yo Ma.
Berliner Philharmoniker.
Lorin Maazel, cond.
CBS Records, 1986 \cdnum{MK~42206}.

\cd*\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Concerto for Cello and Orchestra, op.~104}.
\see{1003}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{\track Concerto pour violin et orchestre op.~53 \; \track Trio
  pour piano, violon et violoncello, op.~65}.
Isabelle Faust (violin), Jean-Guihen Queyras (violoncelle) and Alexander
  Melnikov (piano).
The Prague Philharmonia.
Ji\v{r}{\'\i} B\v{e}lohl\'avek, cond.
Harmonia Mundi, 2004 \cdnum{HMC 901833}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Die Streichquartette}.
The Prager Streichquartett.
Deutsche Grammophon, 1997 \cdnum[9]{429 193-2}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Dvo\v{r}\'ak in Prague}.
Rudolf Firku\v{s}n\'y (piano), Yo-Yo Ma (cello), Itzhak Perlman
  (violin), Frederica von Stade (mezzo-soprano) and Prague Philharmonic
  Chorus.
Boston Symphony Orchestra.
Seiji Ozawa, cond.
Sony Classical, 1993 \cdnum{SK~46687}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{\track Konzert f\"ur Violoncello und Orchester h-moll op.~104
  \; \track \C{Peter Ilyich Tchaikovsky} Variationen \"uber ein
  Rokoko-Thema f\"ur Violoncello und Orchester, op.~33}.
Mstislav Rostropovich.
The Berliner Philharmoniker.
Herbert von Karajan, cond.
PolyGram, 1969 \cdnum{447 413-2}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Piano Quartet in D~major op.~23 \and Piano Quartet in E~flat
  major op.~87}.
Domus.
Hyperion Records, 1988 \cdnum{CDA66287}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{\track Quartet in E-flat Major for Piano and Strings, Op.~87 \;
  \track Romantic Pieces for Violin and Piano \; \track Sonatina in
  G~Major for Violin and Piano, Op.~100}.
Emanuel Ax (piano), Isaac Stern (violin), Jaime Laredo (viola), Yo-Yo Ma
  (cello) and Robert McDonald (piano).
Sony Classical \cdnum{SK~62597}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Rusalka}.
Gabriela Be\v{n}a\v{c}kov\'a-\v{C}\'apov\'a, Wies{\l}aw Ochman,
  Drahomira Drobkov\'a and Richard Nov\'ak.
Czech Philharmonic Orchestra.
V\'aclav Neumann, cond.
Supraphon, 1984 \cdnum[3]{SU 10~3641}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Serenade for Wind \: \track \C{George Enescu} Dixtuour, Op.~14
  \; \track \C{Leo\v{s} Jan\'a\v{c}ek} Ml\'ad{\'\i}}.
Oslo Philharmonic Wind Solists.
Naxos, 2000 \cdnum{8.554173}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Serenade in E, op.~22 \and Serenade in D~minor, op.~44}.
Academy of St~Martin-in-the-Fields.
Sir Neville Marriner, cond.
Philips Classics, 1981 \cdnum{400 020-2}.

\cd*\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Silent Woods, B173}.
\see{1315}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Slavonic Dances opp.~46 and~72}.
Russian National Orchestra.
Mikhail Pletnev, cond.
Deutsche Grammophon, 1995 \cdnum{447 056-2}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Stabat Mater}.
Eva Urbanov\'a (soprano), Marta Be\v{n}a\v{c}kov\'a (contralto), John
  Uhlenhopp (tenor) and Peter Mikul\'a\v{s} (bass).
Prague Symphony Orchestra, Prague Philharmonic Choir and Bambini di
  Praga.
Ji\v{r}{\'\i} B\v{e}lohl\'avek, cond.
Supraphon, 1997 \cdnum{SU 3311-2 231}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{\track String Quartet No.~9 in D~Minor, Op.~34 \; \track
  Terzetto in C~Major, Op.~74}.
Vlach Quartet Prague.
Naxos, 1996 \cdnum{8.553373}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{String Quartets \: \track String Quartet No.~11 in C~Major,
  Op.~61 \; \track String Quartet No.~8 in E~Major, Op.~80}.
Vlach Quartet Prague.
Naxos, 1996 \cdnum{8.553372}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{String Quartets \: \track String Quartet No.~12 ``American'' in
  F~major, Op.~96 \; \track String Quartet No.~13 in G~major, Op.~106}.
Vlach Quartet Prague.
Naxos, 1995 \cdnum{8.553371}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{String Quartets, Volume~4 \: \track String Quartet No.~10 in
  E~Flat Major, Op.~51 \; \track String Quartet No.~14 in A~Flat Major,
  Op.~105}.
Vlach Quartet Prague.
Naxos, 1996 \cdnum{8.553374}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{String Quartets, Volume~5 \: \track Cypresses, B.~152 \; \track
  String Quartet Movement in F~Major, B.~120 \; \track Two Waltzes,
  Op.~54 \; \track Gavotte, B.~164}.
Vlach Quartet Prague.
Naxos, 1998 \cdnum{8.553375}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{String Quartets, Volume~6 \: \track String Quartet No.~5 in
  F~minor, Op.~9 \; \track String Quartet No.~7 in A~minor, Op.~16}.
Vlach Quartet Prague.
Naxos, 1999 \cdnum{8.553377}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Symphonic Poems \: \track Vodn{\'\i}k/The Water Goblin, Op.~107
  \; \track Polednice/The Noon Witch, Op.~108 \; \track Zlat\'y
  kolovrat/The Golden Spinning Wheel, Op.~109 \; \track Holoubek/The
  Wild Dove, Op.~110}.
Czech Philharmonic Orchestra.
V\'aclav Neumann, cond.
Supraphon, 1978 \cdnum{SU~0199-2 011}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{\track Symphony No.~7 in D~minor, op.~70 \; \track Symphony
  No.~8 in G~major, op.~88 \; \track Symphony No.~9 in E~minor, op.~95
  ``The New World'' \; \track The Wood Dove, op.~110 \; \track
  \C{Bedrich Smetana} II.~The Moldau}.
Berlin Philharmonic Orchestra and Bavarian Radio Symphony Orchestra.
Rafael Kubelik, cond.
Deutsche Gramaphon, 1993 \cdnum[2]{439 663-2}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Symphony No.~9 in E~minor, Op.~95 ``From the New World''}.
The Philadelphia Orchestra.
Wolfgang Swallisch, cond.
EMI Records, 1988 \cdnum{CDC 7~49114~2}.

\cd\relax
\artist{Dvo\v{r}\'ak, Anton{\'\i}n}.
\cdtitle{Symphony No.~9 in E~minor, Op.~95 ``From the New World'' \and
  ``Othello'' overture, op.~93 \and ``Karneval'' overture, op.~92}.
The London Symphony Orchestra.
Istv\'an Kert\'esz, cond.
The Decca Record Company, 1995 \cdnum{448 583-2}.

\cd\relax
\artist{Dylan, Bob}.
Volume~1--3 of \emph{The Bootleg Series}.
Columbia Records, March 1991 \cdnum[3]{CK~65302}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Another Side of Bob Dylan}.
Columbia Records, August 1964 \cdnum{CK 8993}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{At Budoken}.
Columbia, 1978 \cdnum[2]{G2K 36067}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Biograph}.
Columbia, 1985 \cdnum[3]{C3K~38830}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Blonde on Blonde}.
Columbia Records, 1966 \cdnum{CGK~841}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Blood on the Tracks}.
Columbia Records, 1974 \cdnum{CK 33235}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Bob Dylan}.
Columbia Records, 1961 \cdnum{CK 08579}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Bringing It All Back Home}.
Columbia Records, March 1965 \cdnum{CK 9128}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Desire}.
Columbia Records, January 1975 \cdnum{CK33893}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Down in the Grove}.
Columbia, June 1988 \cdnum{CK 40957}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Empire Burlesque}.
Columbia, June 1985 \cdnum{CK~40110}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Good As I Been to You}.
Columbia, November 1992 \cdnum{CK 53200}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Hard Rain}.
Columbia, September 1976 \cdnum{CK~34349}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Highway 61 Revisited}.
Columbia Records, August 1965 \cdnum{CK 9189}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Infidels}.
Columbia Records, November 1983 \cdnum{CK~38819}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{John Wesley Harding}.
Columbia Records, January 1968 \cdnum{CK~9604}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Knocked Out Loaded}.
Columbia Records, August 1986 \cdnum{CK~40439}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Live 1964: Concert at Philharmonic Hall}.
Volume~6 of \emph{The Bootleg Series}.
Columbia Records, 2004 \cdnum[2]{C2K 86882}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Live 1966: The ``Royal Albert Hall'' Concert}.
Volume~4 of \emph{The Bootleg Series}.
Columbia Records, 1998 \cdnum[2]{C2K 65759}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Live 1975: The Rolling Thunder Revue}.
Volume~5 of \emph{The Bootleg Series}.
Columbia Records, 2002 \cdnum[2]{C2K 87047}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{MTV Unplugged}.
Columbia, 1995 \cdnum{CK 67000}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Nashville Skyline}.
Columbia Records, April 1969 \cdnum{CK~9825}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{New Morning}.
Columbia Records, October 1970 \cdnum{CK 30290}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Oh Mercy}.
Columbia Records, 1989 \cdnum{CK~45281}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Pat Garrett and Billy the Kid}.
Columbia Records, July 1973 \cdnum{CK 32460}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Planet Waves}.
Columbia Records, January 1974 \cdnum{CK 37637}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Real Live}.
Columbia, December 1984 \cdnum{CK 39944}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Saved}.
Columbia, June 1980 \cdnum{CK 36553}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Self Portrait}.
Columbia Records, June 1970 \cdnum{CK 30050}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Shot of Love}.
Columbia, August 1981 \cdnum{CK 37496}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Slow Train Coming}.
Columbia, August 1979 \cdnum{CK~36120}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Street Legal}.
Columbia, June 1978 \cdnum{CK 35453}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{The Freewheelin' Bob Dylan}.
Columbia Records, May 1963 \cdnum{CK 8786}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{The Times They Are A-Changin'}.
Columbia Records, February 1964 \cdnum{CK 8905}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Time Out of Mind}.
Columbia Records, 1997 \cdnum{CK~68556}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{Under the Red Sky}.
Columbia, 1990 \cdnum{CK 46794}.

\cd\relax
\artist{Dylan, Bob}.
\cdtitle{World Gone Wrong}.
Columbia, 1993 \cdnum{CK 57590}.

\cd\relax
\artist{Dylan, Bob and the Band}.
\cdtitle{The Basement Tapes}.
Columbia Records, 1975 \cdnum[2]{C2K 33682}.

\cd\relax
\artist{Dylan, Bob and the Grateful Dead}.
\cdtitle{Dylan and the Dead}.
CBS Records, June 1989 \cdnum{CK~45056}.

\cd\relax
\artist{Eagles}.
\cdtitle{Desperado}.
Asylum, 1973 \cdnum{5068-2}.

\cd\relax
\artist{Eagles}.
\cdtitle{Hotel California}.
Asylum, 1976 \cdnum{EUR 253 051}.

\cd\relax
\artist{Eagles}.
\cdtitle{One of These Nights}.
Asylum, 1975 \cdnum{7E-1039-2}.

\cd\relax
\artist{Eberhardt, Cliff}.
\cdtitle{The Long Road}.
Windham Hill Records, 1990 \cdnum{WD-1092}.

\cd\relax
\artist{Eisler, Hanns}.
\cdtitle{The Hollywood Songbook}.
Matthias Goerne (baritone) and Eric Schneider (piano).
The Decca Record Company, 1998 \cdnum{289 460 582-2}.

\cd\relax
\artist{Elgar, Edward}.
\cdtitle{Cello Concerto in E~minor, Op.~85 \and Sea Pictures, Op.~37}.
Jacqueline du Pr\'e (cello) and Dame Janet Baker (mezzo-soprano).
The London Symphony Orchestra.
Sir John Barbirolli, cond.
EMI Records, 1997 \cdnum{7243 5 56219 2 4}.

\cd*\relax
\artist{Elgar, Edward}.
\cdtitle{Cello Concerto, Op.~85}.
\see{1002}.

\cd\relax
\artist{Elgar, Edward}.
\cdtitle{Complete Symphonies \: \track Symphony No.~1 in A~flat, Op.~55
  \; \track Pomp and Circumstance, Op.~39 \; \track Symphony No.~ in
  E~flat, Op.~63 \; \track Cockaigne \(In London Town\), Op.~40}.
London Symphony Orchestra and Royal Philharmonic Orchestra.
Andr\'e Previn, cond.
Philips Classics, 1996 \cdnum[2]{454 250-2}.

\cd*\relax
\artist{Elgar, Edward}.
\cdtitle{Concerto for Cello and Orchestra, op.~85}.
\see{1003}.

\cd*\relax
\artist{Elgar, Edward}.
\cdtitle{Concerto for Violin and Orchestra Op.~61 in B~minor}.
\see{1}.

\cd*\relax
\artist{Elgar, Edward}.
\cdtitle{``Romance,'' Op.~62}.
\see{661}.

\cd*\relax
\artist{Elgar, Edward}.
\cdtitle{Romance, Op.~62 for bassoon and orchestra}.
\see{1589}.

\cd\relax
\artist{Elgar, Edward}.
\cdtitle{\track String Quartet in E~minor, Op.~83 \; \track Piano
  Quintet in A~minor, Op.~84}.
Maggini String Quartet and Peter Donohoe (piano).
Naxos, 1997 \cdnum{8.553737}.

\cd*\relax
\artist{Eliasson, Andes}.
\cdtitle{Disegno per trombone}.
\see{964}.

\cd\relax
\artist{Emerson String Quartet}.
\cdtitle{\track \C{Claude Debussy} String Quartet in G~minor op.~10 \;
  \track \C{Maurice Ravel} String Quartet in F~major}.
Deutsche Grammophon, 1986 \cdnum{445 509-2}.

\cd*\relax
\artist{Enescu, George}.
\cdtitle{Dixtuour, Op.~14}.
\see{515}.

\cd*\relax
\artist{Erdmann, Dietrich}.
\cdtitle{Akzente}.
\see{252}.

\cd*\relax
\artist{Erdmann, Dietrich}.
\cdtitle{Concerto for Bass Clarinet and Orchestra}.
\see{1321}.

\cd\relax
\artist{Erdmann, Dietrich}.
\cdtitle{Musik f\"ur Saxophon \: \track Konzert f\"ur Saxophon und
  Orchester \; \track Saxophonata \; \track Resonanzen f\"ur
  Saxophonquartett \; \track Akzente f\"ur Saxophon and Klavier \;
  \track Persiflagen f\"ur Saxophonquartett \; \track Fantasia colorata
  f\"ur Tenorsaxophon \; \track Konzertst\"uck f\"ur Altsaxophon und
  kleines Orchester}.
Thorofon Records, 1996 \cdnum{CTH~2269}.

\cd*\relax
\artist{Erlebach, Philipp Heinrich}.
\cdtitle{Ouverture No.~4}.
\see{10}.

\cd*\relax
\artist{Ern\H{o}.
\cdtitle{Dohn\'anyi} Ruralia Hungarica for Cello and Piano, Op.~32/d.}
\see{804}.

\cd*\relax
\artist{Ernst, Heinrich Wilhelm}.
\cdtitle{Der Erlk\"onig, Grand Caprice op.~26}.
\see{1412}.

\cd\relax
\artist{Ernst, Johannes}.
\cdtitle{New Saxophone Chamber Music \: \track \C{Hanspeter Kyburz}
  Cells \; \track \C{Christoph Staude} Obduktion \; \track \C{Isabelle
  Mundry} Komposition f\"ur Altsaxophon und Tonband \; \track \C{Walter
  Zimmermann} Fragmente der Liebe}.
Ensemble UnitedBerlin.
Peter Hirsch, cond.
col legno, 1996 \cdnum{WWE 1CD 31890}.

\cd\relax
\artist{Eschenbach, Christoph}.
\cdtitle{Beethoven/Haydn/Mozart/Schubert/Schumann \: \track \C{Robert
  Schumann} ``ABEGG'' Variations, Op.~1 \and Six intermezzi for Piano,
  Op.~4 \; \track \C{Franz Schubert} Piano Sonata in~A, D.~959 \; \track
  \C{Joseph Haydn} Piano Sonata in E~minor, Hob.~XVI:34 \and Piano
  Sonata in~E, Hob.~XVI:37 \; \track \C{Wolfang Amadeus Mozart} 12
  Variations in~C, KV~265 on ``Ah, vous dirai-je, Maman'' \and Piano
  Sonata in~F, KV~332 \; \track \C{Ludwig van Beethoven} Piano Concerto
  No.~1 in~C, Op.~15}.
Volume~24 of \emph{Great Pianists of the 20th Century}.
Berliner Philharmoniker.
Herbert von Karajan, cond.
Philips Classics, 1999 \cdnum[2]{456 763-2}.

\cd*\relax
\artist{Etler, Alvin}.
\cdtitle{Sonata for Bassoon and Piano}.
\see{661}.

\cd\relax
\artist{Eurythmics}.
\cdtitle{Sweet Dreams \(Are Made of This\)}.
RCA Records, 1983 \cdnum{PCD14681}.

\cd*\relax
\artist{Falla, Manuel de}.
\cdtitle{Ritual Fire Dance \from El Amor brujo}.
\see{1315}.

\cd*\relax
\artist{Falla, Manuel de}.
\cdtitle{Ritual Fire Dance \from El Amor brujo}.
\see{929}.

\cd*\relax
\artist{Falla, Manuel de}.
\cdtitle{Spanish Dance}.
\see{245}.

\cd*\relax
\artist{Falla, Manuel de}.
\cdtitle{Suite populaire espagnole}.
\see{500}.

\cd*\relax
\artist{Farkas, Ferenc}.
\cdtitle{Ballada}.
\see{804}.

\cd*\relax
\artist{Fasch, Johann Friedrich}.
\cdtitle{Konzert D-dur f\"ur Trompete, 2 Oboen, Streicher und Basso
  continuo}.
\see{1523}.

\cd*\relax
\artist{Faur\'e, Claude}.
\cdtitle{Dolly, Op.~56 \(Piano duet\) \and Pr\'elude in D~flat, Op.~103
  No.~1 \and Pr\'elude in G~minor, Op.~103 No.~3 \and Pr\'elude in
  D~minor, Op.~103 No.~5 \and Nocturne No.~7 in C~sharp minor, Op.~74
  \and Barcarolle No.~5 in F~sharp minor, Op.~66 \and Impromptu No.~5 in
  F~sharp minor, Op.~102}.
\see{407}.

\cd*\relax
\artist{Faur\'e, Gabriel}.
\cdtitle{Apr\`es un r\^eve, Op.~7, No.~1}.
\see{1315}.

\cd*\relax
\artist{Faur\'e, Gabriel}.
\cdtitle{\'El\'egie}.
\see{929}.

\cd*\relax
\artist{Faur\'e, Gabriel}.
\cdtitle{Fleur jet\'ee \and Le berceaux \and Au bord de l'eau \and
  Prison \and Clair de lune \and Nell \and La bonne chanson}.
\see{302}.

\cd*\relax
\artist{Faur\'e, Gabriel}.
\cdtitle{Impromptu No.~2 in F~minor, Op.~31 \and Nocturne No.~2 in~B,
  Op.~33 No.~2}.
\see{617}.

\cd\relax
\artist{Faur\'e, Gabriel}.
\cdtitle{Messe de Requiem, op.~48 \(1893 version\) \and Messe des
  P\^echeurs de Villerville \(\textup{with} \artist{Andr\'e
  Messager}\)}.
La Chapelle Royale, Les Petits Chanteurs de Saint-Louis, and Ensemble
  Musique Oblique.
Philippe Herreweghe, cond.
Harmonia Mundi, 1998 \cdnum{HMD 941292}.

\cd*\relax
\artist{Faur\'e, Gabriel}.
\cdtitle{Nocturne No.~6 in D~flat, Op.~63}.
\see{887}.

\cd\relax
\artist{Faur\'e, Gabriel}.
\cdtitle{Piano Quartet No~1 in C~minor, Op~15 \and Piano Quartet No~2 in
  G~minor, Op~45}.
Domus.
Hyperion Records, 1986 \cdnum{CDA66166}.

\cd\relax
\artist{Faur\'e, Gabriel}.
\cdtitle{Piano Quintet No~1 in D~minor, Op~89 \and Piano Quintet No~2 in
  C~minor, Op~115}.
Domus and Anthony Marwood (violin).
Hyperion Records, 1995 \cdnum{CDA66766}.

\cd*\relax
\artist{Faur\'e, Gabriel}.
\cdtitle{Sonata No.~1 in A~Major for Violin and Piano, Op.~13 \T{Ma}}.
\see{1010}.

\cd*\relax
\artist{Faur\'e, Gabriel}.
\cdtitle{Troi Romances sans Paroles}.
\see{1604}.

\cd*\relax
\artist{Faur\'e, Gabriel}.
\cdtitle{Violin Sonata No.~1 in A~major, op.~13}.
\see{244}.

\cd\relax
\artist{Faur\'e, Gabriel}.
\cdtitle{Works for Cello and Piano \: \track Sonata No.~1 in d~minor
  \(op.~109\) \; \track El\'egie \(op.~24\) \; \track Sonata No.~2 in
  g~minor \(op.~117\) \; \track Apr\`es un R\^eve \(op.~7\) \; \track
  Sicilienne \(op.~78\) \; \track Papillon \(op.~77\) \; \track
  S\'er\'enade \(op.~98\) \; \track Romance \(op.~69\) \and Berceuse
  \(op.~16\)}.
Kim Bak Dinitzen (cello) and Elisabeth Westenholz (piano).
Kontra Punkt, 1995 \cdnum{32220}.

\cd*\relax
\artist{Feinberg, Samuel}.
\cdtitle{Bach Sch\"ubler Chorale No~6 \(transcription\) \and Berceuse
  Op~19a}.
\see{726}.

\cd*\relax
\artist{Feld, Jind\u{r}ich}.
\cdtitle{Sonata for Alto Saxophone and Piano}.
\see{1603}.

\cd*\relax
\artist{Feld, Jindrich}.
\cdtitle{Trio Giocoso}.
\see{1606}.

\cd*\relax
\artist{Ferguson, Howard}.
\cdtitle{Four Short Pieces Op~6}.
\see{894}.

\cd\relax
\artist{Ferrer, Ibrahim}.
\cdtitle{Ibrahim Ferrer}.
World Circuit/Nonesuch, 1999 \cdnum{79532-2}.

\cd\relax
\artist{Field, John}.
\cdtitle{Nocturnes and Sonatas \: \track Sonata in E~flat major, Op.~1,
  No.~1 \; \track Sonata in A~major, Op.~1, No.~2 \; \track Nocturne
  No.~1 in E~flat major \; \track Nocturne No.~2 in C~minor \; \track
  Nocturne No.~3 in A~flat major \; \track Nocturne No.~4 in A~major \;
  \track Nocturne No.~5 in B~flat major \; \track Nocturne No.~6 in
  F~major \; \track Nocturne No.~7 in C~major \; \track Nocturne No.~8
  in A~major \; \track Nocturne No.~9 in E~flat major}.
Volume~1 of \emph{Piano Music}.
Benjamin Frith.
Naxos, 1999 \cdnum{8.550761}.

\cd\relax
\artist{Fingerett, Sally}.
\cdtitle{Unraveled}.
Amerisound, 1991 \cdnum{1~977 798}.

\cd*\relax
\artist{Finzi, Gerald}.
\cdtitle{Five Bagatelles Op.~23}.
\see{894}.

\cd\relax
\artist{Fischer, Edwin}.
\cdtitle{Bach/Bach-Busoni \: \track \C{Johann Sebastian Bach} The
  Well-Tempered Clavier \(excerpts\) \and Chromatic Fantasy and Fugue in
  D~minor, BWV~903 \and Prelude \(Fantasy\) in A~minor, BWV~922 \and
  Fantasy and Fugue in A~minor, BWV~904 \and Concerto in D~minor,
  BWV~1052 \and Concerto in~A, BWV~1055 \and Concerto in F~minor,
  BWV~1056 \; \track \C{Johann Sebastian Bach and Ferruccio Busoni} Ich
  ruf zu dir, Herr Jesu Christ, BWV~639}.
Volume~25 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 766-2}.

\cd\relax
\artist{Fischer, Edwin}.
\cdtitle{Beethoven/Mozart/Schubert \: \track \C{Ludwig van Beethoven}
  Piano Concerto No.~5 in E~flat, Op.~73 ``Emperor'' \and Piano Sonata
  No.~23 in F~minor, Op.~57 ``Appassionata'' \and Piano Sonata No.~31 in
  A~flat, Op.~110 \; \track \C{Franz Schubert} Impromptus, D.~899 \;
  \track \C{Wolfgang Amadeus Mozart} Piano Concerto No.~20 in D~minor,
  KV~466 \and Fantasia in C~minor, KV~475}.
Volume~26 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 769-2}.

\cd\relax
\artist{Fischer-Dieskau, Dietrich}.
\cdtitle{M\'elodies romantiques}.
Hartmut H\"oll (piano).
Teldec Classics, 1987/1994 \cdnum{4509-97457-2}.

\cd*\relax
\artist{Fitkin, Graham}.
\cdtitle{Stub}.
\see{1231}.

\cd\relax
\artist{Fitzgerald, Ella}.
\cdtitle{The Best of the Song Books}.
PolyGram Records, 1993 \cdnum{314 519 804-2}.

\cd\relax
\artist{Fitzgerald, Ella}.
\cdtitle{The Best of the Song Books: Love Songs}.
PolyGram Records, 1996 \cdnum{314 531 762-2}.

\cd\relax
\artist{Fitzgerald, Ella}.
\cdtitle{The Best of the Song Books: The Ballads}.
PolyGram Records, 1994 \cdnum{314 521 867-2}.

\cd\relax
\artist{Flack, Roberta}.
\cdtitle{Killing Me Softly}.
Atlantic Recording Corporation, 1973 \cdnum{82793-2}.

\cd\relax
\artist{Flanders, Michael and Donald Swann}.
\cdtitle{At the Drop of a Hat}.
EMI Records, 1991 \cdnum{CDP~7974652}.

\cd\relax
\artist{Flanders, Michael and Donald Swann}.
\cdtitle{At the Drop of Another Hat}.
EMI Records, 1991 \cdnum{CDP~7974662}.

\cd\relax
\artist{Flanders, Michael and Donald Swann}.
\cdtitle{The Bestiary of Flanders and Swann}.
EMI Records, 1991 \cdnum{CDP~7974672}.

\cd\relax
\artist{Flatt, Lester and Earl Scruggs}.
\cdtitle{The Best of Flatt and Scruggs: The Millennium Collection}.
Mercury Records, 2001 \cdnum{088 170 187-2}.

\cd\relax
\artist{Fleck, B\'ela}.
\cdtitle{Perpetual Motion}.
Sony, 2001 \cdnum{SK~89610}.

\cd\relax
\artist{Fleck, B\'ela and Edgar Meyer}.
\cdtitle{Music for Two}.
Sony, 2004 \cdnum{SK~92106}.
With bonus DVD.

\cd\relax
\artist{Fleetwood Mac}.
\cdtitle{Mystery to Me}.
Reprise Records, 1973 \cdnum{9~25982-2}.

\cd\relax
\artist{Fleetwood Mac}.
\cdtitle{Rumours}.
Warner Brothers, 1977 \cdnum{3010-2}.

\cd\relax
\artist{Fleetwood Mac}.
\cdtitle{Then Play On}.
Reprise Records, 1970 \cdnum{6368-2}.

\cd\relax
\artist{Fleisher, Leon}.
\cdtitle{Copland/Liszt/Mozart/Rachmaninoff/Ravel \: \track \C{Aaron
  Copland} Sonata \; \track \C{Franz Liszt} Piano Sonata in B~minor \;
  \track \C{Wolfgang Amadeus Mozart} Piano Sonata in~C, KV~330 \; \track
  \C{Sergei Rachmaninoff} Rhapsody on a theme by Paganini, Op.~43 \;
  \track \C{Maurice Ravel} Sonatine \and Alborado del gracioso \(No.~4
  from ``Miroirs''\) \and Piano Concerto in~D ``for the left hand'' \;
  \track \C{Ned Rorem} 3~Barcarolles \; \track \C{Carl Maria von Weber}
  Piano Sonata No.~4 in E~minor, Op.~70}.
Volume~27 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 775-2}.

\cd\relax
\artist{Flowers, The}.
\cdtitle{On the Other Side of Happiness~I}.
1999 (7-88308-135-7).

\cd\relax
\artist{Flowers, The}.
\cdtitle{On the Other Side of Happiness~II}.
1999 (7-88308-135-7).

\cd\relax
\artist{Fogerty, John}.
\cdtitle{premonition}.
Reprise Records, 1998 \cdnum{2-46908-AB}.

\cd\relax
\artist{Folds, Ben}.
\cdtitle{Rockin' the Suburbs}.
Sony, 2001 \cdnum{EK 61610}.

\cd\relax
\artist{Fong Naam}.
\cdtitle{Siamese Funeral Music \: \track The Nang Hong Suite for Double
  Piphat Ensemble \; \track The Language Suite}.
Nimbus Records, 1992 \cdnum{NI~5332}.

\cd*\relax
\artist{Fontana, Giovanni Battista}.
\cdtitle{Sonata No.~16 a tre violini}.
\see{1184}.

\cd*\relax
\artist{Fontana, Giovanni Battista}.
\cdtitle{Sonata~V \and Sonata~VI \from ``Sonate a 1. 2. 3.,'' op.~post.}
\see{1308}.

\cd\relax
\artist{Foote, Arthur}.
\cdtitle{Chamber Music, Volume~1 \: \track Piano Quintet in A~minor,
  Op.~38 \; \track String Quartet No.~2 in E~major, Op.~32 \; \track
  String Quartet No.~3 in D~major, Op.~70}.
Da Vinci Quartet and James Barbagallo (piano).
Naxos, 1998 \cdnum{8.559009}.

\cd\relax
\artist{Foote, Arthur}.
\cdtitle{Chamber Music, Volume~2 \: \track Piano Quartet in C~major,
  Op.~23 \; \track Nocturne and Scherzo for Flute and String Quartet
  \(1918\) \; \track String Quartet No.~1 in G~minor, Op.~4}.
Da Vinci Quartet, James Barbagallo (piano) and Jeani Muhonen Foster
  (flute).
Naxos, 1999 \cdnum{8.559014}.

\cd*\relax
\artist{Foote, Rachel}.
\cdtitle{Aggregate~I \emph{for Saxophone and two-channel playback}}.
\see{1429}.

\cd*\relax
\artist{Forster, B. Y.}
\cdtitle{Lullaby of Birdland}.
\see{716}.

\cd\relax
\artist{Fountains of Wayne}.
\cdtitle{Fountains of Wayne}.
Tag Recordings, 1996 \cdnum{92725-2}.

\cd\relax
\artist{Fountains of Wayne}.
\cdtitle{Out-of-State Plates}.
Virgin Records, 2005 \cdnum[2]{7243 5 76987 2~6}.

\cd\relax
\artist{Fountains of Wayne}.
\cdtitle{Utopia Parkway}.
Atlantic Recording Corporation, 1999 \cdnum{83177-2}.

\cd\relax
\artist{Fountains of Wayne}.
\cdtitle{``Welcome Interstate Managers''}.
Virgin Records, 2003 \cdnum{7243 5 90875 2~8}.

\cd*\relax
\artist{Fox, Frederick}.
\cdtitle{Time Weaving}.
\see{1598}.

\cd*\relax
\artist{Francaix, Jean}.
\cdtitle{Divertissement for Bassoon and String Quintet}.
\see{881}.

\cd*\relax
\artist{Fran\c{c}aix, Jean}.
\cdtitle{Petit Quatour pour Saxophone}.
\see{830}.

\cd*\relax
\artist{Fran\c{c}aix, Jean}.
\cdtitle{Wind Quintet No.~1 \(1948\)}.
\see{4}.

\cd*\relax
\artist{Franck, C\'esar}.
\cdtitle{Pr\'elude, choral et fugue}.
\see{1092}.

\cd*\relax
\artist{Franck, C\'esar}.
\cdtitle{Pr\'elude, choral et fugue}.
\see{1320}.

\cd*\relax
\artist{Franck, C\'esar}.
\cdtitle{Pr\'elude, choral et fugue}.
\see{882}.

\cd*\relax
\artist{Franck, Cesar}.
\cdtitle{Pr\'elude, choral et fugue \and Pr\'elude, aria et final \and
  Variations symphoniques}.
\see{448}.

\cd*\relax
\artist{Franck, C\'esar}.
\cdtitle{Sonata in A~Major for Violin and Piano \(version for Cello and
  Piano\)}.
\see{1010}.

\cd*\relax
\artist{Franck, C\'esar}.
\cdtitle{Variations symphoniques}.
\see{637}.

\cd*\relax
\artist{Franck, C\'esar}.
\cdtitle{Violin Sonata in A~major}.
\see{214}.

\cd*\relax
\artist{Franck, C\'esar}.
\cdtitle{Violin Sonata in A~major}.
\see{244}.

\cd\relax
\artist{Franck, C\'esar and Ernest Chausson}.
\cdtitle{Chamber Music \: \track \C{C\'esar Franck} Piano Quintet in
  F~minor \; \track \C{Ernest Chausson} String Quartet in C~minor,
  Op.~35}.
Quatuor Ludwig and Micha\"el Levinas (piano).
Naxos, 1997 \cdnum{8.553645}.

\cd\relax
\artist{Fran\c{c}ois, Samson}.
\cdtitle{Chopin/Debussy/Faur\'e/Mozart/Ravel \: \track \C{Fr\'ed\'eric
  Chopin} Impromptu No.~1 in A~flat, Op.~29 \and Impromptu No.~2 in
  F~sharp, Op.~36 \and Impromptu No.~3 in G~flat, Op.~51 \and Impromptu
  No.~4 in C~sharp minor, Op.~66 \and Piano Sonata No.~2 in B~flat
  minor, Op.~35 \and Waltz in G~flat, Op.~70 No.~1 \and Waltz in E~flat,
  Op.~18 ``Grande Valse brillante'' \and Waltz in C~flat, Op.~70 No.~3
  \and Waltz in C~sharp minor, Op.~64 No.~2 \and Ballade No.~1 in
  G~minor, Op.~23 \and Ballade No.~2 in~F, Op.~38 \and Ballade No.~3 in
  A~flat, Op.~47 \and Ballade No.~4 in F~minor, Op.~52 \; \track
  \C{Johann Sebastian Bach} Toccata, Adagio and Fugue in~C, BWV~564
  \arr{Ferruccio Busoni} \; \track \C{Wolfgang Amadeus Mozart} Twelve
  Variations in~C, KV~265 on ``Ah, vous dirai-je, Maman'' \; \track
  \C{Robert Schumann} Toccata in~C, Op.~7 \; \track \C{Gabriel Faur\'e}
  Impromptu No.~2 in F~minor, Op.~31 \and Nocturne No.~2 in~B, Op.~33
  No.~2 \; \track \C{Claude Debussy} Clair de lune \(\from ``Suite
  bergamasque''\) \and L'isle joyeuse \and Pour le piano. Suite \;
  \track \C{Serge Prokofiev} Toccata, Op.~11 \; \track \C{Maurice Ravel}
  Scarbo \(\from ``Gaspard de la nuit''\)}.
Volume~28 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 778-2}.

\cd\relax
\artist{Frankel, Benjamin}.
\cdtitle{\track Concerto for Violin and Orchestra, Op.~24 ``In memory of
  the six million'' \; \track Viola Concerto, Op.~45 \; \track Serenata
  Concertante for Piano Trio and Orchestra, Op.~37}.
Ulf Hoelscher (violin), Brett Dean (viola), Stephen Emmerson (piano),
  Alan Smith (violin) and David Lale (violoncello).
Queensland Symphony Orchestra.
Werner Andreas Albert, cond.
CPO, 1998 \cdnum{999 422-2}.

\cd\relax
\artist{Frankfurter Kontraba{\ss}-Quartett}.
\cdtitle{\track \C{Jon Alm} Quartet for Four Double Basses \(1984\) \;
  \track \C{Angel Pe\~na} Un petit recueil for Three Double Basses \;
  \track \C{Georg Philipp Telemann} Concerto a quattro violini senza
  basso \; \track \C{Emil Tabakov} Motivy for Double Bass Solo \; \track
  \C{Colin Brumby} Suite for Four Double Basses \(1975\) \; \track
  \C{Joseph Haydn} Divertimento for Two Barytons \; \track \C{Jacques
  Vanherenthals} Varium et mutabile for Four Double Basses}.
MDG, 1995 \cdnum{MDG~603 0634-2}.

\cd\relax
\artist{Franklin, Arethra}.
\cdtitle{30 Greatest Hits}.
Atlantic, 1986 \cdnum[2]{7 81668-2}.

\cd\relax
\artist{Franklin, Arethra}.
\cdtitle{Jazz to Soul}.
Columbia, 1992 \cdnum[2]{C2K 48515}.

\cd\relax
\artist{Franklin, Arethra}.
\cdtitle{Queen of Soul: The Atlantic Recordings}.
Rhino, 1992 \cdnum[4]{RS~71063}.

\cd\relax
\artist{Freire, Nelson}.
\cdtitle{Brahms/Chopin/Liszt/Mozart/Schumann \: \track \C{Johannes
  Brahms} Piano Sonata No.~3 in F~minor, Op.~5 \; \track \C{Fr\'ed\'eric
  Chopin} Scherzo No.~1 in B~minor, Op.~20 \and Impromptu No.~2 in
  F~sharp, Op.~36 \and Mazurka in C~sharp minor, Op.~41 No.~1 \and
  Mazurka in B~flat minor, Op.~24 No.~4 \and Piano Sonata No.~3 in
  B~minor, Op.~58 \; \track \C{Franz Liszt} Hungarian Rhapsody No.~10
  \and Totentanz \; \track \C{Wolfgang Amadeus Mozart} in ~F, KV~332 \;
  \track \C{Robert Schumann} Fantasie in~C, Op.~17 \; \track \C{Johann
  Strauss and Leopold Godowsky} Symphonic Metamorphosis on Themes from
  ``Die Fledermaus'' \; \track \C{Richard Strauss and Leopold Godowsky}
  St\"andchen}.
Volume~29 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 781-2}.

\cd*\relax
\artist{Frescobaldi, Girolamo}.
\cdtitle{Partite sopra l'aria della romananesca \from ``Toccate e
  partite,'' Lib.~I}.
\see{1308}.

\cd*\relax
\artist{Freund, Don}.
\cdtitle{Lounder than Words}.
\see{1606}.

\cd\relax
\artist{Friedlander, Erik}.
\cdtitle{Block Ice and Propane}.
Skipstone Records, 2007.

\cd\relax
\artist{Friedman, Ignaz}.
\cdtitle{Beethoven/Chopin/Liszt/Mendelssohn \: \track \C{Fr\'ed\'eric
  Chopin} Ballade No.~3 in A~flat, Op.~47 \and Impromptu No.~2 in
  F~sharp, Op.~36 \and Polonaise No.~6 in A~flat, Op.~53 ``Heroic'' \and
  Polonaise No.~9 in B~flat, Op.~71, No.~2 \and Prelude in D~flat,
  Op.~28, No.~15 ``Raindrop'' \and Prelude in E~flat, Op.~28, No.~19
  \and Nocturne No.~16 in E~flat, Op.~55, No.~2 \and Mazurka in B~flat,
  Op.~7, No.~1 \and Mazurka in A~minor, Op.~7, No.~2 \and Mazurka in
  F~minor, Op.~7, No.~3 \and Mazurka in~D, Op.~33, No.~2 \and Mazurka in
  B~flat minor, Op.~24, No.~4 \and Mazurka in B~minor, Op.~33, No.~4
  \and Mazurka in C~sharp minor, Op.~41, No.~1 \and Mazurka in A~flat,
  Op.~50, No.~2 \and Mazurka in C~sharp minor, Op.~63, No.~3 \and
  Mazurka in~C, Op.~67, No.~3 \and Mazurka in A~minor, Op.~67, No.~4
  \and Mazurka in A~minor, Op.~68, No.~2 \and Berceuse in D~flat, Op.~57
  \and Waltz in A~minor, Op.~34, No.~2 \and Piano Sonata No.~2 in B~flat
  minor, Op.~35 \(Marche fun\`ebre and Finale\) \and Waltz in D~flat,
  Op.~64, No.~1 ``Minute'' \and Etude in G~sharp minor, Op.~25, No.~6
  \and Etude in G~flat, Op.~10, No.~5 ``Black Keys'' \and Etude in
  G~flat, Op.~25, No.~9 ``Butterfly'' \and Etude in~C, Op.~10, No.~7
  \and Etude in C~minor, Op.~10, No.~12 ``Revolutionary'' \; \track
  \C{Franz Schubert/Franz Liszt} ``Hark! Hark! The Lark''
  \(St\"andchen\) \; \track \C{Franz Liszt} La campanella \and Hungarian
  Rhapsody No.~2 \; \track \C{Johann Nepomuk Hummel} Rondo favori in
  E~flat, Op.~11 \; \track \C{Anton Rubenstein} Valse caprice \; \track
  \C{Carl Maria von Weber} Aufforderung zum Tanz \; \track \C{Felix
  Mendelssohn Bartholdy} Lieder ohne Worte \(selections\) \and Scherzo
  in E~minor, Op.~16, No.~2 \; \track \C{Ludwig van Beethoven} Piano
  Sonata in C~sharp minor, Op.~27, No.~2 ``Moonlight''}.
Volume~30 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 784-2}.

\cd*\relax
\artist{Fritts, Lawrence}.
\cdtitle{Orthogonality \emph{for alto saxophone and tape}}.
\see{1429}.

\cd*\relax
\artist{Froom, David}.
\cdtitle{Arirang Variations}.
\see{1606}.

\cd*\relax
\artist{Fundal, Karsten}.
\cdtitle{The Ways of Lightness and Falling}.
\see{960}.

\cd\relax
\artist{Furtw\"angler, Wilhelm}.
\cdtitle{Maestro Classico, Volume~1 \: \track \C{Peter Iljitsch
  Tschaikowsky} Symphony No.~6 in B~flat major, op.~67 Path\'etique \;
  \track \C{Alexander Glasunow} Stenka Razin, Symphonic Poem in B~minor,
  op.~13 \; \track \C{Wolfgang Amadeus Mozart} Symphony No.~39 in E~flat
  major, KV~543 \and Symphony No.~40 in G~minor, KV~550 \and Eine kleine
  Nachtmusik, Serenade in G~major, KV~525}.
Trumpets of Jericho, 2001 \cdnum[2]{20.3091-HI}.

\cd\relax
\artist{Furtw\"angler, Wilhelm}.
\cdtitle{Maestro Classico, Volume~2 \: \track \C{Franz Schubert}
  Symphony No.~9 in C~major, D~944 \and Rosamunde \; \track \C{Richard
  Wagner} Parsifal: \emph{Prelude to the 2nd Act} and
  \emph{Karfreitagszauber} \and Tristan und Isolde: \emph{Vorspeil und
  Liebestod} \and Lohengrin: \emph{Prelude to the 1st Act} \and Die
  Meistersinger von N\"urnberg: \emph{Prelude to the 1st Act}}.
Trumpets of Jericho, 2001 \cdnum[2]{20.3092-HI}.

\cd\relax
\artist{Furtw\"angler, Wilhelm}.
\cdtitle{Maestro Classico, Volume~3 \: \track \C{Felix
  Mendelssohn-Bartholdy} Ein Sommernachtstraum: Overture \; \track
  \C{Gioacchino Rossini} La gazza ladra: Sinfonia \; \track \C{Ludwig
  van Beethoven} Egmont-Overture, op.~84 \; \track \C{Carl Maria von
  Weber} Der Freisch\"utz: Overture \; \track \C{Johann Strauss Jr.} Die
  Fledermaus: Overture \; \track \C{Wolfgang Amadeus Mozart} Le nozze di
  Figaro \; \track \C{Christoph Willibald Gluck} Alceste: Overture \;
  \track \C{Georg Friedrich H\"andel} Concerto grosso in D~major, op.~6
  no.~5 \; \track \C{Johann Sebastian Bach} Brandenburg Concerto No.~3
  in G~major, BWV~1048 \; \track \C{Wilhelm Furtw\"angler} Symphonic
  Concerto for Piano and Orchestra in B~flat major \; \track \C{Richard
  Straus} Don Juan, Symphonic Poem for Orchestra, op.~20 \and Till
  Eulenspiegels lustige Streiche, op.~28}.
Trumpets of Jericho, 2002 \cdnum[2]{20.3093-HI}.

\cd\relax
\artist{Furtw\"angler, Wilhelm}.
\cdtitle{Maestro Classico, Volume~4 \: \track \C{Johannes Brahms}
  Symphony No.~1 in C~minor, op.~68 \and Haydn Variations, op.~56 \;
  \track \C{Edvard Grieg} Piano Concerto in A~minor, op.~16 \; \track
  \C{Ludwig van Beethoven} Piano Concerto No.~1 in C~major, op.~15}.
Trumpets of Jericho \cdnum[2]{20.3094-HI}.

\cd\relax
\artist{Furtw\"angler, Wilhelm}.
\cdtitle{Maestro Classico, Volume~5 \: \C{Ludwig van Beethoven} Symphony
  No.~5 in C~minor, op.~67 \and Symphony No.~6 in F~major, op.~68
  ``Pastorale'' \and Violin Concerto in D~major, op.~61 \and
  Leonore~III, Overture, op.~138 \and Coriolan-Overture, op.~62}.
Trumpets of Jericho \cdnum[2]{20.3095-HI}.

\cd*\relax
\artist{Gabriel, Wolfgang}.
\cdtitle{Ballade, Op.~23}.
\see{504}.

\cd*\relax
\artist{Gabrieli, Giovanni}.
\cdtitle{Sonata~XXI con tre violini}.
\see{1184}.

\cd*\relax
\artist{Galuppi, Baldassare}.
\cdtitle{Sonata No.~5 in~C}.
\see{1067}.

\cd*\relax
\artist{Gardel, Carlos}.
\cdtitle{El Dia Que Me Querias}.
\see{1344}.

\cd\relax
\artist{Gauthier, Daniel}.
\cdtitle{Hommage \`a Adolphe Sax \: \track \C{Andr\'e Caplet} L\'egende
  \; \track \C{Darius Milhaud} Scaramouche \and La Cr\'eation du Monde
  \; \track \C{Marius Constant} Musique de Concert \; \track \C{Marc
  Patch} Magic Spell}.
L'Ensemble St-Louis-de-France.
Bernard Jean, cond.
Soci\'et\'e nouvelle d'Enregistrement, 1990 \cdnum{SNE-555-CD}.

\cd\relax
\artist{Gavrilov, Andrei}.
\cdtitle{Bach/Scriabin/Schumann/Prokofiev/Rachmaninoff \: \track
  \C{Johann Sebastian Bach} French Suite No.~5 in~G, BWV~816 \; \track
  \C{George Frideric Handel} Suite in D~minor, HWV~447 \; \track
  \C{Wolfang Amadeus Mozart} Fantasia in D~minor, KV~397 \; \track
  \C{Robert Schumann} Papillons, Op.~2 \; \track \C{Fr\'ed\'eric Chopin}
  Ballade No.~2 in~F, Op.~38 \; \track \C{Sergei Rachmaninoff} Moment
  musical in B~minor, Op.~16, No.~3 \and Moment musical in E~minor,
  Op.~16, No.~4 \and Moment musical in D~flat, Op.~16, No.~5 \and Moment
  musical in~C, Op.~16, No.~6 \; \track \C{Edvard Grieg} Norwegian March
  \(Gangar\), Op.~54, No.~2 \; \track \C{Serge Prokofiev} Piano Concerto
  No.~1 in D~flat, Op.~10 \and 10 Pieces for piano from ``Romeo and
  Juliet'', Op.~75 \; \track \C{Alexander Scriabin} Sonata No.~4 in
  F~sharp, Op.~30 \and Etude in C~sharp minor, Op.~42, No.~5 \; \track
  \C{Peter Ilyich Tchaikovsky} Th\`eme original et variations, Op.~19,
  No.~6 \; \track \C{Mily Balakirev} Islamey}.
Volume~31 of \emph{Great Pianists of the 20th Century}.
City of Birmingham Symphony Orchestra.
Sir Simon Rattle, cond.
Philips Classics, 1999 \cdnum[2]{456 787-2}.

\cd\relax
\artist{Gaye, Marvin}.
\cdtitle{Every Great Motown Hit}.
Motown Record Company, 1991 \cdnum{3746360582}.

\cd\relax
\artist{Geminiani, Francesco}.
\cdtitle{Concerti Grossi \(after Corelli, Op.~5\) \: \track Concerto~I
  in D~major \; \track Concerto~II in B-flat major \; \track
  Concerto~III in C~major \; \track Concerto~IV in F~major \; \track
  Concerto~V in G~minor \; \track Concerto~VI in A~major \; \track
  Concerto~VII in D~minor \; \track Concerto~VIII in E~minor \; \track
  Concerto~IX in A~major \; \track Concerto~X in F~major \; \track
  Concerto~XI in E~major \; \track Concerto~XII in D~minor ``Follia'' \;
  \track Cello Sonata in D~minor,Op.~5, No.~2 \; \track \C{Arcangelo
  Corelli} Sonata for Violin and Cello, Op.~5 No.~9 in an ornamented
  version by Geminiani}.
The Academy of Ancient Music.
Andrew Manze, cond.
Harmonia Mundi, 2000 \cdnum[2]{HMU 907261.62}.

\cd*\relax
\artist{Genzmer, Harald}.
\cdtitle{Sonata}.
\see{1599}.

\cd*\relax
\artist{Genzmer, Harald}.
\cdtitle{Sonata for Bass Clarinet Solo \(First Version 1984\)}.
\see{1321}.

\cd*\relax
\artist{Gershwin, George}.
\cdtitle{3 Preludes}.
\see{766}.

\cd*\relax
\artist{Gershwin, George}.
\cdtitle{An American in Paris---blues}.
\see{830}.

\cd*\relax
\artist{Gershwin, George}.
\cdtitle{Gershwin Songbook}.
\see{1684}.

\cd*\relax
\artist{Gershwin, George}.
\cdtitle{Piano Concerto in~F \and The Man I Love \and Embraceable You
  \and I Got Rhythm \and Soemone to Watch over Me \and Boy! What Love
  Has Done to Me!---I've Got a Crush on You \and S' Wonderful \and
  Rhapsody in Blue}.
\see{1217}.

\cd*\relax
\artist{Gershwin, George}.
\cdtitle{Rhapsody in Blue}.
\see{1144}.

\cd*\relax
\artist{Gershwin, George}.
\cdtitle{Rhapsody in Blue}.
\see{50}.

\cd*\relax
\artist{Gershwin, George}.
\cdtitle{Rhapsody in Blue}.
\see{883}.

\cd\relax
\artist{Gershwin, George}.
\cdtitle{Rhapsody in Blue \and An American in Paris}.
Leonard Bernstein (piano).
Columbia Symphony Orchestra and the New York Philharmonic.
Leonard Bernstein, cond.
Sony, 1981 \cdnum{MYK~37242}.

\cd*\relax
\artist{Gershwin, George}.
\cdtitle{Short Story}.
\see{902}.

\cd*\relax
\artist{Gershwin, George}.
\cdtitle{Three Preludes}.
\see{1007}.

\cd*\relax
\artist{Gibbons, Orlando}.
\cdtitle{Fantasy in~C \and Allemande \(Italian Ground\) \and ``Lord of
  Salisbury'' Pavan and Galliard}.
\see{658}.

\cd\relax
\artist{Gibbs, Michael}.
\cdtitle{Hard-Boiled}.
Mute Records, 1993 \cdnum{IONIC~11~CD}.

\cd\relax
\artist{Gieseking, Walter}.
\cdtitle{Beethoven/Chopin/Franck/Mozart/Scriabin \: \track \C{Ludwig van
  Beethoven} Piano Concerto No.~4 in~G, Op.~58 \and Piano Concerto No.~5
  in E~flat, Op.~73 ``Emperor'' \; \track \C{Fr\'ed\'eric Chopin}
  Berceuse in D~flat, Op.~57 \; \track \C{C\'esar Franck} Variations
  symphoniques \; \track \C{Wolfgang Amadeus Mozart} Piano Concerto
  No.~23 in~A, KV~488 \and Piano Concerto No.~24 in C~minor, KV~491 \;
  \track \C{Robert Schumann} Schlummerlied \(from ``Albumbl\"atter,'',
  Op.~124\) \; \track \C{Alexander Scriabin} Po\`eme in F~sharp, Op.~32
  No.~1 \and Prelude in~E, Op.~15 No.~4}.
Volume~32 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 811-2}.

\cd\relax
\artist{Gieseking, Walter}.
\cdtitle{Beethoven/Debussy/Mozart/Ravel \: \track \C{Claude Debussy}
  Pr\'eludes, Book~I \and Pr\'eludes, Book~II \and Estampes \; \track
  \C{Wolgang Amadeus Mozart} Piano Sonata in C~minor, KV~457 \; \track
  \C{Ludwig van Beethoven} Piano Sonata in~C, Op.~53 ``Waldstein'' \and
  Piano Sonata in F~minor, Op.~57 ``Apassionata'' \; \track \C{Maurice
  Ravel} Gaspard de la nuit}.
Volume~33 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 790-2}.

\cd\relax
\artist{Gilbert, William S. and Arthur S. Sullivan}.
\cdtitle{H.M.S. Pinafore}.
The D'Oyly Carte Opera Company and the Royal Philharmonic Orchestra.
Isidore Godfrey, cond.
The Decca Record Company, 1959/1989 \cdnum[2]{412 283-2}.

\cd\relax
\artist{Gilbert, William S. and Arthur S. Sullivan}.
\cdtitle{The Mikado}.
The D'Oyly Carte Opera Company and the Royal Philharmonic Orchestra.
Royston Nash, cond.
The Decca Record Company, 1973/1989 \cdnum[2]{425 190-2}.

\cd\relax
\artist{Gilbert, William S. and Arthur S. Sullivan}.
\cdtitle{The Pirates of Penzance}.
The D'Oyly Carte Opera Company and the Royal Philharmonic Orchestra.
Isidore Godfrey, cond.
The Decca Record Company, 1968/1989 \cdnum[2]{425 196-2}.

\cd\relax
\artist{Gilels, Emil}.
\cdtitle{Bach/Beethoven/Debussy/Mozart/Ravel/Weber \: \track \C{Johann
  Sebastian Bach} Prelude and Fugue in~D, BWV~532 \arr{Ferriccio Busoni}
  \and French Suite No.~5 in~G, BWV~816 \; \track \C{Ludwig van
  Beethoven} Piano Concerto No.~4 in~G, Op.~58 \; \track \C{Claude
  Debussy} Images \(Book~1\) \; \track \C{Wolfgang Amadeus Mozart} Piano
  Concerto No.~27 in B~flat, KV~595 \; \track \C{Maurice Ravel} Jeux
  d'eau \and Toccata \(from ``Le tombeau de Couperin''\) \and Alborada
  del gracioso \(from ``Miroirs''\) \; \track \C{Carl Maria von Weber}
  Piano Sonata No.~2 in A~flat, Op.~39}.
Volume~34 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 793-2}.

\cd\relax
\artist{Gilels, Emil}.
\cdtitle{Brahms/Chopin/Clementi/Grieg/Schubert/Schumann \: \track
  \C{Johannes Brahms} Piano Concerto No.~2 in B~flat, Op.~83 \; \track
  \C{Edvard Grieg} Lyric Pieces \(excerpts\) \; \track \C{Franz
  Schubert} Fantasy in F~minor for Piano Duet, D.~940 \; \track \C{Muzio
  Clementi} Piano Sonata in~C, Op.~34 No.~1 \; \track \C{Robert
  Schumann} Arabeske in~C, Op.~18 \; \track \C{Fr\'ed\'eric Chopin}
  Piano Sonata No.~2 in B~flat minor, Op.~35 ``Funeral March'' \and
  Piano Sonata No.~3 in B~minor, Op.~58 \and Etude in F~minor, Op.~25
  No.~2}.
Volume~36 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 799-2}.

\cd\relax
\artist{Gilels, Emil}.
\cdtitle{Liszt/Prokofiev/Stravinsky/Tchaikovsky \: \track \C{Igor
  Stravinsky} 3 Movements from ``Petrouchka'' \; \track \C{Nicolai
  Medtner} Sonata reminiscenza in A~minor, Op.~38 No.~1 \; \track
  \C{Sergei Prokofiev} Piana Sonata No.~8 in B~flat, Op.~84 \and Visions
  fugitives, Op.~22 \(Excerpts\) \and Sonata No.~3 in A~minor, Op.~28
  \and March from ``The Love for Three Oranges'', Op.~33ter \; \track
  \C{Franz Liszt and Ferruccio Busoni} Fantasia on 2 themes from ``Le
  nozze di Figaro'' \; \track \C{Franz Liszt} Hungarian Rhapsody No.~9
  ``Carnival at Pest'' \and Valse oubli\'ee No.~1 in F~sharp \and
  Spanish Rhapsody \; \track \C{Peter Ilyich Tchaikovsky} Piano Concerto
  No.~2 in~G, Op.~44 \; \track \C{Johann Sebastian Bach and Alexander
  Siloti} Prelude in B~minor}.
Volume~35 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 796-2}.

\cd*\relax
\artist{Gimpel, Jakob}.
\cdtitle{Concert Paraphrase of ``The Song of the Soldiers of the Sea''
  \(\textup{after} \artist{Jacques Offenbach}\)}.
\see{724}.

\cd\relax
\artist{Ginsburg, Grigory}.
\cdtitle{Beethoven/Liszt/Medtner/Miaskovsky/Tchaikovsky \: \track
  \C{Alexander Aliabiev} The Nightingale \arr{Franz Liszt} \; \track
  \C{Ludwig van Beethoven} Turkish March from ``Die Ruinen von Athen''
  \arr{Anton Rubinstein} \and Rondo a capriccio in~G, Op.~129 ``Rage
  Over a Lost Penny'' \; \track \C{Franz Liszt} Hungarian Rhapsody No.~2
  in C~sharp minor \and Hungarian Rhapsody No.~6 in D~flat\and Hungarian
  Rhapsody No.~10 in~E ``Preludio'' \and Hungarian Rhapsody No.~13 in
  A~minor \and Hungarian Rhapsody No.~17 in D~minor \and Hungarian
  Rhapsody No.~18 in F~sharp minor \; \track \C{Nicolai Medtner} Sonata
  reminiscenza in A~minor, Op.~38 No.~1 \; \track \C{Nicolai Miaskovsky}
  Prelude in B~flat minor, Op.~58 ``Song and Rhapsody'' \; \track
  \C{Nicol\`o Paganini} Grande \'etude d'apr\`es Paganini No.~5 ``La
  Chasse'' \arr{Franz Liszt} \; \track \C{Serge Prokofiev} Piano Sonata
  No.~3 in A~minor, Op.~28 \; \track \C{Franz Schubert} St\"andchen
  \arr{Franz Liszt} \; \track \C{Peter Ilyich Tchaikovsky} Polonaise
  from ``Eugene Onegin'' \arr{Franz Liszt} \and ``Eugene Onegin''
  Paraphrase \arr{Paul Pabst} \and Grande Sonate in~G, Op.~37}.
Volume~37 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 802-2}.

\cd*\relax
\artist{Giordani, Tommaso}.
\cdtitle{Duetto~II}.
\see{486}.

\cd\relax
\artist{Giuliani, Mauro}.
\cdtitle{Complete Guitar Concertos \and Variations on ``I bin a
  Kohlbauern Bub'' \and Gran Sonata Eroica in~A \and Introduction, Theme
  with Variations and Polonaise, Op.~65 \and Grande Ouverture, Op.~61
  \and La Melanconia \and Variations on a Theme by Handel, Op.~107 \and
  Variazioni concertanti, Op.~130}.
Pepe Romero and Celedonio Romero (Op.~130).
Academy of St~Martin in the Fields.
Sir Neville Marriner, cond.
Philips Classics, 1996 \cdnum[2]{454 262-2}.

\cd\relax
\artist{Glass, Philip}.
\cdtitle{\track Symphony No.~3 \; \track Interlude No.~1 from
  \textsc{the CIVIL warS} \; \track Mechanical Ballet from \emph{The
  Voyage} \; \track Interlude No.~2 from \textsc{the CIVIL warS} \;
  \track The Light}.
Stuttgart Chamber Orchestra and Vienna Radio Symphony Orchestra.
Dennis Russell Davies, cond.
Nonesuch \cdnum{70581-2}.

\cd*\relax
\artist{Glazunov, Alexander}.
\cdtitle{Concerto Ballata for cello and orchestra, Op.~108}.
\see{1315}.

\cd*\relax
\artist{Glazounov, Alexandre}.
\cdtitle{Concerto en Mi b\'emol, Op.~109}.
\see{151}.

\cd\relax
\artist{Glazunov, Alexander}.
\cdtitle{Concerto for Violin and Orchestra in A~Minor, Op.~82 \: \track
  \C{Dmitri Kabalevsky} Concerto for Violin and Orchestra, Op.~48 \;
  \track \C{Reinhold Gli\`ere} Romance for Violin and Orchestra, Op.~3}.
David Oistrakh.
State Symphony Orchestra of Russia.
Kiril Kondrashin and Dmitri Kabalevsky, cond.
Omega Classics, 1998 \cdnum{OCD~1025}.

\cd*\relax
\artist{Glazunov, Alexander}.
\cdtitle{Concerto in E~flat for alto saxophone and string orchestra}.
\see{744}.

\cd*\relax
\artist{Glazunov, Alexander}.
\cdtitle{\'El\'egie in D-flat, Op.~17 \(Pens\'ee \`a Liszt\) \and
  Entracte \(to scene~II\) from Raymonda}.
\see{929}.

\cd*\relax
\artist{Glazunov, Alexander}.
\cdtitle{Petit Adagio \(extrait des ``Saisons''\) \T{Marc-Andr\'e
  Hamelin}}.
\see{724}.

\cd*\relax
\artist{Glasunow, Alexander}.
\cdtitle{Stenka Razin, Symphonic Poem in B~minor, op.~13}.
\see{626}.

\cd*\relax
\artist{Glazunov, Alexander}.
\cdtitle{The Seasons, op.~67}.
\see{892}.

\cd*\relax
\artist{Glazunov, Alexander}.
\cdtitle{Violin Concerto, Op.~82}.
\see{766}.

\cd\relax
\artist{Glazunov, Alexander Konstantinovich}.
\cdtitle{Works for Cello and Orchestra \: \track Concerto Ballata for
  Cello and Orchestra, Op.~108 \; \track Chant du m\'enestrel for Cello
  and Orchestra, Op.~71 \; \track Two Pieces for Cello and Orchestra,
  Op.~20 \; \track \`A la m\'emoire de Gogol, Op.~87 \; \track \`A la
  m\'emoire d'un h\'eros, Op.~8}.
Volume~11 of \emph{Orchestral Works}.
Alexander Rudin.
Moscow Symphony Orchestra.
Igor Golovschin, cond.
Naxos, 1999 \cdnum{8.553932}.

\cd*\relax
\artist{Gli\`ere, Reinhold}.
\cdtitle{Concerto for Horn and Orchestra, Op.~91}.
\see{1143}.

\cd*\relax
\artist{Gli\`ere, Reinhold}.
\cdtitle{Romance for Violin and Orchestra, Op.~3}.
\see{648}.

\cd*\relax
\artist{Glinka, Mikhail}.
\cdtitle{Russlan and Ludmilla: Overture}.
\see{1137}.

\cd*\relax
\artist{Glinka, Michail Ivanovich}.
\cdtitle{Sonata for viola and piano}.
\see{1699}.

\cd*\relax
\artist{Gluck, Christoph Willibald}.
\cdtitle{Alceste: Overture}.
\see{628}.

\cd*\relax
\artist{Gluck, Christoph Willibald}.
\cdtitle{Gavotte in~A \(\from Paride ed Elena\)}.
\see{775}.

\cd*\relax
\artist{Godowsky, Franz Schubert/Leopold}.
\cdtitle{Morgengruss \(from ``Die sch\"one M\"ullerin''\) \and Gute
  Nacht \(from ``Winterreise''\)}.
\see{650}.

\cd*\relax
\artist{Godowsky, Leopold}.
\cdtitle{Alt Wien}.
\see{724}.

\cd\relax
\artist{Godowsky, Leopold}.
\cdtitle{Beethoven/Chopin/Grieg/Liszt/Schumann \: \track \C{Fr\'ed\'eric
  Chopin} Nocturne No.~19 in E~minor, Op.~72, No.~1 \and Nocturne No.~1
  in B~flat minor, Op.~9, No.~1 \and Nocturne No.~2 in E~flat, Op.~9,
  No.~2 \and Nocturne No.~4 in~F, Op.~15, No.~1 \and Nocturne No.~5 in
  F~sharp, Op.~15, No.~2 \and Nocturne No.~7 in C~sharp minor, Op.~27,
  No.~1 \and Nocturne No.~8 in D~flat, Op.~27, No.~2 \and Nocturne No.~9
  in~B, Op.~32, No.~1 \and Nocturne No.~11 in G~minor, Op.~37, No.~1
  \and Nocturne No.~12 in~G, Op.~37, No.~2 \and Nocturne No.~14 in
  F~sharp minor, Op.~48, No.~2 \and Nocturne No.~15 in F~minor, Op.~55,
  No.~1 \and Etude in G~flat, Op.~10, No.~5 ``Black Keys'' \and Etude in
  G~flat, Op.~25, No.~9 ``Butterfly'' \and Scherzo No.~4 in~E, Op.~54
  \and Piano Sonata No.~2 in B~flat minor, Op.~35 \; \track \C{Franz
  Schubert/Leopold Godowsky} Morgengruss \(from ``Die sch\"one
  M\"ullerin''\) \and Gute Nacht \(from ``Winterreise''\) \; \track
  \C{Giuseppe Verdi/Franz Liszt} ``Rigoletto'' Paraphrase \; \track
  \C{Robert Schumann} Carnaval \; \track \C{Ludwig van Beethoven} Piano
  Sonata in E~flat, Op.~81a ``Les adieux'' \; \track \C{Edvard Grieg}
  Ballade in G~minor, Op.~24}.
Volume~38 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456}.

\cd*\relax
\artist{Godowsky, Leopold}.
\cdtitle{Symphonic Metamorphosis on Themes from ``Die Fledermaus'' \and
  St\"andchen}.
\see{623}.

\cd*\relax
\artist{Godowsky, Leopold}.
\cdtitle{Toccata in G~flat major, Op~13}.
\see{726}.

\cd\relax
\artist{Goerne, Matthias}.
\cdtitle{Arias}.
Dorothea R\"oschmann (soprano).
Swedish Radio Symphony Orchestra.
Manfred Honeck, cond.
The Decca Record Company, 2000 \cdnum{289 467 263-2}.

\cd\relax
\artist{Golden Bough}.
\cdtitle{Beyond the Shadows}.
ARC Music, 1989 \cdnum{EUCD 1092}.

\cd\relax
\artist{Golden Bough}.
\cdtitle{Golden Bough}.
ARC Music, 1990 \cdnum{EUC 1123}.

\cd\relax
\artist{Goldmark, Karl}.
\cdtitle{Orchestral Works \: \track Overture: Im Fr\"uhling, Op.~36 \;
  \track Rustic Wedding Symphony, Op.~26 \; \track Overture: In Italien,
  Op.~49}.
National Symphony Orchestra of Ireland.
Stephen Gunzenhauser, cond.
Naxos, 1995 \cdnum{8.550745}.

\cd*\relax
\artist{Goldstein, Perry}.
\cdtitle{Blow!}
\see{50}.

\cd*\relax
\artist{Goldstein, Perry}.
\cdtitle{Noir}.
\see{1606}.

\cd*\relax
\artist{Gompper, David K.}
\cdtitle{Crossed \emph{for violin, saxophone and piano}}.
\see{1429}.

\cd\relax
\artist{G\'orecki, Henryk}.
\cdtitle{Symphony No.~3, Op.~36 \(1976\)}.
Dawn Upshaw.
London Sinfonietta.
David Zinman, cond.
Elektra/Nonesuch, 1992 \cdnum{9 79282-2}.

\cd\relax
\artist{Gothoni, Ralf}.
\cdtitle{Der Ochs und sein Hirte}.
Soile Isokoski (soprano), Jorma Hynninen (baritone), Jan S\"oderblom
  (violin), Ilari Angervo (viola), Jan-Erik Gustafsson (cello), Marko
  Yl\"onen (cello) and Heini K\"arkk\"ainen (piano).
Ondine, 1994 \cdnum{832-2}.

\cd*\relax
\artist{Gottschalk, Arthur}.
\cdtitle{Shall We Gather \(In memoriam Arnett Cobb\) for Alto Saxophone
  and Electroacoustic Sounds}.
\see{23}.

\cd\relax
\artist{G\"otz, N\'andor and Bal\'azs Szokolay}.
\cdtitle{Satie-Xophone}.
Hungaroton Classic, 1998 \cdnum{HCD~31763}.

\cd\relax
\artist{Gould, Glenn}.
\cdtitle{Byrd/Gibbons/Haydn/Mozart/Prokofiev/Strauss \: \track \C{Berg,
  Alban} Piano Sonata, Op.~1 \; \track \C{Bizet, Georges} Variations
  chromatiques \(de concert\) \; \track \C{Byrd, William} First Pavan
  and Galliard \and Hughe Ashton's Ground \and Sixth Pavan and Galliard
  \and A Voluntary \and Sellinger's Round \; \track \C{Gibbons, Orlando}
  Fantasy in~C \and Allemande \(Italian Ground\) \and ``Lord of
  Salisbury'' Pavan and Galliard \; \track \C{Haydn, Joseph} Sonata in
  E~flat, H.~XVI:49 \; \track \C{Mozart, Wolfgang Amadeus} Fantasia
  \(Prelude\) and Fugue in~C, KV~394 \; \track \C{Prokofiev, Sergei}
  Piano Sonata No.~7, Op.~83 \; \track \C{Scarlatti, Domenico} Sonata
  in~D, K.~430 \(L.~463\) \and Sonata in D~minor, K.~9 \(L.~413\) \and
  Sonata in~G, K.~13 \(L.~486\) \; \track \C{Scriabin, Alexander} 2
  Morceaux, Op.~57 \; \track \C{Strauss, Richard} Five Piano Pieces,
  Op.~3}.
Volume~39 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 808-2}.

\cd\relax
\artist{Gould, Glenn}.
\cdtitle{The Glenn Gould Legacy, Volume~2 \: \track \C{Ludwig van
  Beethoven} Concerto No.~1 for Piano and Orchestra in C~major, op.~15
  \and Concerto No.~2 for Piano and Orchestra in B~flat major, op.~19
  \and Sonata No.~30 in E~major, op.~109 \and Sonata No.~31 in A~flat
  major, op.~110 \and Sonata No.~32 in C~minor, op.~111 \; \track
  \C{Joseph Haydn} Sonata No.~59, Hob.~SVI/49 \; \track \C{Wolfgang
  Amadeus Mozart} Sonata No.~10 in C~major, K.~330 \and Fantasia and
  Fugue in C~major, K.~394}.
CBS, 1985 \cdnum[3]{M3K 39036}.

\cd*\relax
\artist{Gould, Morton}.
\cdtitle{Diversions}.
\see{799}.

\cd\relax
\artist{Gounod, Charles}.
\cdtitle{Faust}.
Jerry Hadley, Cecilia Gasdia and Samuel Ramey.
Chorus and Orchestra of Welsh National Opera.
Carlo Rizzi, cond.
Teldec Classics, 1994 \cdnum[3]{4509-90872-2}.

\cd\relax
\artist{Grainger (basson), Bruce, Gail Niwa (piano) and Gary Stucka
  (cello)}.
\cdtitle{Music for bassoon, piano and cello \: \track \C{Alvin Etler}
  Sonata for Bassoon and Piano \; \track \C{Edward Elgar} ``Romance,''
  Op.~62 \; \track \C{Camille Saint-Sa\"ens} Sonata for Bassoon and
  Piano in~G, Op.~168 \; \track \C{Romeo Cascarino} Sonata for Bassoon
  and Piano \; \track \C{Wolfgang Amadeus Mozart} Sonata for Bassoon and
  Cello in B-Flat, K.~292 \; \track \C{Paul Hindemith} Sonata for
  Bassoon and Piano \; \track \C{Roger Boutry} ``Interferences'' for
  Bassoon and Piano}.
Centaur, 1995 \cdnum{CRC~2244}.

\cd\relax
\artist{Grainger, Percy}.
\cdtitle{Jungle Book}.
Libby Crabtree (soprano), John Mark Ainsley (tenor) and David
  Wilson-Johnson (baritone).
Polyphony.
Stephen Layton, cond.
Hyperion, 1996 \cdnum{CDA66863}.

\cd\relax
\artist{Grainger, Percy}.
\cdtitle{Piano Music}.
Marc-Andr\'e Hamelin.
Hyperion, 1996 \cdnum{CDA66884}.

\cd*\relax
\artist{Grainger, Percy}.
\cdtitle{The Warriors}.
\see{795}.

\cd*\relax
\artist{Granados, Enrique}.
\cdtitle{Goyescas}.
\see{12}.

\cd*\relax
\artist{Granados, Enrique}.
\cdtitle{Intermezzo from Goyescas}.
\see{902}.

\cd*\relax
\artist{Granados, Enrique}.
\cdtitle{Quejas \'o la maja y el ruise\~nor \(from Goyescas\)}.
\see{770}.

\cd*\relax
\artist{Granados, Enrique}.
\cdtitle{Quejas \'o la maja y el ruis\~nor}.
\see{45}.

\cd*\relax
\artist{Granados, Enrique}.
\cdtitle{Spanish Dance, Op.~37 No.~5 ``Andaluza'' \and Goyescus}.
\see{477}.

\cd*\relax
\artist{Grasse, Edwin}.
\cdtitle{Wellenspiel}.
\see{245}.

\cd*\relax
\artist{Grassel, Timothy}.
\cdtitle{Reminiscences}.
\see{1161}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{American Beauty}.
Warner Brothers, November 1970 \cdnum{1893-2}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Anthem of the Sun}.
Warner Brothers, July 1971 \cdnum{1749-2}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Aoxomoxoa}.
Warner Brothers, September 1971 \cdnum{1790-2}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Bear's Choice: History of the Grateful Dead, Volume~1}.
Warner Brothers, July 1973 \cdnum{2721-2}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Blues For Allah}.
Grateful Dead Productions, September 1975 \cdnum{GDCD~4001}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Built to Last}.
Arista, October 1989 \cdnum{ARCD-8575}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Dead Set}.
Arista, August 1981 \cdnum{A2CD-8522}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Dick's Picks, Volume~One}.
Arista Records, 1993 \cdnum[2]{GDCD~40182}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Dozin' at the Knick}.
Grateful Dead Productions, October 1990/1996 \cdnum[3]{GDCD~4025}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Europe~'72}.
Warner Brothers, November 1972 \cdnum[2]{2668-2}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Fallout from the Phil Zone}.
Arista, June 1997 \cdnum{GDCD~4052}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Fillmore East 2-11-69}.
Grateful Dead Records, 1997 \cdnum[2]{GDCD~4054}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{From the Mars Hotel}.
Grateful Dead Productions, June 1974/1989 \cdnum{GDCD~4007}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Go to Heaven}.
Arista, April 1980 \cdnum{ARCD 8181}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Grateful Dead \(Skull \& Roses\)}.
Warner Brothers, October 1971 \cdnum{1935-2}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Gray Folded}.
Swell/Artifact, 1996 \cdnum[2]{S/A 1969--1996}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Hundred Year Hall}.
Grateful Dead Productions, September 1995 \cdnum[2]{GDCD~40202}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{In the Dark}.
Arista, July 1987 \cdnum{ARCD 8452}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{One from the Vault}.
Grateful Dead Records, 1991 \cdnum[2]{GDCD~40132}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Reckoning}.
Arista, April 1981 \cdnum{A2CD-8523}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Shakedown Street}.
Arista Records, November 1978 \cdnum{ARCD~8228}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Steal Your Face!}
Grateful Dead Records, June 1976 \cdnum[2]{GDCD~4006}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Terrapin Station}.
Arista Records, July 1977 \cdnum{ARCD~8065}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Terrapin Station}.
Grateful Dead Records, October 1997 \cdnum[3]{GDCD~4055}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{The Grateful Dead}.
Warner Brothers, March 1967 \cdnum{1689-2}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Two from the Vault}.
Grateful Dead Records, 1992 \cdnum[2]{GDCD~40162}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Wake of the Flood}.
Grateful Dead Productions, November 1973 \cdnum{GDCD~4002}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{What a Long Strange Trip It's Been: The Best of the Grateful
  Dead}.
Warner Brothers, 1977 \cdnum[2]{3091-2}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Without a Net}.
Arista Records, 1990 \cdnum[2]{ACD2-8634}.

\cd\relax
\artist{Grateful Dead, The}.
\cdtitle{Workingman's Dead}.
Warner Brothers, May 1970 \cdnum{1869-2}.

\cd*\relax
\artist{Graun, Johann Gottlieb}.
\cdtitle{Concerto in C~minor for Oboe, Strings and Continuo \and
  Concerto in G~minor for Oboe, Strings and Continuo \and}.
\see{783}.

\cd*\relax
\artist{Green, Edward}.
\cdtitle{Concerto for Alto Saxophone and Strings \and Sextet for Alto
  Saxophone and Brass Quintet}.
\see{23}.

\cd\relax
\artist{Green Linnet}.
\cdtitle{Flight of the Green Linnet}.
Rykodisc, 1988 \cdnum{RCD 20075}.

\cd\relax
\artist{Green Linnet}.
\cdtitle{Heart of the Gaels}.
Green Linnet, 1992 \cdnum{GLCD 105}.

\cd\relax
\artist{Green Linnet}.
\cdtitle{The Celts Rise Again}.
Green Linnet, 1990 \cdnum{GLCD 104}.

\cd\relax
\artist{Green Linnet Records}.
\cdtitle{The Twentieth Anniversary Collection}.
Green Linnet, 1996 \cdnum[2]{GLCD~106}.

\cd\relax
\artist{Greenslade, Dave}.
\cdtitle{From the Discworld}.
Virgin Records, 1994 \cdnum{CDV~2738}.

\cd*\relax
\artist{Gregory, Will}.
\cdtitle{Hoe down}.
\see{35}.

\cd*\relax
\artist{Grieg, Edvard}.
\cdtitle{Ballade in G~minor, Op.~24}.
\see{650}.

\cd*\relax
\artist{Grieg, Edvard}.
\cdtitle{Butterfly \(\from Lyric Pieces, Op.~43\)}.
\see{775}.

\cd\relax
\artist{Grieg, Edvard}.
\cdtitle{Complete Music with Orchestra \: \track Concerto for Piano and
  Orchestra in A~minor, op.~16 \; \track In Autumn, op.~11 \; \track
  Symphonic Dances, op.~64 \; \track From Holberg's Time, op.~40 \;
  \track Two Elegiac Melodies, op.~34 \; \track Two Melodies, op.~53 \;
  \track Two Nordic Melodies, op.~63 \; \track Two Lyric Pieces, op.~68
  \; \track Lyric Suite, op.~54 \; \track Peer Gynt, op.~23 \; \track
  Sigurd Jorsalfar, op.~22 \; \track Funeral March in Memory of Rikard
  Nordraak \; \track Norwegian Dances, op.~35 \; \track Symphony in
  C~minor \; \track Landkjenning, op.~31 \; \track Olav Trygvason,
  op.~50 \; \track Old Norwegian Melody with Variations, op.~51 \;
  \track Songs with Orchestra \; \track Den Bergtekne, op.~32 \; \track
  Foran Sydens kloster, op.~20 \; \track Bergliot, op.~42}.
Deutsche Grammophon, 1993 \cdnum[6]{437 842-2}.

\cd*\relax
\artist{Grieg, Edvard}.
\cdtitle{Lyric Pieces \(excerpts\)}.
\see{643}.

\cd*\relax
\artist{Grieg, Edvard}.
\cdtitle{Lyric Pieces, Op.~43}.
\see{911}.

\cd\relax
\artist{Grieg, Edvard}.
\cdtitle{Lyrische St\"ucke}.
Emil Gilels.
Deutsche Grammophon, 1974 \cdnum{449 721-2}.

\cd*\relax
\artist{Grieg, Edvard}.
\cdtitle{Norwegian Folk Songs, Op.~66 \and Peasant Dances, Op.~72}.
\see{28}.

\cd*\relax
\artist{Grieg, Edvard}.
\cdtitle{Norwegian March \(Gangar\), Op.~54, No.~2}.
\see{632}.

\cd*\relax
\artist{Grieg, Edvard}.
\cdtitle{Piano Concerto in A~minor, Op.~16}.
\see{1196}.

\cd*\relax
\artist{Grieg, Edvard}.
\cdtitle{Piano Concerto in A~minor, Op.~16}.
\see{1319}.

\cd*\relax
\artist{Grieg, Edvard}.
\cdtitle{Piano Concerto in A~minor, Op.~16}.
\see{967}.

\cd*\relax
\artist{Grieg, Edvard}.
\cdtitle{Piano Concerto in A~minor, op.~16}.
\see{629}.

\cd*\relax
\artist{Grieg, Edvard}.
\cdtitle{Piano Concerto in A~minor, Op.~16}.
\see{988}.

\cd\relax
\artist{Grieg, Edvard}.
\cdtitle{Piano Music, Volume~1 \: \track Sigurd Jorsalfar, Op.~22 \;
  \track Peer Gynt, Suite No.~1, Op.~46 \; \track Peer Gynt, Suite
  No.~2, Op.~55 \; \track To stykker fra Olav Trygvason, Op.~50 \;
  \track Bergliot, Op.~42}.
Einar Steen-N{\o}kleberg (piano) and Rut Tellefsen and Per Tofte
  (narrators).
Chamber Choir of the Norwegian State Institute of Music.
Stefan Schi{\o}ll, cond.
Naxos, 1995 \cdnum{8.553397}.

\cd\relax
\artist{Grieg, Edvard}.
\cdtitle{Piano Sonata in E~minor, op.~7 \and Poetic Tone-pictures,
  op.~3, nos.~4, 5, and~6 \and Album Leaves, op. 28, nos.~1 and~4 \and
  Agitato \and Lyric Pieces, op.~43 \and Lyric Pieces, op.~54}.
Leif Ove Andsnes.
Virgin Classics, 1993 \cdnum{CDC~7 59300~2}.

\cd\relax
\artist{Griffes, Charles Tomlinson}.
\cdtitle{Complete Piano Works, Volume~1 \: \track Sonata \; \track Three
  Tone-Pictures, Opus~5 \; \track De Profundis \; \track Roman Sketches,
  Opus~7 \; \track A Winter Landscape \; \track Rhapsody in B~minor \;
  \track Barcarolle \(``Belle Nuit, o Nuit d'Amour''\) from Offenbach's
  ``Les Contes d'Hoffmann'' \; \track Legend in F~sharp minor \; \track
  Prelude in B~minor}.
Michael Levin.
Naxos, 1999 \cdnum{8.559023}.

\cd*\relax
\artist{Griffin, John C.}
\cdtitle{Suite for Solo Saxophone}.
\see{1429}.

\cd\relax
\artist{Griffith, Nanci}.
\cdtitle{Flyer}.
Elektra, 1994 \cdnum{61681-2}.

\cd\relax
\artist{Griffith, Nanci}.
\cdtitle{Late Night Grande Hotel}.
MCA Records, 1991 \cdnum{MCAD-10306}.

\cd\relax
\artist{Griffith, Nanci}.
\cdtitle{Lone Star State of Mind}.
MCA Records, 1987 \cdnum{MCAD-31300}.

\cd\relax
\artist{Griffith, Nanci}.
\cdtitle{Once in a Very Blue Moon}.
Rounder Records, 1984/1986 \cdnum{Philo CD~1096}.

\cd\relax
\artist{Griffith, Nanci}.
\cdtitle{One Fair Summer Evening}.
MCA Records, 1988 \cdnum{MCAD-42255}.

\cd\relax
\artist{Griffith, Nanci}.
\cdtitle{Other Voices/Other Rooms}.
Elektra, 1993 \cdnum{9 61464-2}.

\cd\relax
\artist{Griffith, Nanci}.
\cdtitle{Storms}.
MCA Records, 1989 \cdnum{MCAD-6319}.

\cd\relax
\artist{Griffith, Nanci}.
\cdtitle{There's a Light Beyond These Woods}.
Rounder Records, 1978/1986 \cdnum{Philo CD~1097}.

\cd\relax
\artist{Gruber, HK}.
\cdtitle{Frankenstein!! \and Nebelsteinmusik \(Violin Concerto No.~2\)
  \and Drei Mob St\"ucke \and Drei Songs aus ``Gomorra''}.
HK Gruber (chansonnier~i,~iv) and Ernst Kovacic (violin~ii).
London Mob Ensemble (iii,~iv) and Camerata Academica Salzburg (i,~ii).
HK Gruber (iii,~iv) and Franz Welser-M\"ost (i,~ii), cond.
EMI Classics, 1997 \cdnum{7243 5 56441 2~1}.

\cd\relax
\artist{Guaraldi, Vince}.
\cdtitle{Oh Good Grief!}
Warner Brothers, 1968 \cdnum{1747-2}.

\cd\relax
\artist{Guarnieri, Camargo}.
\cdtitle{Violin Sonatas Nos.~2, 3, and~7 \and Can\c{c}\~ao sertaneja}.
Lavard Skou Larsen (violin) and Alexander M\"ullenbach (piano).
Marco Polo, 1997 \cdnum{8.223885}.

\cd*\relax
\artist{Gubaidulina, Sofia}.
\cdtitle{Duo-Sonata for two baritone saxophones \(1977\)}.
\see{484}.

\cd\relax
\artist{Guettel, Adam}.
\cdtitle{Myths and Hymns}.
Nonesuch Records, 1999 \cdnum{79530-2}.

\cd*\relax
\artist{Guilmant, Alexandre}.
\cdtitle{Morceau symphonique \and Chorale \(Kirchenordnung
  Braunschweig\)}.
\see{1599}.

\cd\relax
\artist{Gulda, Friedrich}.
\cdtitle{Beethoven/Chopin/Strauss/Weber \: \track \C{Ludwig van
  Beethoven} Piano Concerto No.~1 in~C, Op.~15 \; \track \C{Fr\'ed\'eric
  Chopin} Piano Concerto No.~1 in E~minor, Op.~11 \and Ballade No.~1 in
  G~minor, Op.~23 \and Ballade No.~2 in~F, Op.~38 \and Ballade No.~3 in
  A~flat, Op.~47 \and Ballade No.~4 in F~minor, Op.~52 \; \track \C{G.
  Shearing and B. Y. Forster} Lullaby of Birdland \; \track \C{Richard
  Strauss} Burleske \; \track \C{Carl Maria von Weber} Konzertst\"uck in
  F~minor, Op.~79}.
Volume~41 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 820-2}.

\cd\relax
\artist{Gulda, Friedrich}.
\cdtitle{Debussy/Ravel \: \track \C{Claude Debussy} Pr\'eludes, Book~I
  \and Pr\'eludes, Book~II \and L'isle joyeuse \and Reflets dans l'eau
  \(\from ``Images,'' Book~I\) \and Soiree dans Grenade \(\from
  ``Estampes''\) \and Suite bergamasque \and Pour le piano, Suite \;
  \track \C{Maurice Ravel} Sonatine \and Valses nobles et sentimentales
  \and Gaspard de la nuit}.
Volume~40 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 81-2}.

\cd\relax
\artist{Guthrie, Arlo}.
\cdtitle{Hobo's Lullaby}.
KOCH Records, 1997 \cdnum{KOC-CD-7951}.
First released in 1972 by Warner Brothers.

\cd\relax
\artist{Gwozdz, Lawrence}.
\cdtitle{Simply Gifts \: \track \C{Stephen Dankner} Sonata for Alto
  Saxophone and Piano \; \track \C{Zden\v{e}k Luk\'a\v{s}} Lento
  drammatico \; \track \C{Stephen Suber} Angels \; \track \C{Robert
  Starer} Five Preludes \; \track \C{Walter Hartley} Dance Suite for
  Violin, Alto Saxophone, and Piano}.
Lois Leventhal (piano) and Stephen Redfield (violin).
Albany Records, 2000 \cdnum{Troy~378}.

\cd*\relax
\artist{Hacquart, Carolus}.
\cdtitle{Sonata Decima from \emph{Harmonia Parnassia}}.
\see{1184}.

\cd\relax
\artist{Haebler, Ingrid}.
\cdtitle{Bach/Chopin/Haydn/Mozart/Schubert \: \track \C{Johann Sebastian
  Bach} French Suite No.~6 in~E, BWV~817 \; \track \C{Joseph Haydn}
  Andante con variazioni in F~minor, Hob.~XVII:6 \and Piano Concerto
  in~D, Hob.~XVIII:11 \; \track \C{Wolfgang Amadeus Mozart} Piano
  Concerto No.~18 in B~flat, KV~456 \and Nine Variations in~D, KV~573 on
  a minuet by Jean-Pierre Duport \and Piano Sonata in~D, KV~576 \;
  \track \C{Franz Schubert} Piano Sonata in A~minor, D.~784 \; \track
  \C{Robert Schumann} Kinderszenen, Op.~15 \; \track \C{Fr\'ed\'eric
  Chopin} Waltz in E~flat, Op.~18 ``Grande Valse brillante''}.
Volume~42 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 823-2}.

\cd*\relax
\artist{Haendel, Georg Friedrich}.
\cdtitle{Almira}.
\see{10}.

\cd\relax
\artist{Hagen Quartett, The}.
\cdtitle{Verdi, Puccini, Muzio: Werke f\"ur Streichquartett \: \track
  \C{Giuseppe Verdi} Streichquartett e-moll \; \track \C{Giacomo
  Puccini} Crisantemi \; \track \C{Giuseppe Verdi and Emanuele Muzio}
  Luisa Miller}.
Deutsche Grammophon, 1995 \cdnum{447 069-2}.

\cd*\relax
\artist{Halffter, Ernesto}.
\cdtitle{``Sonatina'' \(Ballet\)}.
\see{477}.

\cd\relax
\artist{Hamelin, Marc-Andr\'e}.
\cdtitle{\track \C{Adolf von Henselt} Piano Concerto in F~minor op~16
  \and Variations de Concert op~11 \; \track \C{Charles-Valentin Alkan}
  Concerto da Camera in C~sharp minor op~10 no~2 \and Concerto da Camera
  in A~minor op~10 no~1}.
Volume~7 of \emph{The Romantic Piano Concerto}.
BBC Scottish Symphony Orchestra.
Martyn Brabbins, cond.
Hyperion, 1994 \cdnum{CDA66717}.

\cd\relax
\artist{Hamelin, Marc-Andr\'e}.
\cdtitle{\track \C{Joseph Marx} Romantisches Klavierkonzert in E~major
  \; \track \C{Erich Wolfgang Korngold} Piano Concerto in C~sharp,
  Op~17}.
Volume~18 of \emph{The Romantic Piano Concerto}.
BBC Scottish Symphony Orchestra.
Osmo V\"ansk\"a, cond.
Hyperion, 1998 \cdnum{CDA66990}.

\cd\relax
\artist{Hamelin, Marc-Andr\'e}.
\cdtitle{Kaleidoscope \: \track \C{Edna Bentz Woods} Valse Phantastique
  \; \track \C{Franz Behr} Polka de~W.R. \T{Sergei Rachmaninov} \;
  \track \C{Josef Hofmann} Nocturne \(``Complaint''\) \and Kaleidoskop,
  Op.~40, No.~4 \; \track Etude No.~3 \(d'apr\`es Paganini-Liszt\) \;
  \track \C{Felix Blumenfeld} Etude pour la main gauche seule, Op.~36 \;
  \track \C{Jakob Gimpel} Concert Paraphrase of ``The Song of the
  Soldiers of the Sea'' \(\textup{after} \artist{Jacques Offenbach}\) \;
  \track Etude No.~6: Essercizio per pianoforte \(Omaggio a Domenico
  Scarlatti\) \; \track \C{Jules Massenet} Valse folle \; \track
  \C{Moritz Moszkowski} Etude in A~flat minor, Op.~72, No.~13 \; \track
  \C{Francis Poulenc} Intermezzo in A~flat \; \track \C{Leopold
  Godowsky} Alt Wien \; \track \C{Aleksander Micha{\l}owski} Etude
  d'apr\`es l'Impromptu en la b\'emol majeur de Fr.~Chopin, Op.~29 \;
  \track \C{Arthur (Vincent) Louri\'e} Gigue \; \track \C{Emile-Robert
  Blanchet} Au jardin du vieux s\'erail \(Andrianople\), Op.~18, No.~3
  \; \track \C{Alfredo Casella} Deux Contrastes \; \track \C{John
  Vallier} Toccatina \; \track \C{Alexander Glazunov} Petit Adagio
  \(extrait des ``Saisons''\) \T{Marc-Andr\'e Hamelin} \; \track
  \C{Nikolai Kapustin} Toccatina, Op.~36}.
Hyperion, 2001 \cdnum{CDA67275}.

\cd\relax
\artist{Hamelin, Marc-Andr\'e}.
\cdtitle{Live at Wigmore Hall \: \track \C{Ludwig van Beethoven} First
  movement from Piano Concerto No~3 in C~minor, Op~37, transcribed and
  with cadenza by Charles-Valentin Alkan \; \track \C{Fr\'ed\'eric
  Chopin} Romanza from Piano Concerto No~1 in E~minor, Op~11,
  transcribed by Mily Alexeyevich Balakirev \; \track
  \C{Charles-Valentin Alkan} Trois Grandes \'Etudes, Op~76 \; \track
  \C{Ferruccio Busoni} Sonatina No~6: Kammer-Fantasie \"uber Carmen,
  BV284 \; \track \C{Nikolai Medtner} Danza festiva, Op~38 No~3
  \(Forgotten Meolodies, Vol~I\)}.
Hyperion, 1994 \cdnum{CDA66765}.

\cd\relax
\artist{Hamelin, Marc-Andr\'e}.
\cdtitle{The Composer-Pianists \: \track \C{Leopold Godowsky} Toccata in
  G~flat major, Op~13 \; \track \C{Alexander Scriabin} Po\`eme tragique,
  Op~34 \and Deux Po\`emes, Op.~71 \; \track \C{Marc-Andr\'e Hamelin}
  Etude No~9 \and Etude No~10 \and Prelude and Fugue \(Etude No~12\) \;
  \track \C{Samuel Feinberg} Bach Sch\"ubler Chorale No~6
  \(transcription\) \and Berceuse Op~19a \; \track \C{Charles-Valentin
  Alkan} Haydn Adante from Symphony No~94 \(transcription\) \and
  Esquisses Op~63, Nos.~46 and~47 \; \track \C{Ferruccio Busoni}
  Fantasia nach J~S Bach \; \track \C{Sergei Rachmaninov} Moment Musical
  in E~flat major, Op~16 No~2 \and Etude-Tableau in E~flat Op~33 No~4 \;
  \track \C{Nikolai Medtner} Improvisation No~1 in B~flat minor, Op~31
  No~1 \; \track \C{Kaikhosru Shapurji Sorabji} Pastiche on the Hindu
  Merchant's Song from ``Sadko'' by Rimsky-Korsakov}.
Hyperion, 1998 \cdnum{CDA67050}.

\cd\relax
\artist{Hampson, Thomas and Samuel Ramey}.
\cdtitle{No Tenors Allowed: Famous Italian Duets for Baritone and Bass}.
M\"unchner Rundfunkorchester.
Miguel G\'omez-Mart{\'\i}nez, cond.
Teldec Classics, 1999 \cdnum{0630-13149-2}.

\cd*\relax
\artist{Handel, G. F.}
\cdtitle{Trio Sonata in B-flat major, Op.~2 No.~3 for 2 Oboes and Basso
  Continuo \and}.
\see{784}.

\cd*\relax
\artist{H\"andel, Georg Friedrich}.
\cdtitle{Concerto grosso in D~major, op.~6 no.~5}.
\see{628}.

\cd*\relax
\artist{H\"andel, Georg Friedrich}.
\cdtitle{Messiah, Part the Second: Chorus ``Hallelujah!''}
\see{73}.

\cd\relax
\artist{Handel, George Frideric}.
\cdtitle{Complete Violin Sonatas \: \track Sonata in D~major, Op.~1
  No.~13 HWV~371 \; \track Sonata in F~major, Walsh Op.~1 No.~12 \;
  \track Sonata in D~minor, HWV~359a \; \track Sonata in A~major, Op.~1
  No.~3 HWV~361 \; \track Sonata in G~minor, Op.~1 No.~6 HWV~364 \;
  \track Sonata in A~major ``Roger'', Op.~1 No.~10 \; \track Sonata in
  E~major ``Roger'', Op.~1 No.~12 \; \track Sonata in G~major, HWV~358
  \; \track Andante in A~minor HWV~358 \; \track Allegro in C~minor
  HWV~408}.
Andrew Manze and Richard Egarr (harpsichord).
Harmonia Mundi, 2001 \cdnum{HMU 907259}.

\cd\relax
\artist{Handel, George Frideric}.
\cdtitle{Concerti grossi, Op.~3 \and Organ Concertos Op.~4 \and Concerto
  grosso in~F}.
Daniel Chorzempa.
English Chamber Orchestra and Concerto Amsterdam.
Raymond Leppard and Jaap Schr\"oder, cond.
Philips Classics, 1994 \cdnum[2]{442 263-2}.

\cd\relax
\artist{Handel, George Frideric}.
\cdtitle{Concerti Grossi, op.~6: ``Twelve Grand Concertos in Seven
  Parts''}.
The Academy of Ancient Music.
Andrew Manze, cond.
Harmonia Mundi, 1998 \cdnum[2]{HMU 907228.29}.

\cd\relax
\artist{Handel, George Frideric}.
\cdtitle{Handel Arias}.
Bryn Terfel.
Scottish Chamber Orchestra.
Sir Charles Mackerras, cond.
Deutsche Grammophon, 1997 \cdnum{453 480-2}.

\cd\relax
\artist{Handel, George Frideric}.
\cdtitle{Hercules}.
John Tomlinson, Anthony Rolfe Johnson, Sarah Walker, Jennifer Smith and
  Catherine Denley.
The Monterverdi Choir and the English Baroque Soloists.
John Eliot Gardiner, cond.
Archiv Produktion, 1983 \cdnum[2]{447 689-2}.

\cd\relax
\artist{Handel, George Frideric}.
\cdtitle{Keyboard Suites~I \: \track Suite No.~1 in~A \; \track Suite
  No.~2 in~F \; \track Suite No.~3 in~D~minor \; \track Suite No.~4
  in~E~minor \; \track Suite No.~5 in~E \; \track Suite No.~6 in~F~sharp
  minor \; \track Suite No.~7 in~G~minor \; \track Suite No.~8
  in~F~minor}.
Andrei Gavriolv and Sviatoslav Richter.
EMI Classics, 1996 \cdnum[2]{7243 5~69337~2 9}.

\cd\relax
\artist{Handel, George Frideric}.
\cdtitle{Keyboard Suites~II \: \track Suite No.~9 in~G~minor \; \track
  Suite No.~10 in~D~minor \; \track Suite No.~11 in~D~minor \; \track
  Suite No.~12 in~E~minor \; \track Suite No.~13 in~B~flat \; \track
  Suite No.~14 in~G \; \track Suite No.~15 in~D~minor \; \track Suite
  No.~16 in~G~minor \; \track \C{Ludwig van Beethoven} Piano Sonata
  No.~17 in D~minor, Op.~31, No.~2 ``The Tempest''}.
Andrei Gavriolv and Sviatoslav Richter.
EMI Classics, 1996 \cdnum[2]{7243 5~69340~2 3}.

\cd*\relax
\artist{Handel, George Frideric}.
\cdtitle{Larghetto \from Sonata, HWV~371}.
\see{1315}.

\cd\relax
\artist{Handel, George Frideric}.
\cdtitle{Messiah}.
Heather Harper (soprano), Helen Watts (contralto), John Wakefield
  (tenor) and John Shirley-Quirk (bass).
London Symphony Orchestra and Choir.
Sir Colin Davis, cond.
Philips Classics, 1993 \cdnum[2]{438 356-2}.

\cd\relax
\artist{Handel, George Frideric}.
\cdtitle{Organ Concertos, Opp.~4 and~7}.
Paul Nicholson (organ).
The Brandenburg Consort.
Roy Goodman, cond.
Hyperion, 1997 \cdnum[2]{CDA67291/2}.

\cd*\relax
\artist{Handel, George Frideric}.
\cdtitle{Passacaglia}.
\see{486}.

\cd\relax
\artist{Handel, George Frideric}.
\cdtitle{Saul}.
Donald McIntyre, Margaret Price, Sheila Armstrong, Ryland Davies, James
  Bowman and John Winfield.
Leeds Festival Chorus and the English Chamber Orchestra.
Sir Charles Mackerras, cond.
Archiv Produktion, 1973 \cdnum[3]{447 696-2}.

\cd*\relax
\artist{Handel, George Frideric}.
\cdtitle{Suite in D~minor, HWV~447}.
\see{632}.

\cd*\relax
\artist{Handel, George Frideric}.
\cdtitle{Suite No.~5 in E~Major, HWV~430 \and Chaconne in G~Major,
  HWV~435 \and Suite No.~3 in D~Minor, HWV~428 \and Suite No.~2 in
  F~Major, HWV~427}.
\see{1197}.

\cd*\relax
\artist{Handel, George Frideric}.
\cdtitle{Suite No.~5 in~E, HWV 430 ``The Harmonious Blacksmith''}.
\see{478}.

\cd\relax
\artist{Handel, George Frideric}.
\cdtitle{\track Theodora \; \track La Lucrezia \; \track Serse}.
Lorraine Hunt Lieberson.
Orchestra of the Age of Enlightenment.
Harry Bicket, cond.
Avie \cdnum{AV 0030}.

\cd\relax
\artist{Handel, George Frideric}.
\cdtitle{Water Music \(HWV 348--350\) \and The Alchymist \(HWV~43\) \and
  The Musick for the Royal Fireworks \(HWV~351\) \and Three concerti a
  due cori \(HWV 332--334\) \and Two arias for wind band \(HWV
  410--411\)}.
The Academy of Ancient Music.
Christopher Hogwood, cond.
The Decca Record Company, 1997 \cdnum[2]{455 709-2}.

\cd\relax
\artist{Handel, George Frideric}.
\cdtitle{Watermusick}.
Philharmonia Baroque Orchestra.
Nicholas McGegan, cond.
Harmonia Mundi, 2000 \cdnum{HMX~2907010}.

\cd\relax
\artist{Handel, George Frideric and Wolfgang Amadeus Mozart}.
\cdtitle{Acis und Galatea}.
Barbara Bonney, Jamie MacDougall, Markus Sch\"afer and John Tomlinson.
The English Concert and Choir.
Trevor Pinnock, cond.
Archiv Produktion, 1992 \cdnum[2]{447 700-2}.

\cd*\relax
\artist{Handel, George Friderick}.
\cdtitle{Sonata in G~minor}.
\see{500}.

\cd\relax
\artist{Hapa}.
\cdtitle{Hapa}.
Coconut Grove Records, 1992 \cdnum{CGRC~8191-2}.

\cd\relax
\artist{Hapa}.
\cdtitle{In the Name of Love}.
Coconut Grove Records, 1997 \cdnum{CG~8197-2}.

\cd\relax
\artist{Harle, John}.
\cdtitle{Saxophone Concertos \: \track \C{Claude Debussy} Rapsodie for
  alto saxophone and orchestra \; \track \C{Jacques Ibert} Concertino da
  camera for alto saxophone and eleven instruments \; \track \C{Heitor
  Villa-Lobos} Fantasia for soprano saxophone and chamber orchestra \;
  \track \C{Alexander Glazunov} Concerto in E~flat for alto saxophone
  and string orchestra \; \track \C{Richard Rodney Bennet} Concerto for
  alto saxophone and string orchestra \; \track \C{Dave Heath} Out of
  the Cool}.
Academy of St~Martin in the Fields.
Sir Neville Marriner, cond.
EMI Records, 1991 \cdnum{CDC~7 54301~2}.

\cd\relax
\artist{Harle, John}.
\cdtitle{Saxophone Works \: \track \C{Michael Nyman} Where the Bee
  Dances \; \track \C{Gavin Bryars} The Green Ray \; \track \C{Mike
  Westbrook} Bean Rows and Blues Shots}.
Bournemouth Sinfonietta.
Ivor Bolton, cond.
Argo/The Decca Record Company, 1992 \cdnum{443 847-2}.

\cd\relax
\artist{Harry Allen Quintet}.
\cdtitle{A Night at Bird Land}.
Nagel Heyer Records, 1994 \cdnum{CD~007}.
Recorded at the Birdland Jazzclub, Hamburg, November 19-20, 1993.

\cd*\relax
\artist{Hartley, Walter}.
\cdtitle{Dance Suite for Violin, Alto Saxophone, and Piano}.
\see{719}.

\cd*\relax
\artist{Hartley, Walter}.
\cdtitle{Sonata for Baritone Saxophone and Piano \(1976\)}.
\see{1601}.

\cd\relax
\artist{Haskil, Clara}.
\cdtitle{Beethoven/Mozart/Schubert/Schumann \: \track \C{Ludwig van
  Beethoven} Piano Sonata No.~17 in D~minor, Op.~31 No.~2 ``Tempest''
  \and Piano Sonata No.~18 in E~flat, Op.~31 No.~3 ``La Chasse'' \;
  \track \C{Wolfgang Amadeus Mozart} 12 Variations in~C, KV~265 on ``Ah,
  vous dirai-je, Maman'' \and Piano Sonata in~C, KV~330 \and 9
  Variations in~D, KV~573 on a minuet by Jean-Pierre Duport \and Piano
  Sonata in~F, KV~280 \; \track \C{Franz Schubert} Piano Sonata No.~21
  in B~flat, D.~960 \; \track \C{Robert Schumann} ``ABEGG'' Variations,
  Op.~1 \and Kinderszenen, Op.~15}.
Volume~44 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 829-2}.

\cd\relax
\artist{Haskil, Clara}.
\cdtitle{Mozart \: \C{Wolfgang Amadeus Mozart} Piano Concerto No.~13
  in~C, KV~415 \and Piano Concerto No.~20 in D~minor, KV~466 \and Piano
  Concerto No.~23 in~A, KV~488 \and Piano Concerto No.~24 in C~minor,
  KV~491 \and Piano Concerto No.~27 in~C, KV~595 \and Rondo for Piano
  and Orchestra in~A, KV~386}.
Volume~43 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 826-2}.

\cd\relax
\artist{Hay, Colin}.
\cdtitle{Going Somewhere}.
Compass Records, 2005 \cdnum{7~4406~2}.

\cd\relax
\artist{Hay, Colin}.
\cdtitle{Man @ Work}.
Compass Records, 2003 \cdnum{7~4365~2}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{6 Sonatas for Violin Solo with Bass Accompaniment, op.~23}.
Iidik\'o Hajdu (violin) and Gy\"orgy D\'eri (cello).
Hungaroton Classic, 1995 \cdnum{HCD 31474}.

\cd*\relax
\artist{Haydn, Joseph}.
\cdtitle{Andante con variazioni in F~minor, Hob.~XVII:6}.
\see{478}.

\cd*\relax
\artist{Haydn, Joseph}.
\cdtitle{Andante con variazioni in F~minor, Hob.~XVII:6 \and Piano
  Concerto in~D, Hob.~XVIII:11}.
\see{720}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{Complete Piano Trios}.
The Beaux Arts Trio, Menahem Pressler (piano), Isidore Cohen (violin)
  and Bernard Greenhose (violoncello).
Philips, 1991 \cdnum[9]{454 098-2}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{Concerto for Cello and Orchestra No.~1 in C major, Hob. VII:~1
  \and Concerto for Cello and Orchestra No.~1 in D major, Hob. VII:~2}.
Yo-Yo Ma.
English Chamber Orchestra.
Jos\'e-Luis Garcia, cond.
Sony, 1993 \cdnum{SK~36 674}.

\cd*\relax
\artist{Haydn, Joseph}.
\cdtitle{Concerto for Cello and Orchestra, op.~101}.
\see{1003}.

\cd*\relax
\artist{Haydn, Joseph}.
\cdtitle{Concerto in C~major for cello, Hob.~VIIb:1}.
\see{1141}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{Die Sch\"opfung}.
Luba Orgonasova (soprano), Joan Rodgers (soprano), John Mark Ainsley
  (tenor), Eike Wilm Schulte (bass) and Per Vollestad (bass).
Orchestra of the 18th Century.
Frans Br\"uggen, cond.
Philips Classics, 1995 \cdnum[2]{446 073-2}.

\cd*\relax
\artist{Haydn, Joseph}.
\cdtitle{Divertimento for Two Barytons}.
\see{619}.

\cd*\relax
\artist{Haydn, Joseph}.
\cdtitle{Piano Sonata in E~minor, Hob.~XVI:34 \and Piano Sonata in~E,
  Hob.~XVI:37}.
\see{579}.

\cd*\relax
\artist{Haydn, Joseph}.
\cdtitle{Piano Sonata in E~minor, Hob.~XVI:34 \and Piano Sonata in~G,
  Hob.~XVI:40 \and Piano Sonata in~D, Hob.~XVI:42 \and Piano Sonata in
  E~flat, Hob.~XVI:52}.
\see{337}.

\cd*\relax
\artist{Haydn, Joseph}.
\cdtitle{Piano Sonata in~C, Hob.~XVI:48}.
\see{1032}.

\cd*\relax
\artist{Haydn, Joseph}.
\cdtitle{Sonata in E~flat, H.~XVI:49}.
\see{658}.

\cd*\relax
\artist{Haydn, Joseph}.
\cdtitle{Sonata No.~59, Hob.~SVI/49}.
\see{659}.

\cd*\relax
\artist{Haydn, Joseph}.
\cdtitle{Streichquartette Op.~77, Nos.~1 and~2}.
\see{11}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{String Quartets Op.~20 ``Sun Quartets'', Nos.~1--3}.
The Kod\'aly Quartet.
Naxos, 1993 \cdnum{8.550701}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{String Quartets Op.~20 ``Sun Quartets'', Nos.~4--6}.
The Kod\'aly Quartet.
Naxos, 1993 \cdnum{8.550702}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{String Quartets Op.~33 ``Russian Quartets'', Nos.~1, 2 ``The
  Joke'' and~5 ``How do you do?''}
The Kod\'aly Quartet.
Naxos, 1994 \cdnum{8.550788}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{String Quartets Op.~33 ``Russian Quartets'', Nos.~3 ``The
  Bird'', 4, and~6}.
The Kod\'aly Quartet.
Naxos, 1994 \cdnum{8.550789}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{String Quartets Op.~76: No.~1, No.~2 \(``Fifths''\), No.~3
  \(``Emperor''\)}.
The Kod\'aly Quartet.
Naxos, 1989/1991 \cdnum{8.550314}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{String Quartets Op.~76: No.~4 \(``Sunrise''\), No.~5, No.~6}.
The Kod\'aly Quartet.
Naxos, 1989/1991 \cdnum{8.550315}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{String Quartets ``Prussian,'' Op.~50, Nos. 1--3}.
The Kod\'aly Quartet.
Naxos, 1998 \cdnum{8.553983}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{String Quartets ``Prussian,'' Op.~50, Nos. 4--6}.
The Kod\'aly Quartet.
Naxos, 1998 \cdnum{8.553984}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{\track Symphony No.~23 in G~Major \; \track Symphony No.~24 in
  D~Major \; \track Symphony No.~61 in D~Major}.
Northern Chamber Orchestra.
Nicholas Ward, cond.
Naxos, 1994 \cdnum{8.550723}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{The London Symphonies, Volume~I: Nos. 95, 96 \(``Miracle''\),
  98, 102, 103 \(``Drum Roll''\), and~104 \(``London''\)}.
The Royal Concertgebouw Orchestra.
Sir Colin Davis, cond.
Philips, 1994 \cdnum[2]{442 611-2}.

\cd\relax
\artist{Haydn, Joseph}.
\cdtitle{The London Symphonies, Volume~II: Nos. 93, 94 \(``Surprise''\),
  97, 99, 100 \(``Military\), and~101 \(``Clock''\)}.
The Royal Concertgebouw Orchestra.
Sir Colin Davis, cond.
Philips, 1994 \cdnum[2]{442 614-2}.

\cd*\relax
\artist{Haydn, Joseph}.
\cdtitle{Trumpet Concerto in E~flat major, H.~Viie/1}.
\see{1138}.

\cd*\relax
\artist{Haydn, Michael}.
\cdtitle{Adagio \from\ Notturno in F~Major, P.~106}.
\see{1619}.

\cd*\relax
\artist{Haydn, Michael}.
\cdtitle{Concerto in D~major for Alto Trombone}.
\see{963}.

\cd*\relax
\artist{Heath, Dave}.
\cdtitle{Out of the Cool}.
\see{744}.

\cd*\relax
\artist{Heath, D. C.}
\cdtitle{The Celtic Concerto for Soprano Saxophone and Strings}.
\see{1053}.

\cd*\relax
\artist{Heiden, Bernhard}.
\cdtitle{Solo for Alto Saxophone and Piano}.
\see{253}.

\cd*\relax
\artist{Heiden, Bernhard}.
\cdtitle{Solo for Alto Saxophone and Piano}.
\see{1603}.

\cd\relax
\artist{Heifetz, Jascha}.
\cdtitle{The Supreme \: \track \C{Johann Sebastian Bach} Chaconne
  \(\from Partita No.~2, BWV~1004\) \; \track \C{Johannes Brahms} Violin
  Concerto, Op.~77 \; \track \C{Peter Tchaikovsky} Violin Concerto,
  Op.~35 \; \track \C{Max Bruch} Schottische Fantasie, Op.~46 \; \track
  \C{Jean Sibelius} Violin Concerto, Op.~47 \; \track \C{Alexander
  Glazunov} Violin Concerto, Op.~82 \; \track \C{George Gershwin} 3
  Preludes}.
BGM Entertainment (RCA Red Seal), 2000 \cdnum[2]{74321-63470-2}.

\cd*\relax
\artist{Henselt, Adolf von}.
\cdtitle{Piano Concerto in F~minor op~16 \and Variations de Concert
  op~11}.
\see{722}.

\cd*\relax
\artist{Hento, H. Benne}.
\cdtitle{Nadine for Alto Saxophone and Band}.
\see{23}.

\cd\relax
\artist{Henze, Hans Werner}.
\cdtitle{Das Flo{\ss} der Medusa}.
Edda Moser (sopran), Dietrich Fischer-Dieskau (bariton) and Charles
  Regnier (sprecher).
Chor des norddeutschen Rundfunks, RIAS-Kammerchor, Mitglieder des
  Hamburger Knabenchors St.~Nikolai, and Sinfonieorchester des
  Norddeutschen Rundfunks.
Hans Werner Henze, cond.
Deutsche Grammophon, 1969/1996 \cdnum{449 871-2}.

\cd\relax
\artist{Henze, Hans Werner}.
\cdtitle{F\"unf neapolitanische Lieder \and Whispers from Heavenly Death
  \and Being Beauteous and Versuch \"uber Schweine}.
Dietrich Fischer-Dieskau (bariton), Edda Moser (sopran) and Roy Hart.
Instrumentalisten der Berliner Philharmoniker, des Philharmonischen
  Kammerorchesters Berlin; the Philip Jones Brass Ensemble, and the
  English Chamber Orchestra.
Hans Werner Henze and Richard Kraus, cond.
Deutsche Grammophon, 1958/1968/1996 \cdnum{449 869-2}.

\cd\relax
\artist{Henze, Hans Werner}.
\cdtitle{\track Sechs Ges\"ange aus dem Arabischen \; \track Three Auden
  Songs}.
Ian Bostridge (tenor) and Julius Drake (piano).
EMI Classics, 2001 \cdnum{7243 5~57112~2~9}.

\cd\relax
\artist{Hess, Myra}.
\cdtitle{Bach-Hess/Beethoven/Brahms/Schumann \: \track \C{Johann
  Sebastian Bach} Jesu, Joy of Man's Desiring \arr{Myra Hess} \; \track
  \C{Ludwig van Beethoven} Piano Sonata in~E, Op.~109 \and Piano Sonata
  in A~flat, Op.~110 \; \track \C{Johannes Brahms} Waltz in A~flat,
  Op.~39 No.~15 \and Intermezzo in~C, Op.~119 No.~3 \; \track \C{Enrique
  Granados} Quejas \'o la maja y el ruise\~nor \(from Goyescas\) \;
  \track \C{Felix Mendelssohn Bartholdy} Lieder ohne Worte, Op.~102
  No.~5 \; \track \C{Domenico Scarlatti} Sonata in C~minor, K.~11 \and
  Sonata in~G, K.~14 \; \track \C{Robert Schumann} Carnaval, Op.~9 \and
  Piano Concerto in A~minor, Op.~54 \and Symphonische Et\"uden}.
Volume~45 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 832-2}.

\cd*\relax
\artist{Heucke, Stefan}.
\cdtitle{Sonate, Op.~23}.
\see{293}.

\cd*\relax
\artist{Heussenstamm, George}.
\cdtitle{Seven Etudes for Oboe, Clarinet, and Bassoon}.
\see{1687}.

\cd\relax
\artist{Hildegard of Bingen, Abbess}.
\cdtitle{A feather on the breath of god}.
Emma Kirkby and Gothic~Voices.
Christopher Page, cond.
Hyperion Records, 1986 \cdnum{CDA66039}.

\cd\relax
\artist{Hillier, Paul}.
\cdtitle{Portrait}.
Andrew Lawrence-King (harp and medieval psaltery) and Paul Hillier
  (voice and director).
Theatre of Voices, His Majestie's Clerkes.
Harmonia Mundi, 1997 \cdnum{HMX 2907126}.

\cd\relax
\artist{Hillier, Paul and Andrew Lawrence-King}.
\cdtitle{Bitter Ballads}.
Harmonia Mundi, 1998 \cdnum{HMU 907204}.

\cd*\relax
\artist{Hilner, Andreas}.
\cdtitle{Fantasy after \emph{Tosca} for saxophone quartet}.
\see{19}.

\cd*\relax
\artist{Hindemith, Paul}.
\cdtitle{Sonata}.
\see{504}.

\cd*\relax
\artist{Hindemith, Paul}.
\cdtitle{Sonata}.
\see{293}.

\cd*\relax
\artist{Hindemith, Paul}.
\cdtitle{Sonata \(1943\)}.
\see{298}.

\cd*\relax
\artist{Hindemith, Paul}.
\cdtitle{Sonata for Basson and Piano}.
\see{847}.

\cd*\relax
\artist{Hindemith, Paul}.
\cdtitle{Sonata for Bassoon and Piano}.
\see{661}.

\cd*\relax
\artist{Hindemith, Paul}.
\cdtitle{Sonata for Cello Solo}.
\see{149}.

\cd\relax
\artist{Hindemith, Paul}.
\cdtitle{Sonatas for Viola/Piano and Viola Alone}.
Kim Kashkashian (viola) and Robert Levin (Piano).
BMG Classics, 1988 \cdnum[2]{1330-32}.

\cd*\relax
\artist{Hirose, Ryohei}.
\cdtitle{Hymn \and Meditation}.
\see{943}.

\cd*\relax
\artist{Hoffmeister, Franz Anton}.
\cdtitle{Concerto in D~major for viola}.
\see{1141}.

\cd*\relax
\artist{Hoffstetter, Roman}.
\cdtitle{Andante cantabile \from\ String Quartet in F~Major
  ``Serenade''}.
\see{1619}.

\cd\relax
\artist{Hofmann, Josef}.
\cdtitle{Chopin/Mendelssohn/Liszt/Rachmaninoff \: \track \C{Felix
  Mendelssohn Bartholdy} ``Hunting Song'' \(\from Lieder ohne Worte,
  Op.~19\) \and ``Spring Song'' \(\from Lieder ohne Worte, Op.~62\) \and
  The Bee's Wedding \(\from Lieder ohne Worte, Op.~67`\) \and Rondo
  capriccioso, Op.~14 \(abridged\) \; \track \C{Ludwig van Beethoven and
  Anton Rubinstein} Turkish March from ``Die Ruinen von Athen'' \;
  \track \C{Fr\'ed\'eric Chopin} Polonaise in~A, Op.~40 No.~1
  ``Military'' \and Waltz in E~minor, Op.~posth. \and Waltz in A~flat,
  Op.~34 No.~1 ``Valse brillante'' \and Berceuse in D~flat, Op.~57 \and
  Polonaise No.~3 in~A Op.~40 No.~1 ``Military'' \and Waltz in C~sharp
  minor, Op.~64 No.~2 \and Nocturne in F~sharp, Op.~15 No.~2 \and
  Scherzo in B~minor, Op.~20 \(abridged\) \; \track \C{Fannie Charles
  Dillon} Birds at Dawn, Op.~20 No.~2 \; \track \C{Christoph Willibald
  Gluck and Johannes Brahms} Gavotte in~A \(\from Paride ed Elena\) \;
  \track \C{Edvard Grieg} Butterfly \(\from Lyric Pieces, Op.~43\) \;
  \track \C{Josef Hofmann} The Sanctuary \and Nocturne \(\from
  Mignonettes\) \; \track \C{Franz Liszt} Liebestraum No.~3 in A~flat
  \and Tarantella \(revised version, 1859\) \and Fantaisie-Impromptu in
  C~sharp minor, Op.~66 \and My Darling \(\from 6 Chants polonais de
  F.~Chopin\) \; \track \C{Moritz Moszkowski} Capriccio espagnole,
  Op.~37 \(abridged\) \and La jongleuse, Op.~52 No.~4 \; \track
  \C{Ignacy Jan Paderewski} Minuet c\'el\`ebre in~G, Op.~14 No.~1 \;
  \track \C{Horatio William Parker} Valse gracile \; \track \C{Sergei
  Rachmaninoff} Prelude in C~sharp minor, Op.~3, No.~2 \and Prelude in
  G~minor, Op.~23, No.~5 \; \track \C{Anton Rubinstein} Valse-Caprice in
  E~flat \and Melody in~F, Op.~3 No.~1 \; \track \C{Domenico Scarlatti
  and Carl Tausig} Pastorale e capriccio \; \track \C{Franz Schubert and
  Carl Tausig} Marche militaire No.~1 in~D \(\from D.~733\) \; \track
  \C{Franz Schubert and Franz Liszt} Erlk\"onig \; \track \C{Robert
  Schumann} Warum? \(No.~3 from Fantasiest\"ucke, Op.~12\) \; \track
  \C{Erich Walter Sternberg} Etude No.~3 in C~minor, Op.~120 \; \track
  \C{Richard Wagner and Louis Brassin} Magic Fire Music \(\from Die
  Walk\"ure\)}.
Volume~46 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 835-2}.

\cd*\relax
\artist{Hofmann, Josef}.
\cdtitle{Nocturne \(``Complaint''\) \and Kaleidoskop, Op.~40, No.~4}.
\see{724}.

\cd\relax
\artist{Hofmann, Leopold}.
\cdtitle{Cello Concertos \: \track Concerto in D~major \(Badley D3\) \;
  \track Concerto in C~major \(Badley C3\) \; \track Concerto in D~major
  \(Badley D1\) \; \track Concerto in C~major \(Badley C1\)}.
Tim Hugh (Cello and Director).
Northern Sinfonia.
Naxos, 1998 \cdnum{8.553853}.

\cd\relax
\artist{Hofmann, Leopold}.
\cdtitle{Concertos \: \track Concerto for Violin and Strings in B~flat
  major \(Badley~Bb1\) \; \track Concerto for Violin, Cello and Strings
  in G~major \(Badley~G1\) \; \track Concerto for Violin and Strings in
  A~major \(Badley~A2\)}.
Lorraine McAslan (violin) and Tim Hugh (cello).
Northern Chamber Orchestra.
Nicholas Ward, cond.
Naxos, 1998 \cdnum{8.554233}.

\cd\relax
\artist{Hofmann, Leopold}.
\cdtitle{Five Symphonies \: \track Sinfonia in B~flat Major \(Badley
  Bb1\) \; \track Sinfonia in F~Major \(Badley F1\) \; \track Sinfonia
  in D~Major \(Badley D4\) \; \track Sinfonia in F~Major \(Badley F2\)
  \; \track Sinfonia in C~Major \(Badley C8\)}.
Northern Chamber Orchestra.
Nicholas Ward, cond.
Naxos, 1997 \cdnum{8.553866}.

\cd\relax
\artist{Hofmann, Leopold}.
\cdtitle{Flute Concertos, Volume~1 \: \track Flute Concerto in G~major
  \(Badley G2\) \; \track Flute Concerto in D~major \(Badley D1\) \;
  \track Flute Concerto in A~major \(Badley A2\) \; \track Flute
  Concerto in D~major \(Badley D6\)}.
Kazunori Seo (flute).
Nicolaus Esterh\'azy Sinfonia.
B\'ela Drahos, cond.
Naxos, 2001 \cdnum{8.554747}.

\cd\relax
\artist{Hofmann, Leopold}.
\cdtitle{Flute Concertos, Volume~2 \: \track Flute Concerto in D~major
  \(Badley D3\) \; \track Flute Concerto in G~major \(Badley G3\) \;
  \track Flute Concerto in D~major \(Badley D4\) \; \track Flute
  Concerto in E~minor \(Badley e1\)}.
Kazunori Seo (flute).
Nicolaus Esterh\'azy Sinfonia.
B\'ela Drahos, cond.
Naxos, 2001 \cdnum{8.554748}.

\cd\relax
\artist{Hofmann, Leopold}.
\cdtitle{Oboe Concertos \: \track Oboe Concerto C~major \(Badley~C2\) \;
  \track Concerto for Oboe and Harpsichord in F~major \(Badley~F1\) \;
  \track Concerto for Oboe and Harpsichord in C~major \(Badley~C1\) \;
  \track Oboe Concerto G~major \(Badley~G1\)}.
Stefan Schilli (oboe) and Jen\H{o} Jand\'o (harpsichord).
Nicolaus Esterh\'azy Sinfonia.
B\'ela Drahos, cond.
Naxos, 2002 \cdnum{8.553979}.

\cd\relax
\artist{Holiday, Billie}.
\cdtitle{Billie's Best}.
PolyGram Records, 1992 \cdnum{314 513 943-2}.

\cd*\relax
\artist{Holliger, H.}
\cdtitle{Studie \"uber Mehrkl\"ange for Oboe \(1971\) \and Lied for
  Electric Flute \(1971\)}.
\see{784}.

\cd\relax
\artist{Holliger, Heinz}.
\cdtitle{Oboe Concertos \: \track \C{Johann Gottlieb Graun} Concerto in
  C~minor for Oboe, Strings and Continuo \and Concerto in G~minor for
  Oboe, Strings and Continuo \and \; \track \C{Johann Ludwig Krebs}
  Concerto in B~minor for Harpsichord, Oboe, Strings and Continuo \;
  \track \C{Georg Philipp Telemann} Concerto in E~flat major for Oboe,
  Strings and Continuo \and Concerto in B~major for two Flutes, two
  Oboes, Strings and Continuo}.
Aur\`ele Nicolet (flute), Christiane Nicolet (flute), Louise Pellerin
  (oboe), Christiane Jaccottet (harpsichord) and J\"org E. D\"ahler
  (harpsichord).
Camerata Bern.
Alexander van Wijnkoop and Thomas F\"uri, cond.
Deutsche Grammophon, 1979/1981 \cdnum{00289 477 5002}.

\cd\relax
\artist{Holliger, Heinz}.
\cdtitle{The Artistry of Heinz Holliger \: \track \C{G. Ph. Telemann}
  Fantasy No.~1 in A~major for Oboe Solo \and Fantasy No.~3 in B~minor
  for Oboe Solo \and Suite in G~minor for Oboe and Basso Continuo from
  ``Der getreue Music-Meister'' \; \track \C{G. F. Handel} Trio Sonata
  in B-flat major, Op.~2 No.~3 for 2 Oboes and Basso Continuo \and \;
  \track \C{J. C. Bach} Quartet in B-flat major for Oboe, Violin, Viola
  and Violoncello \; \track \C{W. A. Mozart} Adagio in C~major for
  English horn, Violin, Viola and Violoncello, KV580a \; \track \C{J. S.
  Bach} Ricercare a~6 from ``Musikalisches Opfer'', BVW1079 \; \track
  \C{K. Penderecki} Capriccio for Oboe and 11 Strings \(1965\) \; \track
  \C{H. Holliger} Studie \"uber Mehrkl\"ange for Oboe \(1971\) \and Lied
  for Electric Flute \(1971\)}.
Denon Records, 1987 \cdnum{DC-8006}.

\cd\relax
\artist{Holly, Buddy}.
\cdtitle{Buddy Holly}.
MCA Records, 1985 \cdnum{MCAD-5540}.

\cd\relax
\artist{Holmboe, Vagn}.
\cdtitle{Complete Chamber Concertos, Volume~I \: \track Chamber Concerto
  No.~1, op.~17 for piano, strings and timpani \; \track Chamber
  Concerto No.~2, op.~20 for flute, violin, strings and percussion \;
  \track Chamber Concerto No.~3, op.~21 for clarinet and chamber
  orchestra}.
Anne {\O}land (piano), Niels Thomsen (clarinet), Mikkel Futtrup (violin)
  and Eva {\O}stergaard (flute).
The Danish Radio Sinfonietta.
Hannu Koivula, cond.
Marco Polo/dacapo, 1996 \cdnum{8.224038}.

\cd\relax
\artist{Holmboe, Vagn}.
\cdtitle{Complete Chamber Concertos, Volume~II \: \track Chamber
  Concerto No.~4, op.~30 for piano trio and chamber orchestra \; \track
  Chamber Concerto No.~5, op.~31 for viola and chamber orchestra \;
  \track Chamber Concerto No.~6, op.~33 for violin and chamber
  orchestra}.
Anne {\O}land (piano), Mikkel Futtrup (violin), Tim Frederiksen (viola)
  and Niels Ullner (cello).
The Danish Radio Sinfonietta.
Hannu Koivula, cond.
Marco Polo/dacapo, 1997 \cdnum{8.224063}.

\cd\relax
\artist{Holmboe, Vagn}.
\cdtitle{Complete Chamber Concertos, Volume~~III \: \track Chamber
  Concerto No.~7, op.~37 for oboe and chamber orchestra \; \track
  Chamber Concerto No.~8, op.~38 for orchestra, ``Sinfonia Concertante''
  \; \track Chamber Concerto No.~9, op.~39 for violin, viola and
  orchestra}.
Max Artved (oboe), Mikkel Futtrup (violin) and Tim Frederiksen (viola).
The Danish Radio Sinfonietta.
Hannu Koivula, cond.
Marco Polo/dacapo, 1997 \cdnum{8.224086}.

\cd\relax
\artist{Holmboe, Vagn}.
\cdtitle{\track Concerto for Cello and Orchestra, Op.~120 \; \track
  Benedic Domino, Op.~59 \; \track Triade, Op.~123 \; \track Quintet,
  Op.~79}.
Erling Bl{\o}ndal Bengtsson (cello), Edward H. Tarr (trumpet), Elisabeth
  Westenholz (organ) and Swedish Brass Quintet.
Danish National Radio Symphony Orchestra and Camerata Chamber Choir.
J\'anos Ferencsik and Per Enevold, cond.
BIS, 1992 \cdnum{BIS-CD-78}.

\cd\relax
\artist{Holmboe, Vagn}.
\cdtitle{Four Symphonic Metamorphoses \: \track Epitaph, Op.~68/M.~189
  \; \track Monolith, Op.~76/M.~207 \; \track Epilog, Op.~80/M.~213 \;
  \track Tempo variabile, Op.~108/M.~254}.
Aalborg Symphony Orchestra.
Owain Arwel Hughes, cond.
BIS, 1998 \cdnum{BIS-CD-852}.

\cd\relax
\artist{Holmboe, Vagn}.
\cdtitle{Preludes for Sinfonietta, Volume~2 \: \track To the Seagulls
  and the Cormorants, op.~174, no.~6 \; \track To the Calm Sea, op.~187,
  no.~9 \; \track To a Pine Tree, op.~164, no.~1 \; \track To the
  Pollution of Nature, op.~180, no.~7 \; \track To a Willow Tree,
  op.~170, no.~4 \; \track Sonata for Trombone and Piano, op.~172a \;
  \track Music with Horn, op.~148}.
Jesper Juul S{\o}rensen (trombone), Anne Mette St{\ae}r (piano), Thomas
  Ekman (horn) and Anne S{\o}e Iwan (violin).
Athelas Sinfonietta Copenhagen.
Giordano Bellincampi, cond.
dacapo, 2001 \cdnum{8.224124}.

\cd*\relax
\artist{Holmboe, Vagn}.
\cdtitle{Sonata for Solo Cello, Opus~101}.
\see{1700}.

\cd\relax
\artist{Holmboe, Vagn}.
\cdtitle{String Quartets, Volume~II \: \track String Quartet No.~2,
  Op.~47 \; \track String Quartet No.~5, Op.~66 \; \track String Quartet
  No.~6, Op.~78}.
The Kontra Quartet.
Marco Polo/dacapo, 1995 \cdnum{8.224026}.

\cd\relax
\artist{Holmboe, Vagn}.
\cdtitle{String Quartets, Volume~III \: \track String Quartet No.~7,
  Op.~86 \; \track String Quartet No.~8, Op.~87 \; \track String Quartet
  No.~9, Op.~92}.
The Kontra Quartet.
Marco Polo/dacapo, 1997 \cdnum{8.224073}.

\cd*\relax
\artist{Holst, Gustav}.
\cdtitle{Duet for trombone and organ}.
\see{1599}.

\cd\relax
\artist{Holst, Gustav}.
\cdtitle{Orchestral Works \: \track Somerset Rhapsody \; \track Beni
  Mora \(Oriental Suite\) \; \track Invocation for Cello and Orchestra
  \; \track Fugal Overture \; \track Egdon Heath \; \track Hammersmith}.
Tim Hugh (cello).
Royal Scottish National Orchestra.
David Lloyd-Jones, cond.
Naxos, 1998 \cdnum{8.553696}.

\cd\relax
\artist{Holst, Gustav}.
\cdtitle{\track The Planets \; \track \C{Percy Grainger} The Warriors}.
The Philharmonia Orchestra.
John Eliot Gardiner, cond.
Deutsche Grammophon, 1995 \cdnum{445 860-2}.

\cd*\relax
\artist{Honegger, Arthur}.
\cdtitle{Cello Concerto}.
\see{1315}.

\cd\relax
\artist{Horowitz, Vladimir}.
\cdtitle{Chopin/Beethoven/Rachmaninoff \: \track \C{Ludwig van
  Beethoven} Piano Concerto No.~5 in E~flat, Op.~73 ``Emperor'' \;
  \track \C{Fr\'ed\'eric Chopin} Various \; \track \C{Sergei
  Rachmaninoff} Piano Concerto No.~3 in D~minor, Op.~30}.
Volume~49 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 841-2}.

\cd\relax
\artist{Horowitz, Vladimir}.
\cdtitle{Chopin/Liszt/Prokofiev/Rachmaninoff/Scriabin \: \track
  \C{Fr\'ed\'eric Chopin} Fantasy in F~minor, Op.~49 \and
  Polonais-Fantaisie in A~flat, Op.~61 \; \track \C{Franz Liszt}
  Hungarian Rhapsody No.~6 \and Grande \'etude d'apr\`es Paganini No.~2
  in E~flat \and Au bord d'une source \and Sonetto 104 del Petrarca \and
  Soir\'ees de Vienne \and Piano Sonata in B~minor \and Ballade No.~2 in
  B~minor \and Hungarian Rhapsody No.~2 \; \track \C{Sergei Prokofiev}
  Piano Sonata No.~7 in B~flat, Op.~83 \; \track \C{Sergei Rachmaninoff}
  Piano Sonata No.~2 in B~flat minor, Op.~36 \; \track \C{Alexander
  Scriabin} Piano Sonata No.~5 in F~sharp, Op.~53}.
Volume~48 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 844-2}.

\cd\relax
\artist{Horowitz, Vladimir}.
\cdtitle{Robert Schumann \: \track Toccata in~C, Op.~7 \; \track
  Arabeske in~C, Op.~18 \; \track Traumeswirren \(\from
  ``Fantasiest\"ucke'', Op.~22\) \; \track Presto passionato \; \track
  Kreisleriana, Op.~16 \; \track Humoreske in B~flat, Op.~20 \; \track
  Piano Sonata in F~minor, Op.~14 \(``Concert sans orchestre''\) \;
  \track Novellette in~F, Op.~21, No.~1 \; \track Fantasiest\"ucke,
  Op.~111 \; \track Kinderszenen, Op.~15}.
Volume~47 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 838-2}.

\cd*\relax
\artist{H\"oser, Otto}.
\cdtitle{Romanze}.
\see{1599}.

\cd*\relax
\artist{Hosokawa, Hoshio}.
\cdtitle{Vertical Time Study~II}.
\see{483}.

\cd\relax
\artist{Houlik, James}.
\cdtitle{American Saxophone \: \track \C{Morton Gould} Diversions \;
  \track \C{Robert Ward} Concerto for Tenor Saxophone and Orchestra \;
  \track \C{Russel Peck} The Upward Stream}.
Koch, 1996 \cdnum{3-7390-2 H1}.

\cd\relax
\artist{House Jacks, The}.
\cdtitle{Funkwich}.
The House Jacks, 1997 \cdnum{HJ002CD}.

\cd*\relax
\artist{Howells, Herbert}.
\cdtitle{Sonata for clarinet and piano}.
\see{894}.

\cd\relax
\artist{Hume, Tobias}.
\cdtitle{Captain Humes Poeticall Musicke \(1607\), Volume~1}.
Les Voix Humaines, Stephen Stubbs, Paul Audet, R\'ejean Poirier, Francis
  Colpron and Daniel Taylor.
Naxos, 1997 \cdnum{8.554126}.

\cd\relax
\artist{Hume, Tobias}.
\cdtitle{Captain Humes Poeticall Musicke \(1607\), Volume~2}.
Les Voix Humaines, Stephen Stubbs, Paul Audet, R\'ejean Poirier, Francis
  Colpron and Daniel Taylor.
Naxos, 1997 \cdnum{8.554127}.

\cd\relax
\artist{Humfrey, Pelham}.
\cdtitle{Verse Anthems}.
Donna Deam (soprano), Drew Mintner (countertenor), Rogers Covey-Crump
  (tenor), John Potter (tenor), David Thomas (bass), Cambridge Choir of
  Clare College (Timothy Brown, dir.) and Romanesca.
Nicholas McGegan.
Harmonia Mundi, 1992 \cdnum{HMU 907053}.

\cd*\relax
\artist{Hummel, Johann Nepomuk}.
\cdtitle{Concerto for Trumpet and Orchestra in E~flat major}.
\see{1138}.

\cd*\relax
\artist{Hummel, Johann Nepomuk}.
\cdtitle{Rondo favori in E~flat, Op.~11}.
\see{625}.

\cd\relax
\cdtitle{Hungarian Cello Music \: \track \C{Gy\"orgy Ligeti} Sonata
  (Diaolog e Capriccio) for cello \; \track \C{Ferenc Farkas} Ballada \;
  \track \C{S\'andor Veress} Sonatina per violoncello e pianoforte \and
  Sonata per violoncello \; \track \C{Ferenc Liszt} \emph{Die Zelle in
  Nonnenwerth} for piano and cello \and Elegy No.~2 for Cello and Piano
  \; \track \C{Ern\H{o} Dohn\'anyi} Ruralia Hungarica for Cello and
  Piano, Op.~32/d. \; \track \C{Le\'o Weiner} Romance for Cello and
  Piano, Op.~14 \; \track \C{Andr\'as Mih\'aly} Mouvement for Cello and
  Piano}.
Mikl\'os Per\'enyi (cello) and D\'enes V\'arjon (piano).
Hungaroton Classic, 1999 \cdnum{HCD~31835}.

\cd\relax
\artist{Hunter, Robert}.
\cdtitle{A Box of Rain}.
Ryko, 1991 \cdnum{RCD 10214}.

\cd*\relax
\artist{Hurlstone, William Yeates}.
\cdtitle{Four Characteristic Pieces}.
\see{894}.

\cd*\relax
\artist{Husa, Karel}.
\cdtitle{El\'egie et Roundeau}.
\see{1602}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{Arie Antiche}.
Academy of St~Martin in the Fields.
Sir Neville Marriner, cond.
Philips Classics, 1997 \cdnum{289 456 543-2}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{Bel Canto Arias: Songs of Love and Desire}.
Philharmonia Orchestra.
Ioan Marin, cond.
Philips Classics, 1994 \cdnum{434 912-2}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{Credo}.
St~Petersburg Chamber Choir.
Nikolai Korniev, cond.
Philips Classics, 1996 \cdnum{446 089-2}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{Dark Eyes: Russian Folk Songs}.
The Ossipov Russian Folk Orchestra.
Nikolai Kalinin, cond.
Philips Classics, 1991 \cdnum{434 080-2}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{From Russia with Love}.
Philips Classics, 2001 \cdnum{468 682-2 PH}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{I Met You, My Love: Old Russian Romances}.
Style of Five.
Moscow Chamber Orchestra.
Constantin Orbelian, cond.
Delos, 2002 \cdnum{DE~3293}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{Kalinka: Russian Folk Songs}.
St~Petersburg Chamber Choir.
Nikolai Korniev, cond.
Philips Classics, 1998 \cdnum{289 456 399-2}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{My Restless Soul}.
Mikhail Arkadiev (piano).
Philips Classics, 1995 \cdnum{432 536-2}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{Passione di Napoli}.
Philharmonia of Russia.
Constantin Orbelian, cond.
Delos, 2001 \cdnum{DE~3290}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{Russia Cast Adrift}.
Mikhail Arkadiev (piano).
Philips Classics, 1996 \cdnum{446 666-2}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{Russian Romances \(Tchaikovsky and Rachmaninoff\)}.
Oleg Boshniakovich (piano).
Philips Classics, 1991 \cdnum{432 119-2}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{Songs and Dances of Death}.
The Kirov Orchestra, St~Petersburg.
Valery Gergiev, cond.
Philips Classics, 1994 \cdnum{438 872-2}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{Tchaikovsky and Verdi Arias}.
The Rotterdam Philharmonic Orchestra.
Val\'ery Gergiev, cond.
Philips Classics, 1990 \cdnum{426 740-2}.

\cd\relax
\artist{Hvorostovsky, Dmitri}.
\cdtitle{Verdi Arias}.
Alexander Vinogradov (bass), Vsevolod Grivinov (tenor) and director
  Spiritual Revival Choir of Russia (Lev Kontorovich).
Philharmonia of Russia.
Mario Bernardi, cond.
Delos International, 2002 \cdnum{DE~3292}.

\cd\relax
\artist{Hvorostovsky, Dmitri and Olga Borodina}.
\cdtitle{Arias/Duets}.
English Chamber Orchestra.
Patrick Summers, cond.
Philips Classics, 1998 \cdnum{289 454 439-2}.

\cd*\relax
\artist{Hvoslef, Ketil}.
\cdtitle{Concerto for Saxophone Quartet and Orchestra \(1996\)}.
\see{1248}.

\cd*\relax
\artist{Ibert, Jacques}.
\cdtitle{Concertino da camera for alto saxophone and eleven
  instruments}.
\see{744}.

\cd*\relax
\artist{Imai, Chikade}.
\cdtitle{Seductive Realm, after \emph{Die Zauberfl\"ote} for saxophone
  quartet and piano}.
\see{19}.

\cd\relax
\artist{Ippolitov-Ivanov, Mikhail Mikhailovich}.
\cdtitle{Orchestral Works \: \track Caucasian Sketches---Suite No.~1,
  Op.~10 \; \track Caucasian Sketches---Suite No.~2 ``Iveria'', Op.~42
  \; \track Turkish Marches, Op.~55 \; \track Turkish Fragments,
  Op.~62}.
National Symphony Orchestra of Ukraine.
Arthur Fagen, cond.
Naxos, 1997 \cdnum{8.553405}.

\cd*\relax
\artist{Ireland, John}.
\cdtitle{Sonata for Cello and Piano in G~minor}.
\see{984}.

\cd*\relax
\artist{Ireland, John}.
\cdtitle{The Holy Boy}.
\see{983}.

\cd\relax
\artist{Isaak, Chris}.
\cdtitle{Always Got Tonight}.
Reprise Records, 2002 \cdnum{9~48016-2}.

\cd\relax
\artist{Isaak, Chris}.
\cdtitle{Baja Sessions}.
Reprise Records, 1996 \cdnum{9~46325-2}.

\cd\relax
\artist{Isaak, Chris}.
\cdtitle{Chris Isaak}.
Warner Records, 1987 \cdnum{9~25536-2}.

\cd\relax
\artist{Isaak, Chris}.
\cdtitle{Forever Blue}.
Reprise Records, 1995 \cdnum{9~45845-2}.

\cd\relax
\artist{Isaak, Chris}.
\cdtitle{Heart Shaped World}.
Reprise Records, 1989 \cdnum{9~25837-2}.

\cd\relax
\artist{Isaak, Chris}.
\cdtitle{San Francisco Days}.
Reprise Records, 1993 \cdnum{9~45116-2}.

\cd\relax
\artist{Isaak, Chris}.
\cdtitle{Silverstone}.
Warner Records, 1985 \cdnum{9~25156-2}.

\cd\relax
\artist{Isaak, Chris}.
\cdtitle{Speak of the Devil}.
Reprise Records, 1998 \cdnum{9~46849-2}.

\cd*\relax
\artist{Ishii, Maki}.
\cdtitle{Black Intention \and east$\bullet$green$\bullet$spring}.
\see{943}.

\cd\relax
\artist{Italian Saxophone Quartet}.
\cdtitle{The Sound of the Italian Saxophone Quartet: Live Concert in
  Verona \: \track \C{Domenico Scarlatti and Gabriel Piern\'e} Three
  Pieces \; \track \C{Johann Sebastian Bach} Preludio and Fuga~XVI \;
  \track \C{Paul Reade} Saxophone Quartet \; \track \C{Jean
  Fran\c{c}aix} Petit Quatour pour Saxophone \; \track \C{Pedro
  Itturralde} \from Suite Hell\'enique \; \track \C{Astor Piazzolla}
  Oblivion \and Fugata \and Libertango \; \track \C{Annibal Troilo}
  Contrabajando \; \track \C{Scott Joplin} The Easy Winners \; \track
  \C{George Gershwin} An American in Paris---blues \; \track \C{Paul
  Nagle} Three Shades of Blues \; \track \C{Nina Rota} music from
  Fellini's film ``8~1/2'' \; \track \C{Michael Nyman} Song for Tony}.
Federico Mondelci (soprano), Mario Marzi (tenor), Marco Gerboni (alto)
  and Massimo Mazzoni (baritone).
Delos, 2004 \cdnum{DE~3333}.

\cd*\relax
\artist{Itturralde, Pedro}.
\cdtitle{\from Suite Hell\'enique}.
\see{830}.

\cd\relax
\artist{Ivers, Eileen}.
\cdtitle{Eileen Ivers}.
Green Linnet, 1994 \cdnum{GLCD~1139}.

\cd*\relax
\artist{Ives, Charles}.
\cdtitle{Symphony No.~3}.
\see{152}.

\cd*\relax
\artist{Ives, Charles}.
\cdtitle{Trio for Violin, Cello and Piano}.
\see{1007}.

\cd\relax
\artist{J. Geils Band, The}.
\cdtitle{Flashback}.
EMI America, 1985 \cdnum{CDP 7 46551~2}.

\cd\relax
\artist{Jackson, Joe}.
\cdtitle{Heaven and Hell}.
Joy Askew, Brad Roberts, Jane Siberry, Nadja Salerno-Sonnenberg, Dawn
  Upshaw and Suzanne Vega.
Sony, 1997 \cdnum{SK60273}.

\cd*\relax
\artist{Jacobi, Frederick}.
\cdtitle{Fantasy for Viola and Piano \(1941\)}.
\see{177}.

\cd*\relax
\artist{Jakoulov, Jakov}.
\cdtitle{Sonata for viola and piano \and Mikhail Glinka.
  Valse-fantaisie. Stylistic reminiscences.}
\see{1699}.

\cd*\relax
\artist{Jan\'a\c{c}ek, Leos}.
\cdtitle{C\^ek\'am T\^e \(Waiting for you\) \(arr.~Iva Bittov\'a\)}.
\see{1344}.

\cd\relax
\artist{Jan\'a\v{c}ek, Leo\v{s}}.
\cdtitle{Glagolitic Mass \and Taras Bulba}.
Rafael Kubelik, cond.
Deutsche Grammophon, 1965/1971 \cdnum{429 182-2}.

\cd\relax
\artist{Jan\'a\v{c}ek, Leo\v{s}}.
\cdtitle{Jen\r{u}fa}.
\v{S}t\v{e}p\'anka Jel{\'\i}nkov\'a, Marta Kr\'asov\'a, Beno Blachut and
  Ivo \v{Z}{\'\i}dek.
Prague National Theatre Orchestra and Chorus.
Jaroslav Vogel, cond.
Supraphon, 1954 \cdnum[2]{SU 3331-2 602}.

\cd\relax
\artist{Jan\'a\v{c}ek, Leo\v{s}}.
\cdtitle{K\'at'a Kabanov\'a}.
Gabriela Be\v{n}a\v{c}kov\'a-\v{C}\'apov\'a, Peter Straka, Eva Randov\'a
  and Dagmar Peckov\'a.
Czech Philharmonic Orchestra and Chorus of the Prague National Theatre.
Sir Charles Mackerras, cond.
Supraphon, 1997 \cdnum[2]{SU 3291-2 632}.

\cd\relax
\artist{Jan\'a\v{c}ek, Leo\v{s}}.
\cdtitle{On an Overgrown Path, Series~I and~II}.
Ivan Kl\'ansk\'y.
Supraphon, 1982 \cdnum{SU 3287-2 111}.

\cd\relax
\artist{Jan\'a\v{c}ek, Leo\v{s}}.
\cdtitle{Osud/Fate}.
Brno Jan\'a\v{c}ek Opera Chorus and Orchestra.
Franti\v{s}ek J{\'\i}lek, cond.
Supraphon, 1976 \cdnum{SU 0045-2 611}.

\cd\relax
\artist{Jan\'a\v{c}ek, Leo\v{s}}.
\cdtitle{Sinfonietta \and Taras Bulba \and Lachian Dances \and Suite for
  string orchestra \and Ml\'adi \and Cappriccio \and Concertino}.
The Decca Record Company, 1996 \cdnum[2]{448 255-2}.

\cd\relax
\artist{Jan\'a\v{c}ek, Leo\v{s}}.
\cdtitle{String Quartets No.~1 \(``Kreutzersonate''\) and No.~2
  \(``Intimate Letters''\)}.
The Alban Berg Quartett.
EMI Records, 1995 \cdnum{7243 5~55457~2 5}.

\cd\relax
\artist{Jan\'a\v{c}ek, Leo\v{s}}.
\cdtitle{The Cunning Little Vixen}.
Helena Tattermuschov\'a (soprano), Eva Zikmundov\'a (soprano) and
  Zden\v{e}k Kroupa (bass).
Prague National Theatre Chorus and Orchestra.
Bohumil Gregor, cond.
Supraphon, 1972 \cdnum[2]{SU~3071-2 612}.

\cd\relax
\artist{Jan\'a\v{c}ek, Leo\v{s}}.
\cdtitle{The Diary of One Who Disappeared \(Z\'apisn{\'\i}k zmizel\'eho,
  JW~V/12\) \: \track Moravian Folksongs \(Moravsk\'e lidov\'e
  p{\'\i}sne, JW~VIII/23\) \; \track Vzpom{\'\i}nka, JW~VIII/32 \;
  \track Na pam\'atku, JW~VIII/9 \; \track Andante, JW~VIII/31 \; \track
  Moderato, JW~VIII/21 \; \track Zlat\'y krou\v{z}ek, JW~VIII/33, No.~12
  \; \track \v{C}ek\'am T\v{e}!, JW~VIII/33, No.~13 \; \track Narodil se
  Kristus P\'an, JW~VIII/20}.
Ian Bostridge (tenor), Ruby Philogene (mezzo-soprano) and Thomas Ad\`es
  (piano).
EMI Classics, 2001 \cdnum{7243 5 57219 2~1}.

\cd\relax
\artist{Jan\'a\v{c}ek, Leo\v{s}}.
\cdtitle{Unknown~II \: \track R\'akos R\'akoczy \; \track Lidov\'e
  p{\'\i}sn\v{e} a tance se sborem \(Folk Songs and Dances with
  Chorus\)}.
Zuzana Lap\v{c}{\'\i}kov\'a (soprano), Petr Jul{\'\i}\v{c}ek (tenor),
  Pavla Dittmannov\'a (contralto) and Ond\v{r}ej Sv\'arovsk\'y.
Brno State Philharmonic Orchestra and Czech Philharmonic Chorus Brno.
Leo\v{s} Sv\'arovsk\'y, cond.
Supraphon, 1996 \cdnum{SU3129-2231}.

\cd\relax
\artist{Janis, Byron}.
\cdtitle{Beethoven/Brahms/Chopin/Liszt \: \track \C{Johann Sebastian
  Bach and Franz Liszt} Prelude and Fugue in A~minor, BWV~543 \; \track
  \C{Ludwig van Beethoven} Piano Sonata No.~17 in D~minor, Op.~31, No.~2
  ``Tempest'' \; \track \C{Johannes Brahms} Walzes, Op.~39, Nos.~1, 2,
  6, and~15 \; \track \C{Fr\'ed\'eric Chopin} Ballade No.~1 in G~minor,
  Op.~23 \and Impromptu No.~1 in A~flat, Op.~29 \and Waltz in E~minor,
  Op.~posth.\ \and Waltz in A~minor, Op.~34 No.~2 \and Mazurka in
  A~minor, Op.~67 No.~4 \and Etude in~E, Op.~10 No.~3 ``Tristesse'' \and
  Etude in~F, Op.~25 No.~3 \and Etude in G~flat, Op.~10 No.~5 ``Black
  Keys'' \and Etude in~F, Op.~10 No.~8 \and Piano Sonata No.~2 in B~flat
  minor, Op.~35 ``Funeral March'' \and Scherzo No.~3 in C~sharp minor,
  Op.~39 \; \track \C{Franz Liszt} Liebestraum No.~3 in A~flat \and
  Hungarian Rhapsody No.~6 in D~flat \and Consolation No.~5 in~E \and
  Sonetto 104 del Petrarca \and ``Rigoletto'' Paraphrase \; \track
  \C{Franz Schubert} Impromptu in E~flat, D.~899 No.~2 \; \track
  \C{Johann Strauss and Adolf Schulz-Evler} Arabesques on ``An der
  sch\"onen, blauen Donau''}.
Volume~50 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 847-2}.

\cd\relax
\artist{Janis, Byron}.
\cdtitle{Liszt/Prokofiev/Schumann/Rachmaninoff/Tchaikovsky \: \track
  \C{Franz Liszt} Piano Concerto No.~1 in E~flat \; \track \C{Sergei
  Rachmaninoff} Piano Concerto No.~1 in F~sharp minor, Op.~1 \; \track
  \C{Sergei Prokofiev} Piano Concerto No.~3 in~C, Op.~26 \and Toccata,
  Op.~11 \; \track \C{Sergei Rachmaninoff} Piano Concerto No.~2 in
  C~minor, Op.~18 \; \track \C{Robert Schumann} Variations from Piano
  Sonata No.~3 in F~minor, Op.~14 ``Concerto without Orchestra'' \and 3
  Romanzen, Op.~28 \(No.~2 in F~sharp\) \; \track \C{Peter Ilyich
  Tchaikovsky} Piano Concerto No.~1 in B~flat minor, Op.~23}.
Volume~51 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 850-2}.

\cd\relax
\artist{Jefferson Airplane}.
\cdtitle{The Best of Jefferson Airplane}.
BMG Music, 1993 \cdnum{66197-2}.

\cd\relax
\artist{Jensen, Dag and Midori Kitagawa}.
\cdtitle{Musique pour basson et piano, Volume~2 \: \track \C{Olav Berg}
  Vertigo for Bassoon Solo \and Sonatine for Basson and Piano \; \track
  \C{Paul Hindemith} Sonata for Basson and Piano \; \track \C{Otmar
  Nussio} Variazioni su un' Arietta di Pergolesi for Basson and Piano \;
  \track \C{Otmar Schoeck} Sonata for Basson and Piano, op.~41 \; \track
  \C{Manfred Schoof} Two Impromptus for Basson and Piano \; \track
  \C{Isang Yun} Monologue for Basson}.
MDG, 1998 \cdnum{MDG~603 0831-2}.

\cd\relax
\artist{Jethro Tull}.
\cdtitle{Aqualung}.
Chrysalis Records, 1973 \cdnum{F2 21044}.

\cd\relax
\artist{Jethro Tull}.
\cdtitle{Stand Up}.
Chrysalis Records, 2001 \cdnum{7243 5 35458 2 6}.
Remastered with extra tracks.

\cd\relax
\artist{Jethro Tull}.
\cdtitle{The Broadsword and the Beast}.
Chrysalis Records, 2005 \cdnum{72434-73411-2-0}.
Remastered with extra tracks.

\cd\relax
\artist{Jethro Tull}.
\cdtitle{The Jethro Tull Christmas Album}.
Fuel 2000 Records, 2003 \cdnum{302 061 340~2}.

\cd*\relax
\artist{Joachim, Joseph}.
\cdtitle{Drei St\"ucke, Op.~2, No.~1}.
\see{875}.

\cd\relax
\artist{Joculatores Upsalienses}.
\cdtitle{Antik Musik p{\aa} Wik}.
BIS, 1973/74/82/90 \cdnum{BIS-CD-3}.

\cd\relax
\artist{Joculatores Upsalienses}.
\cdtitle{De Fyra {\AA}rstiderna \(The Four Seasons\)}.
BIS, 1976/82/90 \cdnum{BIS-CD-75}.

\cd\relax
\artist{Joculatores Upsalienses}.
\cdtitle{Skogen, Flickan och Flaskan \(Woods, Women and Wine\)}.
BIS, 1978/82/90 \cdnum{BIS-CD-120}.

\cd\relax
\artist{Joel, Billy}.
\cdtitle{Cold Spring Harbor}.
Columbia Records, 1971 \cdnum{CK~38984}.

\cd\relax
\artist{Joel, Billy}.
\cdtitle{River of Dreams}.
Sony, 1993 \cdnum{CK~53003}.

\cd\relax
\artist{Joel, Billy}.
\cdtitle{Songs in the Attic}.
CBS Records, 1981 \cdnum{CK 37461}.

\cd\relax
\artist{Joel, Billy}.
\cdtitle{The Stranger}.
CBS, 1977 \cdnum{CK~34987}.

\cd*\relax
\artist{Johansen, David Monrad}.
\cdtitle{Pictures from Nordland, Suite No.~1, Op.~5}.
\see{28}.

\cd\relax
\artist{John, Elton}.
\cdtitle{Goodbye Yellow Brick Road}.
Rocket Records, 1973/1995 \cdnum{314-528 159-2}.

\cd\relax
\artist{John, Elton}.
\cdtitle{Rocket Man $\cdot$ Number Ones}.
Mercury Records, 2007 \cdnum{B0008661-02}.

\cd*\relax
\artist{Jolivet, Andr\'e}.
\cdtitle{Arioso barocco}.
\see{1524}.

\cd*\relax
\artist{Jolivet, Andr\'e}.
\cdtitle{Concertino for Trumpet, Piano and Strings}.
\see{1138}.

\cd*\relax
\artist{Jolivet, Andr\'e}.
\cdtitle{Fantaisie-Impromptu}.
\see{253}.

\cd\relax
\artist{Jones, Rickie Lee}.
\cdtitle{Naked Songs}.
Reprise Records, 1995 \cdnum{9 45950-2}.

\cd\relax
\artist{Jones, Rickie Lee}.
\cdtitle{Pirates}.
Warner Brothers, 1981 \cdnum{3432-2}.

\cd\relax
\artist{Jones, Rickie Lee}.
\cdtitle{Rickie Lee Jones}.
Warner Brothers, 1979 \cdnum{3296-2}.

\cd\relax
\artist{Jones, Spike}.
\cdtitle{Dinner Music\dots for people who aren't very hungry!}
Rhino Records, 1988 \cdnum{R2 70261}.

\cd\relax
\artist{Jones, Spike}.
\cdtitle{Spiked!}
BMG Music, 1994 \cdnum{09026-61982-2}.

\cd\relax
\artist{Jones, Spike}.
\cdtitle{The Best of Spike Jones and His City Slickers}.
BMG Music, 1967 \cdnum{53748-2}.

\cd\relax
\artist{Jones, Spike}.
\cdtitle{The Radio Years, Volume~1}.
Rhino Records \cdnum{R2~71156}.
Two original radio broadcasts with guest stars Boris Karloff and Peter
  Lorre.

\cd\relax
\artist{Jones, Spike}.
\cdtitle{The Radio Years, Volume~2}.
Rhino Records \cdnum{R2~71157}.
Two original radio broadcasts with guest stars Frank Sinatra and Lassie.

\cd\relax
\artist{Jones, Spike}.
\cdtitle{The Spike Jones Anthology}.
Rhino Records, 1994 \cdnum[2]{R2~71574}.

\cd\relax
\artist{Joplin, Janice}.
\cdtitle{Farewell Song}.
CBS Records, 1982 \cdnum{CK~37569}.

\cd\relax
\artist{Joplin, Janice}.
\cdtitle{Full Tilt Boogie}.
CBS Records \cdnum{CK~30322}.

\cd\relax
\artist{Joplin, Janice}.
\cdtitle{Greatest Hits}.
Columbia, 1973 \cdnum{CK~32168}.

\cd\relax
\artist{Joplin, Janice}.
\cdtitle{Janice}.
Columbia, 1993 \cdnum[3]{C3K~48845}.

\cd*\relax
\artist{Joplin, Scott}.
\cdtitle{The Easy Winners}.
\see{830}.

\cd*\relax
\artist{Jr., Johann Strauss}.
\cdtitle{Die Fledermaus: Overture}.
\see{628}.

\cd*\relax
\artist{Kabalevsky, Dmitri}.
\cdtitle{Cello Sonata in B~flat major, Op.~71}.
\see{1315}.

\cd*\relax
\artist{Kabalevsky, Dmitri}.
\cdtitle{Colas Breugnon: Overture}.
\see{1137}.

\cd*\relax
\artist{Kabalevsky, Dmitri}.
\cdtitle{Concerto for Violin and Orchestra, Op.~48}.
\see{648}.

\cd*\relax
\artist{Kabalevsky, Dmitri}.
\cdtitle{Concerto No.~1 for Cello and Orchestra, Op.~49}.
\see{1014}.

\cd*\relax
\artist{Kabalevsky, Dmitri}.
\cdtitle{Piano Sonata No.~3 in~F, Op.~46}.
\see{1076}.

\cd\relax
\artist{Kabalevsky, Dmitry Borisovich}.
\cdtitle{\track Cello Concerto No.~1 in G~minor, Op.~49 \; \track Cello
  Concerto No.~2 in G~major, Op.~77 \; \track Symphonic Poem: Spring,
  Op.~65 \(Vesna\)}.
Alexander Rudin (cello).
Moscow Symphony Orchestra.
Igor Golovschin, cond.
Naxos, 1997 \cdnum{8.553788}.

\cd*\relax
\artist{Kagel, Mauricio}.
\cdtitle{Atem f\"ur einen Bl\"aser}.
\see{964}.

\cd*\relax
\artist{Kaipainen, Jouni}.
\cdtitle{Vernal Concerto ``From Equinox to Solstice'', Op.~53 \(1996\)}.
\see{1248}.

\cd*\relax
\artist{Kalliwoda, Johann Wenzel}.
\cdtitle{Variatons and Rondo in B~flat for bassoon and orchestra}.
\see{1589}.

\cd\relax
\artist{Kamiya, Michiko}.
\cdtitle{Violin Recital \: \track \C{Ludwig van Beethoven} Violin Sonata
  in A~major, Op.~12, No.~2 \; \track \C{Franz Schubert} Duo Sonata in
  A~major, D574 \; \track \C{Camille Saint-Sa\"ens} Violin Sonata No.~1
  in D~minor, Op.~75 \; \track \C{Robert Schumann} Violin Sonata No.~1
  in A~minor, Op.~105 \; \track \C{Igor Stravinsky} Duo Concertant \;
  \track \C{T\=oru Takemitsu} Distance de F\'ee \; \track \C{Joseph
  Joachim} Drei St\"ucke, Op.~2, No.~1 \; \track \C{Henryk Wieniawski}
  Polonais brillante, Op.~21}.
Ian Brown (piano).
Naxos, 1999 \cdnum[2]{8.554401--02}.

\cd\relax
\artist{Kansas}.
\cdtitle{Kansas}.
Sony, 1994/1998 \cdnum[2]{Z2K~65432}.

\cd\relax
\artist{Kapell, William}.
\cdtitle{Liszt/Bach/Rachmaninoff/Chopin/Alb\'eniz/Prokofiev \: \track
  \C{Isaac Alb\'eniz} Evocaci\'on \(\from Iberia, Book~1\) \; \track
  \C{Johann Sebastian Bach} Partita No.~4 in~D, BWV~828 \; \track
  \C{Fr\'ed\'eric Chopin} Piano Sonata No.~3 in B~minor, Op.~48 \;
  \track \C{Franz Liszt} Sonetto 104 del Petrarca \and Hungarian
  Rhapsody No.~11 \and ``Mephisto'' Waltz No.~1 \; \track \C{Serge
  Prokofiev} Piano Concerto No.~3 in~C, Op.~25 \; \track \C{Sergei
  Rachmaninoff} Piano Concerto No.~2 in C~minor, Op.~18 \and Rhapsody on
  a Theme by Paganini, Op.~43}.
Volume~52 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 853-2}.

\cd\relax
\artist{Kapilow, Rob}.
\cdtitle{What Makes It Great? Mozart's Eine Kleine Nachtmusik}.
I Solisti di Zagreb.
Antonio Janigro, cond.
Artemis Classics, 2004 \cdnum{ATM CD~1542}.

\cd\relax
\artist{Kapilow, Rob}.
\cdtitle{What Makes It Great? Mozart's Jupiter Symphony}.
Vienna State Opera Orchestra.
Felix Prohaska, cond.
Artemis Classics, 2004 \cdnum{ATM CD~1541}.

\cd*\relax
\artist{Kapsberger, Johann Hieronymus}.
\cdtitle{Toccata~I \from ``Libro IV d'intavolatura di chitarrone''}.
\see{1308}.

\cd*\relax
\artist{Kapustin, Nikolai}.
\cdtitle{Toccatina, Op.~36}.
\see{724}.

\cd*\relax
\artist{Karasikov, Vadim}.
\cdtitle{Casus in terminus \(1995\)}.
\see{484}.

\cd\relax
\artist{Karr, Gary}.
\cdtitle{Virtuose Kontraba{\ss}konzerte \: \track \C{Sergej
  Koussevitzky} Konzert f\"ur Kontraba{\ss} und Orchester op.~3 \;
  \track \C{Domenico Dragonetti} Konzert A-dur f\"ur Kontraba{\ss} und
  Orchester \; \track \C{Niccolo Paganini} Bravourvariationen \"uber ein
  Thema aus der Oper ``Moses in \"Agypten'' von Rossini}.
Koch, 1980 \cdnum{361 332 H1}.

\cd\relax
\artist{Karr, Matthew}.
\cdtitle{A Bassoonist's Voice \: \track \C{Johann Sebastian Bach}
  Partita in a~minor \; \track \C{Heitor Villa-Lobos} Bachianas
  Brasileiras No.~6 \; \track \C{Jean Francaix} Divertissement for
  Bassoon and String Quintet \; \track \C{Giacomo Cervetto} Sicilienne
  \; \track \C{Robert Schumann} Fantasiestucke, Op.~73 \; \track
  \C{Thomas Dunhill} Lyric Suite}.
Centaur Records, 1997 \cdnum{CRC 2330}.

\cd\relax
\artist{Katchen, Julius}.
\cdtitle{Brahms/Chopin/Franck/Liszt/Mendelssohn/Rorem \: \track \C{Mili
  Balakirev} Islamey \; \track \C{Felix Mendelssohn Bartholdy} Prelude
  and Fugue in E~minor, Op.~35 No.~1 \and Rondo capriccioso in~E, Op.~14
  \; \track \C{Johannes Brahms} Piano Sonata in F~minor, Op.~5 \and
  Variations on an Original Theme, Op.~21 No.~1 \and Hungarian Dances,
  Vol.~1 \; \track \C{Fr\'ed\'eric Chopin} Ballade No.~3 in A~flat,
  Op.~47 \and Fantasy in F~minor, Op.~49 \; \track \C{C\'esar Franck}
  Pr\'elude, choral et fugue \; \track \C{Franz Liszt} Hungarian
  Rhapsody No.~12 \; \track \C{Ned Rorem} Piano Sonata No.~2}.
Volume~53 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 856-2}.

\cd\relax
\artist{Katchen, Julius}.
\cdtitle{Dohn\'anyi/Gershwin/Prokofiev/Rachmaninoff \: \track \C{George
  Gershwin} Rhapsody in Blue \; \track \C{Maurice Ravel} Piano Concerto
  in~D ``for the left Hand'' \and Piano Concerto in~G \; \track
  \C{Sergei Rachmaninoff} Rhapsody on a Theme by Paganini, Op.~43 \;
  \track \C{Ludwig van Beethoven} Rondo for Piano and Orchestra in
  B~flat, WoO~6 \; \track \C{Franz Liszt} Piano Concerto No.~2 in~A \;
  \track \C{Ernst von Dohn\'anyi} Variations on a Nursery Tune, Op.~25
  \; \track \C{Sergei Prokofiev} Piano Concerto No.~3, Op.~26}.
Volume~54 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 859-2}.

\cd*\relax
\artist{Kaufmann, Walter}.
\cdtitle{Meditation}.
\see{1603}.

\cd\relax
\artist{Keane, Se{\'a}n}.
\cdtitle{All Heart, No Roses}.
Shanachie Entertainment, 1994 \cdnum{79085}.

\cd\relax
\artist{Keane, Se{\'a}n}.
\cdtitle{Turn a Phrase}.
Kells Music, 1996(?) \cdnum{KM 9508}.

\cd*\relax
\artist{Keiser, Reinhard}.
\cdtitle{Le Ridicule Prince Jodelet}.
\see{10}.

\cd\relax
\artist{Kempff, Wilhelm}.
\cdtitle{Bach-Kempff/Beethoven/Liszt/Mozart/Schubert \: \track \C{Franz
  Schubert} Piano Sonata in A~minor, D.~845 \; \track \C{Ludwig van
  Beethoven} Piano Sonata in E~minor, Op.~90 \; \track \C{Wolfgang
  Amadeus Mozart} Piano Concerto No.~23 in~A, KV~488 \; \track \C{Franz
  Liszt} Deux L\'egendes \and Ann\'ees de p\`elerinage \; \track
  \C{Johann Sebastian Bach and Wilhelm Kempff} Nun komm' der Heiden
  Heiland, BWV~659 \and Jesus bleibet meine Freude \(\from BWV~147\)
  \and Wachtet auf! ruft uns die Stimme \(\from BWV~140\)}.
Volume~56 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 865-2}.

\cd\relax
\artist{Kempff, Wilhelm}.
\cdtitle{Beethoven/Brahms/Faur\'e/Mozart/Schubert \: \track \C{Wolfgang
  Amadeus Mozart} Piano Concerto No.~8 in~C, KV~246 ``L\"utzow'' \and
  Ten Variations in~G, KV~455 on ``Unser dummer P\"obel meint'' \(C.~W.
  Gluck\) \; \track \C{Ludwig van Beethoven} Piano Sonata No.~11 in
  B~flat, Op.~22 \and Rondo in~C, Op.~51 No.~1 \and Piano Sonata No.~2
  in~A, Op.~2 No.~2 \; \track \C{Johannes Brahms} Rhapsody in B~minor,
  Op.~79 No.~1 \and Rhapsody in G~minor, Op.~79 No.~2 \; \track \C{Franz
  Schubert} Piano Sonata in~C, D.~840 ``Reliquie'' \; \track \C{Robert
  Schumann} 3 Romanzen, Op.~28 \; \track \C{Gabriel Faur\'e} Nocturne
  No.~6 in D~flat, Op.~63}.
Volume~57 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 868-2}.

\cd\relax
\artist{Kempff, Wilhelm}.
\cdtitle{Brahms/Schumann \: \track \C{Johannes Brahms} Ballades, Op.~10
  \and Fantasias, Op.~116 \and Intermezzi, Op.~117 \and Klavierst\"ucke,
  Op.~118 \and Klavierst\"ucke, Op.~119 \and Klavierst\"ucke, Op.~76 \;
  \track \C{Robert Schumann} Arabeske in~C, Op.~18 \and Kreisleriana,
  Op.~16}.
Volume~55 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 862-2}.

\cd\relax
\artist{Kenins, Talivaldis}.
\cdtitle{\track Sonata for cello and piano \(1950\) \; \track
  Concertante for flute and piano \(1966\) \; \track Piano Quartet No.~2
  \(1979\)}.
Paul Meyer (violin), Steven Dann (viola), David Hetherington (cello) and
  William Aide (piano).
Centrediscs, 1997 \cdnum{CMC-CD 5997}.

\cd\relax
\artist{Kerman, Joseph}, ed.
\cdtitle{Listen: Third Brief Edition}.
Worth Publishers and Sony Music Special Products, 1995 \cdnum[6]{A6A 26259}.

\cd*\relax
\artist{Keulen, Geert van}.
\cdtitle{Kwartet}.
\see{51}.

\cd*\relax
\artist{Keuris, Tristan}.
\cdtitle{Music for Saxophones}.
\see{51}.

\cd*\relax
\artist{Khachaturian, Aram}.
\cdtitle{Concerto-Rhapsody}.
\see{1315}.

\cd\relax
\artist{Khachaturian, Aram}.
\cdtitle{Piano Concerto \and Violin Concerto \and Masquerade---Suite
  \and Symphony No.~2}.
The Decca Record Company, 1996 \cdnum[2]{448 252-2}.

\cd\relax
\artist{Khachaturian, Aram}.
\cdtitle{\track Spartacas \(excerpts\) \; \track Gayahen \(excerpts\) \;
  \track \C{Alexander Glazunov} The Seasons, op.~67}.
Wiener Philharmoniker.
Aram Khachaturian, cond.
Decca, 1962/1967 \cdnum{289 460 315-2}.

\cd*\relax
\artist{Khachaturian, Karen}.
\cdtitle{Cello Sonata}.
\see{1315}.

\cd*\relax
\artist{Khudoyan, Adam}.
\cdtitle{Sonata No.~1 for Cello Solo \and Sonata No.~2 for Cello Solo
  \and Sonata No.~3 for Cello Solo}.
\see{149}.

\cd*\relax
\artist{Kibbe, Michael}.
\cdtitle{Ebony Suite}.
\see{1598}.

\cd\relax
\artist{King, Ben E.}
\cdtitle{The Best of Ben E. King}.
Curb Records, 1993 \cdnum{D2-77594}.

\cd\relax
\artist{King, Thea and Clifford Benson}.
\cdtitle{English Music for Clarinet \: \track \C{Charles Villiers
  Stanford} Sonata for clarinet and piano Op~129 \; \track \C{Howard
  Ferguson} Four Short Pieces Op~6 \; \track \C{Gerald Finzi} Five
  Bagatelles Op.~23 \; \track \C{William Yeates Hurlstone} Four
  Characteristic Pieces \; \track \C{Herbert Howells} Sonata for
  clarinet and piano \; \track \C{Arthur Bliss} Pastoral \; \track
  \C{Franz Reizenstein} Arabesques Op~47 \; \track \C{Arnold Cooke}
  Sonata in B~flat for clarinet and piano}.
Hyperion, 1997 \cdnum[2]{CDD22027}.

\cd\relax
\artist{King's Singers, The}.
\cdtitle{All at Once Well Met: English Madrigals}.
EMI Records, 1987 \cdnum{CDC~7 49265~2}.

\cd\relax
\artist{King's Singers, The}.
\cdtitle{Good Vibrations}.
RCA Victor, 1992 \cdnum{09026-60938-2}.

\cd\relax
\artist{Kinks, The}.
\cdtitle{Lola versus Powerman and the Moneygoround}.
Reprise Records, 1970 \cdnum{6423-2}.

\cd\relax
\artist{Kinks, The}.
\cdtitle{Muswell Hillbillies}.
Rhino Records, 1971 \cdnum{R2 70934}.

\cd*\relax
\artist{Kirchner, Leon}.
\cdtitle{Music for Cello and Orchestra}.
\see{1012}.

\cd*\relax
\artist{Kirchner, Leon}.
\cdtitle{Tryptych}.
\see{1007}.

\cd\relax
\artist{Kissin, Evgeny}.
\cdtitle{\track \C{Ferruccio Busoni} Chaconne in D~minor \(arr.\ from
  J.~S. Bach's Partita No.~2 for Violi, BWV~1004\) \; \track \C{Ludwig
  van Beethoven} Rondo, Op.~51 No.~2 \and Rondo a capriccio, Op.~129
  ``Rage over a Lost Penny'' \; \track \C{Robert Schumann} Kreisleriana,
  Op.~16}.
BMG Entertainment, 1998 \cdnum{09026-68911-2}.

\cd\relax
\artist{Kissin, Evgeny}.
\cdtitle{Liszt/Prokofiev \: \track \C{Franz Liszt} Hungarian Rhapsody
  No.~12 \and Liebestraum No.~3 \and Soir\'ees de Vienne: Valse-Caprice
  No.~6, S.~427 \(after Schubert\) \and Spanish Rhapsody \and \'Etudes
  d'ex\'ecution transcendante Nos.~10, 11, and~12 \; \track \C{Sergei
  Prokofiev} Piano Sonata No.~6 in~A, Op.~82 \and Overture on Hebrew
  Themes, Op.~34 \and Visions fugitives, Op.~22, Nos.~10, 11, 16, and~17
  \and Piano Concerto No.~3 in~C, Op.~26 \and Etude in C~minor, Op.~2,
  No.~3 \; \track \C{Franz Schubert and Franz Liszt} Gretchen am
  Spinnrade \and Auf dem Wasser zu singen \and Die Forelle \; \track
  \C{Franz Schubert and Carl Tausig} Marche militaire}.
Volume~58 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 871-2}.

\cd\relax
\artist{Klezmonauts, The}.
\cdtitle{Oy to the World! A Klezmer Christmas}.
Satire Records, 1998 \cdnum{0175}.

\cd\relax
\artist{Kliegel, Maria}.
\cdtitle{Virtuoso Cello Encores \: \track \C{Gaspar Cassad\'o} Dance of
  the Green Devil \; \track \C{David Popper} Fantasy on Little Russian
  Songs \and Serenade, Op.~54, No.~2 \; \track \C{Johann Sebastian Bach}
  Air from Suite No.~3 in~D, BWV~1068 \; \track \C{Franz Schubert}
  St\"andchen \(Serenade\) \; \track \C{Franz Schubert} Die Biene \(The
  Bee\) \; \track \C{Enrique Granados} Intermezzo from Goyescas \;
  \track \C{Dmitry Shostakovich} Tarantella from The Gadfly, Op.~97 \;
  \track \C{Maurice Ravel} Habanera \; \track \C{Claude Debussy} The
  Girl with the Flaxen Hair \; \track \C{Jean Baptiste Senaill\'e}
  Allegro spiritoso \; \track \C{Henri Vieuxtemps} Cantilena, Op.~48,
  No.~24 \; \track \C{Siegfried Barchet} Boulevard de Garavan \; \track
  \C{Jacques Offenbach} Danse boh\'emienne, Op.~28 \; \track \C{Sergey
  Rachmaninov} Vocalise, Op.~34, No.~14 \; \track \C{George Gershwin}
  Short Story}.
Raimund Havenith (piano).
Naxos, 1991/2005 \cdnum{8.557943}.

\cd\relax
\artist{Kl\"ocker, Dieter}.
\cdtitle{Die Kunst der Klarinette}.
Orfeo, 2000.

\cd*\relax
\artist{Klughardt, August}.
\cdtitle{Quintet, Op.~79}.
\see{1687}.

\cd*\relax
\artist{Knipper, Lev}.
\cdtitle{Concerto-Monologue for cello, seven brass instruments and two
  kettledrums}.
\see{1315}.

\cd\relax
\artist{Knopfler, Mark}.
\cdtitle{Golden Heart}.
Warner Brothers, 1996 \cdnum{9 46026-2}.

\cd\relax
\artist{Knopfler, Mark}.
\cdtitle{Kill to Get Crimson}.
Warner Brothers, 2007 \cdnum{281660-2}.

\cd\relax
\artist{Knopfler, Mark}.
\cdtitle{Sailing to Philadelphia}.
Warner Brothers, 2000 \cdnum{9 47753-2}.

\cd\relax
\artist{Knopfler, Mark}.
\cdtitle{Shangri-La}.
Warner Brothers, 2004 \cdnum{48858-2}.

\cd\relax
\artist{Knopfler, Mark}.
\cdtitle{The Ragpicker's Dream}.
Warner Brothers, 2002 \cdnum{9 48318-2}.

\cd\relax
\artist{Knots and Crosses}.
\cdtitle{There Was a Time}.
Crossongs Records, 1999 \cdnum{SIG~1252}.

\cd\relax
\artist{Knussen, Oliver and Maurice Sendak}.
\cdtitle{Where the Wild Things Are}.
Rosemary Hardy and Mary King.
London Sinfonietta.
Oliver Knussen, cond.
Arabesque, 1985 \cdnum{Z6535-L}.

\cd\relax
\artist{Kocsis, Zolt\'an}.
\cdtitle{Bart\'ok/Debussy/Dohn\'anyi/Grieg/Rachmaninoff \: \track
  \C{B\'ela Bart\'ok} Roumanian Folk Dances, Sz.~56 \; \track \C{Claude
  Debussy} Deux Arabesques \and D'un cahier d'esquisses \and Suite
  bergamasque \and L'isle joyeuse \and Estampes \and Fantasy for Piano
  and Orchestra \; \track \C{Ernst von Dohn\'anyi} Variations on a
  Nursery Song, Op.~25 \; \track \C{Edvard Grieg} Lyric Pieces, Op.~43
  \; \track \C{Franz Liszt} Les jeux d'eaux \`a la Villa d'Este \;
  \track \C{Sergei Rachmaninoff} Piano Concerto No.~4 in G~minor, Op.~40
  \and Prelude in C~sharp minor, Op.~3, No.~2 \and Vocalise, Op.~34,
  No.~14}.
Volume~59 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 874-2}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{An Ode for Music: Choruses for Mixed Voices}.
Chamber Choir of P\'ecs.
Aur\'el Tillai, cond.
Hungaroton Classic, 1994 \cdnum{HCD 31524}.

\cd*\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{Duo for Violin and Violoncello}.
\see{486}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{H\'ary J\'anos Suite \and Dances of Gal\'anta \and Peacock
  Variations \and Dances of Marossz\'ek \and Theatre Overture \and
  Concerto for Orchestra \and Summer Evening \and Symphony in~C}.
Philharmonia Hungarica.
Antal Dorati, cond.
The Decca Record Company, 1994 \cdnum[2]{443 006-2}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{Music for Cello \: \track Three Chorale Preludes \; \track
  Sonata for Solo Cello, Op.~8 \; \track Sonata for Cello and Piano,
  Op.~4}.
Maria Kliegel (cello) and Jen\H{o} Jand\'o (piano).
Naxos, 1996 \cdnum{8.553160}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{Music for Cello, Volume~2 \: \track Prelude and Fugue for Cello
  and Piano (Bach, tr.~Kod\'aly) \; \track Sonatina for Cello and Piano
  \; \track Adagio for Cello and Piano \; \track Capriccio for Solo
  Cello \; \track Hungarian Rhondo for Cello and Piano \; \track Duo,
  Op.~7, for Violin and Cello}.
Maria Kliegel (cello), William Preucil (violin) and Jen\H{o} Jand\'o
  (piano).
Naxos, 1999 \cdnum{8.554039}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{Music for Solo Piano \: \track Nine Piano Pieces \(Kilenc
  Zongoradarab\), Op.~3 \; \track Seven Piano Pieces, Op.~11 \; \track
  M\'editation sur un motif de Claude Debussy \; \track Dances of
  Marossz\'ek \(Marossz\'eki t\'ancok\)}.
Mary Warnecke.
Tall Poppies Records, 1997 \cdnum{TP104}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{Psalmus Hungaricus op.~13 \and Missa Brevis}.
Budapest Philharmonic Orchestra and Hungarian Radio Choir and Children's
  Choir.
Arp\'ad J\'oo, cond.
Arts Music, 1997 \cdnum{47378-2}.

\cd*\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{Sonata for Solo Cello, Op.~8}.
\see{1017}.

\cd*\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{Sonata for violoncello opus~8}.
\see{1438}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{Sonate pour violoncelle seul op.~8 \and Sonate pour violoncelle
  et piano op.~4}.
Llu{\'\i}s Claret (violoncelle) and Rose-Marie Cabestany (piano).
Harmonia Mundi, 1995 \cdnum{HMA 1901325}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{Spinning Room \and M\'onar Anna \and K\'ad\'ar Kata \and The
  K\'all\' Double Dance}.
Hungarian Radio and Television Chorus, Budapest Philharmonic Orchestra,
  and Hungarian State Orchestra.
J\'anos Ferencsik, Gy\"orgy Lehel, and Zolt\'an V\'as\'arhelyi, cond.
Hungaroton Classic, 1996 \cdnum[2]{HCD 12839-40}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{Starker Plays Kod\'aly \: \track Sonata for Unaccompanied
  Cello, Op.~8 \; \track Duo for Violin and Cello, Op.~7 \; \track
  \C{Bottermund-Starker} Variations on a Theme by Paganini}.
Janos Starker (cello) and Josef Gingold (violin).
Delos International, 1987 \cdnum{DE~105}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{String Quartets Nos.~1 and~2}.
The Audobon Quartet.
Centaur Records, 1998 \cdnum{CRC 2372}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{The Choral Music of Kod\'aly~1 \: \track Hymn of Zr{\'\i}nyi \;
  \track Jesus and the traders \; \track The aged \; \track Norwegian
  girls \; \track Too late \; \track Ode to Liszt}.
Lajos Miller (baritone).
Hungarian Radio and Television Chorus.
J\'anos Ferencsik, cond.
Hungaroton Classic, 1995 \cdnum{HCD 12352}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{The Choral Music of Kod\'aly~3}.
Hungaroton Classic, 1997 \cdnum{HCD 31697}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{The Choral Music of Kod\'aly~7}.
Cantemus (Ny{\'\i}regyh\'aza).
D\'enes Szab\'o, cond.
Hungaroton Classic, 1994 \cdnum{HCD 31291}.

\cd\relax
\artist{Kod\'aly, Zolt\'an}.
\cdtitle{Works with Organ \: \track Organoedia ad missam lectam \;
  \track Psalm No~114 \; \track Pangue lingua \; \track Laudes organi}.
G\'abor Lehotka.
Hungarian Radio and Television Chorus.
J\'anos Ferencsik and Zolt\'an V\'as\'arhelyi, cond.
Hungaroton Classic, 1997 \cdnum{HCD~31682}.

\cd*\relax
\artist{Korngold, Erich Wolfgang}.
\cdtitle{Concerto for Violin and Orchestra in D~major, op.~35}.
\see{1571}.

\cd*\relax
\artist{Korngold, Erich Wolfgang}.
\cdtitle{Piano Concerto in C~sharp, Op~17}.
\see{723}.

\cd\relax
\artist{Korngold, Erich Wolfgant}.
\cdtitle{Suite for 2 Violins, Cello and Piano Left Hand, Op.~25 \and
  \C{Franz Schmidt} Quintet in G~major for 2 Violins, Viola, Cello and
  Piano Left Hand}.
Leon Fleisher (piano), Joseph Silversteen (violin), Joel Smirnoff
  (violin), Michael Tree (viola) and Yo-Yo Ma (cello).
Sony Classical, 1998 \cdnum{SK~48253}.

\cd\relax
\artist{Kornog}.
\cdtitle{Ar Seiz Avel/On Seven Winds}.
Green Linnet, 1985 \cdnum{GLCD 1062}.

\cd\relax
\artist{Kornog}.
\cdtitle{Premi\`ere}.
Green Linnet, 1984 \cdnum{GLCD 1055}.

\cd*\relax
\artist{Kosins, Martin Scot}.
\cdtitle{Rendezvous and Dreams: A Romance for Oboe and Piano}.
\see{432}.

\cd\relax
\artist{Kotova, Nina}.
\cdtitle{\track Reminiscence \; \track Dark Blue \; \track Sketches from
  the Catwalk \; \track \C{Rachmaninov, Sergei} Romance \(Ne poi,
  Krasavitsa\), Op.~4 \and Vocalise, Op.~34, No.~14 \; \track \C{Piotr
  Ilich Tchaikovsky} Nocturne, Op.~19, No.~4 in D~minor \; \track
  \C{Alexander Glazunov} \'El\'egie in D-flat, Op.~17 \(Pens\'ee \`a
  Liszt\) \and Entracte \(to scene~II\) from Raymonda \; \track
  \C{Fr\'ed\'eric Chopin} \'Etude Op.~25, No.~7 \; \track \C{Igor
  Stravinsky} Danse Russe \emph{from} P\'etrouchka \; \track \C{Gabriel
  Faur\'e} \'El\'egie \; \track \C{Nicolai Rimsky-Korsakov} Hymn to the
  Sun \(Turkish Princess\) \; \track \C{Lyavov} Preludia, Op.~11, No.~1
  \; \track \C{Manuel de Falla} Ritual Fire Dance \from El Amor brujo}.
Moscow Chamber Orchestra.
Constantine Orbelian, cond.
Philips Classics, 1999 \cdnum{289 462 612-2}.

\cd*\relax
\artist{Koussevitzky, Sergej}.
\cdtitle{Konzert f\"ur Kontraba{\ss} und Orchester op.~3}.
\see{880}.

\cd\relax
\artist{Kovacevich, Stephen}.
\cdtitle{Beethoven \: \track \C{Ludwig van Beethoven} Piano Sonata in
  C~minor, Op.~10 No.~1 \; \track \C{Fr\'ed\'eric Chopin} Nocturne
  No.~17 in~B, Op.~62, No.~1 \and Nocturne No.~18 in~E, Op.~62, No.~2
  Impromptu No.~3 in G|flat, Op.~51 \; \track \C{Johannes Brahms} 4
  Piano Pieces, Op.~119 \; \track \C{B\'ela Bart\'ok} Out of Doors,
  BB~89, Sz.~81 \and Sonatina, BB~69, Sz.~55 \and Piano Concerto No.~2,
  BB~101, Sz.~95 \; \track \C{Igor Stravinsky} Concerto for Piano and
  Wind Instruments \; \track \C{Richard Rodney Bennett} Piano Concerto
  No.~1}.
Volume~61 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 880-2}.

\cd\relax
\artist{Kovacevich, Stephen}.
\cdtitle{Beethoven \: \C{Ludwig van Beethoven} Piano Sonata in C~minor,
  Op.~13 ``Path\'etique'' \and Piano Sonata in D~minor, Op.~31 No.~2
  ``Tempest'' \and Piano Sonata in E~flat, Op.~31 No.~3 ``Hunt'' \and
  Piano Sonata in~A, Op.~101 \and Piano Sonata in~E, Op.~109 \and Piano
  Sonata in~A~flat, Op.~110 \and Piano Sonata in~C~minor, Op.~111}.
Volume~60 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 877-2}.

\cd*\relax
\artist{Krebs, Johann Ludwig}.
\cdtitle{Concerto in B~minor for Harpsichord, Oboe, Strings and
  Continuo}.
\see{783}.

\cd*\relax
\artist{Kreisler, Fritz}.
\cdtitle{Liebesleid \and Liebesfreud}.
\see{1233}.

\cd*\relax
\artist{Kreisler, Fritz}.
\cdtitle{Praeludium and Allegro \and Sch\"on Rosmarin \and Tamburin
  chinois \and La Pr\'ecieuse \and Liebesfreud \and Liebesleid \and La
  gitana \and Berceuse romantique \and Polichinelle \and Rondino \(on a
  theme by Beethoven\) \and Tempo di minuetto \and Toy-Soldier's March
  \and Allegretto \and Marche miniature viennoise \and Aucassin and
  Nicollete \and Menuett \and Sicilienne and Rigaudon \and Syncopation}.
\see{245}.

\cd*\relax
\artist{Krenek, Ernst}.
\cdtitle{Symphonic Elegy for String Orchestra}.
\see{256}.

\cd*\relax
\artist{Kreutzer, Conradin}.
\cdtitle{Varations in B~flat for bassoon and orchestra}.
\see{1589}.

\cd*\relax
\artist{Krol, Bernhard}.
\cdtitle{Magnificat-Variationen f\"ur Trompete und Streichorchester,
  op.~40}.
\see{1523}.

\cd*\relax
\artist{Krol, Bernhard}.
\cdtitle{Sinfonia sacra ``Jesu, meine Freude'', Op.~56}.
\see{1599}.

\cd\relax
\artist{Krommer, Franz}.
\cdtitle{Clarinet Concertos \: \track Concerto for Two Clarinets in
  E~flat major, Op.~35 \; \track Clarinet Concerto in E~flat major,
  Op.~36 \; \track Concerto for Two Clarinets in E~flat major, Op.~91}.
K\'alm\'an Berkes, Kaori Tsutsui and Tomoko Takashima.
Nicolaus Esterh\'azy Sinfonio.
K\'alm\'an Berkes, cond.
Naxos, 1995 \cdnum{8.553178}.

\cd\relax
\artist{Krommer, Franz}.
\cdtitle{Partitas for Wind Ensemble \: \track Partita in E~flat major,
  Op.~45, No.~1, FVK~1 \; \track Partita in B~flat major, Op.~45, No.~2,
  FVK~2 \; \track Partita in E~flat major with two solo horns, FVK~2d}.
Michael Thompson Wind Ensemble.
Naxos, 1999 \cdnum{8.553868}.

\cd\relax
\artist{Krommer, Franz}.
\cdtitle{Partitas for Wind Ensemble \: \track Partita in F~Major, Op.~57
  \; \track Partita in B~Flat Major, Op.~78 \; \track Partita in E~Flat
  Major, Op.~71 \; \track Three Marches from \emph{Six Marches}
  \(Nos.~3--5\)}.
Budapest Wind Ensemble.
K\'alm\'an Berkes, cond.
Naxos, 1996 \cdnum{8.553498}.

\cd\relax
\artist{Krommer, Franz}.
\cdtitle{Partitas for Wind Ensemble, Volume~3 \: \track Partita in
  E~flat major, Op.~69 \; \track Partita in C~major, Op.~76 \; \track
  Partita in E~flat major, Op.~79}.
Michael Thompson Wind Ensemble.
Naxos, 2001 \cdnum{8.554226}.

\cd*\relax
\artist{Kulesha, Gary}.
\cdtitle{Bagatelles from ``The Devil's Dictionary''}.
\see{4}.

\cd*\relax
\artist{Kulesha, Gary}.
\cdtitle{Political Implications}.
\see{1598}.

\cd*\relax
\artist{Kurrasch, Ann Marie}.
\cdtitle{Ponderings from the Pond}.
\see{1161}.

\cd*\relax
\artist{Kurt\'ag, Gy\"orgy}.
\cdtitle{Hommage \`a Tristan \and Versetto \and Summaia~a}.
\see{1344}.

\cd*\relax
\artist{Kyburz, Hanspeter}.
\cdtitle{Cells}.
\see{578}.

\cd\relax
\artist{Ladysmith Black Mambazo}.
\cdtitle{Thuthukani Ngoxolo: Let's Develop in Peace}.
Shanachie Entertainment, 1996 \cdnum{64064}.

\cd*\relax
\artist{Lajtha, L\'aszl\'o}.
\cdtitle{Sonata for Cello and Piano, Op.~17 \and Concerto for Cello and
  Piano, Op.~31}.
\see{492}.

\cd*\relax
\artist{Lalo, Edouard}.
\cdtitle{Cello Concerto in D~minor}.
\see{1510}.

\cd*\relax
\artist{Lalo, \'Edouard}.
\cdtitle{Symphonie espagnole, op.~21}.
\see{247}.

\cd\relax
\artist{Lambert, Constant}.
\cdtitle{Concerto for Piano and Nine Players \and Eight Poems of Li-Po
  \and Sonata for Piano \and Mr Bear Squash-you-all-flat}.
Ian Brown (piano), Philip Langridge (tenor) and Nigel Hawthorne
  (narrator).
The Nash Ensemble.
Lionel Friend, cond.
Hyperion, 1995 \cdnum{CDA66754}.

\cd*\relax
\artist{Lambert, Constant}.
\cdtitle{Suite from the incidental music to \emph{Salome}}.
\see{1681}.

\cd\relax
\artist{Larkin, Patty}.
\cdtitle{Angels Running}.
Windham Hill Records, 1993 \cdnum{72902 10318-2}.

\cd\relax
\artist{Larkin, Patty}.
\cdtitle{I'm Fine}.
Rounder Records, 1987 \cdnum{Philo CD PH-1115}.

\cd\relax
\artist{Larkin, Patty}.
\cdtitle{Tango}.
Windham Hill Records, 1991 \cdnum{10312-2}.

\cd*\relax
\artist{Larsen, Libby}.
\cdtitle{Holly roller \(1997\)}.
\see{1601}.

\cd\relax
\artist{Larson, Jonathan}.
\cdtitle{Rent}.
Dreamworks, 1996 \cdnum[2]{DRMD2-50003}.
Original Broadway cast recording.

\cd*\relax
\artist{Larsson, Lars-Erik}.
\cdtitle{Concertino for trombone and strings, Op.~45 No.~7}.
\see{965}.

\cd*\relax
\artist{Larsson, Lars-Erik}.
\cdtitle{Concerto for Alto Saxophone and String Orchestra, Op.~14}.
\see{23}.

\cd\relax
\artist{Lau, Andy}.
\cdtitle{???}
EMI Hong Kong, 1989 \cdnum{FH 100712}.

\cd\relax
\artist{Laurin, Dan}.
\cdtitle{The Japanese Recorder \: \track \C{Maki Ishii} Black Intention
  \and east$\bullet$green$\bullet$spring \; \track \C{Ryohei Hirose}
  Hymn \and Meditation \; \track \C{Kikuko Masumoto} Pastorale \; \track
  \C{Makoto Shinohara} Fragmente}.
BIS, 1993/1994 \cdnum{BIS-CD-655}.

\cd\relax
\artist{Lavin, Christine}.
\cdtitle{Future Fossils}.
Palindrome Records, 1986 \cdnum{Philo CD~1104}.

\cd\relax
\artist{Lavin, Christine}.
\cdtitle{Good Thing He Can't Read My Mind}.
Rounder Records, 1988 \cdnum{Philo CD PH~1121}.

\cd\relax
\artist{Lebrun, Ludwig August}.
\cdtitle{Concertos for Oboe and Orchestra \: \track Concerto No.~1 in
  D~minor \; \track Concerto No.~2 in G~minor \; \track Concerto No.~3
  in C~major \; \track Concerto No.~4 in B~flat major \; \track Concerto
  No.~5 in C~major \; \track Concerto No.~6 in F~major \; \track
  \C{Wolfgang Amadeus Mozart} Concerto for Oboe and Orchestra in
  C~major, K.~314 \(285d\)}.
Heinz Holliger (oboe).
Camerata Bern.
Thomas F\"uri, cond.
Deutsche Grammophon, 1980/1982 \cdnum[2]{471 724-2}.

\cd*\relax
\artist{Lee, Hye Kyung}.
\cdtitle{Sonatina for Soprano Saxophone and Piano, movement~II}.
\see{23}.

\cd\relax
\cdtitle{Legacy: A Collection of New Folk Music}.
Windham Hill Records, 1989 \cdnum{WD6-1086}.

\cd\relax
\artist{Lehrer, Tom}.
\cdtitle{An Evening Wasted with Tom Lehrer}.
Reprise Records, 1959 \cdnum{6199-2}.

\cd\relax
\artist{Lehrer, Tom}.
\cdtitle{That Was the Year That Was}.
Reprise Records, 1965 \cdnum{6179-2}.

\cd\relax
\artist{Lehrer, Tom}.
\cdtitle{Tom Lehrer Revisited}.
Reprise Records, 1959 \cdnum{26203-2}.

\cd*\relax
\artist{Lennon, John Anthony}.
\cdtitle{Distances Within Me}.
\see{505}.

\cd\relax
\artist{Leoncavallo, Ruggiero}.
\cdtitle{Pagliacci}.
Coro e Orchestra dell Teatro alla Scala.
Herbert von Karajan, cond.
Deutsche Grammophon, 1966 \cdnum{449 727-2}.

\cd*\relax
\artist{Leo\v{s}.
\cdtitle{Jan\'a\v{c}ek} Ml\'ad{\'\i}}.
\see{515}.

\cd*\relax
\artist{Levine, Alexander}.
\cdtitle{Faces}.
\see{1231}.

\cd*\relax
\artist{Lewis, Leonard Mark}.
\cdtitle{As in Stained Light \(2002\)}.
\see{1601}.

\cd\relax
\artist{Lh\'evinne, Josef and Rosina Lh\'evinne}.
\cdtitle{Chopin/Mozart/Schumann \: \track \C{Wolfgang Amadeus Mozart}
  Sonata for Two Pianos in~D, KV~448 \and Piano Concerto No.~21 in~C,
  KV~467 \; \track \C{Robert Schumann} Toccata in~C, Op.~7 \; \track
  \C{Robert Schumann and Franz Liszt} Fr\"ulingsnacht \; \track
  \C{Fr\'ed\'eric Chopin} Etude in E~flat, Op.~10 No.~11 \and Etude in
  G~sharp minor, Op.~25 No.~6 \and Etude in B~minor, Op.~25 No.~10 \and
  Etude in A~minor, Op.~25 No.~11 \and Prelude in B~flat minor, Op.~28
  No.~16 \and Prelude in A~flat, Op.~28 No.~17 \and Polonaise in A~flat,
  Op.~53 \and Piano Concert No.~1 in E~minor, Op.~11 \; \track \C{Johann
  Strauss and Adolf Schulz-Evler} Arabesques on ``An der sch\"onen,
  blauen Donau'' \; \track \C{Claude Debussy and Maurice Ravel} F\^etes
  \(for two pianos\) \; \track \C{Ludwig van Beethoven and Ferrucio
  Busoni} Ecossaises \; \track \C{Robert Schumann and Karl Tausig} Der
  Kontrabandiste \; \track \C{Peter Ilyich Tchaikovsky} Trepak}.
Volume~64 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 889-2}.

\cd*\relax
\artist{Liebermann, Lowell}.
\cdtitle{Sonata for Violin and Piano \(1984\)}.
\see{177}.

\cd\relax
\artist{Ligeti, Gy\"orgy}.
\cdtitle{A~Cappella Choral Works \: \track \'Ejszaka \; \track Reggel \;
  \track Idegen f\"old\"on \; \track Mag\'any \; \track K\'et k\'anon \;
  \track Betlehemi kir\'alyok \; \track Bujdos\'o \; \track Lux aeterna
  \; \track Lakodalmas \; \track Inaktelki n\'ot\'ak \; \track
  M\'atraszentimrei dalok \; \track P\'apain\'e \; \track Dre Phantasien
  nach Friedrich H\"olderlin \; \track Magya Et\"ud\"ok \; \track Haj,
  ifj\'us\'ag! \; \track H\'usv\'et \; \track Hortob\'agy \; \track
  Magos k\H{o}szikl\'anak \; \track K\'allai kett\H{o}s}.
Volume~2 of \emph{Gy\"orgy Ligeti Edition}.
London Sinfonietta Voices.
Terry Edwards, cond.
Sony Classical, 1996 \cdnum{SK~62305}.

\cd\relax
\artist{Ligeti, Gy\"orgy}.
\cdtitle{Chamber Music \: \track Trio for Violin, Horn and Piano \;
  \track Ten Pieces for Wind Quintet \; \track Six Bagatelles for Wind
  Quintet \; \track Sonata for Solo Viola}.
Volume~7 of \emph{Gy\"orgy Ligeti Edition}.
Saschko Gawriloff (violin), Marie-Luise Neunecker (horn), Pierre-Laurent
  Aimard (piano), Philippa Davies (flute), Gareth Hulse (oboe), Michael
  Collins (clarinet), Robin O'Neill (bassoon), Richard Watkins (Horn)
  and Tabea Zimmermann (viola).
Sony Classical, 1998 \cdnum{SK~62309}.

\cd\relax
\artist{Ligeti, Gy\"orgy}.
\cdtitle{Keyboard Works \: \track Indul\'o \; \track Polif\'on et\"ud \;
  \track H\'arom lakodalmi t\'anc \; \track Sonatina \; \track Allegro
  \; \track Capriccio No.~1 \; \track Invention \; \track Capriccio
  No.~2 \; \track Monument \; \track Selbstportrait mit Reich und Riley
  \(und Chopin sit auch dabei\) \; \track In zart flie{\ss}ender
  Bewegung \; \track Passacaglia \; \track Hungarian Rock \; \track
  Continuum \; \track Ricercare \; \track Harmonies \; \track Coul\'ee
  \; \track Volumina}.
Volume~6 of \emph{Gy\"orgy Ligeti Edition}.
Sony Classical, 1997 \cdnum{SK~62307}.

\cd\relax
\artist{Ligeti, Gy\"orgy}.
\cdtitle{Mechanical Music \: \track Adaptations for Barrel Organ:
  Continuum \and Hungarian Rock \and Capriccio No.~1 \and Invention \and
  Capriccio No.~2 \and Musica ricercata \; \track Po\`eme Symphonique
  for 100 Metronomes \; \track Adaptations for Play Piano: \'Etudes pour
  piano \and Continuum}.
Volume~5 of \emph{Gy\"orgy Ligeti Edition}.
Pierre Charial (barrel organ), Fran\c{c}oise Terrioux (metronomes) and
  J\"urgen Hocker (player pianos).
Sony Classical, 1997 \cdnum{SK~62310}.

\cd*\relax
\artist{Ligeti, Gy\"orgy}.
\cdtitle{Six Bagatelles}.
\see{4}.

\cd*\relax
\artist{Ligeti, Gy\"orgy}.
\cdtitle{Sonata (Diaolog e Capriccio) for cello}.
\see{804}.

\cd\relax
\artist{Ligeti, Gy\"orgy}.
\cdtitle{String Quartets and Duets \: \track String Quartet No.~1
  ``M\'etamorphoses nocturnes'' \; \track Hommage \`a Hilding Rosenberg
  for Violin and Violoncello \; \track Balad\u{a} \c{s}i joc \(Ballade
  and Dance for Two Violins\) \; \track Andante and Allegretto for
  String Quartet}.
Volume~1 of \emph{Gy\"orgy Ligeti Edition}.
Arditti String Quartet.
Sony Classical, 1996 \cdnum{SK~62306}.

\cd\relax
\artist{Ligeti, Gy\"orgy}.
\cdtitle{Vocal Works \: \track Nonsense Madrigals \; \track Mysteries of
  the Macabre \; \track Aventures \; \track Nouvelles Aventures \;
  \track Der Sommer \; \track H\'arom We\"ores-dal \(Three We\"ores
  Songs\) \; \track \"Ot Arany-dat \(Five Arany Songs\) \; \track N\'egy
  lakodalmi t\'anc \(Four Wedding Dances\)}.
Volume~4 of \emph{Gy\"orgy Ligeti Edition}.
The King's Singers, Rosemary Hardy, Christian Oelze, Phyllis
  Bryn-Julson, Sibylle Ehlert, Eva Wedin, Malena Ernman, Rose Taylor,
  Omar Ebrahim, Pierre-Laurent Aimard (piano), Irini Kataeva (piano) and
  Members of the Philharmonia Orchestra.
Esa-Pekka Salonen, cond.
Sony Classical, 1996 \cdnum{SK~62311}.

\cd\relax
\artist{Ligeti, Gy\"orgy}.
\cdtitle{Works for Piano \: \track \'Etudes pour piano \(Premier livre\)
  \; \track \'Etudes pour piano \(Deuxi\`eme livre\) \; \track Musica
  ricercata \; \track \'Etudes pour piano \(extrait du Troisi\`eme
  livre\): XV.~White on White}.
Volume~3 of \emph{Gy\"orgy Ligeti Edition}.
Sony Classical, 1996 \cdnum{SK~62308}.

\cd\relax
\artist{LIN Ensemble}.
\cdtitle{Clarinet Trios \: \track \C{Wayne Siegel} Sound Patterns \;
  \track \C{Karsten Fundal} The Ways of Lightness and Falling \; \track
  \C{Svend Hvidtfelt Nielsen} Fable \; \track \C{Pierre D{\o}rge} The
  Big Bird}.
Jens Schou (clarinet), John Ehde (cello) and Erik Kaltoft (piano).
dacapo, 1999 \cdnum{8.224122}.

\cd\relax
\artist{Lindberg, Christian}.
\cdtitle{American Trombone Concertos \: \track \C{Paul Creston} Fantasy
  for Trombone and Orchestra, Op.~42 \; \track \C{George Walker}
  Concerto for Trombone and Orchestra \(1957\) \; \track \C{Gunther
  Schuller} Eine Kleine Posaunenmusik \(1980\) \; \track \C{Ellen Taaffe
  Zwilich} Concerto for Trombone and Orchestra \(1988\)}.
Malm\"o Symphony Orchestra.
James DePreist, cond.
BIS, 1993 \cdnum{BIS-CD-628}.

\cd\relax
\artist{Lindberg, Christian}.
\cdtitle{American Trombone Concertos, Volume~2 \: \track \C{Christopher
  Rouse} Trombone Concerto \(1991\) \; \track \C{Carlos Ch\'avez}
  Concerto para tromb\'on y orquesta \; \track \C{August Read Thomas}
  Meditation for Trombone and Orchestra}.
BBC National Orchestra of Wales.
Grant Llewellyn, cond.
BIS, 1999 \cdnum{BIS-CD-788}.

\cd\relax
\artist{Lindberg, Christian}.
\cdtitle{Classical Trombone Concertos \: \track \C{Michael Haydn}
  Concerto in D~major for Alto Trombone \; \track \C{Georg Christoph
  Wagenseil} Concerto in E~flat major for Alto Trombone \; \track
  \C{Johann Georg Albrechtsberger} Concerto in B~flat major for Alto
  Trombone \; \track \C{Leopold Mozart} Concerto in D major for Alto
  Trombone}.
Australian Chamber Orchestra.
Richard Tognetti, cond.
BIS, 2004 \cdnum{BIS-CD-1248}.

\cd\relax
\artist{Lindberg, Christian}.
\cdtitle{The Solitary Trombone \: \track \C{Luciano Berio} Sequenza~V
  per trombone solo \; \track \C{Iannis Xenakis} Keren per trombone solo
  \; \track \C{Mauricio Kagel} Atem f\"ur einen Bl\"aser \; \track
  \C{Andes Eliasson} Disegno per trombone \; \track \C{John Cage} Solo
  for Sliding Trombone \; \track \C{Karlheinz Stockhausen} In
  Freundschaft f\"ur Solo-Posaune, Werke~46$12\over13$}.
BIS, 1988/1989 \cdnum{BIS-CD-388}.

\cd\relax
\artist{Lindberg, Christian}.
\cdtitle{The Winter Trombone \: \track \C{Antonio Vivaldi} ``Inverno''
  from the Four Seasons, Op.~8 No.~4 \; \track \C{Darius Milhaud}
  Concertino d'hiver for trombone and strings \; \track \C{Lars-Erik
  Larsson} Concertino for trombone and strings, Op.~45 No.~7 \; \track
  \C{Georg Philipp Telemann} Concerto in C~minor \; \track \C{Roland
  P\"ontinen} Bl\'a Vinter}.
New Stockholm Chamber Orchestra.
Okko Kamu, cond.
BIS, 1987/1988 \cdnum{BIS-CD-348}.

\cd\relax
\artist{Lindberg, Christian and Roland P\"ontinen}.
\cdtitle{The Criminal Trombone}.
BIS, 1986/87 \cdnum{BIS-CD-328}.

\cd*\relax
\artist{Linn, Robert}.
\cdtitle{Woodwin Quintet}.
\see{1687}.

\cd\relax
\artist{Lipatti, Dinu}.
\cdtitle{Bach/Chopin/Greig/Ravel/Schubert/Schumann \: \track \C{Johann
  Sebastian Bach} Partita in B~flat, BWV~825 \and ``Jesu, Joy of Man's
  Desiring'' \T{Myra Hess} \; \track \C{Wolfgang Amadeus Mozart} Piano
  Sonata in A~minor, KV~310 \; \track \C{Johannes Brahms} Waltzes,
  Op.~39 \(Excerpts\) \(with Nadia Boulanger\) \; \track \C{Fr\'ed\'eric
  Chopin} Piano Sonata in B~minor, Op.~58 \and Barcarolle in F~sharp,
  Op.~60 \and Nocturne in D~flat, Op.~27, No.~2 \; \track \C{Maurice
  Ravel} Alborada del gracioso \(\from Miroirs\) \; \track \C{Robert
  Schumann} Piano Concerto in A~minor, Op.~54 \; \track \C{Edvard Grieg}
  Piano Concerto in A~minor, Op.~16 \; \track \C{Franz Schubert}
  Impromptu in G~flat, D.~899, No.~3 \and Impromptu in E~flat, D.~899,
  No.~2}.
Volume~65 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 892-2}.

\cd\relax
\artist{Lippa, Andrew and Tom Greenwald}.
\cdtitle{John and Jen}.
Fynsworth Alley, 2003 \cdnum{302 062 1822}.

\cd*\relax
\artist{Liszt, Ferenc}.
\cdtitle{\emph{Die Zelle in Nonnenwerth} for piano and cello \and Elegy
  No.~2 for Cello and Piano}.
\see{804}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{6 Grandes \'etudes d'apr\`es Paganini}.
\see{1032}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Aida: Danza sacra e duetto final \and Vall\'ee d'Obermann}.
\see{45}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Ann\'ees de p\`elerinage: Deuxi\`eme ann\'ee: Italie \and
  Isoldens Liebestod}.
\see{158}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Chants polonais de Fr\'ed\'eric Chopin, S.~480}.
\see{1233}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Chants polonais de Fr\'ed\'eric Chopin, S.~480 \and 3 Etudes de
  Concert, No.~2 in F~minor ``La leggierezza'' \and 6 Etudes
  d'ex\'ecution transcedante d'apr\`es Paganini, No.~3 La Campanella
  \and Hungarian Rhapsody No.~2 in C~sharp minor \and Hungarian Rhapsody
  No.~10 in~E, ``Preludio'' \and Spinning Song \(transcription from
  Richard Wagner's ``The Flying Dutchman''\)}.
\see{1187}.

\cd\relax
\artist{Liszt, Franz}.
\cdtitle{Complete Tone Poems, Volume~1 \: \track Ce qu'on entend sur la
  montagne \; \track Tasso, lamento e trionfo \; \track Les Pr\'eludes
  \; \track Orpheus \; \track Prometheus \; \track Mazeppa \; \track
  Festkl\"ange}.
The London Philharmonic Orchestra.
Bernard Haitink, cond.
The Decca Record Company, 1993 \cdnum[2]{438 751-2}.

\cd\relax
\artist{Liszt, Franz}.
\cdtitle{Complete Tone Poems, Volume~2 \: \track H\'ero{\"\i}de
  fun\`ebre \; \track Hungaria \; \track Hamlet \; \track Hunnenschlacht
  \; \track Die Ideale \; \track Von der Wiege bis zum Grabe \; \track
  Mephisto Waltz No.~1}.
The London Philharmonic Orchestra.
Bernard Haitink, cond.
The Decca Record Company, 1993 \cdnum[2]{438 754-2}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Consolation No.~3 in D~flat}.
\see{1196}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Deux L\'egendes \and Ann\'ees de p\`elerinage}.
\see{886}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{\'Etude de concert No.~2 in F~minor ``La leggierezza''}.
\see{1076}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{\'Etudes d'ex\'ecution transcendante \(excerpts\) \and Mephisto
  Waltz No.~1}.
\see{48}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Fantasia on 2 themes from ``Le nozze di Figaro'' \and Hungarian
  Rhapsody No.~9 ``Carnival at Pest'' \and Valse oubli\'ee No.~1 in
  F~sharp \and Spanish Rhapsody}.
\see{644}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Fr\"ulingsnacht}.
\see{952}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Fun\'erailles \and Totentanz \(Dans macabre\)}.
\see{1702}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Grand Duo concertant sur la Romance de M.~Lafont ``La Marin''
  \(Searle~128\) \and La lugubre gondola \(Searle~134\) \and
  Valse-Caprice No.~6 aus ``Soir\'ees de Vienne'' \(Searle~427\) \and
  Erlk\"onig \(Searle~558, No.~4\)}.
\see{1412}.

\cd\relax
\artist{Liszt, Franz}.
\cdtitle{Horowitz plays Liszt \: \track Sonata in B~Minor \; \track
  Ballade No.~2 in B~Minor \; \track Consolation No.~3 \; \track
  Fun\'erailles \; \track Mephisto Waltz No.~1}.
Vladimir Horowitz.
BMG Classics, 1993 \cdnum{09026-61415-2}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Hosannah}.
\see{1599}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Hungarian Rhapsody No.~10 \and Totentanz}.
\see{623}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Hungarian Rhapsody No.~12}.
\see{882}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Hungarian Rhapsody No.~12 \and Liebestraum No.~3 \and Soir\'ees
  de Vienne: Valse-Caprice No.~6, S.~427 \(after Schubert\) \and Spanish
  Rhapsody \and \'Etudes d'ex\'ecution transcendante Nos.~10, 11, and~12
  \and Gretchen am Spinnrade \and Auf dem Wasser zu singen \and Die
  Forelle}.
\see{900}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Hungarian Rhapsody No.~2 in C~sharp minor \and Hungarian
  Rhapsody No.~11 in A~minor \and ``Rigoletto'' Paraphrase}.
\see{449}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Hungarian Rhapsody No.~2 in C~sharp minor \and Hungarian
  Rhapsody No.~6 in D~flat\and Hungarian Rhapsody No.~10 in~E
  ``Preludio'' \and Hungarian Rhapsody No.~13 in A~minor \and Hungarian
  Rhapsody No.~17 in D~minor \and Hungarian Rhapsody No.~18 in F~sharp
  minor}.
\see{645}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Hungarian Rhapsody No.~6 \and Grande \'etude d'apr\`es Paganini
  No.~2 in E~flat \and Au bord d'une source \and Sonetto 104 del
  Petrarca \and Soir\'ees de Vienne \and Piano Sonata in B~minor \and
  Ballade No.~2 in B~minor \and Hungarian Rhapsody No.~2}.
\see{797}.

\cd\relax
\artist{Liszt, Franz}.
\cdtitle{Konzert f\"ur Klavier und Orchester Nr.~1 Es-dur \and Konzert
  f\"ur Klavier und Orchester Nr.~2 A-dur \and Totentanz}.
Krystian Zimerman (piano).
Boston Symphony Orchestra.
Seiji Ozawa, cond.
Deutsche Grammophon, 1988 \cdnum{423 571-2}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{La campanella \and Hungarian Rhapsody No.~2}.
\see{625}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Les jeux d'eaux \`a la Villa d'Este}.
\see{911}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Liebestraum No.~3 in A~flat \and Tarantella \(revised version,
  1859\) \and Fantaisie-Impromptu in C~sharp minor, Op.~66 \and My
  Darling \(\from 6 Chants polonais de F.~Chopin\) \and Erlk\"onig}.
\see{775}.

\cd\relax
\artist{Liszt, Franz}.
\cdtitle{Lieder}.
Dietrich Fischer-Dieskau (bariton) and Daniel Barenboim (piano).
Deutsche Grammophon, 1981 \cdnum[3]{447 508-2}.

\cd\relax
\artist{Liszt, Franz}.
\cdtitle{Marc-Andr\'e Hamelin plays Liszt \: \track Apparition No~1 in
  F~sharp major S155 No~1 \; \track Waldesrauschen S145 No~1 \; \track
  Un Sospiro S144 No~3 \; \track Hungarian Rhapsody No~10 in E~major
  S244 \; \track Hungarian Rhapsody No~13 in A~minor S244 \; \track
  Hungarian Rhapsody No~2 in C~sharp minor S244 \; \track Nuages gris
  S199 \; \track En r\^eve---Nocturne S207 \; \track R\'eminiscences de
  Don Juan S418}.
Marc-Andr\'e Hamelin.
Hyperion, 1997 \cdnum{CDA66874}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{``Mephisto'' Waltz No.~1 \and R\'eminiscences de Don Juan \and
  Liebestraum No.~3 in A~flat \and La campanella \(\textup{with}
  \artist{Ferruccio Busoni}\) \and Les fun\'erailles \and
  R\'eminiscences de Simone Boccanegra \and Apr\`es une lecture du Dante
  \(Fantasia quasi Sonata\)}.
\see{1178}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Piano Concerto No.~1 in E~flat}.
\see{845}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Piano Concerto No.~1 in E~flat \and Grande \'Etude de Paganini
  No.~3 ``La campanella'' \and \'Etude d'ex\'ecution transcendante
  No.~10 in F~minor \and Hungarian Rhapsody No.~13 \and Totentanz}.
\see{1684}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Piano Concerto No.~1 in E~flat, S.~124}.
\see{38}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Piano Concerto No.~2 in~A}.
\see{883}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Piano Sonata in B~minor}.
\see{604}.

\cd\relax
\artist{Liszt, Franz}.
\cdtitle{\track Piano Sonata in B~minor \; \track La Campanella \;
  \track Liebeslied \(``Widmung''\) \; \track Liebestraum No.~3 \;
  \track Tarantella \; \track ``Rigoletto'' de Verdi: Paraphrase de
  concert}.
Yundi Li.
Deutsche Grammophon, 2003 \cdnum{B0000851-02}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Piano Sonata in B~minor \and Hungarian Rhapsody No.~6 in
  D~flat}.
\see{39}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Piano Sonata in B~minor, S.~178}.
\see{44}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Piano Sonata in B~minor, S.~178}.
\see{1207}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Polonaise No.~2 in~E \and Sonetto 123 del Petrarca \and Fantasy
  and Fugue on the Name B-A-C-H \and Etude de concert No.~3 in D~flat
  ``Un sospiro'' \and Tarantella \(Supplement to ``Ann\'ees de
  p\`elerinage'', Deuxi\`eme ann\'ee: Italie\)\and Etude de concert
  No.~2 in F~minor ``La leggierezza'' \and L\'egende No.~2 ``St.
  Fran\c{c}ois de Paule marchant sur les flots'' \and Chasse-neige
  \(Etude d'ex\'ecution transcedante No.~12\) \and Tarantella di bravura
  \and Mephisto Waltz No.~1}.
\see{472}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Prelude and Fugue in A~minor, BWV~543 \and La leggierezza \and
  Au bord d'une source}.
\see{1485}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Prelude and Fugue in A~minor, BWV~543 \and Liebestraum No.~3 in
  A~flat \and Hungarian Rhapsody No.~6 in D~flat \and Consolation No.~5
  in~E \and Sonetto 104 del Petrarca \and ``Rigoletto'' Paraphrase}.
\see{844}.

\cd\relax
\artist{Liszt, Franz}.
\cdtitle{Rhapsodies hongroises \and les Ann\'ees de p\`elerinage}.
Georges Cziffra.
EMI Classics, 1993 \cdnum[4]{0777 7~64882~2 6}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Soir\'ees de Vienne: Valse-Caprice No.~6, S.~427 \(after
  Schubert\)}.
\see{140}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Sonetto 104 del Petrarca \and Hungarian Rhapsody No.~11 \and
  ``Mephisto'' Waltz No.~1}.
\see{877}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Spanish Rhapsody \and B\'en\'ediction de Dieu dans la solitude
  \and Les jeux d'eaux \`a la Villa d'Este \and Chasse-neige \(\'Etude
  d'execution transcendante No.~12\)}.
\see{43}.

\cd\relax
\artist{Liszt, Franz}.
\cdtitle{The Complete Etudes: 12 Etudes d'ex\'ecution transcendante,
  S.~139 \and 3~Etudes de concert, S.~144 \and 2~Etudes de concert,
  S.~145 \and 6~Etudes d'ec\'ecution transcendante d'apr\`es Paganini,
  S.~140}.
Claudio Arrau and Nikita Magaloff.
Philips Classics, 1997 \cdnum[2]{456 339-2}.

\cd\relax
\artist{Liszt, Franz}.
\cdtitle{The Early Beethoven Transcriptions \: \track Symphony No~5 \;
  \track Adela{\"\i}de \; \track Cadenza for the first movement of
  Beethoven's Piano Concerto No~3 \; \track Marche fun\`ebre \; \track
  Symphony No~6 \; \track Ad\'ela{\"\i}de \; \track Fifth movement from
  Symphony No~6 \; \track \C{Ludwig van Beethoven} Symphony No~7
  \(Fragment transcribed by the composer\) \; \track Fantasie \"uber
  Themen aus Beethovens Ruinen von Athen \; \track Marche au supplice de
  la Sinfonie fantastique}.
Volume~44 of \emph{The Complete Music for Solo Piano}.
Hyperion, 1997 \cdnum[3]{CDA67111/3}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Valle\'e d'Obermann \and Orage \and Totentanz \and Sposalizio
  \and Bagatelle sans Tonalit\'e \and Hungarian Rhapsody No.~15 in
  A~minor ``R\'ak\'oczy March''}.
\see{336}.

\cd*\relax
\artist{Liszt, Franz}.
\cdtitle{Valse oubli\'ee No.~1 in F~sharp \and Valse oubli\'ee No.~2 in
  A~flat \and Etudes d'ex\'ecution transcendante Nos.~5 and~11}.
\see{1270}.

\cd*\relax
\artist{Liszt, Franz Schubert/Franz}.
\cdtitle{``Hark! Hark! The Lark'' \(St\"andchen\)}.
\see{625}.

\cd*\relax
\artist{Liszt, Giuseppe Verdi/Franz}.
\cdtitle{``Rigoletto'' Paraphrase}.
\see{650}.

\cd*\relax
\artist{Litolff, Henry}.
\cdtitle{Scherzo from Concerto Symphonique, Op.~102}.
\see{418}.

\cd\relax
\artist{Lloyd Webber, Andrew and Charles Hart}.
\cdtitle{The Phantom of the Opera}.
The Really Useful Group, 1987 \cdnum[2]{831 273-2 Y-2}.

\cd\relax
\artist{Lloyd Webber, Andrew and Tim Rice}.
\cdtitle{Evita \(London Cast\)}.
MCA Records, 1979 \cdnum[2]{MCAD2-11007}.

\cd\relax
\artist{Lloyd Webber, Andrew and Tim Rice}.
\cdtitle{Evita \(Premiere American Recording\)}.
MCA Records, 1976 \cdnum[2]{MCAD2-11541}.

\cd\relax
\artist{Lloyd Webber, Andrew and Tim Rice}.
\cdtitle{Jesus Christ, Superstar}.
MCA Records, 1970 \cdnum[2]{MCAD2-10000}.

\cd\relax
\artist{Lloyd Webber, Julian}.
\cdtitle{British Cello Music \: \track \C{Benjamin Britten} Tema
  ``Sacher'' \; \track \C{Alan Rawsthorne} Sonata for Cello and Piano \;
  \track \C{John Ireland} The Holy Boy \; \track \C{Malcolm Arnold}
  Fantasy for Cello \; \track \C{William Walton} Passacaglia for
  Violoncello Solo \; \track \C{Benjamin Britten} Third Suite for Cello,
  Op.~87}.
John McCabe (piano).
Academy Sound and Vision, 1987 \cdnum{CD DCA 592}.

\cd\relax
\artist{Lloyd Webber, Julian}.
\cdtitle{British Cello Music, Volume~2 \: \track \C{Charles Villiers
  Stanford} Sonata No.~2 for Cello and Piano, Op.~39 \; \track \C{Frank
  Bridge} Elegy for Cello and Piano \and Scherzetto for Cello and Piano
  \; \track \C{John Ireland} Sonata for Cello and Piano in G~minor}.
John McCabe (piano).
Academy Sound and Vision, 1992 \cdnum{CD DCA 807}.

\cd\relax
\artist{Loewe, Carl}.
\cdtitle{Balladen und Lieder}.
Dietrich Fischer-Dieskau (baritone) and J\"org Demus (piano).
Deutsche Grammophon, 1996 \cdnum[2]{449 516-2}.

\cd\relax
\artist{Londeix, Jean-Marie}.
\cdtitle{Le Saxophone Fran\c{c}ais}.
EMI Classics, 1997 \cdnum[3]{7243 5 72360 2~7}.

\cd\relax
\artist{Long, Zhou}.
\cdtitle{The Flowering Stream: Chinese Folk Songs and Tone Poems}.
The Shanghai Quartet.
Delos International, 1998 \cdnum{DE~3233}.

\cd*\relax
\artist{Lonquich, Heinz Martin}.
\cdtitle{Preisungen}.
\see{1524}.

\cd*\relax
\artist{Lopes-Gra\c{c}a, Fernando}.
\cdtitle{Concerto da c\`amera}.
\see{1315}.

\cd*\relax
\artist{Louri\'e, Arthur (Vincent)}.
\cdtitle{Gigue}.
\see{724}.

\cd*\relax
\artist{Luk\'a\v{s}, Zden\v{e}k}.
\cdtitle{Lento drammatico}.
\see{719}.

\cd\relax
\artist{Lupu, Radu}.
\cdtitle{Beethoven/Brahms/Grieg/Schubert/Schumann \: \track \C{Ludwig
  van Beethoven} 32 Variations in C~minor, WoO~80 \and Piano Sonata in
  C~sharp minor, Op.~27 No.~2 ``Moonlight'' \; \track \C{Johannes
  Brahms} Intermezzi, Op.~117 \and Theme and Variations in D~minor
  \(transcribed from String Sextet, Op.~18\) \; \track \C{Franz
  Schubert} Moments musicaux, D.~780 \and Piano Sonata in A~minor,
  D.~784 \; \track \C{Robert Schumann} Kinderszenen, Op.~15 \; \track
  \C{Edvard Grieg} Piano Concerto in A~minor, Op.~16}.
Volume~66 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 895-2}.

\cd\relax
\artist{Lutos{\l}awski, Witold}.
\cdtitle{Orchestral Works, Volume~1 \: \track Funeral Music for Strings
  \; \track Chain~II: Dialogue for Violin and Orchestra \; \track
  Interlude \; \track Partita for Violin and Orchestra \; \track
  Symphony No.~4}.
Krzysztof Bakowski (violin).
Polish National Radio Symphony Orchestra (Katowice).
Antoni Wit, cond.
Naxos, 1996 \cdnum{8.553202}.

\cd\relax
\artist{Lutos{\l}awski, Witold}.
\cdtitle{Orchestral Works, Volume~2 \: \track Symphonic Variations \;
  \track Little Suite \(Mala suita\) \; \track Symphony No.~2 \; \track
  Concerto for Piano and Orchestra}.
Piotr Paleczny (piano).
Polish National Radio Symphony Orchestra (Katowice).
Antoni Wit, cond.
Naxos, 1996 \cdnum{8.553169}.

\cd\relax
\artist{Lutos{\l}awski, Witold}.
\cdtitle{Orchestral Works, Volume~3 \: \track Paganini Variations \;
  \track Paroles Tiss\'ees \; \track Les Espaces du Sommeil \; \track
  Symphony No.~3}.
Bernd Glemser (piano), Piotr Kusiewicz (tenor) and Adam Kruszewski
  (baritone).
Polish National Radio Symphony Orchestra (Katowice).
Antoni Wit, cond.
Naxos, 1996 \cdnum{8.553423}.

\cd\relax
\artist{Lutos{\l}awski, Witold}.
\cdtitle{Orchestral Works, Volume~4 \: \track Livre pour orchestre \;
  \track Concerto for Cello and Orchestra \; \track Novelette \; \track
  Chain No.~3}.
Andrzej Bauer (cello).
Polish National Radio Symphony Orchestra.
Antoni Wit, cond.
Naxos, 1998 \cdnum{8.553625}.

\cd\relax
\artist{Lutos{\l}awski, Witold}.
\cdtitle{Orchestral Works, Volume~5 \: \track Concerto for Orchestra \;
  \track Three Poems by Henri Michaux \; \track Mi-Parti for Symphony
  Orchestra \; \track Overture for Strings}.
Camerata Silesia and Polish National Radio Symphony Orchestra
  (Katowice).
Antoni Wit, cond.
Naxos, 1998 \cdnum{8.553779}.

\cd\relax
\artist{Lutos{\l}awski, Witold}.
\cdtitle{Orchestral Works, Volume~6 \: \track Symphony No.~1 \; \track
  Silesian Triptych \; \track Jeux v\'enitiens \; \track Chantefleurs et
  Chantefables \; \track Postludium~I}.
Olga Pasiecznik (soprano).
Polish National Radio Symphony Orchestra.
Antoni Wit, cond.
Naxos, 1999 \cdnum{8.554283}.

\cd*\relax
\artist{Lyavov}.
\cdtitle{Preludia, Op.~11, No.~1}.
\see{929}.

\cd\relax
\artist{Lynch, Stephen}.
\cdtitle{A Little Bit Special}.
What Are Records?, 2000 \cdnum{61002-2}.

\cd\relax
\artist{Lynch, Stephen}.
\cdtitle{Superhero}.
What Are Records?, 2002 \cdnum{61003}.

\cd\relax
\artist{Lynch, Stephen}.
\cdtitle{The Craig Machine}.
What Are Records?, 2005.

\cd\relax
\cdtitle{Lynyrd Skynyrd}.
MCA Records, 1991 \cdnum{MCAD3-10390}.

\cd\relax
\artist{Lynyrd Skynyrd}.
\cdtitle{Lynyrd Skynyrd \(expanded edition\)}.
MCA Records, 2001 \cdnum{088 112 727-2}.

\cd\relax
\artist{Lynyrd Skynyrd}.
\cdtitle{What's Your Name}.
MCA Records, 1987 \cdnum{MCAD-20401}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{``Anything Goes''}.
Stephane Grappelli.
CBS Records, 1989 \cdnum{MK~45574}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{\track \C{Edward Elgar} Cello Concerto, Op.~85 \; \track
  \C{William Walton} Concerto for Cello and Orchestra}.
London Symphony Orchestra.
Andr\'e Previn, cond.
CBS Records, 1985 \cdnum{MK~39541}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Great Cello Concertos \: \track \C{Joseph Haydn} Concerto for
  Cello and Orchestra, op.~101 \; \track \C{Camille Saint-Sa\"ens}
  Concerto No.~1 for Cello and Orchestra, op.~33 \; \track \C{Robert
  Schumann} Concerto for Cello and Orchestra, op.~129 \; \track
  \C{Anton{\'\i}n Dvo\v{r}\'ak} Concerto for Cello and Orchestra,
  op.~104 \; \track \C{Edward Elgar} Concerto for Cello and Orchestra,
  op.~85}.
CBS Records, 1989 \cdnum[2]{M2K 44562}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Japanese Melodies}.
Sumire Yoshiwara (percussion), Hiroaki Naka (bass) and Masami Nakagawa
  (flute).
CBS Records, 1984 \cdnum{MK~39703}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{\track \C{Johannes Brahms} Trio for Piano, Clarinet and Cello
  in A~minor, Op.~114 \; \track \C{Ludwig van Beethoven} Trio for Piano,
  Clarinet and Cello, Op.~11 \; \track \C{Wolfgang Amadeus Mozart} Trio
  for Piano, Clarinet and Viola \(Cello\) ``Kegelstatt'' in E-flat
  Major, K.~498}.
Emanuel Ax (piano) and Richard Stoltzman (clarinet).
Sony Classical \cdnum{SK~57~499}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Kreisler/Paganini}.
Patricia Zander (piano).
CBS Records, 1982 \cdnum{MK~37280}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Made in America \: \track \C{Leonard Bernstein} Clarinet Sonata
  \(transcribed for cello and piano by Yo-Yo Ma\) \; \track \C{Leon
  Kirchner} Tryptych \; \track \C{George Gershwin} Three Preludes \;
  \track \C{Charles Ives} Trio for Violin, Cello and Piano}.
Jeffrey Kahane (piano), Lynn Chang (violin), Ronan Lefkowitz (violin)
  and Gilbert Kalish (piano).
Sony Classical, 1993 \cdnum{SK~53126}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Obrigado Brazil}.
Sony, 2003 \cdnum{SK~89935}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Obrigado Brazil Live in Concert}.
Sony, 2004 \cdnum{SK~90970}.
With bonus DVD.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Paris: La Belle \'Epoque \: \track \C{Jules Massenet}
  ``M\'editation'' from \emph{Tha{\"\i}s} \T{Ma} \; \track \C{Gabriel
  Faur\'e} Sonata No.~1 in A~Major for Violin and Piano, Op.~13 \T{Ma}
  \; \track \C{Camille Saint-Sa\"ens} Havanais, Op.~83 \T{Ma} \; \track
  \C{C\'esar Franck} Sonata in A~Major for Violin and Piano \(version
  for Cello and Piano\)}.
Kathryn Stott (piano).
Sony Classical, 2003 \cdnum{SK~87287}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Portrait of Yo-Yo Ma}.
CBS Records, 1989 \cdnum{MK~44796}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Premieres \: \track \C{Richard Danielpour} Concerto for Cello
  and Orchestra \(1994\) \; \track \C{Leon Kirchner} Music for Cello and
  Orchestra \; \track \C{Christopher Rouse} Violoncello Concerto}.
Philadelphia Orchestra.
David Zinman, cond.
Sony Classical, 1996 \cdnum{SK~66299}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{\track \C{Samuel Barber} Concerto for Cello and Orchestra,
  Op.~22 \; \track \C{Benjamin Britten} Symphony for Cello and
  Orchestra, Op.~68}.
The Baltimore Symphony Orchestra.
David Zinman, cond.
CBS Records, 1989 \cdnum{MK~44900}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Shostakovich and Kabalevsky \: \track \C{Dmitri Shostakovich}
  Concerto No.~1 for Cello and Orchestra, Op.~107 \; \track \C{Dmitri
  Kabalevsky} Concerto No.~1 for Cello and Orchestra, Op.~49}.
Nolan Miller (french horn).
Philadelphia Orchestra.
Eugene Ormandy, cond.
CBS Records, 1983 \cdnum{MK~37840}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Simply Baroque}.
The Amsterdam Baroque Orchestra.
Ton Koopman, cond.
Sony Classical, 1999 \cdnum{SK~60680}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Simply Baroque II}.
The Amsterdam Baroque Orchestra.
Ton Koopman, cond.
Sony Classical, 2000 \cdnum{SK~60681}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Solo \: \track \C{Mark O'Connor} Appalachia Waltz \; \track
  \C{Bright Sheng} Seven Tunes Heard in China \; \track \C{David Wilde}
  The Cellist of Sarajevo \; \track \C{Alexander Tcherepnin} Suite for
  Solo Cello \; \track \C{Zolt\'an Kod\'aly} Sonata for Solo Cello,
  Op.~8}.
Sony Classical, 1999 \cdnum{SK~64114}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Soul of the Tango: The Music of Astor Piazzolla}.
Sony, 1997 \cdnum{SK~63122}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{The New York Album \: \track \C{Stephen Albert} Concerto for
  Cello and Orchestra \; \track \C{B\'ela Bart\'ok} Concerto for Viola
  and Orchestra \; \track \C{Ernest Bloch} Schelomo: Hebraic Rhapsody
  for Cello and Orchestra}.
Baltimore Symphony Orchestra.
David Zinman, cond.
Sony, 1994 \cdnum{SK 57961}.

\cd\relax
\artist{Ma, Yo-Yo}.
\cdtitle{Vivaldi's Cello}.
The Amsterdam Baroque Orchestra.
Ton Koopman, cond.
Sony Classical, 2004 \cdnum{SK~90916}.

\cd\relax
\artist{Ma, Yo-Yo and Bobby McFerrin}.
\cdtitle{Hush}.
Sony, 1992 \cdnum{SK 48177}.

\cd\relax
\artist{Ma, Yo-Yo, Edgar Meyer and Mark O'Connor}.
\cdtitle{Appalachia Journey}.
Sony, 2000 \cdnum{SK~66782}.

\cd\relax
\artist{Ma, Yo-Yo, Edgar Meyer and Mark O'Connor}.
\cdtitle{Appalachia Waltz}.
Sony, 1996 \cdnum{SK~68460}.

\cd\relax
\artist{Ma, Yo-Yo and the Silk-Road Ensemble}.
\cdtitle{Silk Road Journeys: Beyond the Horizon}.
Sony, 2004 \cdnum{SK 93962}.

\cd\relax
\artist{Ma, Yo-Yo and the Silk-Road Ensemble}.
\cdtitle{Silk Road Journeys: When Strangers Meet}.
Sony, 2001 \cdnum{SK 89782}.

\cd\relax
\artist{MacDowell, Edward}.
\cdtitle{Piano Music, Volume~1 \: \track Woodland Sketches, Op.~51 \;
  \track Sea Pieces, Op.~55 \; \track Fireside Tales, Op.~61 \; \track
  New England Idyls, Op.~62}.
James Barbagallo.
Naxos, 1998 \cdnum{8.559010}.

\cd\relax
\artist{MacDowell, Edward}.
\cdtitle{Piano Music, Volume~2 \: \track First Modern Suite, Op.~10 \;
  \track In Lilting Rhythm, Op.~2 \; \track Six Idyls after Goethe,
  Op.~28 \; \track Sonata No.~3 ``Norse'', Op.~57}.
James Barbagallo.
Naxos, 1998 \cdnum{8.559011}.

\cd\relax
\artist{MacDowell, Edward}.
\cdtitle{Piano Music, Volume~3 \: \track Sonata No.~4 ``Keltic'', Op.~59
  \; \track Forgotten Fairy Tales, Op.~4 \; \track Six Poems after
  Heine, Op.~31 \; \track Twelve Virtuoso Studies, Op.~46}.
James Barbagallo.
Naxos, 1999 \cdnum{8.559019}.

\cd\relax
\artist{MacDowell, Edward}.
\cdtitle{Piano Music, Volume~4 \: \track \'Etude de Concert, Op.~36 \;
  \track Second Modern Suite, Op.~14 \; \track Serenata, Op.~16 \;
  \track Two Fantasy Pieces, Op.~17 \; \track Twelve \'Etudes, Op.~39}.
James Barbagallo.
Naxos, 1999 \cdnum{8.559030}.

\cd*\relax
\artist{M\'acha, Otmar}.
\cdtitle{Plac saxophone/The wailing of the saxophone}.
\see{253}.

\cd*\relax
\artist{Macy, Carleton}.
\cdtitle{Faust}.
\see{151}.

\cd\relax
\artist{Mader}.
\cdtitle{Eat Drink Man Woman}.
Varese Sarabande, 1994 \cdnum{VSD-5528}.

\cd\relax
\artist{Mader}.
\cdtitle{The Wedding Banquet}.
Varese Sarabande, 1993 \cdnum{VSD-5457}.

\cd\relax
\artist{Magaloff, Nikita}.
\cdtitle{Chopin/Haydn/Liszt/Schumann \: \track \C{Joseph Haydn} Piano
  Sonata in~C, Hob.~XVI:48 \; \track \C{Fr\'ed\'eric Chopin} Nocturne in
  B~flat minor, Op.~9 No.~1 \and Nocturne in E~flat, Op.~9 No.~2 \and
  Nocturne in~B, Op.~9 No.~3 \and Bol\'ero in~C, Op.~19 \and Piano
  Sonata No.~1 in C~minor, Op.~4 \and Tarantelle in A~flat, Op.~43 \and
  Mazurka in B~flat, Op.~17 No.~1 \and Mazurka in E~minor, Op.~17 No.~2
  \and Mazurka in A~flat, Op.~17 No.~3 \and Mazurka in A~minor, Op.~17
  No.~4 \and Rondo \`a la Mazur in~F, Op.~5 \and Variations brillantes,
  Op.~12 \and Allegro de concert in~A, Op.~46 \and Ecossaise No.~1 in~D,
  Op.~72 No.~3 \and Ecossaise No.~2 in~G, Op.~72 No.~4 \and Ecossaise
  No.~3 in D~flat, Op.~72 No.~5 \; \track \C{Franz Liszt} 6 Grandes
  \'etudes d'apr\`es Paganini \; \track \C{Robert Schumann} Carnaval,
  Op.~9}.
Volume~67 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 898-2}.

\cd\relax
\artist{Magnetic Fields, The}.
\cdtitle{69 Love Songs, Volume~1}.
Merge Records, 1999 \cdnum{MRG~166}.

\cd\relax
\artist{Magnetic Fields, The}.
\cdtitle{69 Love Songs, Volume~2}.
Merge Records, 1999 \cdnum{MRG~167}.

\cd\relax
\artist{Magnetic Fields, The}.
\cdtitle{69 Love Songs, Volume~3}.
Merge Records, 1999 \cdnum{MRG~168}.

\cd\relax
\artist{Magnetic Fields, The}.
\cdtitle{i}.
Nonesuch Records, 2004 \cdnum{79683-2}.

\cd\relax
\artist{Mahler, Gustav}.
\cdtitle{Das Lied von der Erde}.
James King (tenor) and Dietrich Fischer-Dieskau (baritone).
Wiener Philharmoniker.
Leonard Bernstein, cond.
The Decca Record Company, 1999 \cdnum{289 466 381-2}.
Recorded April 1966.

\cd\relax
\artist{Mahler, Gustav}.
\cdtitle{\track Lieder eines Fahrenden Gesellen \; \track
  Kindertotenlieder \; \track 5 R\"uckert-Lieder}.
Thomas Hampson (baritone).
Wiener Philharmoniker.
Leonard Bernstein, cond.
Deutsche Grammophon, 1991/1989 \cdnum{431 682-2}.

\cd\relax
\artist{Mahler, Gustav}.
\cdtitle{Symphony No.~4 in G Major \and Songs of a Wayfarer \(Lieder
  eines fahrenden Gesellen\)}.
Judith Raskin (soprano) and Frederica von Stade (mezzo-soprano).
The Cleaveland Orchestra and the London Philharmonic Orchestra.
George Szell and Andrew Davis, cond.
Sony Classical, 1979 \cdnum{SBK~46535}.

\cd\relax
\artist{Mahler, Gustav}.
\cdtitle{Symphony No.~5 in C~sharp minor}.
New Philharmonia Orchestra.
Sir John Barbirolli, cond.
EMI Classics, 1969/1988 \cdnum{7~64749~2}.

\cd\relax
\artist{Mahler, Gustav}.
\cdtitle{Symphony No.~8 in E~flat major ``Symphony of a Thousand''}.
Heather Harper (soprano), Lucia Popp (soprano), Arleen Auger (soprano),
  Yvonne Minton (contralto), Helen Watts (contralto), Ren\'e Kollo
  (tenor), John Shirley-Quark (baritone) and Martti Talvela (bass).
Wiener Staatsopernchor, Wiener Singverein, Wiener S\"angerknaben, and
  the Chicago Symphony Orchestra.
Georg Solti, cond.
The Decca Record Company, 1999 \cdnum{289 469 972-2}.
Recorded August/September 1971.

\cd\relax
\artist{Mahler, Gustav}.
\cdtitle{Symphony No.~9}.
Philharmonia Orchestra.
Benjamin Zander, cond.
Telarc, 1999 \cdnum[3]{3CD-80527}.

\cd*\relax
\artist{Mancini, Francesco}.
\cdtitle{Sonata in E~minor \and Sonata in D~minor}.
\see{1653}.

\cd*\relax
\artist{Marcello, Alessandro}.
\cdtitle{Concerto in C~minor}.
\see{1139}.

\cd\relax
\artist{Marcus, Greil}, ed.
\cdtitle{The Rose and the Briar}.
Columbia/Legacy, 2004 \cdnum{CK~92866}.

\cd\relax
\artist{Marek, Czeslaw}.
\cdtitle{The Orchestral Works, Volume~1 \: \track Suite f\"ur Orchester,
  Op.~25 \; \track M\'editations, Op.~14 \; \track Sinfonia, Op.~28}.
The Philharmonia Orchestra London.
Gary Brain, cond.
Koch, 1996 \cdnum{3-6439-2}.

\cd\relax
\artist{Marini, Biagio}.
\cdtitle{Curiose and Moderne Inventioni}.
Romanesca, Andrew Manze (violin), Nigel North (chitarrone and chitarra
  alla spagnola), John Toll (harpsichord and organ), Caroline Balding
  (violin), Jan Schlapp (viola) and David Watkin (cello).
Harmonia Mundi, 1997 \cdnum{HMU 907175}.

\cd*\relax
\artist{Marini, Biagio}.
\cdtitle{Sonata in Ecco con tre violini from \emph{Opus~8} \and Sonata
  Terza par tre violini from \emph{Opus~22}}.
\see{1184}.

\cd\relax
\artist{Markevitch, Igor}.
\cdtitle{Complete Orchestral Music, Volume~1 \: \track Le Nouvel \^Age
  \; \track Sinfonietta in~F \; \track Cin\'ema-Ouverture}.
Arnhem Philharmonic Orchestra.
Christopher Lyndon-Gee, cond.
Marco Polo, 1997 \cdnum{8.223653}.

\cd\relax
\artist{Markevitch, Igor}.
\cdtitle{Complete Orchestral Music, Volume~2 \: \track Cantique d'Amour
  \; \track L'Envol d'Icare \; \track Concerto Grosso}.
Arnhem Philharmonic Orchestra.
Christopher Lyndon-Gee, cond.
Marco Polo, 1997 \cdnum{8.223666}.

\cd\relax
\artist{Marsalis, Wynton}.
\cdtitle{Marsalis Standard Time, Volume~1}.
Columbia, 1987 \cdnum{CK~40461}.

\cd\relax
\artist{Marsalis, Wynton and Ellis Marsalis}.
\cdtitle{Joe Cool's Blues}.
Columbia, 1995 \cdnum{CK~66880}.

\cd\relax
\artist{Marshall Tucker Band, The}.
\cdtitle{Searchin' for a Rainbow}.
AJK Music, 1975 \cdnum{A~702-2}.

\cd\relax
\artist{Martin\r{u}, Bohuslav}.
\cdtitle{Chamber Music \: \track Piano Quartet No.~1 \(1942\) \; \track
  Quartet for Oboe, Violin, Cello and Piano \(1947\) \; \track Sonata
  No.~1 for Viola and Piano \(1955\) \; \track String Quintet for Two
  Violins, Two Violas and Cello \(1927\)}.
Naxos, 1996 \cdnum{8.553916}.

\cd*\relax
\artist{Martin\r{u}, Bohuslav}.
\cdtitle{Duo for Violin and Violoncello}.
\see{486}.

\cd*\relax
\artist{Marx, Joseph}.
\cdtitle{Romantisches Klavierkonzert in E~major}.
\see{723}.

\cd*\relax
\artist{Maslanka, David}.
\cdtitle{Sonata for Alto Saxophone and Piano}.
\see{1605}.

\cd*\relax
\artist{Massella, Thomas}.
\cdtitle{Three Lyrics for Saxophone Quartet \(1998\)}.
\see{1146}.

\cd*\relax
\artist{Massenet, Jules}.
\cdtitle{M\'editation}.
\see{1144}.

\cd*\relax
\artist{Massenet, Jules}.
\cdtitle{M\'editation \from Tha{\"\i}s}.
\see{247}.

\cd*\relax
\artist{Massenet, Jules}.
\cdtitle{``M\'editation'' from \emph{Tha{\"\i}s} \T{Ma}}.
\see{1010}.

\cd*\relax
\artist{Massenet, Jules}.
\cdtitle{Valse folle}.
\see{724}.

\cd*\relax
\artist{Masumoto, Kikuko}.
\cdtitle{Pastorale}.
\see{943}.

\cd*\relax
\artist{Matsushita, Isao}.
\cdtitle{Atoll~II}.
\see{252}.

\cd\relax
\artist{McArthur, Doug and Garnet Rogers}.
\cdtitle{Doug McArthur with Garnet Rogers}.
Snow Goose Records, 1989 \cdnum{SGS-1116D}.

\cd\relax
\artist{McChrystal, Gerard}.
\cdtitle{Meeting Point \: \track \C{D. C. Heath} The Celtic Concerto for
  Soprano Saxophone and Strings \; \track \C{Ian Wilson} I Sleep at
  Waking \; \track \C{Michael Torke} Saxophone Concerto \; \track
  \C{Michael McGlynn} From Nowhere to Nowhere \; \track \C{Michael
  Nyman} Where the Bee Dances}.
Silva Screen Records, 1996 \cdnum{SILKD~6010}.

\cd\relax
\artist{McDonough, Megon, Christine Lavin, Patty Larkin and Sally
  Fingerett}.
\cdtitle{Buy Me, Bring Me, Take Me: Don't Mess My Hair!!!}
Rounder Records, 1991 \cdnum{PHILCO CD PH~1140}.

\cd*\relax
\artist{McGlynn, Michael}.
\cdtitle{From Nowhere to Nowhere}.
\see{1053}.

\cd*\relax
\artist{McKenna, Edward}.
\cdtitle{Bagatelle}.
\see{1161}.

\cd\relax
\artist{McLean, Don}.
\cdtitle{American Pie}.
EMI-Manhattan, 1980 \cdnum{CDP~7 46555~2}.

\cd\relax
\artist{McLoughlin, Noel}.
\cdtitle{Best of Ireland}.
ARC Music \cdnum{EUCD 1111}.

\cd\relax
\artist{McLoughlin, Noel}.
\cdtitle{Famous Irish Ballads}.
ARC Music, 1994 \cdnum{EUCD 1307}.

\cd*\relax
\artist{Medtner, Nicolai}.
\cdtitle{Piano Sonata in G~minor, Op.~22}.
\see{1076}.

\cd*\relax
\artist{Medtner, Nicolai}.
\cdtitle{Sonata reminiscenza in A~minor, Op.~38 No.~1}.
\see{645}.

\cd*\relax
\artist{Medtner, Nicolai}.
\cdtitle{Sonata reminiscenza in A~minor, Op.~38 No.~1}.
\see{644}.

\cd\relax
\artist{Medtner, Nicolas}.
\cdtitle{The Complete Piano Sonatas \and Forgotten Melodies~I,~II}.
Marc-Andr\'e Hamelin.
Hyperion Records, 1998 \cdnum[4]{CDA67221/4}.

\cd*\relax
\artist{Medtner, Nikolai}.
\cdtitle{Danza festiva, Op~38 No~3 \(Forgotten Meolodies, Vol~I\)}.
\see{725}.

\cd*\relax
\artist{Medtner, Nikolai}.
\cdtitle{Improvisation No~1 in B~flat minor, Op~31 No~1}.
\see{726}.

\cd\relax
\artist{Medtner, Nikolay Karlovich}.
\cdtitle{\track Piano Concerto No.~2 in C~minor, Op.~50 \; \track Piano
  Quintet in C~major, Op.~posth.}
Konstantin Scherbakov (piano), Ewald Danel (violin~I), Milan Tedla
  (violin~II), Zuzana Bou\v{r}ov\'a (viola) and Jozef Podhoransk\'y
  (cello).
Moscow Symphony Orchestra.
Igor Golovschin, cond.
Naxos, 1997 \cdnum{8.553390}.

\cd\relax
\artist{Men at Work}.
\cdtitle{The Essential Men at Work}.
Sony Music, 2003 \cdnum{CK~87188}.

\cd*\relax
\artist{Mendelssohn, Felix}.
\cdtitle{Concerto in D~minor for violin}.
\see{1141}.

\cd\relax
\artist{Mendelssohn, Felix}.
\cdtitle{Lieder ohne Worte}.
Daniel Barenboim.
Deutsche Grammophon, 1974 \cdnum[2]{453 061-2}.

\cd*\relax
\artist{Mendelssohn, Felix}.
\cdtitle{Scherzo from ``A Midsummer Night's Dream''}.
\see{1233}.

\cd*\relax
\artist{Mendelssohn, Felix}.
\cdtitle{Sonata in D~major, Op.~58}.
\see{1156}.

\cd*\relax
\artist{Mendelssohn, Felix}.
\cdtitle{Violin Concerto in E minor, op.~64}.
\see{243}.

\cd*\relax
\artist{Mendelssohn, Felix}.
\cdtitle{Violin Concerto in E~minor, Op.~64}.
\see{1576}.

\cd*\relax
\artist{Mendelssohn, Felix Mendelssohn}.
\cdtitle{Variations S\'erieuses, Op.~54}.
\see{336}.

\cd*\relax
\artist{Mendelssohn-Bartholdy, Felix}.
\cdtitle{Ein Sommernachtstraum: Overture}.
\see{628}.

\cd\relax
\artist{Mendelssohn-Bartholdy, Felix}.
\cdtitle{The Complete Works for Cello and Piano \: \track Sonata No.~1
  in B~flat major, op.~45 \; \track Sonata No.~2 in D major, op.~58 \;
  \track Variations concertantes, op.~17 \; \track Song without Words,
  op.~109}.
Christophe Coin (violoncello) and Patrick Cohen (fortepiano).
The Decca Record Company, 1992 \cdnum{430 245-2}.

\cd*\relax
\artist{Mendelssohn Bartholdy, Felix}.
\cdtitle{Variations s\'erieuses, Op.~54}.
\see{1196}.

\cd\relax
\artist{Messiaen, Oliver}.
\cdtitle{\track Catalogue d'oiseaux \; \track Petites esquisses
  d'oiseaux}.
H{\aa}kon Austb{\o} (piano).
Naxos, 1997 \cdnum[3]{8.553532--34}.

\cd\relax
\artist{Messiaen, Oliver}.
\cdtitle{Vingt regards su l'enfant J\'esus}.
H{\aa}kon Austb{\o} (piano).
Naxos, 1994 \cdnum[2]{8.550829--30}.

\cd*\relax
\artist{Messiaen, Olivier}.
\cdtitle{Ab\^{\i}me des oiseaux \from \emph{Quatuor pour la Fin du
  Temps}}.
\see{1321}.

\cd\relax
\artist{Meyer, Edgar}.
\cdtitle{Meyer and Bottesini Concertos \: \track Double Concerto for
  Cello and Double Bass \; \track Concerto in~D for Double Bass and
  Orchestra \; \track \C{Giovanni Bottesini} Concerto No.~2 in B~Minor
  for Double Bass and Orchestra \and Gran Duo Concertante}.
Edgar Meyer (double bass), Yo-Yo Ma (cello) and Joshua Bell (violin).
The Saint Paul Chamber Orchestra.
Hugh Wolff, cond.
Sony Classical, 2002 \cdnum{SK~60956}.

\cd*\relax
\artist{Miaskovsky, Nicolai}.
\cdtitle{Prelude in B~flat minor, Op.~58 ``Song and Rhapsody''}.
\see{645}.

\cd*\relax
\artist{Miaskovsky, Nikolai}.
\cdtitle{Cello Concerto, Op.~66 \and Cello Sonata No.~2, Op.~81}.
\see{1315}.

\cd*\relax
\artist{Micha{\l}owski, Aleksander}.
\cdtitle{Etude d'apr\`es l'Impromptu en la b\'emol majeur de Fr.~Chopin,
  Op.~29}.
\see{724}.

\cd\relax
\artist{Michelangeli, Arturo Benedetti}.
\cdtitle{Beethoven/Brahms/Chopin/Mompou/Schumann \: \track \C{Ludwin van
  Beethoven} Piano Sonata in E~flat, Op.~7 \; \track \C{Robert Schumann}
  3 Pieces from ``Album f\"ur die Jugend'', Op.~68 \and Carnaval, Op.~9
  \; \track \C{Johannes Brahms} Variations on a Theme by Paganini,
  Op.~35 \and Ballades, Op.~10 \; \track \C{Fr\'ed\'eric Chopin} Mazurka
  in G~minor, Op.~67 No.~2 \and Mazurka in~C, Op.~56 No.~2 \and Mazurka
  in A~minor, Op.~67 No.~4 \and Mazurka in A~minor, Op.~68 No.~2 \and
  Mazurka in~C, Op.~68 No.~1 \and Mazurka in G~sharp minor, Op.~33 No.~1
  \and Mazurka in D~flat, Op.~30 No.~3 \and Mazurka in B~minor, Op.~30
  No.~2 \and Mazurka in B~minor, Op.~33 No.~4 \and Mazurka in F~minor,
  Op.~68 No.~4 \; \track \C{Federico Mompou} Canci\'on y danza No.~1}.
Volume~69 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 904-2}.

\cd\relax
\artist{Michelangeli, Arturo Benedetti}.
\cdtitle{Debussy/Galuppi/Scarlatti/Ravel \: \track \C{Claude Debussy}
  Images, Book~1 \and Images, Book~2 \and Pr\'eludes, Book~1
  \(Excerpts\) \and Pr\'eludes, Book~2 \(Excerpts\) \; \track
  \C{Baldassare Galuppi} Sonata No.~5 in~C \; \track \C{Maurice Ravel}
  Gaspard de la nuit \and Piano Concerto in~G \; \track \C{Domenico
  Scarlatti} Sonata in C~minor, K.~11 \and Sonata in~C, K.~159 \and
  Sonata in~A, K.~322}.
Volume~68 of \emph{Great Pianists of the 20th Century}.
Philharmonia Orchestra.
Ettore Gracis, cond.
Philips Classics, 1998 \cdnum[2]{456 901-2}.

\cd\relax
\artist{Mieg, Peter}.
\cdtitle{\track Triple concerto dans le go\^ut italien for violin,
  viola, violoncello and string orchestra \; \track Mit Nacht und Nacht
  for tenor and orchestra \; \track Morceau \'el\'egant for flute and
  harp \; \track Musik f\"ur Cembalo, zwei Bl\"aser und vier Streicher
  \(Septet for harpsichord, flute, oboe, violin, viola, violoncello and
  double bass\) \; \track Sonate for violoncello and piano}.
Jecklin, 1996 \cdnum{JS~314-2}.

\cd*\relax
\artist{Mih\'aly, Andr\'as}.
\cdtitle{Mouvement for Cello and Piano}.
\see{804}.

\cd*\relax
\artist{Milhaud, Darius}.
\cdtitle{Concertino d'hiver for trombone and strings}.
\see{965}.

\cd*\relax
\artist{Milhaud, Darius}.
\cdtitle{Scaramouche}.
\see{252}.

\cd*\relax
\artist{Milhaud, Darius}.
\cdtitle{Scaramouche \and La Cr\'eation du Monde}.
\see{631}.

\cd*\relax
\artist{Milhaud, Darius}.
\cdtitle{Scaramouche, Suite for Two Pianos, Op.~165b}.
\see{380}.

\cd*\relax
\artist{Milhaud, Darius}.
\cdtitle{Sonatina, Op.~100}.
\see{439}.

\cd*\relax
\artist{Milhaud, Darius}.
\cdtitle{Tijuca \from Saudades do Brasil, Op.~67}.
\see{1315}.

\cd\relax
\artist{Miner, Mark Robert}.
\cdtitle{Readings from Wheelock's Latin}.
Bolchazy-Carducci Publishers, 2006 (978-0-86516-638-7).

\cd*\relax
\artist{Mintzer, Bob}.
\cdtitle{Quartet \#1 in Three Movements}.
\see{1147}.

\cd\relax
\artist{Mitchell, Joni}.
\cdtitle{Blue}.
Reprise Records, 1971 \cdnum{2038-2}.

\cd\relax
\artist{Mitchell, Joni}.
\cdtitle{Court and Spark}.
Elektra/Asylum Records, 1974 \cdnum{1001-2 EUR 253 002}.

\cd\relax
\artist{Mitchell, Joni}.
\cdtitle{Hejira}.
Elektra/Asylum Records, 1976 \cdnum{1087-2}.

\cd\relax
\artist{Mitchell, Joni}.
\cdtitle{Ladies of the Canyon}.
Reprise Records, 1970 \cdnum{6376-2}.

\cd\relax
\artist{Mitchell, Joni}.
\cdtitle{Night Ride Home}.
Geffen Records, 1991 \cdnum{GEFD-24302}.

\cd\relax
\artist{Moeran, E. J.}
\cdtitle{\track String Quartet in E~flat major \; \track String Quartet
  in A~minor \; \track String Trio in G~major}.
Maggini String Quartet.
Naxos, 1997 \cdnum{8.554079}.

\cd\relax
\artist{Moiseiwitsch, Benno}.
\cdtitle{Chopin/Kabalevsky/Liszt/Mednter/Rachmaninoff \: \track
  \C{Fr\'ed\'eric Chopin} Ballade No.~3 in A~flat, Op.~47 \and Ballade
  No.~4 in F~minor, Op.~52 \and Barcarolle in F~sharp, Op.~60 \and
  Fantaisie-Impromptu in C~sharp minor, Op.~66 \and Nocturne in~E,
  Op.~62 No.~2 \and Nocturne in~G, Op.~37 No.~2 \and Scherzo No.~2 in
  B~flat minor, Op.~31 \and Scherzo No.~4 in~E, Op.~54 \; \track
  \C{Dmitri Kabalevsky} Piano Sonata No.~3 in~F, Op.~46 \; \track
  \C{Franz Liszt} \'Etude de concert No.~2 in F~minor ``La leggierezza''
  \; \track \C{Nicolai Medtner} Piano Sonata in G~minor, Op.~22 \;
  \track \C{Felix Mendelssohn Bartholdy and Sergei Rachmaninoff} Scherzo
  from ``A Midsummer Night's Dream'' \; \track \C{Sergei Prokofiev}
  Suggestion diabolique, Op.~4 No.~4 \; \track \C{Sergei Rachmaninoff}
  Moment musical in E~minor, Op.~16 No.~4 \and Prelude in~G, Op.~32
  No.~5 \and Piano Concerto No.~2 in C~minor, Op.~18}.
Volume~70 of \emph{Great Pianists of the 20th Century}.
Philharmonia Orchestra.
Hugo Rignold, cond.
Philips Classics, 1998 \cdnum[2]{456 907-2}.

\cd\relax
\artist{Molam Lao}.
\cdtitle{Music from Southern Laos \: \track Pheng Sat Niao \; \track Lam
  Saravane \; \track Pheng Borane \; \track Lam Khonsavane \; \track Kao
  Nok \; \track Lam Tangvay \; \track Pheng Sat Soy \; \track Lam
  Phuthay \; \track Pheng Lom Phat Phay \; \track Lam Mahaxay \; \track
  Lam Khone}.
Nimbus Records, 1994 \cdnum{NI~5401}.

\cd*\relax
\artist{Mompou, Federico}.
\cdtitle{Canci\'on y danza No.~1}.
\see{1066}.

\cd*\relax
\artist{Mompou, Federico}.
\cdtitle{Can\c{c}ons i dansas \(Excerpts\)}.
\see{477}.

\cd\relax
\artist{Mompou, Federico}.
\cdtitle{Piano Music}.
Stephen Hough.
Hyperion, 1997 \cdnum{CDA66963}.
Recorded in St George's, Brandon Hill, Bristol on 22, 23~July, 1996.

\cd\relax
\artist{Monk, Thelonious}.
\cdtitle{The Complete London Collection, Volume~One}.
Black Lion, 1972 \cdnum{BLCD~760101}.

\cd\relax
\artist{Monk, Thelonious}.
\cdtitle{The Complete London Collection, Volume~Three}.
Black Lion, 1989 \cdnum{BLCD~760142}.

\cd\relax
\artist{Monk, Thelonious}.
\cdtitle{The Complete London Collection, Volume~Two}.
Black Lion, 1988 \cdnum{BLCD~760116}.

\cd\relax
\artist{Monteverdi, Claudio}.
\cdtitle{L'Orfeo}.
The Monteverdi Choir, the English Baroque Soloists and His Majesties
  Sagbutts and Cornetts.
John Eliot Gardiner, cond.
Deutsche Grammophon, 1987 \cdnum[2]{419 250-2}.

\cd\relax
\artist{Monteverdi, Claudio}.
\cdtitle{\track Vespro Della Beata Vergine \(1610\) \; \track Magnificat
  a Sei Voci}.
The Monteverdi Choir, the London Oratory Junior Choir, the English
  Baroque Soloists and His Majesties Sagbutts and Cornetts.
John Eliot Gardiner, cond.
Deutsche Grammophon, 1990 \cdnum[2]{429 565-2}.

\cd\relax
\artist{Monty Python}.
\cdtitle{Another Monty Python CD}.
Virgin Records, 1971 \cdnum{CASCD~1049}.

\cd\relax
\artist{Monty Python}.
\cdtitle{Live! At City Center}.
Arista, 1997 \cdnum{07822-18957-2}.

\cd\relax
\artist{Monty Python}.
\cdtitle{Monty Python's Contractual Obligation Album}.
Virgin Records, 1980 \cdnum{CASCD~1152}.

\cd\relax
\artist{Monty Python}.
\cdtitle{Monty Python's Previous Album}.
Virgin Records, 1972 \cdnum{CASCD~1063}.

\cd\relax
\artist{Monty Python}.
\cdtitle{The Album of the Soundtrack of the Trailer of the Film of Monty
  Python and the Holy Grail}.
Virgin Records, 1975 \cdnum{CASCD 1103}.

\cd\relax
\artist{Monty Python}.
\cdtitle{The Final Rip Off}.
Virgin Records America, 1987 \cdnum[2]{0777 7 86033-2~0}.

\cd\relax
\artist{Monty Python}.
\cdtitle{The Monty Python Instant Record Collection}.
Arista, 1981 \cdnum{ARCD-8296}.

\cd\relax
\artist{Monty Python}.
\cdtitle{The Monty Python Matching Tie and Handkerchief}.
Virgin Records, 1973 \cdnum{CASCD 1080}.

\cd\relax
\artist{Moravec, Ivan}.
\cdtitle{Chopin/Debussy/Franck/Ravel \: \track \C{Fr\'ed\'eric Chopin}
  Polonaise in A~flat, Op.~61 ``Polonaise-Fantasie'' \and Mazurka in
  F~minor, Op.~63 No.~2 \and Mazurka in A~minor, Op.~68 No.~2 \and
  Mazurka in C~sharp minor, Op.~50 No.~3 \and Mazurka in C~sharp minor,
  Op.~63 No.~3 \and Mazurka in F~minor, Op.~68 No.~4 \and Mazurka in~C,
  Op.~56 No.~2 \and Mazurka in E~minor, Op.~41 No.~2 \and Scherzo No.~2
  in B~flat minor, Op.~31 \and Nocturne No.~17 in~B, Op.~62 No.~1 \and
  Nocturne No.~18 in~E, Op.~62, No.~2 \and Barcarolle in F~sharp, Op.~60
  \and Ballade No.~4 in F~minor, Op.~52 \; \track \C{C\'esar Franck}
  Pr\'elude, choral et fugue \; \track \C{Claude Debussy} Images
  \(Book~1\) \and Images \(Book~2\) \and Pour le piano. Suite \; \track
  \C{Maurice Ravel} Sonatine}.
Volume~71 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 910-2}.

\cd*\relax
\artist{Morini, G.}
\cdtitle{La luna}.
\see{1344}.

\cd*\relax
\artist{Morosco, Victor}.
\cdtitle{Blue Caprice}.
\see{1603}.

\cd\relax
\artist{Morrison, Van}.
\cdtitle{Moondance}.
Warner Brothers, 19770 \cdnum{3103-2}.

\cd\relax
\artist{Morrison, Van}.
\cdtitle{Tupelo Honey}.
Warner Brothers, 1971 \cdnum{1950-2}.

\cd\relax
\artist{Morrissey, Bill}.
\cdtitle{Bill Morrissey}.
Rounder Records, 1991 \cdnum{Philo CD PH~1105}.

\cd\relax
\artist{Morrissey, Bill}.
\cdtitle{Inside}.
Rounder Records, 1992 \cdnum{Philo CD PH~1145}.

\cd\relax
\artist{Morrissey, Bill}.
\cdtitle{Night Train}.
Rounder Records, 1993 \cdnum{Philo CD PH~1154}.

\cd\relax
\artist{Morrissey, Bill}.
\cdtitle{North}.
Rounder Records, 1986/1991 \cdnum{Philo CD PH~1106}.

\cd\relax
\artist{Morrissey, Bill}.
\cdtitle{Something I Saw or Thought I Saw}.
Rounder Records, 2001 \cdnum{Philo 11671-1227-2}.

\cd\relax
\artist{Morrissey, Bill}.
\cdtitle{Standing Eight}.
Rounder Records, 1989 \cdnum{Philo CD PH~1123}.

\cd\relax
\artist{Morrissey, Bill}.
\cdtitle{You'll Never Get to Heaven}.
Rounder Records, 1996 \cdnum{Philo CD PH~1194}.

\cd\relax
\artist{Morrissey, Bill and Greg Brown}.
\cdtitle{Friend of Mine}.
Rounder Records, 1993 \cdnum{Philo CD PH~1151}.

\cd\relax
\artist{Mosonyi, Mih\'aly}.
\cdtitle{\track Piano Trio in B~flat major, Op.~1 \; \track Grand
  Nocturne for Piano, Violin and Violoncello}.
Kassai Trio.
Marco Polo, 1999 \cdnum{9.225042}.

\cd*\relax
\artist{Moss, Lawrence}.
\cdtitle{Rivermusic for Saxophone Quartet}.
\see{23}.

\cd*\relax
\artist{Moszkowski, Moritz}.
\cdtitle{Capriccio espagnole, Op.~37 \(abridged\) \and La jongleuse,
  Op.~52 No.~4}.
\see{775}.

\cd*\relax
\artist{Moszkowski, Moritz}.
\cdtitle{Etude in A~flat minor, Op.~72, No.~13}.
\see{724}.

\cd*\relax
\artist{Moussorgsky, Modest}.
\cdtitle{Pictures at an Exhibition}.
\see{1270}.

\cd*\relax
\artist{Mozart, Leopold}.
\cdtitle{Concerto in D major for Alto Trombone}.
\see{963}.

\cd*\relax
\artist{Mozart, Leopold}.
\cdtitle{Konzert d-dur f\"ur Trompete, H\"orner und Streicher}.
\see{1523}.

\cd*\relax
\artist{Mozart, W. A.}
\cdtitle{Adagio in C~major for English horn, Violin, Viola and
  Violoncello, KV580a}.
\see{784}.

\cd*\relax
\artist{Mozart, W. A.}
\cdtitle{Sonata for Bassoon and Cello}.
\see{1164}.

\cd*\relax
\artist{Mozart, Wolfang Amadeus}.
\cdtitle{12 Variations in~C, KV~265 on ``Ah, vous dirai-je, Maman'' \and
  Piano Sonata in~F, KV~332}.
\see{579}.

\cd*\relax
\artist{Mozart, Wolfang Amadeus}.
\cdtitle{Fantasia in D~minor, KV~397}.
\see{632}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{10 Variations in~G, KV~455 on ``Unser dummer P\"obel meint''
  \(C. W. Gluck\) \and Rondo in A~minor, KV~511 \and Piano Sonata in~D,
  KV~576 \and Adagio in B~minor, KV~540 \and Piano Concerto No.~9 in
  E~flat, KV~271 ``Jeunehomme''}.
\see{1610}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{12 Variations in~C, KV~265 on ``Ah, vous dirai-je, Maman'' \and
  Piano Sonata in~C, KV~330 \and 9 Variations in~D, KV~573 on a minuet
  by Jean-Pierre Duport \and Piano Sonata in~F, KV~280}.
\see{747}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{3 Violin Concertos \: \track Concerto in G~major, K.~216 \;
  \track Concerto in D~major, K.~218 \; \track Concerto in A~major,
  K.~219}.
Andrew Manze.
The English Concert, cond.
Harmonia Mundi, 2006 \cdnum{HMU 907385}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Complete String Trios and Duos \: \track Divertimento \(String
  Trio\) in E~flat, KV~563 \; \track Duo for Violin and Viola in~G,
  KV~423 \; \track Duo for Violin and Viola in B~flat, KV~424 \; \track
  Sonate \(Trio\) in B~flat, KV~266 \; \track Six Preludes and Fugues
  for Violin, Viola and Cello, KV~404a}.
The Grumiaux Trio, Arrigo Pelliccia and the Academy of St~Martin in the
  Fields Chamber Ensemble.
Philips Classics, 1996 \cdnum[2]{454 023-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Complete Wind Music \(K166, K186, K213, KA226, KA227, K240,
  K252, K253, K270, K289, K361, K375, K388, K410, K411\)}.
The London Wind Soloists.
Jack Brymer, cond.
The Decca Record Company, 1963 \cdnum[3]{455 794-2}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Concerto for Oboe and Orchestra in C~major, K.~314 \(285d\)}.
\see{946}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Concerto for Two Pianos in E~flat, KV~365}.
\see{380}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Cos{\`\i} fan tutte}.
Elisabeth Schwarzkopf, Christa Ludwig, Alfredo Kraus, Giuseppe Taddei,
  Walter Berry and Hanny Steffek.
Philharmonia Orchestra and Choir.
Karl B\"ohm, cond.
EMI Records, 1963/1988 \cdnum[3]{CMS~7 69330~2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Die Zauberfl\"ote}.
Academy of St~Martin in the Fields.
Sir Neville Marriner, cond.
Philips Classics, 1990 \cdnum[2]{426 276-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Don Giovanni}.
Cesare Siepi, Suzanne Danco, Lisa della Casa, Fernando Corena, Anton
  Dermota, Hilde Gueden, Walter Berry and Kurt B\"ohme.
Wiener Philharmoniker.
Josef Krips, cond.
Decca, 1955/2000 \cdnum[3]{289 466 389-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Eine Kleine Nachtmusik \(K.~525\) \and Notturno for four
  orchestras \(K.~286\) \and Serenata notturna \(K.~239\)}.
The Academy of Ancient Music.
Christopher Hogwood, cond.
The Decca Record Company, 1984 \cdnum{411~720-2}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Fantasia in C~minor, KV~475}.
\see{337}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Fantasia \(Prelude\) and Fugue in~C, KV~394}.
\see{658}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Fantasie in C~minor, KV~475}.
\see{45}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Horn Concertos Nos.~1--4 \and Quintet in E~flat for piano and
  wind, K.~452}.
Dennis Brain.
The Philharmonia Orchestra.
Herbert von Karajan, cond.
EMI Records, 1997 \cdnum{7243 5 56231 2~6}.
Quintet performed by Colin Horsley (piano) and the Dennis Brain Wind
  Ensemble.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{in ~F, KV~332}.
\see{623}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Le nozze di Figaro}.
\see{628}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Le Nozze di Figaro}.
Kiri Te Kanawa, Lucia Popp, Frederica von Stade, Kurt Moll and Jeffrey
  Tate (continuo).
London Philharmonic Orchestra.
Sir Georg Solti, cond.
The Decca Record Company, 1983 \cdnum[3]{410 150-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Music for 2~Pianos and Piano Duets \: \track Sonata in~C for
  Piano Duet, KV~19d \; \track Sonata in~D for Piano Duet, KV~381/123a
  \; \track Sonata in B~flat for Piano Duet, KV~358/186c \; \track
  Sonata in~D for Two Pianos, KV~448 \; \track Fugue in C~minor for Two
  Pianos, KV~426 \; \track Larghetto and Allegro in E~flat for Two
  Pianos, KV~deest \; \track Sonata in~F for Piano Duet, KV~497 \;
  \track Sonata in~G for Piano Duet, KV~357/497a + 500a \; \track Adante
  with Five Variations in~G for Piano Duet, KV~501 \; \track Sonata in~C
  for Piano Duet, KV~521}.
Ingrid Haebler, Ludwig Hoffmann, J\"org Demus and Paul Badura-Skoda.
Philips Classics, 1996 \cdnum[2]{454 026-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Night Music \: \track Serenade in G~major, K.~525 ``Eine kleine
  Nachtmusik'' \; \track Adagio and Fugue in C~minor, K.~546 \; \track
  Menuet and Trio in C~major, K.~485a \; \track Serenade in D~major,
  K.~522 ``Serenata Notturna'' \; \track Ein musikalischer Spa\ss,
  K.~522}.
The English Concert.
Andrew Manze, cond.
Harmonia Mundi, 2003 \cdnum{HMU 907280}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Organ Sonatas and Solos}.
Daniel Chorzempa.
Deutsche Bachsolisten.
Helmut Winschermann, cond.
Philips, 1973/1991 \cdnum[2]{422 521-2}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~13 in~C, KV~415 \and Piano Concerto No.~20
  in D~minor, KV~466 \and Piano Concerto No.~23 in~A, KV~488 \and Piano
  Concerto No.~24 in C~minor, KV~491 \and Piano Concerto No.~27 in~C,
  KV~595 \and Rondo for Piano and Orchestra in~A, KV~386}.
\see{748}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~14 in E~flat, KV~449 \and Piano Concerto
  No.~17 in~G, KV~453 \and Piano Concerto No.~12 in~A, KV~414 \and Piano
  Concerto No.~16 in~D, KV~451 \and Piano Concerto No.~19 in~F, KV~459}.
\see{1428}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~14 in E~flat, KV~449 \and Piano Sonata in~C,
  KV~545 ``For Beginners'' \and Piano Sonata in E~flat, KV~282 \and
  Piano Sonata in B~flat, KV~333 \and Piano Sonata in~A, KV~331}.
\see{1201}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~17 in~G, KV~453}.
\see{1217}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~18 in B~flat, KV~456 \and Nine Variations
  in~D, KV~573 on a minuet by Jean-Pierre Duport \and Piano Sonata in~D,
  KV~576}.
\see{720}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~20 in D~minor, KV~466 \and Fantasia in
  C~minor, KV~475}.
\see{589}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~21 in~C, KV~467}.
\see{25}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~23 in~A, KV~488}.
\see{886}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~23 in~A, KV~488 \and Piano Concerto No.~24
  in C~minor, KV~491}.
\see{637}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~25 in~C, KV~503}.
\see{1196}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~25 in~C, Op.~15}.
\see{158}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~26 in~D, KV~537 ``Coronation'' \and Piano
  Concerto No.~27 in B~flat, KV~595}.
\see{471}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~27 in B~flat, KV~595}.
\see{642}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Concerto No.~8 in~C, KV~246 ``L\"utzow'' \and Ten
  Variations in~G, KV~455 on ``Unser dummer P\"obel meint'' \(C.~W.
  Gluck\)}.
\see{887}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Sonata in A~minor, K.~310 \(300~d\) \and Piano Sonata in
  A~major, K.~331 \(300i\) \and Piano Sonata in F~major, K.~533/494}.
Murray Perahia.
Sony, 1992 \cdnum{SK 48 233}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Sonata in A~minor, KV~310}.
\see{967}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Sonata in B~flat, KV~333}.
\see{1485}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Sonata in~C, KV~330}.
\see{604}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Piano Sonatas \and Fantasia in C~minor, KV~475}.
Mitsuko Uchida.
Philips, 1991 \cdnum[5]{422 517-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{\track Requiem, K.~626 \; \track Kyrie, K.~341}.
Sibylla Rubens (soprano), Annette Markert (alto), Ian Bostridge (tenor)
  and Hanno M\"uller-Brachmann (baryton).
La Chapelle Royale, Collegium Vocale and Orchestre des Chaps
  \'Elys\'ees.
Philippe Herreweghe, cond.
Harmonia Mundi, 1997, 2000 \cdnum{HMX 2901620}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Requiem, KV~626 and Kyrie in D~minor, KV~341}.
John Eliot Gardiner, cond.
Philips, 1987 \cdnum{420 197-2}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Rondo in~D, KV~485 \and Piano Sonata in~C, KV~330 \and Piano
  Sonata in~A, KV~331 ``Alla Turca'' \and Piano Sonata in~D, KV~576}.
\see{478}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Serenade in B flat, KKV~361, ``Gran Partita''}.
Academy of St~Martin-in-the-Fields.
Sir Neville Marriner, cond.
Philips, 1986 \cdnum{412 726-2}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Sonata for Bassoon and Cello in B-Flat, K.~292}.
\see{661}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Sonata for Two Pianos in~D, KV~448 \and Piano Concerto No.~21
  in~C, KV~467}.
\see{952}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Sonata in~C, KV~545 \(``for beginners''\) \and Sonata in~D,
  KV~576}.
\see{1340}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Sonata No.~10 in C~major, K.~330 \and Fantasia and Fugue in
  C~major, K.~394}.
\see{659}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Symphonien Nos. 40 and~41 \(``Jupiter''\)}.
The Wiener Philharmoniker.
Leonard Bernstein, cond.
Polygram Records, 1984/1985 \cdnum{445 548-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{\track Symphony No.~25 in G~minor, K183 \; \track Serenata
  notturna in D~major, K239 \; \track Symphony No.~29 in A~major, K201
  \; \track Symphony No.~40 in G~minor, K550 \; \track Symphony No.~38
  in D~major, K504 ``Prague''}.
English Chamber Orchestra.
Benjamin Britten, cond.
The Decca Record Company, 1995 \cdnum[2]{444 323-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{\track Symphony No.~27 in G~major, K.~199 \; \track Clarinet
  Concerto in A~major, K.~622 \; \track Symphony No.~21 in A~major,
  K.~134}.
Michel Portal (clarinet).
Wiener Kammerorchester.
Philippe Entremont, cond.
Harmonia Mundi, 1999 \cdnum{HMX 2901304}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{\track Symphony No.~28 in C~Major, K.~200 \(189k) \; \track
  Symphony No.~29 in A~Major, K.~201 \(186a) \; \track Symphony No.~35
  in D~Major, K.~385 ``Haffner''}.
Berlin Philharmonic.
Claudia Abbado, cond.
Sony Classical, 2004 \cdnum{SK~92762}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Symphony No.~39 in E~flat major, KV~543 \and Symphony No.~40 in
  G~minor, KV~550 \and Eine kleine Nachtmusik, Serenade in G~major,
  KV~525}.
\see{626}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{The Complete Piano Sonatas \and Fantasias K.~397 and K.~475}.
Glenn Gould.
Sony, 1994 \cdnum[4]{SM4K 52~627}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{The Complete Piano Trios \(K.~254, K.~496, K.~502, K.~542,
  K.~548, K.~564\) \and The Clarinet Trio in E~flat \(K.~498,
  ``Kegelstatt''\)}.
The Beaux Arts Trio, Stephen Kovacevich (piano), Jack Brymer (clarinet)
  and Patrick Ireland (viola).
Philips Classics, 1995 \cdnum[2]{446 154-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{The Complete Quintets, Volume~1 \(KV~174, KV~406 \(516b\),
  KV~407, KV~411, KV~452, KV~515\)}.
Philips Classics, 1997 \cdnum[2]{456 055-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{The Complete Quintets, Volume~2 \(KV~516, KV~546, KV~581,
  KV~593, KV~614, KV~617\)}.
Philips Classics, 1997 \cdnum[2]{456 058-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{The Concertos for Piano and Orchestra \and Rondos K.~382
  and~386}.
Murray Perahia.
Sony, 1991 \cdnum[12]{SX12K 46 41}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{The Great Violin Sonatas, Volume~1 \(KV~296, 301--306, 359,
  376, 377\)}.
Henryk Szeryng (violin) and Ingrid Haebler (piano).
Philips Classics, 1998 \cdnum[2]{289 462 185-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{The Great Violin Sonatas, Volume~2 \: \track Sonata in B~flat,
  KV~378 \; \track Sonata in~G, KV~379 \; \track Sonata in E~flat,
  KV~380 \; \track Sonata in B~flat, KV~454 \; \track Sonata in E~flat,
  KV~481 \; \track Sonata in~A, KV~526 \; \track Sonata in~F, KV~547
  ``for beginners'' \; \track Six Variations in G~minor, KV~360 on
  ``H\'elas, j'ai perdu mon amant''}.
Henryk Szeryng (violin) and Ingrid Haebler (piano).
Philips Classics, 1999 \cdnum[2]{289 462 303-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{The Ten Celebrated String Quartets \(K.~387, K.~421, K.~428,
  K.~458, K.~464, K.~465, K.~499, K.~575, K.~589, K.~590\)}.
The Franz Schubert Quartett of Vienna.
Nimbus Records, 1997 \cdnum[5]{NI 1778}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{The Violin Concertos, Two Rondos and Adagio K261 \(K207, K211,
  K216, K269 \(261a\), K218, K219, K261, K373\)}.
Simon Standage (violin).
The Academy of Ancient Music.
Christopher Hogwood, cond.
The Decca Record Company, 1997 \cdnum[2]{455 721-2}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{The Works for Flute \(K.~313--315, K.~298--299, K.~285,
  K.~285a, K.~285b, K.~297b)}.
Philips Classics, 1994 \cdnum[2]{442 299-2}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Trio for Piano, Clarinet and Viola \(Cello\) ``Kegelstatt'' in
  E-flat Major, K.~498}.
\see{1005}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Twelve Variations in~C, KV~265 on ``Ah, vous dirai-je,
  Maman''}.
\see{617}.

\cd*\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Violin Concerto No.~3 in G major, K216 \and Adagio in E major
  for violin and orchestra, K261 \and Violin Concerto No.~5 in A major,
  K219 \and Rondo in C major for violin and orchestra, K373}.
\see{243}.

\cd\relax
\artist{Mozart, Wolfgang Amadeus}.
\cdtitle{Violin Concertos Nos.~2, 3,~5}.
Vadim Repin.
The Wiener Kammerorchester.
Yehudi Menuhin, cond.
Erato, 1998 \cdnum{3984-21660-2}.

\cd*\relax
\artist{Mozart, Wolgang Amadeus}.
\cdtitle{Piano Sonata in C~minor, KV~457}.
\see{638}.

\cd*\relax
\artist{Muczynski, Robert}.
\cdtitle{Sonata Op.~29}.
\see{1603}.

\cd*\relax
\artist{Muffat, Georg}.
\cdtitle{Sonata Violino Solo in D~major}.
\see{259}.

\cd*\relax
\artist{Mundry, Isabelle}.
\cdtitle{Komposition f\"ur Altsaxophon und Tonband}.
\see{578}.

\cd\relax
\artist{Munro, David}.
\cdtitle{Early Music Festival}.
Early Music Consort and Musica Reservata.
David Munrow and John Beckett, cond.
The Decca Record Company, 1998 \cdnum[2]{289 452 967-2}.

\cd*\relax
\artist{Muradian, Vazgen}.
\cdtitle{Concerto for Oboe and String Quartet, Opus~25}.
\see{432}.

\cd*\relax
\artist{Muradian, Vazgen}.
\cdtitle{Contrabassoon Concerto, op.~86}.
\see{1163}.

\cd\relax
\artist{Mussorgsky, Modest}.
\cdtitle{\track Pictures at an Exhibition \; \track \C{Piotr Ilich
  Tchaikovsky} Marche miniature \; \track \C{Modest Mussorgsky} A Night
  on Bald Mountain \; \track \C{Alexander Borodin} Prince Igor:
  Polovtsian March \; \track \C{Piotr Ilich Tchaikovsky} Marche slave \;
  \track \C{Dmitri Kabalevsky} Colas Breugnon: Overture \; \track
  \C{Mikhail Glinka} Russlan and Ludmilla: Overture}.
Chicago Symphony Orchestra.
Fritz Reiner, cond.
BMG Classics, 1994 \cdnum{09026-61958-2}.

\cd*\relax
\artist{Mussorgsky, Modest P.}
\cdtitle{A Night on Bald Mountain}.
\see{299}.

\cd*\relax
\artist{Muzio, Emanuele}.
\cdtitle{Luisa Miller}.
\see{721}.

\cd*\relax
\artist{Nagao, Jun}.
\cdtitle{Rhapsody on \emph{Carmen} de Georges Bizet}.
\see{19}.

\cd*\relax
\artist{Nagle, Paul}.
\cdtitle{Three Shades of Blues}.
\see{830}.

\cd\relax
\artist{Nakariakov, Sergei}.
\cdtitle{\track \C{Andr\'e Jolivet} Concertino for Trumpet, Piano and
  Strings \; \track \C{Johann Nepomuk Hummel} Concerto for Trumpet and
  Orchestra in E~flat major \; \track \C{Henri Tomasi} Concerto for
  Trumpet and Orchestra \; \track \C{Joseph Haydn} Trumpet Concerto in
  E~flat major, H.~Viie/1}.
Alexander Markovich (piano).
Orchestre de Chambre de Lausanne.
Jesus Lopez-Coboz, cond.
Teldec Classics, 1993 \cdnum{4509-90846-2}.

\cd\relax
\artist{Nakariakov, Sergei}.
\cdtitle{Baroque Trumpet Concertos \: \track \C{Antonio Vivaldi}
  Concerto in B~flat major \; \track \C{Georg Philipp Telemann} Concerto
  in D~major \and Concerto in F~minor \; \track \C{Johann Baptist Georg
  Neruda} Concerto in E~flat major \; \track \C{Alessandro Marcello}
  Concerto in C~minor \; \track \C{Johann Sebastian Bach} Agnus Dei from
  Mass in B~minor arr.\ for flugelhorn}.
The Saint Paul Chamber Orchestra.
Hugh Wolff, cond.
Teldec Classics, 1996 \cdnum{0630-10788-2}.

\cd\relax
\artist{Nakariakov, Sergei}.
\cdtitle{Carmen Fantasy: Virtuoso Music for Trumpet}.
Alexander Markovich (piano).
Teldec Classics, 1994 \cdnum{4509-94554-2}.

\cd\relax
\artist{Nakariakov, Sergei}.
\cdtitle{Concertos for Trumpet \: \track \C{Joseph Haydn} Concerto in
  C~major for cello, Hob.~VIIb:1 \; \track \C{Franz Anton Hoffmeister}
  Concerto in D~major for viola \; \track \C{Felix Mendelssohn} Concerto
  in D~minor for violin}.
W\"urttembergisches Kammerorchester Heilbronn.
J\"org Faerber, cond.
Teldec Classics, 1999 \cdnum{3984-24276-2}.

\cd\relax
\artist{Nakariakov, Sergei}.
\cdtitle{\'El\'egie}.
Vera Nakariakova (piano).
Teldec Classics, 1997 \cdnum{0630-15687-2}.

\cd\relax
\artist{Nakariakov, Sergei}.
\cdtitle{From Moscow with Love \: \track \C{Alexander Arutiunian}
  Concerto for Trumpet and Orchestra \; \track \C{Moissei Vainberg}
  Concerto for Trumpet and Orchestra, Op.~94 \; \track \C{Reinhold
  Gli\`ere} Concerto for Horn and Orchestra, Op.~91}.
Jenaer Philharmonie.
Andrey Boreyko, cond.
Teldec Classics, 2001 \cdnum{8573-85558-2}.

\cd\relax
\artist{Nakariakov, Sergei}.
\cdtitle{No Limit \: \track \C{Camille Saint-Sa\"ens} Introduction and
  Rondo capriccioso \; \track \C{Peter Tchaikovsky} Andante cantabile
  \and Variations on a Rococo Theme \; \track \C{Max Bruch} Canzone \;
  \track \C{Jules Massenet} M\'editation \; \track \C{George Gershwin}
  Rhapsody in Blue}.
The Philharmonia.
Vladimir Ashkenazy, cond.
Teldec Classics, 2000 \cdnum{8573-80651-2}.

\cd\relax
\artist{Nakarjakov, Sergei}.
\cdtitle{Trumpet Works}.
Alexander Markovich (piano).
Teldec Classics, 1992 \cdnum{9031-77705-2}.

\cd*\relax
\artist{Natsuda, Masakazu}.
\cdtitle{West, or Evening Song in Autumn}.
\see{483}.

\cd*\relax
\artist{Naulais, J\'er\^ome}.
\cdtitle{Frissons}.
\see{1602}.

\cd*\relax
\artist{Naulais, J\'er\^ome}.
\cdtitle{Sax de Voyage}.
\see{1604}.

\cd*\relax
\artist{Neruda, Johann Baptist Georg}.
\cdtitle{Concerto in E~flat major}.
\see{1139}.

\cd\relax
\artist{New Century Saxophone Quartet}.
\cdtitle{Home Grown \: \track \C{Sherwood Shaffer} Sinfonia for
  Saxophone Quartet \(1992\) \; \track \C{Lenny Pickett} Saxophone
  Quartet No.~2 \(1995\) \; \track \C{Thomas Massella} Three Lyrics for
  Saxophone Quartet \(1998\) \; \track \C{Ken Valitsky} Saxomaphone
  \(1998\) \; \track \C{David Ott} Three Moods \(1998\) \; \track
  \C{Benjamin Boone} Alley Dance \(1996\)}.
Volume~1 of \emph{Commisions}.
Channel Classics, 1999 \cdnum{CCS~15498}.

\cd\relax
\artist{New Century Saxophone Quartet}.
\cdtitle{Standards \: \track \C{Jean-Baptiste Singel\'ee} Premier
  Quatuor, Op.~53 \(1857\) \; \track \C{Alfred Desenglos} Quatuor
  \(1962\) \; \track \C{Elliot Del Borgo} Quartet for Saxophone \(1982\)
  \; \track \C{Bob Mintzer} Quartet \#1 in Three Movements \; \track
  \C{Michael Torke} July \(1995\)}.
Channel Classics, 2002 \cdnum{CCS~17998}.

\cd\relax
\artist{New Christy Minstrels, The}.
\cdtitle{Green, Green}.
Sony, 2003 \cdnum{COL-CD-9332}.

\cd\relax
\artist{New Christy Minstrels, The}.
\cdtitle{\track Tell Tall Tales! Legends and Nonsense \; \track Land of
  Giants}.
Collectors Choice Music (Sony), 2003 \cdnum{CCM-348-2}.

\cd\relax
\artist{New York Philharmonic}.
\cdtitle{The Historic Broadcasts 1923 to~1987}.
New York Philharmonic Special Editions, 1997 \cdnum[10]{NYP~9701}.

\cd\relax
\artist{Newhart, Bob}.
\cdtitle{Behind the Button-Down Mind of Bob Newhart}.
Warner Brothers, 1961 \cdnum{1417-2}.
Re-released, 1998.

\cd\relax
\artist{Newhart, Bob}.
\cdtitle{Button Down Concert}.
Sony, 1997 \cdnum{BK 63399}.

\cd\relax
\artist{Newhart, Bob}.
\cdtitle{``Something like this\dots'': The Bob Newhart Anthology}.
Rhino Records, 2001 \cdnum[2]{R2~76742}.

\cd\relax
\artist{Newhart, Bob}.
\cdtitle{The Button-Down Mind of Bob Newhart}.
Warner Brothers, 1960 \cdnum{9 45690-2}.

\cd\relax
\artist{Newhart, Bob}.
\cdtitle{The Button-Down Mind Strikes Back!}
Warner Brothers, 1960 \cdnum{1393-2}.
Re-released, 1998.

\cd\relax
\artist{Ni, Hai-Ye}.
\cdtitle{Cello Recital \: \track \C{Robert Schuman} Fantasiest\"ucke,
  Op.~73 \; \track \C{Ludwig van Beethoven} Seven Variations on Bei
  M\"annern welche Liebe f\"uhlen from Mozart's Die Zauberfl\"ote,
  WoO~46 \; \track \C{Franz Schubert} Sonata in A~minor, D.~821
  ``Arpeggione'' \; \track \C{Felix Mendelssohn} Sonata in D~major,
  Op.~58 \; \track \C{David Popper} Elfentanz, Op.~39}.
H\'el\`ene Jeanney (piano).
Naxos, 1998 \cdnum{8.554356}.

\cd*\relax
\artist{Nicholson, Ralph}.
\cdtitle{Miniature Suite}.
\see{1163}.

\cd*\relax
\artist{Nielsen, Carl}.
\cdtitle{Canto Serioso}.
\see{504}.

\cd\relax
\artist{Nielsen, Carl}.
\cdtitle{String Quartets, Volume~1 \: \track String Quartet in E~flat
  major, Op.~14 \; \track String Quartet in F~major, Op.~44}.
Oslo String Quartet.
Naxos, 1999 \cdnum{8.553907}.

\cd\relax
\artist{Nielsen, Carl}.
\cdtitle{Symphonic Rhapsody \and Helios Overture, Op.~17 \and
  Saga-dr{\o}m, Op.~39 \and Violin Concerto, Op.~33 \(Arve Tellefsen,
  violin\) \and Pan og Syrinx, Op.~49 \and Flute Concerto \(Frantz
  Lemmser, flute\) \and Rhapsody Overture: An Imaginary Journey to the
  F{\ae}roe Islands \and Clarinet Concerto, Op.~57 \(Kjell-Inge
  Stevennson, clarinet; Ib Jarlkov, side drum\)}.
Danis Radio Symphony Orchestra.
Herbert Blomstedt, cond.
EMI Records, 1997 \cdnum[2]{7243~5 69758 2~8}.

\cd*\relax
\artist{Nielsen, Carl}.
\cdtitle{Wind Quintet, Op.~43}.
\see{4}.

\cd*\relax
\artist{Nielsen, Svend}.
\cdtitle{Siciliano, ``Once upon a Time''}.
\see{1700}.

\cd*\relax
\artist{Nielsen, Svend Hvidtfelt}.
\cdtitle{Fable}.
\see{960}.

\cd\relax
\artist{Nietzsche, Friedrich}.
\cdtitle{Leider, Piano Works, Melodrama}.
Dietrich Fischer-Dieskau (baritone and piano), Aribert Reimann (piano)
  and Elmar Budde (piano).
Philips Classics, 1995 \cdnum{426 863-2}.

\cd\relax
\artist{Nigro, Susan}.
\cdtitle{Little Tunes for the Big Bassoon}.
Mark Lindeblad (piano).
Crystal Records, 1997 \cdnum{CD348}.

\cd\relax
\artist{Nigro, Susan}.
\cdtitle{New Tunes for the Big Bassoon \: \track \C{Barton Cummings}
  Concertino for Contrabassoon \and Arioso \; \track \C{Timothy Grassel}
  Reminiscences \; \track \C{P. Kellach Waddle} Broken Icicle Twilight
  \and Severe Thunderstorm Warning \; \track \C{Edward McKenna}
  Bagatelle \; \track \C{Ann Marie Kurrasch} Ponderings from the Pond \;
  \track \C{Graham Powning} Sonata}.
Mark Lindeblad (piano).
Crystal Records, 2004 \cdnum{CD843}.

\cd\relax
\artist{Nigro, Susan}.
\cdtitle{The Bass Nightingale \: \track \C{Ervin Schulhoff} Bass
  Nightingale \; \track \C{Burrill Phillips} Concert Piece \; \track
  \C{Gunther Schuller} Concerto for Contrabassoon \; \track \C{Carl
  Phillip Stamitz} Concerto in F~Major}.
Russell Hodgkinson (piano) and Leslie Amper (piano).
GM Recordings, 2001 \cdnum{GM2069CD}.

\cd\relax
\artist{Nigro, Susan}.
\cdtitle{The Big Bassoon \: \track \C{Vazgen Muradian} Contrabassoon
  Concerto, op.~86 \; \track \C{Donald Draganski} Heart's Desire \;
  \track \C{Alan Palider} The Narwhal, op.~11 \; \track \C{Ralph
  Nicholson} Miniature Suite \; \track \C{Frank Warren} Music for
  Contrabassoon and Piano, op.~28 \; \track \C{Matt Doran} Four
  Movements}.
Mark Lindeblad (piano).
Crystal Records, 1995 \cdnum{CD346}.

\cd\relax
\artist{Nigro, Susan and Burl Lane}.
\cdtitle{The 2 Contras \: \track \C{Daniel Dorff} Sonatina d'Amore \;
  \track \C{Etienne Ozi} Sonata No.~1 for Two Bassoons \; \track
  \C{Arthur Weisberg} From the Deep \; \track \C{W. A. Mozart} Sonata
  for Bassoon and Cello \; \track \C{Johann B. Vanhal} Concerto in
  F~Major \; \track \C{Michael Curtis} The Impish Imp}.
Crystal Records, 1999 \cdnum{CD349}.

\cd*\relax
\artist{Nilsson, Anders}.
\cdtitle{Concerto grosso for saxophone quartet and orchestra \(1995\)}.
\see{1248}.

\cd*\relax
\artist{Noda{\"\i}ra, Ichiro}.
\cdtitle{Arabesque~III}.
\see{483}.

\cd\relax
\artist{Nordic Guitar Quartet}.
\cdtitle{Images}.
Danica Records, 1994 \cdnum{DCD 8161}.

\cd*\relax
\artist{N{\o}rg{\aa}rd, Per}.
\cdtitle{Sonate Breve: Sonata for Solo Cello No.~3 ``What---is the
  word!''}
\see{1700}.

\cd\relax
\artist{Norman, Marsha and Lucy Simon}.
\cdtitle{The Secret Garden}.
Sony, 1991 \cdnum{CK~48817}.

\cd*\relax
\artist{Nov\'a\v{c}ek, Ottokar}.
\cdtitle{Perpetuum mobile}.
\see{245}.

\cd*\relax
\artist{Nussio, Otmar}.
\cdtitle{Variazioni su un' Arietta di Pergolesi for Basson and Piano}.
\see{847}.

\cd\relax
\artist{Nylons, The}.
\cdtitle{Happy Together}.
Attic Records, 1987 \cdnum{OD-0306}.

\cd\relax
\artist{Nylons, The}.
\cdtitle{Rockapella}.
Attic Records, 1989 \cdnum{WD~1085}.

\cd\relax
\artist{Nylons, The}.
\cdtitle{Seamless}.
Attic Records, 1986 \cdnum{OD-0304}.

\cd\relax
\artist{Nyman, Michael}.
\cdtitle{\track Double Concerto for Saxophone, Cello and Orchestra \;
  \track Concerto for Harpsichord and Strings \; \track Concerto for
  Trombone and Orchestra}.
John Harle (soprano and alto saxophones), Julian Lloyd Weber (cello),
  Elisabeth Chojnacka (harpsichord) and Christian Lindberg (trombone).
Philharmonia Orchestra, Michaaael Nyman String Orchestra and BBC
  Symphony Orchestra.
Michael Nyman, cond.
EMI Classics, 1997 \cdnum{7243 5 56487 2~3}.

\cd*\relax
\artist{Nyman, Michael}.
\cdtitle{Song for Tony}.
\see{830}.

\cd*\relax
\artist{Nyman, Michael}.
\cdtitle{Songs for Tony}.
\see{35}.

\cd*\relax
\artist{Nyman, Michael}.
\cdtitle{Songs for Tony}.
\see{1231}.

\cd\relax
\artist{Nyman, Michael}.
\cdtitle{The Piano Concerto \and On the Fiddle \and Prospero's Books}.
Peter Lawson (solo piano) and Jonathan Carney (solo violin).
Royal Philharmonic Orchestra.
Jonathan Carney, cond.
Platinum Entertainment, 1996 \cdnum{2860}.

\cd*\relax
\artist{Nyman, Michael}.
\cdtitle{Where the Bee Dances}.
\see{1053}.

\cd*\relax
\artist{Nyman, Michael}.
\cdtitle{Where the Bee Dances}.
\see{745}.

\cd\relax
\artist{Ochs, Phil}.
\cdtitle{A Toast to Those Who Are Gone}.
Rhino Records, 1989 \cdnum{R2 70080}.

\cd\relax
\artist{Ochs, Phil}.
\cdtitle{All the News That's Fit to Sing}.
Warner Brothers, 1987 \cdnum{HNCD 4427}.

\cd\relax
\artist{Ochs, Phil}.
\cdtitle{I Ain't Marching Any More}.
Warner Brothers, 1965/1986 \cdnum{HNCD 4422}.

\cd\relax
\artist{Ochs, Phil}.
\cdtitle{There but for Fortune}.
Elektra/Asylum Records, 1989 \cdnum{960832-2}.

\cd*\relax
\artist{O'Connor, Mark}.
\cdtitle{Appalachia Waltz}.
\see{1017}.

\cd\relax
\artist{O'Connor, Mark}.
\cdtitle{Midnight on the Water}.
Sony, 1998 \cdnum{SK 62862}.

\cd*\relax
\artist{Offenbach, Jacques}.
\cdtitle{Danse boh\'emienne, Op.~28}.
\see{902}.

\cd*\relax
\artist{Offenbach, Jacques}.
\cdtitle{Le Papillon}.
\see{1574}.

\cd\relax
\artist{Ogdon, John}.
\cdtitle{Alkan/Busoni/Rachmaninoff/Scriabin \: \track \C{Valentin Alkan}
  Concerto pour piano seul \from 12 \'Etudes dans les tons mineurs,
  Op.~39 \; \track \C{Ferruccio Busoni} Variations and Fugue on Prelude
  in C~minor by Fr\'ed\'eric Chopin \and Piano Concerto, Op.~39 \;
  \track \C{Sergei Rachmaninoff} Piano Sonata No.~2 in B~flat minor,
  Op.~36 \; \track \C{Alexander Scriabin} Piano Sonata No.~4 in F~sharp,
  Op.~30}.
Volume~72 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 913-2}.

\cd\relax
\artist{Ogdon, John}.
\cdtitle{Balakirev/Liszt/Rachmaninoff \: \track \C{Sergei Rachmaninoff}
  Prelude in C~sharp minor, Op.~3, No.~2 \and Prelude in G~minor,
  Op.~23, No.~5 \and Prelude in~G, Op.~32, No.~5 \and Prelude in G~sharp
  minor, Op.~32, No.~12 \and \'Etudes-Tableaux, Op.~33 \and
  \'Etudes-Tableaux, Op.~39 \; \track \C{Mili Balakirev} Islamey \;
  \track \C{Franz Liszt} ``Mephisto'' Waltz No.~1 \and R\'eminiscences
  de Don Juan \and Liebestraum No.~3 in A~flat \and La campanella
  \(\textup{with} \artist{Ferruccio Busoni}\) \and Les fun\'erailles
  \and R\'eminiscences de Simone Boccanegra \and Apr\`es une lecture du
  Dante \(Fantasia quasi Sonata\)}.
Volume~73 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 916-2}.

\cd\relax
\cdtitle{Once Upon a Time in China and America}.
BM-Star Music, 1997 \cdnum{7 4321 46413 2}.

\cd\relax
\cdtitle{Once Upon a Time in China: The Best of Chinese Film Music,
  Volume~One}.
Varese Sarabande Records, 1993 \cdnum{VSD-5455}.

\cd*\relax
\artist{Onna, Peter van}.
\cdtitle{The Gravity of~D}.
\see{51}.

\cd\relax
\artist{Orff, Carl}.
\cdtitle{Carmina Burana}.
Janice Harsanyi (soprano), Rudolf Petrak (tenor) and Harve Presnell
  (baritone).
The Philadelphia Orchestra.
Eugene Ormandy, cond.
Sony, 1991 \cdnum{SBK 47668}.

\cd\relax
\artist{Orff, Carl}.
\cdtitle{Catulli Carmina}.
Thomas Dewald (tenor) and Lisa Griffith (soprano).
Members of the Royal Flemish Philharmonia, Antwerpen.
Wolfgang Sch\"afer, cond.
Intuition Classics, 1996 \cdnum{INT 3169~2}.

\cd\relax
\artist{O'Sullivan, Jerry}.
\cdtitle{The Invasion}.
Green Linnet, 1987 \cdnum{GLCD~1074}.

\cd*\relax
\artist{Ott, David}.
\cdtitle{Three Moods \(1998\)}.
\see{1146}.

\cd*\relax
\artist{Ozi, Etienne}.
\cdtitle{Sonata No.~1 for Two Bassoons}.
\see{1164}.

\cd\relax
\artist{Pachelbel, Johann}.
\cdtitle{Pachelbel Canon \(original version\) and other 17th century
  music for three violins \: \track \C{Henry Purcell} Three Parts Upon a
  Ground \; \track \C{Giovanni Battista Buonamente} Sonata a tre violini
  from \emph{Book~6} \; \track \C{Giovanni Gabrieli} Sonata~XXI con tre
  violini \; \track \C{Biagio Marini} Sonata in Ecco con tre violini
  from \emph{Opus~8} \and Sonata Terza par tre violini from
  \emph{Opus~22} \; \track \C{Marco Uccellini} Sinfonia Nona a tre
  violini from \emph{Opus~9} \; \track \C{Giovanni Battista Fontana}
  Sonata No.~16 a tre violini \; \track \C{Louis Constantin} ``Pavan''
  from \emph{'t Uitnemend Kabinet} \; \track \C{Johann Heinrich
  Schmelzer} Sonata a tre violini \; \track \C{Carolus Hacquart} Sonata
  Decima from \emph{Harmonia Parnassia} \; \track \C{Carl Rosier} Suite
  f\"ur drei Violinen from \emph{Antwerpsche Vrede-Vreught} \; \track
  \C{Johann Pachelbel} Canon ``a 3 Violinis con suo Basso'' \and Gigue
  ``a 3 Violinis con suo Basso''}.
John Holloway (violin), Stanley Ritchie (violin), Andrew Manze (violin),
  John Toll (harpsichord and organ), Nigel North (theorbo) and Mary
  Springfels (viola da gamba).
Harmonia Mundi, 1998 \cdnum{HMT 7907091}.

\cd\relax
\artist{Pachelbel, Johann}.
\cdtitle{Pachelbel's Greatest Hit: Canon in~D}.
BMG Music, 1991 \cdnum{60712-2-RG}.

\cd\relax
\artist{Pachelbel, Johann}.
\cdtitle{The Ultimate Canon: Pachelbel's Greatest Hit}.
RCA Victor, 2003 \cdnum{82876-55307-2}.

\cd*\relax
\artist{Padding, Martijn}.
\cdtitle{Ritorno}.
\see{51}.

\cd*\relax
\artist{Paderewski, Ignacy Jan}.
\cdtitle{Menuet c\'el\`ebre in~G, Op.~14 No.~1}.
\see{1187}.

\cd*\relax
\artist{Paderewski, Ignacy Jan}.
\cdtitle{Minuet c\'el\`ebre in~G, Op.~14 No.~1}.
\see{775}.

\cd\relax
\artist{Paderweski, Ignacy Jan}.
\cdtitle{Chopin/Liszt/Schubert/Paderewski \: \track \C{Fr\'ed\'eric
  Chopin} Etude in C~minor, Op.~10 No.~12 ``Revolutionary'' \and Etude
  in~E, Op.~10 No.~3 ``Tristesse'' \and Etude in G~flat, Op.~10 No.~5
  ``Black Keys'' \and Etude in~C, Op.~10 No.~7 \and Nocturne in~F,
  Op.~15 No.~1 \and Nocturne in F~sharp, Op.~15 No.~2 \and Nocturne in
  E~flat, Op.!9 No.~2 \and Waltz in E~flat, Op.~18 ``Grande valse
  brillante'' \and Mazurka in A~minor, Op.~17 No.~4 \and Etude in
  A~flat, Op.~25 No.~1 ``Aeolian Harp'' \and Etude in F~minor, Op.~25
  No.~2 \and Etude in G~sharp minor, Op.~24 No.~6 \and Etude in C~sharp
  minor, Op.~25 No.~7 \and Etude in G~flat, Op.~25 No.~9 ``Butterfly''
  \and Etude in A~minor, Op.~25 No.~11 ``Winter Wind'' \and Polonaise in
  E~flat minor, Op.~26 No.~2 \and Prelude in D~flat, Op.~28 No.~15
  ``Raindrop'' \and Prelude in A~flat, Op.~28 No.~17 \and Mazurka in~D,
  Op.~33 No.~2 \and Waltz in A~flat, Op.~34 No.~1 ``Valse brillante''
  \and Marche fun\`ebre from Piano Sonata No.~2 in B~flat minor, Op.~35
  \and Polonaise in~A, Op.~40 No.~1 ``Military'' \and Waltz in A~flat,
  Op.~42 ``Grande valse'' \and Berceuse in D~flat, Op.~57 \and Mazurka
  in A~flat, Op.~59 No.~2 \and Mazurka in F~sharp minor, Op.~59 No.~3
  \and Mazurka in C~sharp minor, Op.~63 No.~3 \and \; \track \C{Franz
  Liszt} Chants polonais de Fr\'ed\'eric Chopin, S.~480 \and 3 Etudes de
  Concert, No.~2 in F~minor ``La leggierezza'' \and 6 Etudes
  d'ex\'ecution transcedante d'apr\`es Paganini, No.~3 La Campanella
  \and Hungarian Rhapsody No.~2 in C~sharp minor \and Hungarian Rhapsody
  No.~10 in~E, ``Preludio'' \and Spinning Song \(transcription from
  Richard Wagner's ``The Flying Dutchman''\) \; \track \C{Franz
  Schubert} Impromptu in A~flat, D.~935 No.~2 \and Impromptu in B~flat,
  D.~935 No.~3 \; \track \C{Ignacy Jan Paderewski} Menuet c\'el\`ebre
  in~G, Op.~14 No.~1}.
Volume~74 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 919-2}.

\cd\relax
\artist{Paganini, Niccol\`o}.
\cdtitle{24 Caprices, Op.~1 for solo violin}.
Itzhak Perlman.
EMI Records, 1986 \cdnum{CDC~7 47171~2}.

\cd*\relax
\artist{Paganini, Niccolo}.
\cdtitle{Bravourvariationen \"uber ein Thema aus der Oper ``Moses in
  \"Agypten'' von Rossini}.
\see{880}.

\cd*\relax
\artist{Paganini, Nicol\`o}.
\cdtitle{Grande \'etude d'apr\`es Paganini No.~5 ``La Chasse''
  \arr{Franz Liszt}}.
\see{645}.

\cd\relax
\artist{Palestrina}.
\cdtitle{Palestrina Masses: Missa Asumpta est Maria \and Missa Sicut
  lilium}.
The Tallis Scholars.
Peter Phillips, cond.
Gimell, 1989 \cdnum{454 920-2}.

\cd\relax
\artist{Palestrina, Giovanni Pierluigi}.
\cdtitle{Christmas Mass in Rome \: Missa ``Hodie Christus Natus Est''
  \and Three Christmas Masses}.
Paul McCreesh.
Gabrieli Consrt and Players, cond.
Deutsche Grammophon, 1993 \cdnum{437 833-2}.

\cd*\relax
\artist{Palider, Alan}.
\cdtitle{The Narwhal, op.~11}.
\see{1163}.

\cd*\relax
\artist{Pandolfi, Giovanni Antonio}.
\cdtitle{Sonata ``La Monella Romanesca'', Op.~IV, No.~3}.
\see{1308}.

\cd\relax
\artist{Pandolfi Mealli, Giovanni Antonio}.
\cdtitle{Complete Violin Sonatas}.
Andrew Manze (violin) and Richard Egarr (harpsichord).
Harmonia Mundi, 1999 \cdnum{HMU 907241}.

\cd*\relax
\artist{Pape, Andy}.
\cdtitle{Siciliano Sconfortevole}.
\see{1700}.

\cd\relax
\artist{Parker, Charlie}.
\cdtitle{The Best of Charlie Parker}.
Universal Music, 2004 \cdnum{B0002990-02}.

\cd*\relax
\artist{Parker, Horatio William}.
\cdtitle{Valse gracile}.
\see{775}.

\cd*\relax
\artist{Pasculli, Antonino}.
\cdtitle{Le Api}.
\see{1604}.

\cd\relax
\artist{Pasculli, Antonio}.
\cdtitle{Character Pieces and Fantasias \: \track Fantasia Sull' opera
  \emph{Poliuto} di G. Donizetti \; \track Le Api \; \track Gran
  Concerto su temi dall'opera \emph{I vespri siciliani} di Verdi \;
  \track Ommaggio a Bellini \; \track Concerto sopra motivi dell'opera
  \emph{La Favorita} di Donizetti \; \track Ricordo di napoli}.
Yeon-Hee Kwak (oboe), Chia Chou (piano) and Ursula Eisert (harp).
MDG, 2000 \cdnum{MDG 603 0942-2}.

\cd\relax
\artist{Pasculli, Antonio}.
\cdtitle{The Paganini of the Oboe \: \track Characteristic Study---Le
  Api \; \track Grand Concerto on themes from \emph{I vespri siciliani}
  by Verdi \; \track Fantasia on themes from \emph{Les Huguenots} by
  Meyerbeer \; \track Concerto on themes from \emph{La Favorita} by
  Donizetti \; \track Concerto on themes from \emph{Poliuto} by
  Donizetti}.
Christopher Redgate.
Oboe Classics, 2003 \cdnum{CC2006}.

\cd*\relax
\artist{Patch, Marc}.
\cdtitle{Magic Spell}.
\see{631}.

\cd\relax
\artist{Patrick Street}.
\cdtitle{Cornerboys}.
Green Linnet, 1996 \cdnum{GLCD~1160}.

\cd*\relax
\artist{Peck, Russel}.
\cdtitle{The Upward Stream}.
\see{799}.

\cd*\relax
\artist{Pe\~na, Angel}.
\cdtitle{Un petit recueil for Three Double Basses}.
\see{619}.

\cd*\relax
\artist{Penderecki, K.}
\cdtitle{Capriccio for Oboe and 11 Strings \(1965\)}.
\see{784}.

\cd\relax
\artist{Perahia, Murray}.
\cdtitle{Beethoven/Grieg/Mozart/Mendelssohn/Scarlatti \: \track
  \C{B\'ela Bart\'ok} Improvisations on Hungarian Peasant Songs, Op.~20
  \; \track \C{Ludwig van Beethoven} Variations in C~minor, WoO~80 \;
  \track \C{Johannes Brahms} Rhapsody in B~minor, Op.~79 No.~1 \; \track
  \C{Fr\'ed\'eric Chopin} Ballade No.~1 in G~minor, Op.~23 \; \track
  \C{Edvard Grieg} Piano Concerto in A~minor, Op.~16 \; \track \C{Franz
  Liszt} Consolation No.~3 in D~flat \; \track \C{Mendelssohn Bartholdy,
  Felix} Variations s\'erieuses, Op.~54 \; \track \C{Wolfgang Amadeus
  Mozart} Piano Concerto No.~25 in~C, KV~503 \; \track \C{Domenico
  Scarlatti} Sonata in B~minor, K.~27 \and Sonata in~A, K.~212 \; \track
  \C{Franz Schubert} Impromptu in B~flat, D.~935 No.~3}.
Volume~75 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 922-2}.

\cd\relax
\artist{Perahia, Murray}.
\cdtitle{\track \C{George Frideric Handel} Suite No.~5 in E~Major,
  HWV~430 \and Chaconne in G~Major, HWV~435 \and Suite No.~3 in D~Minor,
  HWV~428 \and Suite No.~2 in F~Major, HWV~427 \; \track \C{Domenico
  Scarlatti} Sonata in D~Major, K.~491 \and Sonata in B~Minor, K.~27
  \and Sonata in C-sharp Minor, K.~247 \and Sonata in D~Major, K.~29
  \and Sonata in A~Major, K.~537 \and Sonata in E~Major, K.~206 \and
  Sonata in A~Major, K.~212}.
Sony Classical, 1997 \cdnum{SK~62785}.

\cd\relax
\artist{Persuasions, The}.
\cdtitle{Sincerely}.
Rounder Records, 1996 \cdnum{Bullseye Blues CD BB~9576}.

\cd\relax
\artist{Persuasions, The}.
\cdtitle{We Came to Play}.
Collectables Records, 1991 \cdnum{COL-CD-5234}.

\cd\relax
\artist{Peterson-Berger, Wilhelm}.
\cdtitle{Fr\"os\"oblomster, Op.~16 \(Books~1--3\)}.
Niklas Sivel\"ov.
Naxos, 1999 \cdnum{8.554343}.

\cd*\relax
\artist{Phillips, Burrill}.
\cdtitle{Concert Piece}.
\see{1162}.

\cd*\relax
\artist{Piazzolla, Astor}.
\cdtitle{Le Grand Tango}.
\see{1315}.

\cd*\relax
\artist{Piazzolla, Astor}.
\cdtitle{Oblivion \and Chiquilin de Bach{\'\i}n}.
\see{1344}.

\cd*\relax
\artist{Piazzolla, Astor}.
\cdtitle{Oblivion \and Fugata \and Libertango}.
\see{830}.

\cd*\relax
\artist{Piazzolla, Astor}.
\cdtitle{Prelude \(for Kenneth Tse\)}.
\see{1604}.

\cd*\relax
\artist{Piccinini, Alessandro}.
\cdtitle{Romanesca con partite variate \from ``Intavolatura di liuto,''
  Lib.~I}.
\see{1308}.

\cd*\relax
\artist{Pickett, Lenny}.
\cdtitle{Saxophone Quartet No.~2 \(1995\)}.
\see{1146}.

\cd*\relax
\artist{Piern\'e, Gabriel}.
\cdtitle{Three Pieces}.
\see{830}.

\cd*\relax
\artist{Pillin, Boris}.
\cdtitle{Scherzo}.
\see{1687}.

\cd\relax
\artist{Pires, Maria Jo\~ao}.
\cdtitle{Bach/Chopin/Mozart/Schubert/Schumann \: \track \C{Johann
  Sebastian Bach} French Suite No.~2 in C~minor, BWV~813 \; \track
  \C{Robert Schumann} Arabeske \; \track \C{Franz Schubert} Moment
  musical in A~flat, D.~780, No.~6 \; \track \C{Fr\'ed\'eric Chopin}
  Nocturne in C~minor, Op.~48, No.~1 \and Nocturne in F~sharp minor,
  Op.~48, No.~2 \and Nocturne in~E, Op.~62, No.~2 \; \track \C{Wolfgang
  Amadeus Mozart} Piano Concerto No.~14 in E~flat, KV~449 \and Piano
  Sonata in~C, KV~545 ``For Beginners'' \and Piano Sonata in E~flat,
  KV~282 \and Piano Sonata in B~flat, KV~333 \and Piano Sonata in~A,
  KV~331}.
Volume~76 of \emph{Great Pianists of the 20th Century}.
Wiener Philharmoniker.
Claudio Abbado, cond.
Philips Classics, 1999 \cdnum[2]{456 928-2}.

\cd*\relax
\artist{Platti, Giovanni}.
\cdtitle{Sonata in G~major}.
\see{505}.

\cd\relax
\artist{Plethyn}.
\cdtitle{Seidir Ddoe}.
SAIN, 1994 \cdnum{SCD 2083}.

\cd\relax
\artist{Pletnev, Mikhail}.
\cdtitle{Tchaikovsky \: \C{Peter Ilyich Tchaikovsky} Concert Suite from
  ``The Nutcracker'' \(arr.~Pletnev\) \and Romance in F~minor, Op.~5
  \and Valse-Scherzo in~A, Op.~7 \and Capriccio in G~flat, Op.~8 \and
  Les saisons, Op.~37b \(The Months\) \and Music from ``The Sleeping
  Beauty'' \and Piano Concerto No.~2 in~G, Op.~44}.
Volume~77 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 931-2}.

\cd*\relax
\artist{Pokorny, Franz Xavier}.
\cdtitle{Quintet No.~4 for Guitar and Strings in D~Major, G.~448
  ``Fandango'' \and Symphony No.~3 in C~Major, Op.~12}.
\see{1619}.

\cd\relax
\artist{Police, The}.
\cdtitle{Reggatta de Blanc}.
A\&M Records, 1979 \cdnum{CD-3312}.

\cd\relax
\artist{Police, The}.
\cdtitle{Synchronicity}.
A\&M Records, 1983 \cdnum{CD-3735}.

\cd\relax
\artist{Pollini, Maurizio}.
\cdtitle{Chopin \: \track Piano Concerto No.~1 in E~minor, Op.~11 \;
  \track Piano Concerto No.~2 in B~flat minor, Op.~35 \; \track Nocturne
  in~F, Op.~15 No.~1 \; \track Nocturne in F~sharp, Op.~15 No.~2 \;
  \track Nocturne in C~sharp minor, Op.~27 No.~1 \; \track Nocturne in
  D~flat, Op.~27 No.~2 \; \track Polonaise in F~sharp minor, Op.~44 \;
  \track Polonaise in A~flat, Op.~53 ``Heroic'' \; \track
  Polonaise-Fantaisie in A~flat, Op.~61 \; \track Etudes, Op.~10 \;
  \track Berceuse in D~flat, Op.~57 \; \track Barcarolle in F~sharp,
  Op.~60}.
Volume~79 of \emph{Great Pianists of the 20th Century}.
Philharmonia Orchestra.
Paul Kletzki, cond.
Philips Classics, 1999 \cdnum[2]{456 940-2}.

\cd\relax
\artist{Pollini, Maurizio}.
\cdtitle{Chopin/Debussy/Liszt/Schumann/Stravinsky \: \track \C{Robert
  Schumann} Piano Sonata No.~1 in F~sharp minor, Op.~111 \and Arabeske
  in~C, Op.~18 \; \track \C{Franz Liszt} Piano Sonata in B~minor, S.~178
  \; \track \C{Fr\'ed\'eric Chopin} Scherzo No.~ in B~minor, Op.~20 \;
  \track \C{Franz Schubert} Drei Klavierst\"ucke, D.~946 \; \track
  \C{Anton Webern} Piano Variations, Op.~27 \; \track \C{Claude Debussy}
  Douz Etudes pour le piano \(Excerpts\) \; \track \C{Igor Stravinsky}
  Petrouchka \(Three movements\)}.
Volume~78 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 937-2}.

\cd*\relax
\artist{P\"ontinen, Roland}.
\cdtitle{Bl\'a Vinter}.
\see{965}.

\cd*\relax
\artist{Popper, David}.
\cdtitle{Dance of the Elves, Op.~39}.
\see{1315}.

\cd*\relax
\artist{Popper, David}.
\cdtitle{Elfentanz, Op.~39}.
\see{1156}.

\cd*\relax
\artist{Popper, David}.
\cdtitle{Fantasy on Little Russian Songs \and Serenade, Op.~54, No.~2}.
\see{902}.

\cd\relax
\artist{Porter, Cole}.
\cdtitle{De-Lovely}.
Sony Music, 2004 \cdnum{CK 90640}.

\cd\relax
\artist{Porter, Cole}.
\cdtitle{The Cole Porter Songbook, Volume~1}.
Ella Fitzgerald.
PolyGram Records, 1984 \cdnum{821-989-2}.

\cd\relax
\artist{Porter, Cole}.
\cdtitle{The Cole Porter Songbook, Volume~2}.
Ella Fitzgerald.
PolyGram Records, 1984 \cdnum{821-990-2}.

\cd*\relax
\artist{Porter, Quincy}.
\cdtitle{Speed Etude \(1948\)}.
\see{177}.

\cd*\relax
\artist{Poulenc, Francis}.
\cdtitle{Chanson d'Orkenise \and H\^otel \and Le Carafon \and ``C'' \and
  F\^etes galantes}.
\see{461}.

\cd*\relax
\artist{Poulenc, Francis}.
\cdtitle{Concerto for Two Pianos in D~minor \and Sonata for Two Pianos}.
\see{380}.

\cd*\relax
\artist{Poulenc, Francis}.
\cdtitle{Intermezzo in A~flat}.
\see{724}.

\cd*\relax
\artist{Poulenc, Francis}.
\cdtitle{Montparnasse \and Deux po\`emes de uillaume Apollinaire \and
  Deux po\`emes de Louis Aragon \and Tel jour telle nuit}.
\see{302}.

\cd*\relax
\artist{Poulenc, Francis}.
\cdtitle{Sonata}.
\see{439}.

\cd*\relax
\artist{Poulenc, Francis}.
\cdtitle{Sonata for Oboe and Piano}.
\see{1664}.

\cd*\relax
\artist{Poulenc, Francis}.
\cdtitle{Trois pi\`eces \and M\'elancolie \and Suite fran\c{c}aise
  d'apr\~es Claude Gervaise \and Presto in B~flat}.
\see{1217}.

\cd*\relax
\artist{Powell, roy}.
\cdtitle{Bow out}.
\see{35}.

\cd*\relax
\artist{Powning, Graham}.
\cdtitle{Sonata}.
\see{1161}.

\cd\relax
\artist{Preisner, Zbigniew}.
\cdtitle{10 Easy Pieces for Piano}.
Leszek Mo\.zd\.zer.
EMI Classics, 1999 \cdnum{7243 5~56971~@ 7}.

\cd\relax
\artist{Preisner, Zbigniew}.
\cdtitle{Olivier Olivier/Europa Europa}.
DRG Records, 1992 \cdnum{12606}.

\cd\relax
\artist{Preisner, Zbigniew}.
\cdtitle{Requiem for My Friend}.
El\.zbieta Towarnicka.
Sinfonia Varsovia and Varsov Chamber Choir.
Jacek Kaspszyk, cond.
Erato, 1998 \cdnum{3984-2146-2}.

\cd\relax
\artist{Preisner, Zbigniew}.
\cdtitle{Trois Couleurs: Bleu}.
Virgin Records America, 1993 \cdnum{7243 8 39027 2~9}.

\cd\relax
\artist{Preisner, Zbigniew}.
\cdtitle{Trois Couleurs: Red}.
Virgin Records America, 1994 \cdnum{7243 8 39860 2~6}.

\cd\relax
\artist{Preisner, Zbigniew}.
\cdtitle{Trois Couleurs: White}.
Virgin Records America, 1994 \cdnum{7243 8 39662 2~6}.

\cd\relax
\artist{Previn, Andr\'e}.
\cdtitle{Gershwin/Mozart/Poulenc/Shostakovich \: \track \C{George
  Gershwin} Piano Concerto in~F \and The Man I Love \and Embraceable You
  \and I Got Rhythm \and Soemone to Watch over Me \and Boy! What Love
  Has Done to Me!---I've Got a Crush on You \and S' Wonderful \and
  Rhapsody in Blue \; \track \C{Wolfgang Amadeus Mozart} Piano Concerto
  No.~17 in~G, KV~453 \; \track \C{Francis Poulenc} Trois pi\`eces \and
  M\'elancolie \and Suite fran\c{c}aise d'apr\~es Claude Gervaise \and
  Presto in B~flat \; \track \C{Dmitri Shostakovich} Concerto in C~minor
  for Piano, Trumpet and Strings, Op.~35 \(Piano Concerto No.~1\)}.
Volume~80 of \emph{Great Pianists of the 20th Century}.
David Finck (double bass).
Philips Classics, 1998 \cdnum[2]{456 934-2}.

\cd\relax
\artist{Prine, John}.
\cdtitle{Aimless Love}.
Oh Boy Records, 1984/1989 \cdnum{OBR~002CD}.

\cd\relax
\artist{Prine, John}.
\cdtitle{Sweet Revenge}.
Atlantic, 1973 \cdnum{7274-2}.

\cd\relax
\artist{Procol Harum}.
\cdtitle{Procol Harum/Shine on Brightly}.
BGO Records, 2002 \cdnum[2]{BGOCD556}.

\cd\relax
\artist{Procol Harum}.
\cdtitle{The Best of Procol Harum}.
A\&M Records, 1972 \cdnum{CD 3259}.

\cd\relax
\artist{Prokofiev, Serge}.
\cdtitle{Favourite Orchestral Suites \: \track The Love for Three
  Oranges, Op.~33 bis \; \track Romeo and Juliet, Op.~64 \(excerpts\) \;
  \track Symphony No.~1 in~D, Op.~25 \(``Classical''\) \; \track
  Lieutenant Kij\'e, Op.~60 \; \track Peter and the Wolf, Op.~67 \;
  \track Ala and Lolly, Scythian Suite, Op.~20}.
Philips Classics, 1994 \cdnum[2]{442 278-2}.

\cd*\relax
\artist{Prokofiev, Serge}.
\cdtitle{Konzert f\"ur Klavier und Orchester Nr.~3 C-dur op.~26}.
\see{40}.

\cd*\relax
\artist{Prokofiev, Serge}.
\cdtitle{Piano Concerto No.~1 in D~flat, Op.~10 \and 10 Pieces for piano
  from ``Romeo and Juliet'', Op.~75}.
\see{632}.

\cd*\relax
\artist{Prokofiev, Serge}.
\cdtitle{Piano Concerto No.~3 in~C, Op.~25}.
\see{877}.

\cd*\relax
\artist{Prokofiev, Serge}.
\cdtitle{Piano Sonata No.~3 in A~minor, Op.~28}.
\see{645}.

\cd*\relax
\artist{Prokofiev, Serge}.
\cdtitle{Toccata, Op.~11}.
\see{617}.

\cd\relax
\artist{Prokofiev, Serge}.
\cdtitle{War and Peace}.
Orchestre National de France and Choeurs de Radio France.
Mstislav Rostropovitch, cond.
Erato, 1988 \cdnum[4]{2292-45331-2}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Adagio \from Cinderella \and Waltz-Coda \from Cinderella \and
  March \from The Love for Three Oranges \and Cello Sonata, Op.~119 \and
  Symphony-Concerto for cello and orchestra, Op.~125 \and Cello
  Concertino, Op.~132}.
\see{1315}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Piana Sonata No.~8 in B~flat, Op.~84 \and Visions fugitives,
  Op.~22 \(Excerpts\) \and Sonata No.~3 in A~minor, Op.~28 \and March
  from ``The Love for Three Oranges'', Op.~33ter}.
\see{644}.

\cd\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Piano Concerto No.~1 in D~flat, Op.~10 \and Piano Concerto
  No.~3 in~C, Op.~26 \and \C{B\'ela Bart\'ok} Piano Concerto No.~3,
  Sz.~119}.
Martha Argerich.
Orchestre Symphonique de Montr\'eal.
Charles Dutoit, cond.
EMI Classics, 1998 \cdnum{7243 5~56654~2 3}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Piano Concerto No.~3 in~C, Op.~26}.
\see{38}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Piano Concerto No.~3 in~C, Op.~26 \and Toccata, Op.~11}.
\see{845}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Piano Concerto No.~3, Op.~26}.
\see{883}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Piano Sonata No.~3 in A~minor, Op.~28 \and Suggestion
  diabolique \(from 4~Pieces, Op.~4\)}.
\see{1683}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Piano Sonata No.~6 in~A, Op.~82 \and Overture on Hebrew Themes,
  Op.~34 \and Visions fugitives, Op.~22, Nos.~10, 11, 16, and~17 \and
  Piano Concerto No.~3 in~C, Op.~26 \and Etude in C~minor, Op.~2,
  No.~3}.
\see{900}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Piano Sonata No.~6 in~A, Op.~82 \and Piano Sonata No.~7
  in~B~flat, Op.~83 \and Piano Sonata No.~8 in~B~flat, Op.~84}.
\see{1270}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Piano Sonata No.~7 in B~flat, Op.~83}.
\see{797}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Piano Sonata No.~7, Op.~83}.
\see{658}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{``Romeo and Juliet before parting''}.
\see{48}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Suggestion diabolique, Op.~4 No.~4}.
\see{1076}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Violin Concerto No.~1 in D~major, op.~19 \and Violin Concerto
  No.~2 in G~minor, op.~63}.
\see{433}.

\cd*\relax
\artist{Prokofiev, Sergei}.
\cdtitle{Visions Fugitives, Op.~22}.
\see{505}.

\cd*\relax
\artist{Puccini, Giacomo}.
\cdtitle{Crisantemi}.
\see{721}.

\cd\relax
\artist{Puccini, Giacomo}.
\cdtitle{La Boh\`eme}.
Angela Gheorghiu, Roberto Alagna, Elisabetta Scano, Simon Keenlyside,
  Roberto de Candia and Ildebrando D'Arcangelo.
Orchestra e coro del Teatro alla Scala di Milano.
Chailly, Riccardo, cond.
Decca, 1999 \cdnum{289 466 070-2}.

\cd\relax
\artist{Puccini, Giacomo}.
\cdtitle{Madama Butterfly}.
Renata Scotto, Anna di Stasio, Carlo Bergonzi, Rolando Panerai and Piero
  de Palma.
Coro e Orchestra del Teatro dell'Opera di Roma.
Sir John Barbirolli, cond.
EMI Classics, 1967/2002 \cdnum[2]{7243 5 67888 2 4}.

\cd\relax
\artist{Puccini, Giacomo}.
\cdtitle{Turandot at the Forbidden City of Beijing}.
Giovanna Casolla, Sergej Larin and Barbara Frittoli.
Orchestra and Chorus of Maggio Musicale Fiorentino Coro di Voci Bianche.
Zubin Mehta, cond.
RCA Victor, 1998 \cdnum[2]{74321-60617-2}.

\cd\relax
\artist{Purcell, Henry}.
\cdtitle{Dido and Aeneas}.
Janet Baker, Patricia Clark, Monica Sinclair and Raimund Herincx.
The St. Anthony Singers and the English Chamber Orchestra.
Anthony Lewis, cond.
The Decca Record Company, 1962/1990 \cdnum{425 720-2}.

\cd\relax
\artist{Purcell, Henry}.
\cdtitle{Dido and Aeneas}.
Susan Graham (mezzo-soprano), Ian Bostridge (tenor), Camilla Tilling
  (soprano), C\'ecile de Boever (soprano), Felicity Palmer (contralto),
  David Daniels (countertenor), Paul Agnew (tenor) and European Voices.
Le Concert d'Astr\'ee.
Emmanuelle Ha\"im, cond.
Veritas/EMI, 2003 \cdnum{7243 5 45605 2~1}.

\cd\relax
\artist{Purcell, Henry}.
\cdtitle{Dioclesian \and Timon of Athens}.
Nancy Argenta, Ann Monoyios, Paul Agnew, Richard Edgar-Wilson, Stephen
  Gadd, Simon Birchall, Lawrence Wallington, Brian Bannatyne-Scott and
  Christopher Foster.
The English Concert and Choir.
Trevor Pinnock, cond.
Deutsche Grammophon, 1995 \cdnum[2]{447 071-2}.

\cd*\relax
\artist{Purcell, Henry}.
\cdtitle{Three Parts Upon a Ground}.
\see{1184}.

\cd\relax
\artist{Quartz Saxophone Quartet}.
\cdtitle{Faces \: \track \C{Michael Nyman} Songs for Tony \; \track
  \C{Gary Carpenter} Une Semaine de Bont\'e \; \track \C{Johann
  Sebastian Bach} Contrapunctus~III \; \track \C{Alexander Levine} Faces
  \; \track \C{Graham Fitkin} Stub \; \track \C{John Buckley} Saxophone
  Quartet}.
Black Box Music \cdnum{BBM1024}.

\cd\relax
\artist{Quintessence Saxophone Quintet}.
\cdtitle{Jazzentials of Bach}.
CPO, 1998 \cdnum{999 587-2}.

\cd*\relax
\artist{Rachmaninoff, Serge}.
\cdtitle{Variations on a theme by Corelli, Op.~42}.
\see{48}.

\cd\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Beethoven/Chopin/Rachmaninoff/Schumann \: \track \C{Johann
  Sebastian Bach} Preludio, Gavotte and Gigue from Violin Partita No.~3
  in~E, BWV~1006 \; \track \C{Ludwig van Beethoven} Variations in
  C~minor, WoO~80 \(Excerpts\) \; \track \C{Fr\'ed\'eric Chopin} Ballade
  No.~3 in A~flat, Op.~47 \and Scherzo No.~3 in C~sharp minor, Op.~39
  Waltz No.~7 in C~sharp minor, Op.~64 No.~2 Waltz No.~8 in A~flat,
  Op.~64 No.~3 Piano Sonata No.~2 in B~flat minor, Op.~35 ``Funeral
  March'' \; \track \C{Fritz Kreisler} Liebesleid \and Liebesfreud \;
  \track \C{Franz Liszt and Fr\'ed\'eric Chopin} Chants polonais de
  Fr\'ed\'eric Chopin, S.~480 \; \track \C{Felix Mendelssohn} Scherzo
  from ``A Midsummer Night's Dream'' \; \track \C{Sergei Rachmaninoff}
  Polka de~V.R. \and Prelude in C~sharp minor, Op.~3 No.~2 \and Melody
  in~E, Op.~3 No.~3 \and Humoresque in~G, Op.~10, No.~5 \and Moment
  musical in E~flat minor, Op.~16 No.~2 \and Prelude in G~flat, Op.~23
  No.~10 \and Prelude in~E, Op.~32 No.~3 \and Prelude in F~minor, Op.~32
  No.~6 \and Prelude in~F, Op.~33 No.~2 \and Etude-Tableau in~C, Op.~33
  No.~2 \and Etude-Tableau in E~flat, Op.~33 No.~7 \and Daisies, Op.~38
  No.~3 \and Oriental Sketch \; \track \C{Nikolai Rimsky-Korsakov}
  Flight of the Bumble-Bee \; \track \C{Robert Schumann} Carnaval, Op.~9
  \; \track \C{Johann Strauss} Man lebt nur einmal \(Valse caprice,
  Op.~167 No.~2\) \; \track \C{Peter Ilyich Tchaikovsky} Novembre:
  Tro{\"\i}ka \(from ``Les saisons,'' Op.~37b\)}.
Volume~81 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 943-2}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Moment musical in B~minor, Op.~16, No.~3 \and Moment musical in
  E~minor, Op.~16, No.~4 \and Moment musical in D~flat, Op.~16, No.~5
  \and Moment musical in~C, Op.~16, No.~6}.
\see{632}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Piano Concerto No.~1 in F~sharp minor, Op.~1 \and Piano
  Concerto No.~2 in C~minor, Op.~18}.
\see{845}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Piano Concerto No.~2 in C~minor, Op.~18 \and Preludes, Op.~32,
  Nos.~1--2 \and Preludes, Op.~23, Nos.~2, 4, 5,~7}.
\see{1271}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Piano Concerto No.~2 in C~minor, Op.~18 \and Rhapsody on a
  Theme by Paganini, Op.~43}.
\see{877}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Piano Concerto No.~3 in D~minor, Op.~30}.
\see{38}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Piano Concerto No.~3 in D~minor, Op.~30}.
\see{796}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Piano Concerto No.~3 in D~minor, Op.~30 \and Piano Sonata No.~2
  in B~flat minor, Op.~36 \and Prelude in D, Op.~23 No.~4 \and Prelude
  in G~minor, Op.~23 No.~5 \and Prelude in E~flat, Op.~23 No.~6 \and
  Prelude in C~minor, Op.~23 No.~7 \and Etude-Tableau in E~flat minor,
  Op.~39 No.~5 \and Prelude in C~sharp minor, Op.~3 No.~2 \and Prelude
  in~G, Op.~32 No.~5 \and Prelude in G~sharp minor, Op.~32 No.~12}.
\see{435}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Piano Concerto No.~4 in G~minor, Op.~40 \and Prelude in C~sharp
  minor, Op.~3, No.~2 \and Vocalise, Op.~34, No.~14}.
\see{911}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Piano Sonata No.~2 in B~flat minor, Op.~36}.
\see{1177}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Piano Sonata No.~2 in B~flat minor, Op.~36}.
\see{797}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Prelude in B~minor, Op.~32 No.~10 \and Piano Sonata No.~1 in
  D~minor, Op.~28}.
\see{1683}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Prelude in C~sharp minor, Op.~3, No.~2 \and Prelude in G~minor,
  Op.~23, No.~5}.
\see{775}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Prelude in C~sharp minor, Op.~3, No.~2 \and Prelude in G~minor,
  Op.~23, No.~5 \and Prelude in~G, Op.~32, No.~5 \and Prelude in G~sharp
  minor, Op.~32, No.~12 \and \'Etudes-Tableaux, Op.~33 \and
  \'Etudes-Tableaux, Op.~39}.
\see{1178}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Prelude in G~sharp minor, Op.~32 No.~12}.
\see{1270}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Rhapsody on a theme by Paganini, Op.~43}.
\see{604}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Rhapsody on a Theme by Paganini, Op.~43}.
\see{883}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Scherzo from ``A Midsummer Night's Dream'' \and Moment musical
  in E~minor, Op.~16 No.~4 \and Prelude in~G, Op.~32 No.~5 \and Piano
  Concerto No.~2 in C~minor, Op.~18}.
\see{1076}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Suite No.~1 for Two Pianos in G~minor, Op.~5 \and Suite No.~2
  for Two Pianos, Op.~17}.
\see{380}.

\cd*\relax
\artist{Rachmaninoff, Sergei}.
\cdtitle{Variations on a Theme by Corelli, Op.~42}.
\see{1684}.

\cd\relax
\artist{Rachmaninov, Sergei}.
\cdtitle{\track Concerto for Piano and Orchestra No.~2 in C~minor,
  Op.~18 \; \track Rhapsody on a Theme of Paganini, Op.~43}.
Lang Lang.
Orchestra of the Mariinsky Theatre.
Valery Gergiev, cond.
Deutsche Grammophon, 2005 \cdnum{B0003902-02}.
Live recording.

\cd*\relax
\artist{Rachmaninov, Sergei}.
\cdtitle{Moment Musical in E~flat major, Op~16 No~2 \and Etude-Tableau
  in E~flat Op~33 No~4}.
\see{726}.

\cd\relax
\artist{Rachmaninov, Sergei}.
\cdtitle{Piano Concertos 1--4}.
Vladimir Ashkenazy.
The London Symphony Orchestra.
Andr\'e Previn, cond.
The Decca Record Company, 1995 \cdnum[2]{444 839-2}.

\cd*\relax
\artist{Rachmaninov, Sergei}.
\cdtitle{Romance \(Ne poi, Krasavitsa\), Op.~4 \and Vocalise, Op.~34,
  No.~14}.
\see{929}.

\cd\relax
\artist{Rachmaninov, Sergei}.
\cdtitle{Suite No.~1 for 2 pianos, op.~5 \and Suite No.~2 for 2 pianos,
  op.~17 \and \'Etudes tableaux, op.~33 \and Symphonic Dances, op.~45
  \and Russian Rhapsody \and Variations on a theme by Corelli, op.~42}.
Vladimir Ashkenazy and Andr\'e Previn.
The Decca Record Company, 1995 \cdnum[2]{444 845-2}.

\cd\relax
\artist{Rachmaninov, Sergei}.
\cdtitle{The Symphonies 1--3 \and The Bells \and Symphonic Dances \and
  The Isle of the Dead}.
The Concertgebouw Orchestra.
Vladimir Ashkenazy, cond.
The Decca Record Company, 1997 \cdnum[3]{455 798-2}.

\cd*\relax
\artist{Rachmaninov, Sergei}.
\cdtitle{Vocalise, Op. 34, no.~14}.
\see{504}.

\cd\relax
\artist{Rachmaninov, Sergej}.
\cdtitle{Evening and Morning Hymns of Praise: Russian Easter Vespers,
  Op.~37}.
Bulgarian National Choir ``Svetoslav Obretenov''.
Georgi Robev, cond.
Capriccio, 1996 \cdnum{10~524}.

\cd\relax
\artist{Rachmaninov, Sergey}.
\cdtitle{Complete Works for Cello and Piano \: \track Sonata in G~minor
  for Cello and Piano, Op.~19 \; \track Romance in F~Major, Op.~4, No.~3
  \; \track Lied in F~minor \; \track Melodie in D~Major \; \track
  Prelude in F~Major, Op.~2, No.~1 \; \track Vocalise in E~minor,
  Op.~34, No.~14 \; \track Danse Orientale in A~Major, Op.~2, No.~2}.
Michael Grebanier (cello) and Janet Guggenheim (piano).
Naxos, 1999 \cdnum{8.550987}.

\cd\relax
\artist{Rachmaninov, Sergey}.
\cdtitle{\track Piano Concerto No.~1 in F~shar minor, Op.~1 \; \track
  Piano Concerto No.~4 in G~minor, Op.~40 \; \track Rhapsody on a Theme
  of Paganini, Op.~43 \; \track Sergey Rachmaninov}.
The Philadelphia Orchestra.
Eugene Ormandy and Leopold Stokowski, cond.
Naxos, 1999 \cdnum{8.110602}.

\cd\relax
\artist{Rachmaninov, Sergey}.
\cdtitle{Vespers}.
The Saint Petersburg Cappella.
Vladislav Chernushenko, cond.
Harmonia Mundi, 1992/1997 \cdnum{RUS~788050}.

\cd*\relax
\artist{Rachmaninov, Sergey}.
\cdtitle{Vocalise, Op.~34, No.~14}.
\see{902}.

\cd\relax
\artist{Rachmaninov, Sergey Vasil'yevich}.
\cdtitle{Complete Songs, Volume~1}.
Joan Rodgers (soprano), Maria Popescu (mezzo-soprano), Alexandre
  Naoumenko (tenor), Sergei Leiferkus (bass) and Howard Shelley (piano).
Chandos Records, 1996 \cdnum{CHAN~9405}.

\cd\relax
\artist{Rachmaninov, Sergey Vasil'yevich}.
\cdtitle{Complete Songs, Volume~2}.
Joan Rodgers (soprano), Maria Popescu (mezzo-soprano), Alexandre
  Naoumenko (tenor), Sergei Leiferkus (bass) and Howard Shelley (piano).
Chandos Records, 1996 \cdnum{CHAN~9451}.

\cd\relax
\artist{Rachmaninov, Sergey Vasil'yevich}.
\cdtitle{Complete Songs, Volume~3}.
Joan Rodgers (soprano), Maria Popescu (mezzo-soprano), Alexandre
  Naoumenko (tenor), Sergei Leiferkus (bass) and Howard Shelley (piano).
Chandos Records, 1996 \cdnum{CHAN~9477}.

\cd\relax
\artist{Ragni, Gerome, James Rado and Galt MacDermot}.
\cdtitle{Hair---The Original Broadway Cast Recording}.
RCA Victor, 1988 \cdnum{1150-2-RC}.

\cd*\relax
\artist{Rameau, Jean-Philippe}.
\cdtitle{Gavotte \and Le rappel des oiseaux \and Les sauvages \and Les
  nials de Sologne}.
\see{407}.

\cd*\relax
\artist{Raphael, G\"unter}.
\cdtitle{R\'ecitatif pour Saxophone alto et piano}.
\see{253}.

\cd\relax
\artist{Rare Air}.
\cdtitle{Primeval}.
Green Linnet, 1989 \cdnum{GLCD 1104}.

\cd\relax
\artist{Rare Air}.
\cdtitle{Space Piper}.
Green Linnet, 1991 \cdnum{GLCD 1115}.

\cd\relax
\artist{Rasch\`er Saxophone Quartet}.
\cdtitle{From Equinox to Solstice \: \track \C{Anders Nilsson} Concerto
  grosso for saxophone quartet and orchestra \(1995\) \; \track \C{Ketil
  Hvoslef} Concerto for Saxophone Quartet and Orchestra \(1996\) \;
  \track \C{Jouni Kaipainen} Vernal Concerto ``From Equinox to
  Solstice'', Op.~53 \(1996\)}.
Swedish Chamber Orchestra.
Petter Sundkvist, cond.
BIS Records, 2003.

\cd*\relax
\artist{Raskatov, Alexander}.
\cdtitle{Pas de deux \(1994\)}.
\see{484}.

\cd*\relax
\artist{Rasmussen, Karl Aage}.
\cdtitle{Silhouette to a Poem by Naja Marie Aidt}.
\see{1700}.

\cd\relax
\artist{Rautavaara, Einojuhani}.
\cdtitle{\track Cantus Arcticus, Op.~61 \(Concerto for Birds and
  Orchestra\) \; \track Piano Concerto No.~1, Op.~45 \; \track Symphony
  No.~3, Op.~20}.
Laura Mikkola (piano).
Royal Scottish National Orchestra.
Hannu Lintu, cond.
Naxos, 1998 \cdnum{8.554147}.

\cd\relax
\artist{Rautavaara, Einojuhani}.
\cdtitle{Works for Piano \: \track Etudes, Op.~42 \; \track Icons, Op.~6
  \; \track Preludes, Op.~7 \; \track Partita, Op.~34 \; \track Piano
  Sonata No.~1, Op.~50 ``Christus und die Fischer'' \; \track Piano
  Sonata No.~2, Op.~64 ``The Fire Sermon''}.
Laura Mikkola.
Naxos, 1999 \cdnum{8.554292}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Alborada del gracioso \(\from Miroirs\)}.
\see{967}.

\cd\relax
\artist{Ravel, Maurice}.
\cdtitle{Complete Music for Piano Solo \and Complete Piano Concertos \:
  \track Piano Concerto in~G \; \track Gaspard de la nuit \; \track
  Menuet antique \; \track Menuet sur le nom de Haydn \; \track A la
  mani\`ere de\dots Borodine \; \track A la mani\`ere de\dots Chabrier
  \; \track Miroirs \; \track Piano Concerto in~D ``for the left hand''
  \; \track Le tombeau de Couperin \; \track Pr\'elude \; \track Jeux
  d'eau \; \track Sonatine \; \track Valses nobles et sentimentales \;
  \track Pavane pour une infante d\'efunte}.
Werner Haas.
Orchestre National de L'Op\'era de Monte-Carlo.
Alceo Galliera, cond.
Philips Classics, 1993 \cdnum[2]{438 353-2}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{F\^etes \(for two pianos\)}.
\see{952}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Five-o'clock Foxtrot \and Pi\`ece en forme de Habanera}.
\see{252}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Gaspard de la nuit}.
\see{48}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Gaspard de la nuit}.
\see{638}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Gaspard de la nuit \and Piano Concerto in~G}.
\see{1067}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Habanera}.
\see{902}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Jeux d'eau}.
\see{449}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Jeux d'eau \and Toccata \(from ``Le tombeau de Couperin''\)
  \and Alborada del gracioso \(from ``Miroirs''\)}.
\see{642}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Konzert f\"ur Klavier unde Orchester G-dur \and Gaspard de la
  nuit}.
\see{40}.

\cd\relax
\artist{Ravel, Maurice}.
\cdtitle{Orchestral Works \: \track Bol\'ero \; \track Alborada del
  gracioso \; \track Rapsodie espagnole \; \track La Valse \; \track Ma
  M\`ere l'Oye \; \track Pavane pour une infante d\'efunte \; \track Le
  Tombeau de Couperin \; \track Valses nobles et sentimentales \; \track
  Piano Concerot in G~major \; \track Menuet antique \; \track Piano
  Concerto for the left hand \; \track Une barque sur l'oc\'ean \;
  \track Fanfare from L'Eventail de Jeanne \; \track Daphnis et
  Chlo\'e}.
The Orchestre symphonique de Montr\'eal.
Charles Dutoit, cond.
The Decca Record Company, 1988 \cdnum[4]{421 458-2}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Piano Concerto in~D ``for the left hand''}.
\see{407}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Piano Concerto in~D ``for the left Hand'' \and Piano Concerto
  in~G}.
\see{883}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Piano Concerto in~G \and Sonatine \and Gaspard de la nuit}.
\see{38}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Pi\`ece en forme de Habanera}.
\see{505}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Scarbo \(\from ``Gaspard de la nuit''\)}.
\see{617}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Sh\'eh\'erazade}.
\see{461}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Sonatine}.
\see{448}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Sonatine}.
\see{1092}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Sonatine \and Alborado del gracioso \(No.~4 from ``Miroirs''\)
  \and Piano Concerto in~D ``for the left hand''}.
\see{604}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Sonatine \and Valses nobles et sentimentales \and Gaspard de la
  nuit}.
\see{717}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{String Quartet in F~major}.
\see{576}.

\cd\relax
\artist{Ravel, Maurice}.
\cdtitle{The Ultimate Bolero: Ravel's Greatest Hit}.
RCA Victor \cdnum{82876-61386-2}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Trio for piano, violin and cello}.
\see{244}.

\cd*\relax
\artist{Ravel, Maurice}.
\cdtitle{Tzigane}.
\see{247}.

\cd\relax
\artist{Rawsthorne, Alan}.
\cdtitle{Chamber Music \: \track Quintet for Piano and Strings \; \track
  Concertante for Violin and Piano \; \track Trio for Piano, Violin and
  Cello \; \track Sonata for Viola and Piano \; \track Sonata for Cello
  and Piano}.
Nadia Myerscough, Peter Adams, Yoshiko Endo, John McCabe, Mark
  Messenger, Helen Roberts, Martin Outram and Julian Rolton.
Naxos, 1999 \cdnum{8.554352}.

\cd*\relax
\artist{Rawsthorne, Alan}.
\cdtitle{Sonata for Cello and Piano}.
\see{983}.

\cd*\relax
\artist{Reade, Paul}.
\cdtitle{Saxophone Quartet}.
\see{830}.

\cd\relax
\artist{Rebel, Jean-F\'ery}.
\cdtitle{Violin Sonatas \(1713\)}.
Andrew Manze (violin), Richard Egarr (harpsichord) and Jaap ter Linden
  (viola da gamba).
Harmonia Mundi, 1999 \cdnum{HMU 907221}.

\cd\relax
\artist{Redhot Chili Peppers}.
\cdtitle{What Hits!?}
EMI Records, 1992 \cdnum{0777 7 94762 2 0}.

\cd*\relax
\artist{Reed, Alfred}.
\cdtitle{Ballade}.
\see{1602}.

\cd\relax
\artist{Reed, Lou}.
\cdtitle{Rock and Roll Diary: 1967--1980}.
Arista, 1993 \cdnum{07822-18434-2}.

\cd\relax
\artist{Reger, Max}.
\cdtitle{3 Suites for Cello solo Op.~131c \: \C{Eug\`ene Ysa\"ye} Sonata
  for Cello solo Op.~28}.
Erling Bl\"ondel Bengtsson.
Danacord Records, 1992 \cdnum{DACOCD~372}.

\cd\relax
\artist{Reger, Max}.
\cdtitle{\track Variations and Fugue on a theme of Johann Sebastian
  Bach, Op~81 \; \track Five Humoresques, Op~20 \; \track Variations and
  Fugue on a theme of Georg Philipp Telemann, Op~134}.
Marc-Andr\'e Hamelin.
Hyperion Records, 1999 \cdnum{CDA66996}.

\cd*\relax
\artist{Rehak, V\'aclav}.
\cdtitle{Sonnet~III}.
\see{293}.

\cd\relax
\artist{Reicha, Antoine}.
\cdtitle{\track Wind Quintet in C~minor, Op.~91, No.~6 \; \track Wind
  Quintet in F~major, Op.~88, No.~6}.
Michael Thompson Wind Quintet.
Naxos, 2000 \cdnum{8.554228}.

\cd\relax
\artist{Reicha, Antoine}.
\cdtitle{\track Wind Quintet in E~flat major, Op.~88, No.~2 \; \track
  Wind Quintet in A~minor, Op.~100, No.~5}.
Michael Thompson Wind Quintet.
Naxos, 1995 \cdnum{8.550432}.

\cd\relax
\artist{Reicha, Antoine}.
\cdtitle{\track Wind Quintet in G~major, Op.~99, No.~6 \; \track Wind
  Quintet in D~minor, Op.~88, No.~4}.
Michael Thompson Wind Quintet.
Naxos, 1997 \cdnum{8.553528}.

\cd\relax
\artist{Reinecke, Carl Heinrich}.
\cdtitle{The Three Cello Sonatas \: \track Sonata op.~42 in A~minor \;
  \track Sonata op.~98 in D~major \; \track Sonata op.~238 in G~major}.
Claudius Herrmann (cello) and Saiko Sasaki (piano).
CPO, 1995 \cdnum{999 342-2}.

\cd*\relax
\artist{Reizenstein, Franz}.
\cdtitle{Arabesques Op~47}.
\see{894}.

\cd\relax
\artist{Relativity}.
\cdtitle{Gathering Pace}.
Green Linnet, 1987 \cdnum{GLCD~1076}.

\cd\relax
\artist{Relativity}.
\cdtitle{Relativity}.
Green Linnet, 1985 \cdnum{GLCD~1059}.

\cd\relax
\artist{Renaissance}.
\cdtitle{At the Royal Albert Hall with the Royal Philharmonic Orchestra,
  Part~1}.
King Biscuit Flower Hour Records, 1997 \cdnum{70710-88020-2}.

\cd\relax
\artist{Renaissance}.
\cdtitle{At the Royal Albert Hall with the Royal Philharmonic Orchestra,
  Part~2}.
King Biscuit Flower Hour Records, 1997 \cdnum{70710-88026-2}.

\cd*\relax
\artist{Resphighi, Ottorino}.
\cdtitle{Adagio con variazioni}.
\see{1315}.

\cd\relax
\artist{Respighi, Ottorino}.
\cdtitle{\track Pini di Roma \; \track Fontane di Roma \; \track Feste
  romane}.
Oslo Philharmonic Orchestra.
Mariss Jansons, cond.
EMI Classics, 1990/1996 \cdnum{7243~5~55600~2~5}.

\cd\relax
\artist{Richter, Sviatoslav}.
\cdtitle{Beethoven \: \C{Ludwig van Beethoven} Sonata in A~flat
  ``Funeral March'' \and Sonata in D~minor ``Tempest'' \and Sonata in
  F~minor ``Appassionata'' \and Sonata in~E, Op.~109 \and Sonata in
  A~flat, Op.~110 \and Sonata in C~minor, Op.~111 \and Rondo in B~flat
  for Piano and Orchestra, WoO~6 \and Andante favori in~F, WoO~57}.
Volume~83 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 949-2}.

\cd\relax
\artist{Richter, Sviatoslav}.
\cdtitle{Liszt/Moussorgsky/Prokoviev/Schubert \: \track \C{Fr\'ed\'eric
  Chopin} Etude in~E, Op.~10 No.~3 ``Tristesse'' \; \track \C{Franz
  Liszt} Valse oubli\'ee No.~1 in F~sharp \and Valse oubli\'ee No.~2 in
  A~flat \and Etudes d'ex\'ecution transcendante Nos.~5 and~11 \; \track
  \C{Modest Moussorgsky} Pictures at an Exhibition \; \track \C{Sergei
  Prokofiev} Piano Sonata No.~6 in~A, Op.~82 \and Piano Sonata No.~7
  in~B~flat, Op.~83 \and Piano Sonata No.~8 in~B~flat, Op.~84 \; \track
  \C{Sergei Rachmaninoff} Prelude in G~sharp minor, Op.~32 No.~12 \;
  \track \C{Franz Schubert} Moment musical in~C, D.~780 No.~1 \and
  Impromptu in E~flat, D.~899 No.~2 \and Impromptu in A~flat, D.~899
  No.~4}.
Volume~82 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 946-2}.

\cd\relax
\artist{Richter, Sviatoslav}.
\cdtitle{Rachmaninoff/Schumann/Scriabin \: \track \C{Sergei
  Rachmaninoff} Piano Concerto No.~2 in C~minor, Op.~18 \and Preludes,
  Op.~32, Nos.~1--2 \and Preludes, Op.~23, Nos.~2, 4, 5,~7 \; \track
  \C{Alexander Scriabin} Etudes Op.~2, No.~1, Op.~8, Nos.~5,~11, Op.~42,
  Nos.~2--6,~8, Op.~65, Nos.~1--3 \; \track \C{Robert Schumann}
  Waldszenen, Op.~82 \and Fantasiest\"ucke, Op.~12 \(excerpts\} \and
  Toccata in~C, Op.~7 \and Fantasie in~C, Op.~17}.
Volume~84 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 952-2}.

\cd*\relax
\artist{Ries, Ferdinand}.
\cdtitle{Clarinet Trio Op.~28}.
\see{191}.

\cd*\relax
\artist{Rimsky-Korsakov, Nicolai}.
\cdtitle{Hymn to the Sun \(Turkish Princess\)}.
\see{929}.

\cd*\relax
\artist{Rimsky-Korsakov, Nicolai}.
\cdtitle{Russian Easter Overture, Op.~36}.
\see{299}.

\cd\relax
\artist{Rimsky-Korsakov, Nicolai}.
\cdtitle{\track Scheherazade, Op.~35 \; \track \C{Alexander Borodin}
  Polovtsian Dances \(Prince Igor, Act~II\)}.
Steven Staryk (violin).
Royal Philharmonic Orchestra and the Beecham Choral Society.
Thomas Beecham, cond.
EMI Classics, 1999 \cdnum{7243 5~66998~2~3}.

\cd*\relax
\artist{Rimsky-Korsakov, Nikolai}.
\cdtitle{Flight of the Bumble-Bee}.
\see{1233}.

\cd\relax
\artist{Rimsky-Korsakov, Nikolai}.
\cdtitle{Scheherazade \and Capriccio Espagnol}.
The London Symphony Orchestra.
Sir Charles Mackerras, cond.
Telarc, 1990 \cdnum{CD-80208}.

\cd\relax
\artist{Rimsky-Korsakov, Nikolai}.
\cdtitle{Scheherazade \and May night \and The tale of Tsar Saltan,
  op.~57 \and The flight of the bumblebee \and Russian Easter Festival
  overture, op.~36 \and Christmas Eve \and Dubinushka, op.~62 \and
  Sadko, op.~5 \and The Snow Maiden}.
L'Orchestre de la Suisse Romande.
Ernest Ansermet, cond.
The Decca Record Company, 1994 \cdnum[2]{443 464-2}.

\cd*\relax
\artist{Rische, Michael}.
\cdtitle{permanent isolation}.
\see{253}.

\cd\relax
\artist{Robinson, Smokey and the Miracles}.
\cdtitle{Anthology}.
Motown Record Company, 1995 \cdnum[2]{31453-0472-2}.

\cd*\relax
\artist{Rochberg, George}.
\cdtitle{Sonata for Viola and Piano \(1979\)}.
\see{177}.

\cd\relax
\artist{Rockapella}.
\cdtitle{Don't Tell Me You Do\dots}.
J-Bird Records, 1998 \cdnum{JBD 80264-2}.

\cd\relax
\artist{Rockapella}.
\cdtitle{Lucky Seven}.
For Life, Fall 1996 \cdnum{FLCF-3669}.

\cd\relax
\artist{Rockapella}.
\cdtitle{Primer}.
Summer 1995.

\cd\relax
\artist{Rockapella}.
\cdtitle{Rockapella}.
Rockapella, 1997.

\cd\relax
\artist{Rockapella}.
\cdtitle{Rockapella Five: Out Cold}.
For Life, Fall 1994 \cdnum{FLCF-3534}.

\cd\relax
\artist{Rockapella}.
\cdtitle{Rockapella Four: Vocobeat}.
For Life, Summer 1994 \cdnum{FLCF-3503}.

\cd\relax
\artist{Rockapella}.
\cdtitle{Rockapella One: To N.Y.}
For Life, Spring 1992 \cdnum{FLCF-30136}.

\cd\relax
\artist{Rockapella}.
\cdtitle{Rockapella Six: Best Fest}.
For Life, Fall 1995 \cdnum{FLCF-3602}.

\cd\relax
\artist{Rockapella}.
\cdtitle{Rockapella Three: Bash!}
For Life, Fall 1992 \cdnum{FLCF-30171}.

\cd\relax
\artist{Rockapella}.
\cdtitle{Rockapella Two: From N.Y.}
For Life, Spring 1992 \cdnum{FLCF-30137}.

\cd\relax
\artist{Rockapella}.
\cdtitle{Smilin'}.
Amerigo Records, 2002 \cdnum{33709}.

\cd\relax
\artist{Rockapella and others}.
\cdtitle{Where in the World is Carmen Sandeigo?}
Zoom Express and Fight Records, 1992 \cdnum{74860 30018-2}.

\cd\relax
\artist{Rodgers, Jimmie}.
\cdtitle{The Best of Jimmie Rodgers}.
Rhino, 1990 \cdnum{R2~70942}.

\cd\relax
\artist{Rodrigo, Joaqu{\'\i}n}.
\cdtitle{The Rodrigo Edition: Concertos and Orchestral Works \: \track
  Concierto Serenata \; \track Concierto pastoral \; \track concierto
  heroico \; \track Concierto madrigal \; \track Concierto de est{\'\i}o
  \; \track Concierto de Aranjuez \; \track Fantasia para un
  gentilhombre \; \track Concierto Andaluz \; \track Concierto en modo
  galante \; \track Per la flor del Iliri blau \; \track M\'usica para
  un jard{\'\i}n \; \track A la busca del m\'as all\'a \; \track
  Zarabanda lejana y villancico \; \track Cinco piezas infantiles \;
  \track Soleriana}.
Nancy Allen (harp), Lisa Hansen (flute), Jorge Federico Osorio (piano),
  Alfonso Moreno (guitar), Deborah Mariotti (guitar), Agust{\'\i}n
  Le\'on Ara (violin), Minerva Garibay (guitar), Cecilia L\'opez
  (guitar), Jes\'us Ruiz (guitar) and Robert Cohen (cello).
Royal Philharmonic Orchestra, London Symphony Orchestra, and Orquesta
  Sinf\'onica del Estado de Mexico.
Enrique B\'atiz, cond.
EMI Classics, 1992 \cdnum[4]{CZS~7 67435~2}.

\cd\relax
\artist{Rogers, Garnet}.
\cdtitle{All That Is}.
Red House Records, 2002 \cdnum{RHR CD~160}.

\cd\relax
\artist{Rogers, Garnet}.
\cdtitle{At a High Window}.
Snow Goose Songs, 1992 \cdnum{SGS 1121CD}.

\cd\relax
\artist{Rogers, Garnet}.
\cdtitle{Firefly}.
Snow Goose Songs, 2001 \cdnum{SGS 1129}.

\cd\relax
\artist{Rogers, Garnet}.
\cdtitle{Garnet Rogers}.
Snow Goose Songs, 1984 \cdnum{SGS 1111~CD}.

\cd\relax
\artist{Rogers, Garnet}.
\cdtitle{Night Drive}.
Snow Goose Records, 1996 \cdnum{SGS~1125}.

\cd\relax
\artist{Rogers, Garnet}.
\cdtitle{Small Victories}.
Snow Goose Songs, 1990 \cdnum{SGS 1117~CD}.

\cd\relax
\artist{Rogers, Garnet}.
\cdtitle{Speaking Softly in the Dark}.
Snow Goose Songs, 1988 \cdnum{SGS 1115~D}.

\cd\relax
\artist{Rogers, Garnet}.
\cdtitle{The Outside Track}.
Snow Goose Songs, 1986 \cdnum{SGS 1113~CD}.

\cd\relax
\artist{Rogers, Garnet and Doug Long}.
\cdtitle{Summer Lightning}.
Snow Goose Songs, 1994 \cdnum{SGS 1123~CD}.

\cd*\relax
\artist{Rogers, Rodney}.
\cdtitle{Lessons of the Sky}.
\see{505}.

\cd\relax
\artist{Rogers, Stan}.
\cdtitle{Between the Breaks\dots Live!}
Fogarty's Cove Music, 1979 \cdnum{FCM-002D}.

\cd\relax
\artist{Rogers, Stan}.
\cdtitle{Fogarty's Cove}.
Fogarty's Cove Music, 1977 \cdnum{FCM-P/1001D}.

\cd\relax
\artist{Rogers, Stan}.
\cdtitle{For the Family}.
Folk Tradition Records, 1983 \cdnum{R002}.

\cd\relax
\artist{Rogers, Stan}.
\cdtitle{From Coffee House to Concert Hall}.
Fogarty's Cove Music, 1999 \cdnum{FCM 012D}.

\cd\relax
\artist{Rogers, Stan}.
\cdtitle{From Fresh Water}.
Fogarty's Cove Music, 1984 \cdnum{FCM 007D}.

\cd\relax
\artist{Rogers, Stan}.
\cdtitle{Home in Halifax}.
Fogarty's Cove Music, 1992 \cdnum{FCM 010D}.

\cd\relax
\artist{Rogers, Stan}.
\cdtitle{Northwest Passage}.
Fogarty's Cove Music, 1981 \cdnum{FCM 004D}.

\cd\relax
\artist{Rogers, Stan}.
\cdtitle{Poetic Justic}.
Fogarty's Cove Music, 1996 \cdnum{FCM 011D}.

\cd\relax
\artist{Rogers, Stan}.
\cdtitle{Turnaround}.
Fogarty's Cove Music, 1978 \cdnum{FCM 001D}.

\cd\relax
\artist{Romanesca}.
\cdtitle{Phantasticus \: \track \C{Giovanni Antonio Pandolfi} Sonata
  ``La Monella Romanesca'', Op.~IV, No.~3 \; \track \C{Giovanni Paolo
  Cima} Sonata per il Violino \and Sonata \from ``Concerti
  ecclesiastici'' \; \track \C{Dario Castello} Sonata~I \and Sonata~II
  \from ``Sonate concertate in stil moderno,'' Lib.~II \; \track
  \C{Alessandro Piccinini} Romanesca con partite variate \from
  ``Intavolatura di liuto,'' Lib.~I \; \track \C{Girolamo Frescobaldi}
  Partite sopra l'aria della romananesca \from ``Toccate e partite,''
  Lib.~I \; \track \C{Giovanni Battista Fontana} Sonata~V \and Sonata~VI
  \from ``Sonate a 1. 2. 3.,'' op.~post. \; \track \C{Johann Hieronymus
  Kapsberger} Toccata~I \from ``Libro IV d'intavolatura di chitarrone''
  \; \track \C{Nicol\`o Corradini} Sonata ``La Sfondrata'' \from ``Il
  primo libro de canzoni francese''}.
Andrew Manze (violin), Nigel North (theorbo) and John Toll (harpsichord
  and chamber organ).
Harmonia Mundi, 1998 \cdnum{HMU 907211}.

\cd*\relax
\artist{Rorem, Ned}.
\cdtitle{3~Barcarolles}.
\see{604}.

\cd*\relax
\artist{Rorem, Ned}.
\cdtitle{Piano Sonata No.~2}.
\see{882}.

\cd*\relax
\artist{Rosier, Carl}.
\cdtitle{Suite f\"ur drei Violinen from \emph{Antwerpsche
  Vrede-Vreught}}.
\see{1184}.

\cd*\relax
\artist{Rosing-Schow, Niels}.
\cdtitle{Siciliana}.
\see{1700}.

\cd\relax
\artist{Roslavets, Nikolay}.
\cdtitle{Piano Music \: \track Three Compositions \(1914\) \; \track
  Three Etudes \(1914\) \; \track Piano Sonata No~1 \(1914\) \; \track
  Prelude \(1915\) \; \track Two Compositions \(1915\) \; \track Piano
  Sonata No~2 \(1916\) \; \track Two Poems \(1920\) \; \track Five
  Preludes \(1919--1922\) \; \track Piano Sonata No~5 \(1923\)}.
Marc-Andr\'e Hamelin.
Hyperion, 1997 \cdnum{CDA66926}.

\cd*\relax
\artist{Rossini, Gioacchino}.
\cdtitle{La gazza ladra: Sinfonia}.
\see{628}.

\cd*\relax
\artist{Rossini, Gioacchino}.
\cdtitle{Overture from \emph{Il barbiere di Siviglia} \arr{Sebastian
  Pottmeier for saxophone quartet}}.
\see{19}.

\cd\relax
\artist{Rossini, Gioachino}.
\cdtitle{Il Barbiere di Siviglia}.
Andr\'as D\'eri (fortepiano), B\'ela Sztankovits (guitar), Roberto
  Servile, Sonia Ganassi, Ramon Vargas, Angelo Romero, Franco de
  Grandis, Ingrid Kertesi, K\'azm\'er S\'ark\'any, L\'aszl\'o Orb\'an
  and Ferencz Korp\'as.
Failoni Chamber Orchestra, Budapest, and the Hungarian Radio Chorus.
Will Humburg, cond.
Naxos, 1993 \cdnum[3]{8.660027--29}.

\cd\relax
\artist{Rossini, Gioachino}.
\cdtitle{Il barbiere di Siviglia}.
Academy of St~Martin in the Fields.
Sir Neville Marriner, cond.
Philips Classics, 1995 \cdnum[2]{446 448-2}.

\cd\relax
\artist{Rossini, Gioachino}.
\cdtitle{Overtures \: \track Guillaume Tell \; \track Il signor
  Bruschino \; \track Il viaggio a Reims \; \track La scala de seta \;
  \track La gazza Iadra \; \track Il turco in Italia \; \track
  L'italiana in Algeri \; \track Il barbiere di Siviglia \; \track
  Torvaldo e Dorliska \; \track La cambiale de matrimonio \; \track
  Otello \; \track Semiramide \; \track Le Si\`ege de Corinthe \; \track
  Tancredi}.
National Philharmonic Orchestra.
Riccardo Chailly, cond.
The Decca Record Company, 1995 \cdnum[2]{443 850-2}.

\cd\relax
\artist{Rossini, Gioachino}.
\cdtitle{\track String Sonatas 1--6 \; \track \C{Gaetano Donizetti}
  String Quartet in~D \(arranged for String Orchestra\) \; \track
  \C{Luigi Cherubini} \'Etude No.~2 for French Horn and strings \;
  \track \C{Vincenzo Bellini} Concerto in E~flat major for oboe and
  strings}.
Academy of St~Martin-in-the-Fields.
Sir Neville Marriner, cond.
The Decca Record Company, 1995 \cdnum[2]{444 838-2}.

\cd\relax
\artist{Rostropovich, Mstislav}.
\cdtitle{Cello Concertos \: \track \C{Antonio Vivaldi} Concerto in
  D~minor, RV~406 \; \track \C{Giuseppe Tartini} Concerto in D~major \;
  \track \C{Carl Philipp Emanuel Bach} Concerto No.~2 in B~flat major,
  Wq~171 \(H~436\)}.
The Saint Paul Chamber Orchestra.
Hugh Wolff, cond.
Teldec Classics, 1993 \cdnum{9031-77311-2}.

\cd\relax
\artist{Rostropovich, Mstislav}.
\cdtitle{The Russian Years 1950--1974}.
EMI Records, 1997 \cdnum[13]{7243 5 72016 2~9}.

\cd\relax
\artist{Rostropovich, Mstislav and Benjamin Britten}.
\cdtitle{\track \C{Franz Schubert} Sonata for arpeggione and piano, D821
  \; \track \C{Robert Schumann} F\"unf St\"ucke im Volkston, op.~102 \;
  \track \C{Claude Debussy} Sonata for cello and piano}.
The Decca Record Company, 1999 \cdnum{289 460 974-2}.

\cd*\relax
\artist{Rota, Nina}.
\cdtitle{music from Fellini's film ``8~1/2''}.
\see{830}.

\cd\relax
\artist{Rota, Nino}.
\cdtitle{\track Piano Concerto in~C \; \track Piano Concerto in~E
  ``Piccolo mondo antico''}.
Giorgia Tomassi.
Filarmonica della Scala.
Riccardo Muti, cond.
EMI Classics, 1999 \cdnum{7243 5~56869~2 3}.

\cd*\relax
\artist{Rouse, Christopher}.
\cdtitle{Trombone Concerto \(1991\)}.
\see{962}.

\cd*\relax
\artist{Rouse, Christopher}.
\cdtitle{Violoncello Concerto}.
\see{1012}.

\cd*\relax
\artist{Rubenstein, Anton}.
\cdtitle{Valse caprice}.
\see{625}.

\cd*\relax
\artist{Rubinstein, Anton}.
\cdtitle{Turkish March from ``Die Ruinen von Athen'' \and Valse-Caprice
  in E~flat \and Melody in~F, Op.~3 No.~1}.
\see{775}.

\cd\relax
\artist{Rubinstein, Artur}.
\cdtitle{Chopin \: \C{Fr\'ed\'eric Chopin} Andante spianato and Grande
  Polonaise brillante, Op.~22 \and Nocturne in C~minor, Op.~48, No.~1
  \and Nocturne in F~sharp minor, Op.~48, No.~2 \and Polonaise in~A,
  Op.~40 No.~1 ``Military'' \and Waltz in C~sharm minor, Op.~64 No.~2
  \and Nocturne in C~sharm minor, Op.~27 No.~1 \and Nocturne in D~flat,
  Op.~27 No.~2 \and Waltz in D~flat, Op.~64 No.~1 ``Minute'' \and
  Berceuse in D~flat, Op.~57 \and Impromptu No.~1 in A~flat, Op.~29 \and
  Impromptu No.~2 in F~sharp, Op.~36 \and Impromptu No.~3 in G~flat,
  Op.~51 \and Scherzo No.~3 in C~sharp minor, Op.~39 \and Ballade No.~3
  in A~flat, Op.~47 \and Trois nouvelles \'etudes, Op.~posth. \and
  Fantaisie-Impromptu in C~sharp minor, Op.~66 \and Waltz in A~flat,
  Op.~34, No.~1 \and Waltz in A~flat, Op.~42 ``Two-Four Waltz'' \and
  Mazurkas, Op.~68 \and Piano Sonata No.~2 in B~flat minor, Op.~35
  ``Funeral March'' \and Ballade No.~4 in F~minor, Op.~52 \and Polonaise
  No.~6 in A~flat ``Heroic''}.
Volume~85 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 955-2}.

\cd\relax
\artist{Rubinstein, Artur}.
\cdtitle{Chopin/Grieg/Saint-Saens/Schumann/Tchaikovsky \: \track
  \C{Robert Schumann} Piano Concerto in A~minor, Op.~54 \; \track
  \C{Edvard Grieg} Piano Concerto in A~minor, Op.~16 \; \track
  \C{Camille Saint-Sa\"ens} Piano Concerto No.~2 in G~minor, Op.~22 \;
  \track \C{Fr\'ed\'eric Chopin} Piano Concerto No.~2 in F~minor, Op.~21
  \; \track \C{Peter Ilyich Tchaikovsky} Piano Concerto No.~1 in B~flat
  minor, Op.~23}.
Volume~86 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 958-2}.

\cd\relax
\artist{Rubinstein, Artur}.
\cdtitle{Schubert/Brahms/Franck/Beethoven/Schumann \: \track \C{Ludwig
  van Beethoven} Piano Sonata No.~18 in E~flat, Op.~31 No.~3 ``Hunt'' \;
  \track \C{C\'esar Franck} Pr\'elude, choral et fugue \; \track
  \C{Franz Schubert} Piano Sonata in B~flat, D.~960 \; \track
  \C{Johannes Brahms} Piano Sonata No.~3 in F~minor, Op.~5 \and Romance
  in~F, Op.~118 No.~5 \and Intermezzo in~E, Op.~116 No.~6 \and Ballade
  in~B, Op.~10 No.~4 \; \track \C{Robert Schumann} Fantasiest\"ucke,
  Op.~12}.
Volume~87 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 967-2}.

\cd*\relax
\artist{Ruders, Poul}.
\cdtitle{Bravour Studies for Solo Cello over ``L'Homme arm\'e''}.
\see{1700}.

\cd*\relax
\artist{Rueff, Jeanine}.
\cdtitle{Sonata for Alto Saxophone}.
\see{1605}.

\cd\relax
\artist{Rusche, Renate}.
\cdtitle{Bass Clarinet \: \track \C{Othmar Schoeck} Sonata for Bass
  Clarinet and Piano, Op.~41 \; \track \C{Olivier Messiaen} Ab\^{\i}me
  des oiseaux \from \emph{Quatuor pour la Fin du Temps} \; \track
  \C{Frits Celis} Da Uno a Cinque for Bass Clarinet and String Quartet,
  Op.~27 \; \track \C{Harald Genzmer} Sonata for Bass Clarinet Solo
  \(First Version 1984\) \; \track \C{Dietrich Erdmann} Concerto for
  Bass Clarinet and Orchestra}.
MDG, 1994 \cdnum{MDG 624 0556-2}.

\cd\relax
\artist{Russell, Anna}.
\cdtitle{Again?}
Sony Classical, 1998 \cdnum{SFK~60317}.

\cd\relax
\artist{Russell, Anna}.
\cdtitle{Encore?}
Sony, 1998 \cdnum{SFK 60316}.

\cd\relax
\artist{Russell, Anna}.
\cdtitle{The Anna Russell Album}.
Sony, 1972 \cdnum{MDK~47252}.

\cd\relax
\artist{Rzewski, Frederic}.
\cdtitle{\track The People Will Never Be Defeated! \; \track Down by the
  Riverside \; \track Winnsboro Cotton Mill Blues}.
Marc-Andr\'e Hamelin.
Hyperion, 1999 \cdnum{CDA67077}.

\cd*\relax
\artist{S{\ae}verud, Harald}.
\cdtitle{Tunes and Dances from ``Siljust{\o}l'', Opp.~22, 24, and~25
  \and Peer Gynt: Hymn against the Boyg, Op.~28}.
\see{28}.

\cd\relax
\cdtitle{Sailors' Songs and Sea Shanties}.
Highpoint Recordings, 2004 \cdnum{HPO 6007}.

\cd*\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{Cello Concerto in A~minor, Op.~33}.
\see{1510}.

\cd\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{Concerto No.~1 for Cello and Orchestra in A~minor, Op.~33 \and
  Concerto No.~2 for Piano and Orchestra in G~minor, Op.~22 \and
  Concerto No.~3 for Violin and Orchestra in B~minor, Op.~61}.
Yo-Yo Ma (cello), Cecile Licad (piano) and Cho-Liang Lin (violin).
CBS Records, 1990 \cdnum{MDK 46506}.

\cd*\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{Concerto No.~1 for Cello and Orchestra, op.~33}.
\see{1003}.

\cd*\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{Havanais, Op.~83 \T{Ma}}.
\see{1010}.

\cd*\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{Introduction and Rondo capriccioso}.
\see{1144}.

\cd\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{\track La Carnaval des Animaux \; \track Works for two pianos:
  Polonais, Op.~77 \and Caprice arabe, Op.~96 \and Scherzo, Op.~87 \and
  Variations on a theme by Beethoven, Op.~35 \and Dans macabre, Op.~40}.
Julian Reynolds (piano) and Peter Lockwood (piano).
Concentus Bestiales.
Julian Reynolds, cond.
Globe, 1996 \cdnum{GLO~5152}.

\cd*\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{Piano Concerto No.~2 in G~minor, Op.~22}.
\see{1319}.

\cd*\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{Piano Concerto No.~4 in C~minor, Op.~44}.
\see{448}.

\cd*\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{Sonata for Bassoon and Piano in~G, Op.~168}.
\see{661}.

\cd*\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{Sonata for Oboe and Piano, Op. 166}.
\see{1664}.

\cd*\relax
\artist{Saint-Saens, Camille}.
\cdtitle{Sonata for Oboe and Piano, Op.~166}.
\see{1605}.

\cd\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{Songs by Camille Saint-Sa\"ens}.
Fran\c{c}ois Le Roux (baritone), Graham Johnson (piano), Krysia
  Osostowicz (violin) and Philipa Davies (flute).
Hyperion, 1997 \cdnum{CDA66856}.

\cd\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{The Best of Saint-Sa\"ens \: \track Violin Concerto No.~3 in
  B~minor, Op.~61 \; \track Le carnaval des animaux \; \track Danse
  macabre, Op.~40 \; \track Piano Concerto No.~2 in G~minor, Op.~22 \;
  \track Introduction et Rondo capriccioso, Op.~28 \; \track Le carnaval
  des animaux: Le cygne \; \track Piano concerto No.~4 in C~minor,
  Op.~44 \; \track Symphony No.~3 in C~minor, Op.~78 \(``Organ''\)}.
The Decca Record Company, 1994 \cdnum[2]{442 608-2}.

\cd\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{The Complete \'Etudes \: \track Six \'Etudes, Op.~52 \; \track
  Six \'Etudes, Op.~111 \; \track Six \'Etudes pour la main gauche
  seule, Op.~135 \; \track Th\`eme Vari\'e, Op.~97}.
Piers Lane.
Hyperion Records, 1998 \cdnum{CDA67037}.

\cd*\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{Violin Concerto No.~3 in B minor, op.~61 \and Introduction et
  Rondo capriccioso, op.~21}.
\see{247}.

\cd*\relax
\artist{Saint-Sa\"ens, Camille}.
\cdtitle{Violin Sonata No.~1 in D~minor, Op.~75}.
\see{875}.

\cd\relax
\artist{San Francisco Saxophone Quartet}.
\cdtitle{Tails of the City}.
Angel Records, 1991 \cdnum{CDC 7~54132~2}.

\cd*\relax
\artist{Sarasate, Pablo de}.
\cdtitle{Carmen Fantasy, op.~25}.
\see{245}.

\cd*\relax
\artist{Sarasate, Pablo de}.
\cdtitle{Zigeunerweisen, op.~20}.
\see{247}.

\cd*\relax
\artist{Sargon, Simon A.}
\cdtitle{Deep Ellum Nights: Three Sketches}.
\see{438}.

\cd\relax
\artist{Satie, Erik}.
\cdtitle{Gymnop\'edie Nos.~1--3 \and Je te veux \and 4 Pr\'eludes
  flasques \and Pr\'elude en tapisserie \and 4\`eme Nocturne \and Vieux
  Sequins et Vieilles Cuirasses \and Embryons dess\'ech\'es \and
  Gnossienne Nos.~1--6 \and Sonatine bureaucratique \and Le Picadilly}.
Pascal Rog\'e.
The Decca Record Company, 1984 \cdnum{410 220-2}.

\cd\relax
\artist{Sax Players, The}.
\cdtitle{Les Saxs de SAX \: \track \C{Jean-Baptiste Singel\'ee} Duo
  concertant, Op.~55 \; \track Fantaise Pastorale \; \track Concerto,
  Op.~57 \; \track Septi\`eme solo de Concert, Op.~93 \; \track Premier
  Quatuor, Op.~53 \; \track \C{Jules Demersseman} Serenade, Op.~33}.
Christian Debecq (soprano saxophone), Guy Goethals (alto saxophone),
  Roland Schneider (tenor saxophone), Ulrich Berg (baritone saxophone)
  and Guy Penson (piano).
Ricercar, 2002 \cdnum{RIC 203}.

\cd*\relax
\artist{Scarlatti, Alessandro}.
\cdtitle{Infirmata vulnerata}.
\see{69}.

\cd*\relax
\artist{Scarlatti, Domenico}.
\cdtitle{Pastorale e capriccio}.
\see{775}.

\cd*\relax
\artist{Scarlatti, Domenico}.
\cdtitle{Sonata in A~minor, K.~109 \and Sonata in~F, K.~107 \and Sonata
  in B~minor, K.~87 \and Sonata in F~minor, K.~184}.
\see{1683}.

\cd*\relax
\artist{Scarlatti, Domenico}.
\cdtitle{Sonata in B~minor, K.~27 \and Sonata in~A, K.~212}.
\see{1196}.

\cd*\relax
\artist{Scarlatti, Domenico}.
\cdtitle{Sonata in C~minor, K.~11 \and Sonata in~C, K.~159 \and Sonata
  in~A, K.~322}.
\see{1067}.

\cd*\relax
\artist{Scarlatti, Domenico}.
\cdtitle{Sonata in C~minor, K.~11 \and Sonata in~G, K.~14}.
\see{770}.

\cd*\relax
\artist{Scarlatti, Domenico}.
\cdtitle{Sonata in D~Major, K.~491 \and Sonata in B~Minor, K.~27 \and
  Sonata in C-sharp Minor, K.~247 \and Sonata in D~Major, K.~29 \and
  Sonata in A~Major, K.~537 \and Sonata in E~Major, K.~206 \and Sonata
  in A~Major, K.~212}.
\see{1197}.

\cd*\relax
\artist{Scarlatti, Domenico}.
\cdtitle{Sonata in D~minor, K.~9 ``Pastorale'' \and Sonata in~F, K.~6
  \and Sonata in~G, K.~13 \and Sonata in C~minor, K.~11 \and Sonata
  in~E, K.~28}.
\see{478}.

\cd*\relax
\artist{Scarlatti, Domenico}.
\cdtitle{Sonata in~D, K.~430 \(L.~463\) \and Sonata in D~minor, K.~9
  \(L.~413\) \and Sonata in~G, K.~13 \(L.~486\)}.
\see{658}.

\cd*\relax
\artist{Scarlatti, Domenico}.
\cdtitle{Sonata in~E, K.~380 \and Sonata in~A, K.~533 \and Sonata in~D,
  K.~23 \and Sonata in~G, K.~14 \and Sonata in B~minor, K.~27 \and
  Sonata in~D, K.~430}.
\see{407}.

\cd*\relax
\artist{Scarlatti, Domenico}.
\cdtitle{Three Pieces}.
\see{830}.

\cd\relax
\artist{Scharwenka, Xaver}.
\cdtitle{The Complete Chamber Music \: \track Piano Trio No~1 in F~sharp
  minor, Op~1 \; \track Violin Sonata in D~minor, Op~2 \; \track Cello
  Sonata in E~minor, Op~46a \; \track Serenade for violin and piano,
  Op~70 \; \track Piano Quartet in F~major, Op~37 \; \track Piano Trio
  No~2 in A~minor, Op~45}.
Seta Tanyel (piano), Lydia Mordkovitch (violin), Colin Carr (cello),
  Levon Chlingirian (violin), Ivo-Jan van der Werff (viola) and Garbis
  Atmacayan (cello).
Hyperion, 2002 \cdnum[2]{CDD22046}.

\cd\relax
\artist{Schickele, Peter}.
\cdtitle{\track Bestiary: A Music Theater Piece for Renaissance Ensemble
  \; \track Quartet for Clarinet, Violin, Cello, and Piano}.
Calliope: A Renaissance Band, David Shifrin (clarinet), Eriko Sato
  (violin), Fred Sherry (cello) and David Oei (piano).
Vanguard Classics, 1984 \cdnum{OVC~4066}.

\cd*\relax
\artist{Schickele, Peter}.
\cdtitle{Dances for Three}.
\see{1598}.

\cd\relax
\artist{Schickele, Peter}.
\cdtitle{Hornsmoke \: \track Piano Concerto No.~2 in F~Major \(``Ole''\)
  \; \track Variations on a Joke \; \track Brass Calendar \; \track A
  little Mosey Music \; \track Hornsmoke \(A Horse Opera\)}.
The Chestnut Brass Company.
Newport Classic, 1998 \cdnum{NCD~85638}.

\cd\relax
\artist{Schickele, Peter}.
\cdtitle{On a Lark \: \track Sextet \; \track String Quartet No.~2
  \(``In Memorium''\) \; \track Quintet No.~2 for Piano and Strings}.
The Lark Quartet.
Arabesque Recordings, 1998 \cdnum{Z6719}.

\cd\relax
\artist{Schickele, Peter}.
\cdtitle{\track The Emperor's New Clothes \; \track Aesop Suite for An
  die Musik}.
An die Musik.
Newport Classic, 2003 \cdnum{NPD 85668}.

\cd*\relax
\artist{Schieferdecker, Johann Christian}.
\cdtitle{Concerts musicaux \(1713\): Premier concert}.
\see{10}.

\cd\relax
\artist{Schiff, Andr\'as}.
\cdtitle{Bach/Mozart/Schubert \: \track \C{Johann Sebastian Bach} 15
  Two-Part Inventions, BWV~772--786 \and 15 Three-Part Inventions
  \(Sinfoniae\), BWV~787--801 \and Chromatic Fantasy and Fugue, BWV~903
  \and English Suite No.~2 in A~minor, BWV~807 \; \track \C{Wolfgang
  Amadeus Mozart} Sonata in~C, KV~545 \(``for beginners''\) \and Sonata
  in~D, KV~576 \; \track \C{Franz Schubert} 6 Moments musicaux, D.~780
  \and 3 Klavierst\"ucke, D.~946}.
Volume~88 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 925-2}.

\cd*\relax
\artist{Schiffmann, Ernst}.
\cdtitle{Intermezzo, Op.~53}.
\see{1599}.

\cd*\relax
\artist{Schmelzer, Johann Heinrich}.
\cdtitle{Sonata a tre violini}.
\see{1184}.

\cd*\relax
\artist{Schmelzer, Johann Heinrich}.
\cdtitle{Sonata~XII \from \emph{Sacro-profanus concentus musicus}}.
\see{260}.

\cd\relax
\artist{Schmelzer, Johann Heinrich}.
\cdtitle{Violin Sonatas: Sonatas I--VI from ``Sonat{\ae} unarum fidium''
  \and Sonata, ``Cuc\`u'' \and Sonata, ``Victori der Christen''}.
Romanesca, Andrew Manze (violin), Nigel North (theorbo) and John Toll
  (harpsichord and organ).
Harmonia Mundi, 1996 \cdnum{HMU 907143}.

\cd\relax
\artist{Schmidt, Franz}.
\cdtitle{Book of the Seven Seals}.
Chor und Symphonieorchester des Bayerischen Rundfunks.
Franz Welser-M\"ost, cond.
EMI Records, 1998 \cdnum[2]{7243 5~56660 2~4}.

\cd*\relax
\artist{Schmidt, Franz}.
\cdtitle{Quintet in G~major for 2 Violins, Viola, Cello and Piano Left
  Hand}.
\see{926}.

\cd*\relax
\artist{Schmitt, Florent}.
\cdtitle{L\'egende, op.~66}.
\see{298}.

\cd\relax
\artist{Schnabel, Artur}.
\cdtitle{Beethoven \: \C{Ludwig van Beethoven} Piano Sonata No.~21 in~C,
  Op.~53 ``Waldstein'' \and 33 Variations on a Waltz by Anton Diabelli
  in~C, Op.~120 \and Piano Sonata No.~30 in~E, Op.~109 \and Piano Sonata
  No.~32 in~C~minor, Op.~111 \and Piano Concerto No.~4 in~G, Op.~58}.
Volume~89 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 961-2}.

\cd\relax
\artist{Schneemann, Bart}.
\cdtitle{It Takes Two \: \track \C{Iva Bittov\'a} Hoboj \and Divn\'a
  slecinka \(A strange young lady\) \and V zemi Neoran\'e \(On
  unploughed land\) \; \track \C{Astor Piazzolla} Oblivion \and
  Chiquilin de Bach{\'\i}n \; \track \C{Simon Burgers} `Pastiche' \;
  \track \C{Leos Jan\'a\c{c}ek} C\^ek\'am T\^e \(Waiting for you\)
  \(arr.~Iva Bittov\'a\) \; \track \C{Harrison Birtwistle} Pulse Sampler
  \; \track \C{Carlos Gardel} El Dia Que Me Querias \; \track \C{Louis
  Andriessen} `Vergeet me niet' \; \track \C{Gy\"orgy Kurt\'ag} Hommage
  \`a Tristan \and Versetto \and Summaia~a \; \track \C{Bela Bart\'ok}
  H\'arom Csikmegyei N\'epdal \(Three folksongs from the country of
  Csik\) \and Este a sz\'ekelyekn\'el \(An evening in the village\) \;
  \track \C{Ralph Vaughan Williams} Infant joy \and Cruelty has a human
  heart \and The piper \and Eternity \(\emph{from} Ten Blake Songs\) \;
  \track \C{Jacob ter Veldhuis} the Garden of Love \; \track \C{G.
  Morini} La luna}.
Daniel Raiskin (viola), Alfredo Marcucci (bandone\'on), Gerrit Boonstra
  (clarinet), Peter Prommen (claves), Gerrit Boonstra (bassclarinet),
  Jan Rokyta (cymbalon), Johannette Zomer (soprano) and Peter Promell
  (marimba).
Channel Classics, 2002 \cdnum{CCS~18598}.

\cd\relax
\artist{Schnittke, Alfred}.
\cdtitle{\track Cello Concerto \(1986\) \; \track Stille Musik for
  violin and cello \(1979\) \; \track Sonata for violoncello and piano
  \(1978\)}.
Maria Kliegel (cello), Raimund Havenith (piano) and Burkhard Godhoff
  (violin).
Saarbr\"ucken Radio Symphony Orchestra.
Gerhard Markson, cond.
Naxos, 1990/1998 \cdnum{8.554465}.

\cd*\relax
\artist{Schnittke, Alfred}.
\cdtitle{Cello Sonata No.~2 \and Epilogue for cello, piano and tape
  \emph{from the ballet} Peer Gynt}.
\see{1315}.

\cd*\relax
\artist{Schoeck, Othmar}.
\cdtitle{Sonata for Bass Clarinet and Piano, Op.~41}.
\see{1321}.

\cd*\relax
\artist{Schoeck, Othmar}.
\cdtitle{Sonata, Op.~41}.
\see{293}.

\cd*\relax
\artist{Schoeck, Otmar}.
\cdtitle{Sonata for Basson and Piano, op.~41}.
\see{847}.

\cd\relax
\artist{Schoenberg, Arnold}.
\cdtitle{\track Chamber Symphony No.~1, Op.~9 \; \track Concerto for
  Piano and Orchestra, Op.~42 \; \track Chamber Symphony No.~2, Op.~38}.
Alfred Brendel (piano).
SWF Sinfonieorchester Baden-Baden.
Michael Gielen, cond.
Philips Classics, 1996 \cdnum{446 683-2}.

\cd*\relax
\artist{Schoenberg, Arnold}.
\cdtitle{Drei Klavierst\"ucke, Op.~11}.
\see{1610}.

\cd*\relax
\artist{Schoenberg, Arnold}.
\cdtitle{Erwartung, Op.~17}.
\see{256}.

\cd\relax
\artist{Schoenberg, Arnold}.
\cdtitle{Verkl\"arte Nacht, op.~4 \and Pelleas und Melisande, op.~5}.
Berliner Philharmoniker.
Herbert von Karajan, cond.
Deutsche Grammophon, 1974 \cdnum{289 457 721-2}.

\cd\relax
\artist{Scholl, Andreas}.
\cdtitle{A Musicall Banquet}.
guitar, orpharion Edin Karamazov (lutes), Markus M\"arki (harpsichord)
  and Christophe Coin (bass viol).
The Decca Record Company, 2001 \cdnum{289 466 917-2}.

\cd*\relax
\artist{Sch\"onberg, Arnold}.
\cdtitle{Brettl-Lieder \(1901\)}.
\see{37}.

\cd*\relax
\artist{Sch\"onberg, Arnold}.
\cdtitle{Canons arranged for saxophones}.
\see{1686}.

\cd*\relax
\artist{Schoof, Manfred}.
\cdtitle{Two Impromptus for Basson and Piano}.
\see{847}.

\cd\relax
\artist{Schoolhouse Rock}.
\cdtitle{The Best of Schoolhouse Rock}.
Rhino/ABC, 1998 \cdnum{R2 75315}.

\cd\relax
\artist{Schooner Fare}.
\cdtitle{Closer to the Wind}.
Outer Green Records, 1989 \cdnum{OGR8882D}.

\cd\relax
\artist{Schooner Fare}.
\cdtitle{Day of the Clipper}.
Outer Green Records, 1989 \cdnum{OGR8878D}.

\cd\relax
\artist{Schooner Fare}.
\cdtitle{For the Times}.
Outer Green Records, 1993 \cdnum{OGR8909D}.

\cd\relax
\artist{Schooner Fare}.
\cdtitle{The First Ten Years}.
Outer Green Records, 1990 \cdnum{OGR8886D}.

\cd*\relax
\artist{Schubert}.
\cdtitle{Moments musicaux, D.~780}.
\see{45}.

\cd\relax
\artist{Schubert, Franz}.
Volume~1 of \emph{The Hyperion Schubert Edition}.
Dame Janet Baker (mezzo soprano) and Graham Johnson (piano).
Hyperion Records, 1988 \cdnum{CDJ33001}.

\cd\relax
\artist{Schubert, Franz}.
Volume~10 of \emph{The Hyperion Schubert Edition}.
Martyn Hill (tenor) and Graham Johnson (piano).
Hyperion Records, 1991 \cdnum{CDJ33010}.

\cd\relax
\artist{Schubert, Franz}.
Volume~11 of \emph{The Hyperion Schubert Edition}.
Brigitte Fassbaender (mezzo soprano) and Graham Johnson (piano).
Hyperion Records, 1991 \cdnum{CDJ33011}.

\cd\relax
\artist{Schubert, Franz}.
Volume~12 of \emph{The Hyperion Schubert Edition}.
Adrian Thompson (tenor) and Graham Johnson (piano).
Hyperion Records, 1991 \cdnum{CDJ33012}.

\cd\relax
\artist{Schubert, Franz}.
Volume~13 of \emph{The Hyperion Schubert Edition}.
Marie McLaughlin (soprano), Thomas Hampson (baritone) and Graham Johnson
  (piano).
Hyperion Records, 1992 \cdnum{CDJ33013}.

\cd\relax
\artist{Schubert, Franz}.
Volume~14 of \emph{The Hyperion Schubert Edition}.
Thomas Hampson (baritone), Marie McLaughlin (soprano) and Graham Johnson
  (piano).
Hyperion Records, 1992 \cdnum{CDJ33014}.

\cd\relax
\artist{Schubert, Franz}.
Volume~15 of \emph{The Hyperion Schubert Edition}.
Margaret Price (soprano) and Graham Johnson (piano).
Hyperion Records, 1992 \cdnum{CDJ33015}.

\cd\relax
\artist{Schubert, Franz}.
Volume~16 of \emph{The Hyperion Schubert Edition}.
Thomas Allen (baritone) and Graham Johnson (piano).
Hyperion Records, 1993 \cdnum{CDJ33016}.

\cd\relax
\artist{Schubert, Franz}.
Volume~17 of \emph{The Hyperion Schubert Edition}.
Lucia Popp (soprano) and Graham Johnson (piano).
Hyperion Records, 1993 \cdnum{CDJ33017}.

\cd\relax
\artist{Schubert, Franz}.
Volume~18 of \emph{The Hyperion Schubert Edition}.
Peter Schreier (tenor) and Graham Johnson (piano).
Hyperion Records, 1993 \cdnum{CDJ33018}.

\cd\relax
\artist{Schubert, Franz}.
Volume~19 of \emph{The Hyperion Schubert Edition}.
Felicity Lott (soprano) and Graham Johnson (piano).
Hyperion Records, 1993 \cdnum{CDJ33019}.

\cd\relax
\artist{Schubert, Franz}.
Volume~2 of \emph{The Hyperion Schubert Edition}.
Stephen Varcoe (baritone) and Graham Johnson (piano).
Hyperion Records, 1988 \cdnum{CDJ33002}.

\cd\relax
\artist{Schubert, Franz}.
Volume~21 of \emph{The Hyperion Schubert Edition}.
Edith Mathis (soprano) and Graham Johnson (piano).
Hyperion Records, 1994 \cdnum{CDJ33021}.

\cd\relax
\artist{Schubert, Franz}.
Volume~23 of \emph{The Hyperion Schubert Edition}.
Christoph Pr\'egardien (tenor) and Graham Johnson (piano).
Hyperion Records, 1995 \cdnum{CDJ33023}.

\cd\relax
\artist{Schubert, Franz}.
Volume~27 of \emph{The Hyperion Schubert Edition}.
Matthias G\"orne (baritone), Graham Johnson (piano) and Christine
  Sch\"afer (soprano).
Hyperion Records, 1996 \cdnum{CDJ33027}.

\cd\relax
\artist{Schubert, Franz}.
Volume~29 of \emph{The Hyperion Schubert Edition}.
Marjana Lipov\v{s}ek (mezzo soprano), Nathan Berg (baritone) and Graham
  Johnson (piano).
Hyperion Records, 1997 \cdnum{CDJ33029}.

\cd\relax
\artist{Schubert, Franz}.
Volume~3 of \emph{The Hyperion Schubert Edition}.
Ann Murray (mezzo soprano) and Graham Johnson (piano).
Hyperion Records, 1989 \cdnum{CDJ33003}.

\cd\relax
\artist{Schubert, Franz}.
Volume~31 of \emph{The Hyperion Schubert Edition}.
Christine Brewer (soprano) and Graham Johnson (piano).
Hyperion Records, 1998 \cdnum{CDJ33031}.

\cd\relax
\artist{Schubert, Franz}.
Volume~36 of \emph{The Hyperion Schubert Edition}.
Juliane Banse (soprano), Michael Schade (tenor), Gerald Finley
  (baritone), Lynne Dawson (soprano), Graham Johnson (piano) and Eugene
  Asti (piano).
Holst Singers.
Stephen Layton, cond.
Hyperion Records, 2000 \cdnum{CDJ33036}.

\cd\relax
\artist{Schubert, Franz}.
Volume~4 of \emph{The Hyperion Schubert Edition}.
Philip Langridge (teno) and Graham Johnson (piano).
Hyperion Records, 1989 \cdnum{CDJ33004}.

\cd\relax
\artist{Schubert, Franz}.
Volume~5 of \emph{The Hyperion Schubert Edition}.
Elizabeth Connell (soprano) and Graham Johnson (piano).
Hyperion Records, 1989 \cdnum{CDJ33005}.

\cd\relax
\artist{Schubert, Franz}.
Volume~6 of \emph{The Hyperion Schubert Edition}.
Anthony Rolfe Johnson (tenor) and Graham Johnson (piano).
Hyperion Records, 1990 \cdnum{CDJ33006}.

\cd\relax
\artist{Schubert, Franz}.
Volume~7 of \emph{The Hyperion Schubert Edition}.
Elly Ameling (soprano) and Graham Johnson (piano).
Hyperion Records, 1990 \cdnum{CDJ33007}.

\cd\relax
\artist{Schubert, Franz}.
Volume~8 of \emph{The Hyperion Schubert Edition}.
Sarah Walker (mezzo soprano) and Graham Johnson (piano).
Hyperion Records, 1990 \cdnum{CDJ33008}.

\cd\relax
\artist{Schubert, Franz}.
Volume~9 of \emph{The Hyperion Schubert Edition}.
Arleen Auger (soprano) and Graham Johnson (piano).
Hyperion Records, 1990 \cdnum{CDJ33009}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{6 Moments musicaux, D.~780 \and 3 Klavierst\"ucke, D.~946}.
\see{1340}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{8 Symphonies \(1--6, 8--9\)}.
Berliner Philharmoniker.
Karl B\"ohm, cond.
Deutsche Grammophon, 1987 \cdnum[4]{419 318-2}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{A Goethe Schubertiad}.
Volume~24 of \emph{The Hyperion Schubert Edition}.
Christine Sch\"afer (soprano), John Mark Ainsley (tenor), Simon
  Keenlyside (baritone), Michael George (bass) and Graham Johnson
  (piano).
The London Schubert Chorale.
Hyperion Records, 1995 \cdnum{CDJ33024}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{An 1815 Schubertiad}.
Volume~20 of \emph{The Hyperion Schubert Edition}.
Patricia Rozario (soprano), John Mark Ainsley (tenor), Ian Bostridge
  (tenor), Michael George (bass), Graham Johnson (piano) and the
  Schubert Chorale.
Hyperion Records, 1994 \cdnum{CDJ33020}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{An 1815 Schubertiad II}.
Volume~22 of \emph{The Hyperion Schubert Edition}.
Lorna Anderson (soprano), Catherine Wyn-Rogers (mezzo soprano), Jamie
  MacDougall (tenor), Simon Keenlyside (baritone) and Graham Johnson
  (piano).
Hyperion Records, 1994 \cdnum{CDJ33022}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{An 1816 Schubertiad}.
Volume~32 of \emph{The Hyperion Schubert Edition}.
Lynne Dawson (soprano), Christine Sch\"afer (soprano), Ann Murray (mezzo
  soprano), John Mark Ainsley (tenor), Daniel Norman (tenor), Christoph
  Pr\'egardie (tenor)n, Michael Schade (tenor), Toby Spence (tenor),
  Christopher Maltman (baritone), Stephen Varcoe (baritone) and Graham
  Johnson (piano).
The London Schubert Chorale.
Hyperion Records, 1999 \cdnum{CDJ33032}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{An 1822 Schubertiad}.
Volume~28 of \emph{The Hyperion Schubert Edition}.
John Mark Ainsley (tenor), Maarten Koningsberger (baritone) and Graham
  Johnson (piano).
Hyperion Records, 1997 \cdnum{CDJ33028}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{An 1826 Schubertiad}.
Volume~26 of \emph{The Hyperion Schubert Edition}.
Christine Sch\"afer (soprano), John Mark Ainsley (tenor), Richard
  Jackson (baritone) and Graham Johnson (piano).
The London Schubert Chorale.
Hyperion Records, 1996 \cdnum{CDJ33026}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Die Sch\"one M\"ullerin}.
Volume~25 of \emph{The Hyperion Schubert Edition}.
Ian Bostridge (tenor), Graham Johnson (piano) and Dietrich
  Fischer-Dieskau (reader).
Hyperion Records, 1995 \cdnum{CDJ33025}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Die Sch\"one M\"ullerin \and Winterreise}.
Peter Pears (tenor) and Benjamin Britten (piano).
The Decca Record Company, 1997 \cdnum[2]{452 402-2}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Die Sch\"one M\"ullerin, D795}.
Matthias Goerne (baritone) and Eric Schneider (piano).
Decca, 2002 \cdnum{289 470 025-2}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Drei Klavierst\"ucke, D.~946}.
\see{1207}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Duo Sonata in A~major, D574}.
\see{875}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Fantasia in~C, Op.~15/D.~760 \(``Wanderer'' Fantasy\) \and
  Impromptus, Op.~90/D.~899 \and Sonata in B-Flat, Op.~Posth./D.~960}.
Artur Rubinstein.
RCA, 1987 \cdnum{6257-2-RC}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Fantasy in F~minor for Piano Duet, D.~940}.
\see{643}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Fantasy in~C, D.~760 ``Wanderer-Fantasie''}.
\see{1684}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Goethe-Lieder}.
Matthias Goerne (baritone) and Andreas Haefliger (piano).
The Decca Record Company, 1997 \cdnum{452 917-2}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Gretchen am Spinnrade \and Auf dem Wasser zu singen \and Die
  Forelle \and Marche militaire}.
\see{900}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Impromptu in A~flat, D.~935 No.~2 \and Impromptu in B~flat,
  D.~935 No.~3}.
\see{1187}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Impromptu in B~flat, D.~935 No.~3}.
\see{1196}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Impromptu in E~flat, D.~899 No.~2}.
\see{140}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Impromptu in E~flat, D.~899 No.~2}.
\see{844}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Impromptu in G~flat, D.~899, No.~3 \and Impromptu in E~flat,
  D.~899, No.~2}.
\see{967}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Impromptu No.~3, D899/3}.
\see{1315}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Impromptus, D.~899}.
\see{589}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Impromptus, D.~899 \and Impromptus, D.~935}.
\see{337}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Impromptus, D.~935 \and Fantasie in~C, D.~760
  ``Wanderer-Fantasie'' \and Impromptus, D.~899}.
\see{471}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Impromptus, Op.~90 \(D.~899\) and Op.~142 \(D.~935\)}.
Mitsuko Uchida.
Philips, 1997 \cdnum{456~245-2}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{L'Abeille \(``The Bee''\), Op. 13, no.~9}.
\see{504}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Lieder}.
Janet Baker (mezzo-soprano), Gerald Moore (piano) and Geoffrey Parsons
  (piano).
EMI Records, 1996 \cdnum[2]{7243 5 69389 2~2}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Lieder}.
Ian Bostridge (tenor) and Julius Drake (piano).
EMI Classics, 1998 \cdnum{7243 5 56347 2 6}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Lieder, Volume~I}.
Dietrich Fischer-Dieskau (bariton) and Gerald Moore (piano).
Deutsche Grammophon, \noop{1969a}1970 \cdnum[9]{437 215-2}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Lieder, Volume~II}.
Dietrich Fischer-Dieskau (bariton) and Gerald Moore (piano).
Deutsche Grammophon, \noop{1969b}1969 \cdnum[9]{437 225-2}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Lieder, Volume~II}.
Ian Bostridge (tenor) and Julius Drake (piano).
EMI Classics, 2001 \cdnum{7243 5 57141 2~1}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Lieder, Volume~III \: \track Die Sch\"one M\"ullerin \; \track
  Winterreise \; \track Schwanengesang}.
Dietrich Fischer-Dieskau (bariton) and Gerald Moore (piano).
Deutsche Grammophon, \noop{1969c}1972 \cdnum[3]{437 235-2}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Marche militaire No.~1 in~D \(\from D.~733\) \and Erlk\"onig}.
\see{775}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Moment musical in A~flat, D.~780, No.~6}.
\see{1201}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Moment musical in~C, D.~780 No.~1 \and Impromptu in E~flat,
  D.~899 No.~2 \and Impromptu in A~flat, D.~899 No.~4}.
\see{1270}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Moments musicaux, D.~780 \and Piano Sonata in A~minor, D.~784}.
\see{988}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{\track Piano Quintet in A~Major, D.~677 \(Op.\ posth.~114\)
  ``The Trout'' \; \track Sonata for Arpeggione and Piano, D.~821
  ``Arpeggione'' \; \track Adagio for Piano Trio, D.~897 \(Op.\
  posth.~148\) ``Notturno''}.
Jos van Immerseel (piano), Vera Beths (violin), Anner Bylsma (cello),
  J\"urgen Kussmaul (viola) and Marji Danilow (double bass).
Sony Classical, 1998 \cdnum{SK~63361}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Piano Sonata in A~minor, D.~784}.
\see{720}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Piano Sonata in A~minor, D.~845}.
\see{886}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Piano Sonata in B~flat, D.~960}.
\see{1320}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Piano Sonata in~A, D.~959}.
\see{579}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Piano Sonata in~C, D.~840 ``Reliquie''}.
\see{887}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{\track Piano Sonata in~D \(D~850\) \; \track Der liebliche
  Stern \(D~861\) \; \track Tiefes Lind \(D~876\) \; \track Auf der
  Bruck \(D~853\) \; \track Der Wanderer \(D~649\) \; \track F\"ulle der
  Liebe \(D~854\) \; \track Wiedersehn \(D~855\) \; \track Vom Mitleiden
  Mari\"a \(D~632\) \; \track Im Walde \(D~708\) \; \track Der
  Schmetterling \(D~633\)}.
Ian Bostridge (tenor) and Leif Ove Andsnes (piano).
EMI Classics, 2003 \cdnum{7243 5 57509 2~1}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Piano Sonata No.~21 in B~flat, D.~960}.
\see{747}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Quintet for Two Violins, Viola, and Two Cellos in C~Major,
  D.~956 \: \C{Luigi Boccherini} Quintet for Two Violins, Viola, and Two
  Cellos in E~Major, Op..~13, No.~5}.
Isaac Stern (violin), Cho-Liang Lin (violin), Jaime Laredo (viola),
  Yo-Yo Ma (cello) and Sharon Robinson (cello).
Sony Classical, 1996 \cdnum{SK~53983}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Quintet in A~major, D667, ``The Trout'' \and Violin Sonata in
  D~major, D384 \and Violin Sonata in A~minor, D385 \and Violin Sonata
  in G~minor, D408 \and Octet in F~major}.
The Academy of Ancient Music Chamber Ensemble, Christopher Hogwood
  (fortepiano), Steven Lubin (fortepiano) and Jaap Schr\"oder (violin).
The Decca Record Company, 1997 \cdnum[2]{455 724-2}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{\track Quintett f\"ur Klavier, Violine, Viola, Violoncello und
  Kontraba{\ss} A-Dur, Op.~post.~114, D.~677 \(``Die Forelle''\) \;
  \track Sonate f\"ur Klavier und Arpeggione a-moll, D.~821 \; \track
  ``Die Forelle'', D.~550}.
Emanuel Ax (klavier), Pamela Frank (violine), Rebecca Young (viola),
  Yo-Yo Ma (violoncello), Edgar Meyer (kontraba\ss) and Barbara Bonney
  (soprano).
Sony Classical, 1996 \cdnum{SK~61964}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Schubert, 1817--1821}.
Volume~34 of \emph{The Hyperion Schubert Edition}.
Graham Johnson (piano).
Hyperion Records, 2000 \cdnum{CDJ33034}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Schubert, 1822--1825}.
Volume~35 of \emph{The Hyperion Schubert Edition}.
Graham Johnson (piano).
Hyperion Records, 2000 \cdnum{CDJ33035}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Sonata for arpeggione and piano, D821}.
\see{1316}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Sonata in A~minor, D.~821 ``Arpeggione''}.
\see{1156}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Songs for Male Chorus}.
Robert Shaw Chamber Singers.
Robert Shaw, cond.
Telarc, 1994 \cdnum{CD-80340}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{St\"andchen \arr{Franz Liszt}}.
\see{645}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{St\"andchen \(Serenade\) \and Die Biene \(The Bee\)}.
\see{902}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{String Quartets Nos.~13 and~14}.
The Guarneri String Quartet.
Arabesque Recordings, 1997 \cdnum{Z6687}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{String Quintet in~C, D956}.
The Lindsay String Quartet and Douglas Cummings (cello).
ASV, 1995 \cdnum{CD DCA 537}.

\cd*\relax
\artist{Schubert, Franz}.
\cdtitle{Symphony No.~9 in C~major, D~944 \and Rosamunde}.
\see{627}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{The Complete Finished Sonatas for Piano \(D537, D568, D575,
  D664, D784, D845, D850, D894, D958, D959, D960\)}.
John Damgaard.
Classico, 1998 \cdnum[5]{245-49}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{The Final Year}.
Volume~37 of \emph{The Hyperion Schubert Edition}.
John Mark Ainsley, Anthony Rolfe Johnson, Michael Schade, Graham Johnson
  (piano) and David Pyatt (french horn).
Hyperion Records, 2000 \cdnum{CDJ33037}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{The Young Schubert}.
Volume~33 of \emph{The Hyperion Schubert Edition}.
Marie McLaughlin (soprano), Ann Murray (mezzo soprano), Catherine
  Wyn-Rogers (mezzo soprano), Philip Langridge (tenor), Daniel Norman
  (tenor), Adrian Thompson (tenor), Maarten Koningsberger (baritone),
  Stephen Varcoe (baritone) and Graham Johnson (piano).
Hyperion Records, 1999 \cdnum{CDJ33033}.

\cd\relax
\artist{Schubert, Franz}.
\cdtitle{Winterreise}.
Volume~30 of \emph{The Hyperion Schubert Edition}.
Matthias Goerne (baritone) and Graham Johnson (piano).
Hyperion Records, 1997 \cdnum{CDJ33030}.

\cd\relax
\artist{Schubert, Franz and Franz Liszt}.
\cdtitle{Erlk\"onig: Duos and Transcriptions \: \track \C{Heinrich
  Wilhelm Ernst} Der Erlk\"onig, Grand Caprice op.~26 \; \track \C{Franz
  Liszt} Grand Duo concertant sur la Romance de M.~Lafont ``La Marin''
  \(Searle~128\) \and La lugubre gondola \(Searle~134\) \and
  Valse-Caprice No.~6 aus ``Soir\'ees de Vienne'' \(Searle~427\) \;
  \track \C{Franz Schubert} Variationen f\"ur violine under Klavier
  \"uber ``Trockne Blumen'' \; \track \C{Franz Liszt} Erlk\"onig
  \(Searle~558, No.~4\)}.
Gidon Kremer (violin) and Oleg Maisenberg (piano).
Deutsche Grammophon, 1995 \cdnum{445 820-2}.

\cd*\relax
\artist{Schulhoff, Ervin}.
\cdtitle{Bass Nightingale}.
\see{1162}.

\cd*\relax
\artist{Schulhoff, Erwin}.
\cdtitle{Hot-Sonate}.
\see{252}.

\cd*\relax
\artist{Schulhoff, Erwin}.
\cdtitle{Susi \(Fox-Song\)}.
\see{253}.

\cd*\relax
\artist{Schuller, Gunther}.
\cdtitle{Concerto for Contrabassoon}.
\see{1162}.

\cd*\relax
\artist{Schuller, Gunther}.
\cdtitle{Eine Kleine Posaunenmusik \(1980\)}.
\see{961}.

\cd*\relax
\artist{Schulz-Evler, Adolf}.
\cdtitle{Arabesques on ``An der sch\"onen, blauen Donau''}.
\see{844}.

\cd*\relax
\artist{Schulz-Evler, Adolf}.
\cdtitle{Arabesques on ``An der sch\"onen, blauen Donau''}.
\see{952}.

\cd*\relax
\artist{Schuman, Robert}.
\cdtitle{Fantasiest\"ucke, Op.~73}.
\see{1156}.

\cd\relax
\artist{Schumann, Robert}.
Volume~1 of \emph{The Songs of Robert Schumann}.
Christine Sch\"afer (soprano) and Graham Johnson (piano).
Hyperion Records, 1996 \cdnum{CDJ33101}.

\cd\relax
\artist{Schumann, Robert}.
Volume~2 of \emph{The Songs of Robert Schumann}.
Simon Keenlyside (baritone) and Graham Johnson (piano).
Hyperion Records, 1998 \cdnum{CDJ33102}.

\cd\relax
\artist{Schumann, Robert}.
Volume~3 of \emph{The Songs of Robert Schumann}.
Juliane Banse (soprano) and Graham Johnson (piano).
Hyperion Records, 1999 \cdnum{CDJ33103}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{3 Pieces from ``Album f\"ur die Jugend'', Op.~68 \and Carnaval,
  Op.~9}.
\see{1066}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{3 Romanzen, Op.~28}.
\see{887}.

\cd\relax
\artist{Schumann, Robert}.
\cdtitle{4 Symphonies}.
Staatskapelle Dresden.
Giuseppe Sinopoli, cond.
Deutsche Grammophon, 1995 \cdnum[2]{439 923-2}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{``ABEGG'' Variations, Op.~1 \and Kinderszenen, Op.~15}.
\see{747}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{``ABEGG'' Variations, Op.~1 \and Six intermezzi for Piano,
  Op.~4}.
\see{579}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Arabeske}.
\see{1201}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Arabeske in~C, Op.~18}.
\see{643}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Arabeske in~C, Op.~18 \and Kreisleriana, Op.~16}.
\see{888}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Carnaval}.
\see{650}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Carnaval, Op.~9}.
\see{1233}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Carnaval, Op.~9}.
\see{1032}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Carnaval, Op.~9 \and Piano Concerto in A~minor, Op.~54 \and
  Symphonische Et\"uden}.
\see{770}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Cello Concerto in A~minor, Op.~129}.
\see{1510}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Cello Concerto, Op.~129}.
\see{1315}.

\cd\relax
\artist{Schumann, Robert}.
\cdtitle{Complete Piano Trios \and Piano Quintet in E~flat, Op.~44 \and
  Piano Quartet in E~flat, Op.~47}.
The Beaux Arts Trio, Dolf Bettelheim (violin) and Samuel Rhodes (viola).
Philips, 1997 \cdnum[2]{456 323-2}.

\cd\relax
\artist{Schumann, Robert}.
\cdtitle{Complete Works for Piano and Orchestra \: \track Concerto for
  Piano and Orchestra, Op.~54 \; \track Konzertst\"uck, Op.~92 \; \track
  Konzertst\"uck, Op.~134}.
Murray Perahia.
Berlin Philharmonic.
Claudio Abbado, cond.
Sony Classical, 1997 \cdnum{SK~64577}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Concerto for Cello and Orchestra, op.~129}.
\see{1003}.

\cd\relax
\artist{Schumann, Robert}.
\cdtitle{Dichterliebe, op.~48 \and Liederkreis, op.~24}.
Matthias Goerne and Vladimir Ashkenazy.
The Decca Record Company, 1998 \cdnum{289 458 265-2}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Fantasie in~C, Op.~17}.
\see{623}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Fantasie in~C, Op.~17}.
\see{44}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Fantasiest\"ucke, Op.~12}.
\see{337}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Fantasiest\"ucke, Op.~12}.
\see{1320}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Fantasiest\"ucke, Op.~12, No.~3: Warum?}
\see{140}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Fantasiestucke, Op.~73}.
\see{881}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Fantasy Pieces, Op.~73}.
\see{439}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{F\"unf St\"ucke im Volkston, op.~102}.
\see{1316}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Humoreske, Op.~20}.
\see{48}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Kinderszenen, Op.~15}.
\see{720}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Kinderszenen, Op.~15}.
\see{988}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Kreisleriana, Op.~16}.
\see{899}.

\cd\relax
\artist{Schumann, Robert}.
\cdtitle{Kreisleriana op.~16 \and Carnaval op.~9}.
Mitsuko Uchida.
Philips Classics, 1995 \cdnum{442 777-2}.

\cd\relax
\artist{Schumann, Robert}.
\cdtitle{Lieder}.
Dietrich Fischer-Dieskau (bariton) and Christoph Eschenbach (piano).
Deutsche Grammophon, 1979 \cdnum[6]{445 660-2}.

\cd\relax
\artist{Schumann, Robert}.
\cdtitle{Lieder}.
Matthias Goerne (baritone) and Eric Schneider (piano).
Decca, 2004 \cdnum{475 6012}.

\cd\relax
\artist{Schumann, Robert}.
\cdtitle{Liederkreis, op.~24 \and Dichterliebe, op.~48 \and 7 Lieder}.
Ian Bostridge (tenor) and Julius Drake (piano).
EMI Classics, 1998 \cdnum{7243 5 56575 2 7}.

\cd\relax
\artist{Schumann, Robert}.
\cdtitle{\track Liederkreis, op.~39 \; \track 12 Gedichte, op.~35}.
Matthias Goerne (baritone) and Eric Schneider (piano).
The Decca Record Company, 1999 \cdnum{289 460 797-2}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Papillons, Op.~2}.
\see{632}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Piano Concerto in A~minor, Op.~54}.
\see{1319}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Piano Concerto in A~minor, Op.~54}.
\see{967}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Piano Sonata No.~1 in F~sharp minor, Op.~111 \and Arabeske
  in~C, Op.~18}.
\see{1207}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Piano Sonata No.~2 in G~minor, Op.~22}.
\see{39}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Schlummerlied \(from ``Albumbl\"atter,'', Op.~124\)}.
\see{637}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Symphonische Et\"uden, Op.~13 \and Carnaval, Op.~9 \and
  Kreisleriana, Op.~18}.
\see{449}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Symphonische Et\"uden, Op.~13 \and Kreisleriana, Op.~16}.
\see{418}.

\cd\relax
\artist{Schumann, Robert}.
\cdtitle{Szenen aus Goethes Faust}.
The English Chamber Orchestra.
Benjamin Britten, cond.
The Decca Record Company, 1990 \cdnum[2]{425 705-2}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Three Romances for Oboe and Piano}.
\see{1664}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Toccata in~C, Op.~7}.
\see{617}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Toccata in~C, Op.~7 \and Fr\"ulingsnacht \and Der
  Kontrabandiste}.
\see{952}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Variations from Piano Sonata No.~3 in F~minor, Op.~14
  ``Concerto without Orchestra'' \and 3 Romanzen, Op.~28 \(No.~2 in
  F~sharp\)}.
\see{845}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Violin Concerto in D minor}.
\see{246}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Violin Sonata No.~1 in A~minor, Op.~105}.
\see{875}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Vogel als Prophet}.
\see{245}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Waldszenen, Op.~82 \and Fantasiest\"ucke, Op.~12 \(excerpts\}
  \and Toccata in~C, Op.~7 \and Fantasie in~C, Op.~17}.
\see{1271}.

\cd*\relax
\artist{Schumann, Robert}.
\cdtitle{Warum? \(No.~3 from Fantasiest\"ucke, Op.~12\)}.
\see{775}.

\cd*\relax
\artist{Sch\"urmann, Georg Caspar}.
\cdtitle{Suite ``Ludovicus Pius''}.
\see{10}.

\cd*\relax
\artist{Sch\"utz, Heinrich}.
\cdtitle{Geistliche Chormusik No.~28: Auf dem Gebirge hat man ein
  Geschrei geh\"ort}.
\see{73}.

\cd*\relax
\artist{Scriabin, Alexander}.
\cdtitle{2 Morceaux, Op.~57}.
\see{658}.

\cd*\relax
\artist{Scriabin, Alexander}.
\cdtitle{Etude in B~flat minor, Op.~8 No.~11 \and Nocturne in D~flat
  ``for the left hand'', Op.~9 No.~2}.
\see{1683}.

\cd*\relax
\artist{Scriabin, Alexander}.
\cdtitle{Etude, Op.~8, No.~11}.
\see{1315}.

\cd*\relax
\artist{Scriabin, Alexander}.
\cdtitle{Etudes Op.~2, No.~1, Op.~8, Nos.~5,~11, Op.~42, Nos.~2--6,~8,
  Op.~65, Nos.~1--3}.
\see{1271}.

\cd*\relax
\artist{Scriabin, Alexander}.
\cdtitle{Piano Sonata No.~3 in F~sharp minor, Op.~23 \and Piano Sonata
  No.~9, Op.~68 ``Messe noire'' \and Andante from Piano Sonata No.~2 in
  G~sharp minor, Op.~19 ``Sonata Fantasy'' \and Vers la flamme, Op.~72
  \and Deux Danses, Op.~73 \and Prelude in B~flat minor, Op.~22, No.~16
  \and Prelude in B~flat, Op.~35, No.~2 \and Prelude in B~flat, Op.~37,
  No.~1 \and Deux Po\`emes, Op.~32 \and Etude in F~sharp minor, Op.~42,
  No.~3 \and Piano Sonata No.~4 in F~sharp, Op.~30}.
\see{1484}.

\cd*\relax
\artist{Scriabin, Alexander}.
\cdtitle{Piano Sonata No.~4 in F~sharp, Op.~30}.
\see{1177}.

\cd*\relax
\artist{Scriabin, Alexander}.
\cdtitle{Piano Sonata No.~5 in F~sharp, Op.~53}.
\see{797}.

\cd*\relax
\artist{Scriabin, Alexander}.
\cdtitle{Po\`eme in F~sharp, Op.~32 No.~1 \and Prelude in~E, Op.~15
  No.~4}.
\see{637}.

\cd*\relax
\artist{Scriabin, Alexander}.
\cdtitle{Po\`eme tragique, Op~34 \and Deux Po\`emes, Op.~71}.
\see{726}.

\cd*\relax
\artist{Scriabin, Alexander}.
\cdtitle{Prometheus---the Poem of Fire}.
\see{1534}.

\cd*\relax
\artist{Scriabin, Alexander}.
\cdtitle{Sonata No.~4 in F~sharp, Op.~30 \and Etude in C~sharp minor,
  Op.~42, No.~5}.
\see{632}.

\cd\relax
\artist{Scriabin, Alexander}.
\cdtitle{The Complete Piano Sonatas}.
Marc-Andr\'e Hamelin.
Hyperion, 1995 \cdnum[2]{CDA67131/2}.

\cd\relax
\artist{Scriabin, Alexander}.
\cdtitle{The Piano Sonatas}.
Vladimir Ashkenazy.
The Decca Record Company, 1997 \cdnum[2]{452 961-2}.

\cd*\relax
\artist{Senaill\'e, Jean Baptiste}.
\cdtitle{Allegro spiritoso}.
\see{902}.

\cd\relax
\artist{Serkin, Rudolph}.
\cdtitle{Beethoven/Mozart \: \track \C{Ludwig van Beethoven} Piano
  Sonata in F~minor, Op.~57 ``Appassionata'' \; \track \C{Wolfgang
  Amadeus Mozart} Piano Concerto No.~14 in E~flat, KV~449 \and Piano
  Concerto No.~17 in~G, KV~453 \and Piano Concerto No.~12 in~A, KV~414
  \and Piano Concerto No.~16 in~D, KV~451 \and Piano Concerto No.~19
  in~F, KV~459}.
Volume~90 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 964-2}.

\cd\relax
\cdtitle{Seven Settings: Works for Saxophone by University of Iowa
  Composers \: \track \C{Luke Dahn} Prolepsis \emph{for alto sax} \;
  \track \C{Lawrence Fritts} Orthogonality \emph{for alto saxophone and
  tape} \; \track \C{Brian Vlasak} La Joie de Sax \emph{for saxophone
  quartet} \; \track \C{Scott A. Shoemaker} Sanctuary! \emph{for alto
  saxophone and piano} \; \track \C{David K. Gompper} Crossed \emph{for
  violin, saxophone and piano} \; \track \C{Rachel Foote} Aggregate~I
  \emph{for Saxophone and two-channel playback} \; \track \C{John C.
  Griffin} Suite for Solo Saxophone}.
Kenneth Tse and others.

\cd*\relax
\artist{Shaffer, Sherwood}.
\cdtitle{Sinfonia for Saxophone Quartet \(1992\)}.
\see{1146}.

\cd\relax
\artist{Shakespeare, William}.
\cdtitle{Complete Arkangel Shakespeare}.
2003 (978-1-932219-00-5).

\cd\relax
\artist{Shakespeare, William}.
\cdtitle{Hamlet}.
Complete Arkangel Shakespeare, 2003 (1-932219-08-0).

\cd\relax
\artist{Shakespeare, William}.
\cdtitle{Julius Caesar}.
Complete Arkangel Shakespeare, 2003 (1-932219-16-1).

\cd*\relax
\artist{Shaporin, Yuri}.
\cdtitle{Romance: I see you \and Elegy \and Scherzo, Op.~25, No.~5 \and
  Five pieces, Op.~25}.
\see{1315}.

\cd*\relax
\artist{Shearing, G.}
\cdtitle{Lullaby of Birdland}.
\see{716}.

\cd\relax
\artist{Sheik, Duncan and Steven Sater}.
\cdtitle{Spring Awakening}.
Decca, 2006 \cdnum{B0008020-02}.

\cd*\relax
\artist{Sheng, Bright}.
\cdtitle{Seven Tunes Heard in China}.
\see{1017}.

\cd*\relax
\artist{Shinohara, Makoto}.
\cdtitle{Fragmente}.
\see{943}.

\cd*\relax
\artist{Shinohara, Makoto}.
\cdtitle{Obsession for Oboe and Piano}.
\see{1664}.

\cd\relax
\artist{Shocked, Michelle}.
\cdtitle{Arkansas Traveler}.
PolyGram Records, 1992 \cdnum{314 512 101-2}.

\cd\relax
\artist{Shocked, Michelle}.
\cdtitle{Captain Swing}.
PolyGram Records, 1989 \cdnum{838 878-2}.

\cd\relax
\artist{Shocked, Michelle}.
\cdtitle{Short Sharp Shocked}.
PolyGram Records, 1988 \cdnum{834 924-2}.

\cd*\relax
\artist{Shoemaker, Scott A.}
\cdtitle{Sanctuary! \emph{for alto saxophone and piano}}.
\see{1429}.

\cd\relax
\artist{Shostakovich, Dmitri}.
\cdtitle{24 Preludes and Fugues, Op.~87}.
Vladimir Ashkenazy.
The Decca Record Company, 1999 \cdnum[2]{289 466 066-2}.

\cd\relax
\artist{Shostakovich, Dmitri}.
\cdtitle{\track Concerto No.~1 for Cello and Orchestra, Op.~107 \;
  \track \C{Zolt\'an Kod\'aly} Sonata for violoncello opus~8}.
Pieter Wispelwey.
Australian Chamber Orchestra.
Richard Tognetti, cond.
Channel Classics, 1999 \cdnum{CCS~15398}.

\cd\relax
\artist{Shostakovich, Dmitri}.
\cdtitle{Konzert f\"ur Violoncello und Orchester Nr.~2, op.~126 \and
  Symphonie Nr.~5 d-moll, op.~47}.
Mstislav Rostropovich.
Boston Symphony Orchestra.
Seiji Ozawa, cond.
Deutsche Grammophon, 1876/1983 \cdnum{439 481-2}.

\cd\relax
\artist{Shostakovich, Dmitri}.
\cdtitle{The String Quartets}.
The Fitzwilliam String Quartet.
The Decca Record Company, 1992 \cdnum[6]{455 776-2}.

\cd\relax
\artist{Shostakovich, Dmitri}.
\cdtitle{\track Trio No.~2 for Violin, Cello and Piano, Op.~67 \; \track
  Sonata for Cello and Piano, Op.~40}.
Yo-Yo Ma, Isaac Stern and Emanuel Ax.
CBS Records, 1988 \cdnum{MK~44664}.

\cd\relax
\artist{Shostakovich, Dmitri}.
\cdtitle{\track Violin Concerto No.~1 in A~minor, Op.~77 \(Op.~99\) \;
  \track Violin Concerto No.~2 in C~charp minor, Op.~129}.
Maxim Vengerov.
London Symphony Orchestra.
Mstislav Rostropovich, cond.
Warner Classics \cdnum{0927-46742-2}.

\cd*\relax
\artist{Shostakovich, Dmitri}.
\cdtitle{Cello Concerto No.~1, Op.~107 \and Cello Concerto No.~2,
  Op.~126 \and Cello Sonata in D~minor, Op.~40}.
\see{1315}.

\cd*\relax
\artist{Shostakovich, Dmitri}.
\cdtitle{Concerto for Violin and Orchestra No.~1 in A~minor, Op.~77}.
\see{1570}.

\cd*\relax
\artist{Shostakovich, Dmitri}.
\cdtitle{Concerto in C~minor for Piano, Trumpet and Strings, Op.~35
  \(Piano Concerto No.~1\)}.
\see{1217}.

\cd*\relax
\artist{Shostakovich, Dmitri}.
\cdtitle{Concerto No.~1 for Cello and Orchestra, Op.~107}.
\see{1014}.

\cd*\relax
\artist{Shostakovich, Dmitri Dmitrievich}.
\cdtitle{Sonata for viola and piano}.
\see{1699}.

\cd\relax
\artist{Shostakovich, Dmitry}.
\cdtitle{24 Preludes and Fugues for Piano, Op.~87}.
Tatiana Nikolaeva.
Melodiya, 1987 \cdnum[3]{74321198492}.

\cd\relax
\artist{Shostakovich, Dmitry}.
\cdtitle{Cello Concertos \: \track Cello Concerto No.~1 in E~flat major,
  Op.~107 \; \track Cello Concerto No.~2 in G~major, Op.~126}.
Maria Kliegel (cello).
Polish National Radio Symphony Orchestra (Katowice).
Antoni Wit, cond.
Naxos, 1996 \cdnum{8.550813}.

\cd\relax
\artist{Shostakovich, Dmitry}.
\cdtitle{\track Piano Concerto No.~1 in C~minor, Op.~35 \; \track Piano
  Concerto No.~2 in F, Op.~102 \; \track Concertino for Two Pianos in
  A~minor, Op.~94 \; \track Piano Trio No.~2 in E~minor, Op.~67}.
Volume~5 of \emph{Shostakovich Plays Shostakovich}.
Maxim Shostakovich (piano), David Oistrakh (violin) and Milo\v{s}
  S\'adlo (cello).
Moscow Philharmonic Orchestra and Moscow Radio Symphony Orchestra.
Revelation, 1998 \cdnum{RV70006}.

\cd\relax
\artist{Shostakovich, Dmitry}.
\cdtitle{\track Preludes and Fugues, Op.~87, Nos.~16--18, 20, 22--24 \;
  \track Three Fantastic Dances, Op.~5}.
Volume~3 of \emph{Shostakovich Plays Shostakovich}.
Revelation, 1997 \cdnum{RV70003}.

\cd\relax
\artist{Shostakovich, Dmitry}.
\cdtitle{Preludes and Fugues, Op.~87, Nos.~1--8, 12--14}.
Volume~1 of \emph{Shostakovich Plays Shostakovich}.
Revelation, 1997 \cdnum{RV70001}.

\cd\relax
\artist{Shostakovich, Dmitry}.
\cdtitle{\track Sonata for Cello and Piano in D~minor, Op.~40 \; \track
  Piano Quintet in G~minor, Op.~57}.
Volume~4 of \emph{Shostakovich Plays Shostakovich}.
Mstislav Rostropovich (cello) and Beethoven String Quartet.
Revelation, 1998 \cdnum{RV70005}.

\cd\relax
\artist{Shostakovich, Dmitry}.
\cdtitle{\track Symphony No.~10 in E~minor, Op.~93 \(arranged for piano
  duet\) \; \track Four Preludes for Violin and Piano from ``24
  Preludes,'' Op.~34 \(arranged by Dmitry Tsyganov\) \; \track Music
  from the film ``Ovod'' \(The Gadfly\), Op.~97}.
Volume~2 of \emph{Shostakovich Plays Shostakovich}.
Moisei Vainberg (piano) and Leonid Kogan (violin).
Revelation, 1997 \cdnum{RV70002}.

\cd*\relax
\artist{Shostakovich, Dmitry}.
\cdtitle{Tarantella from The Gadfly, Op.~97}.
\see{902}.

\cd*\relax
\artist{Shulman, Alan}.
\cdtitle{Theme and Variations \(1940\)}.
\see{177}.

\cd*\relax
\artist{Sibelius, Jean}.
\cdtitle{Concerto for Violin and Orchestra in D~minor, Op.~47}.
\see{1568}.

\cd\relax
\artist{Sibelius, Jean}.
\cdtitle{Concerto for Violin and Orchestra in D~minor, op.~47 \and
  Serenade for Violin and Orchestra in G~minor, op.~69, no.~2 \and En
  Saga, op.~9}.
Julian Rachlin.
Pittsburgh Symphony Orchestra.
Lorin Maazel, cond.
Sony, 1994 \cdnum{SK~53272}.

\cd\relax
\artist{Sibelius, Jean}.
\cdtitle{\track Finlandia, op.~26 \; \track Valse triste, op.~44 \;
  \track Der Schwan von Tuonela, op.~22 Nr.~3 \; \track Festivo, op.~25
  Nr.~3 \; \track Karelia-Suite, op.~11 \; \track Tapiola, op.~112}.
Berliner Philharmoniker.
Hans Rosbaud, cond.
Deutsche Grammophon, 1955/1958 \cdnum{447 453-2}.

\cd*\relax
\artist{Sibelius, Jean}.
\cdtitle{Romance, op.~78, no.~2 \and Mazurka, op.~81, no.~1}.
\see{245}.

\cd\relax
\artist{Sibelius, Jean}.
\cdtitle{The Complete Symphonies, Volume~I \: \track Symphony No.~1 in
  E~minor, Op.~39 \; \track Symphony No.~2 in D, Op.~43 \; \track
  Symphony No.~4 in A~minor, Op.~63 \; \track Symphony No.~5 in E~flat,
  Op.~82}.
Boston Symphony Orchestra.
Sir Colin Davis, cond.
The Decca Record Company, 1995 \cdnum[2]{446 157-2}.

\cd\relax
\artist{Sibelius, Jean}.
\cdtitle{The Complete Symphonies, Volume~II \: \track Symphony No.~3 in
  C~major, op.~52 \; \track Symphony No.~6 in D~minor, op.~104 \; \track
  Tapiola, op.~112 \; \track Symphony No.~5 in E~flat minor, op.~82 \;
  \track Symphony No.~7 in C~major, op.~105 \; \track En saga, op.~9.}
Philharmonia Orchestra.
Vladimir Ashkenazy, cond.
The Decca Record Company, 1997 \cdnum[2]{455 405-2}.

\cd*\relax
\artist{Sibelius, Jean}.
\cdtitle{Violin Concerto, Op.~47}.
\see{766}.

\cd\relax
\artist{Sibelius, Johan (Jean)}.
\cdtitle{Songs, Volume~2 \: \track S{\aa}ngen om korsspindeln \; \track
  Five Christmas Songs, Op.~1 \; \track Eight Songs, Op.~57 \; \track
  Hymn to Tha{\"\i}s \; \track Six Songs, Op.~72 \; \track Six Songs,
  Op.~86 \; \track Sm{\aa} flickorna}.
Monica Groop (mezzo-soprano) and Love Derwinger (piano).
BIS \cdnum{BIS-CD-657}.

\cd*\relax
\artist{Siegel, Wayne}.
\cdtitle{Sound Patterns}.
\see{960}.

\cd\relax
\artist{Siegmeister, Elie}.
\cdtitle{Piano Music, Volume~1 \: \track American Sonata \; \track On
  This Ground \; \track Theme and Variations No.~2 \; \track Piano
  Sonata No.~4 \(Prelude, Blues, Toccata\) \; \track Piano Sonata
  No.~5}.
Kenneth Boulton.
Naxos, 1999 \cdnum{8.559020}.

\cd\relax
\artist{Silly Wizard}.
\cdtitle{A Glint of Silver}.
Green Linnet, 1986 \cdnum{GLCD~1070}.

\cd\relax
\artist{Silly Wizard}.
\cdtitle{Caledonia's Hardy Sons}.
Shanachie, 1989 \cdnum{79015}.

\cd\relax
\artist{Silly Wizard}.
\cdtitle{Kiss the Tears Away}.
Shanachie Records, 1987 \cdnum{79037}.

\cd\relax
\artist{Silly Wizard}.
\cdtitle{Live Wizardry}.
Green Linnet, 1988 \cdnum{GLCD 3036/36}.

\cd\relax
\artist{Silly Wizard}.
\cdtitle{So Many Partings}.
Shanachie, 1989 \cdnum{79016}.

\cd\relax
\artist{Silly Wizard}.
\cdtitle{Wild and Beautiful}.
Shanachie Records, 1991 \cdnum{79028}.

\cd*\relax
\artist{Siloti, Alexander}.
\cdtitle{Prelude in B~minor}.
\see{644}.

\cd\relax
\artist{Simon and Garfunkel}.
\cdtitle{Bookends}.
Columbia, 1968 \cdnum{CK 9529}.

\cd\relax
\artist{Simon and Garfunkel}.
\cdtitle{Bridge over Troubled Water}.
Columbia, 1970 \cdnum{CK 9914}.

\cd\relax
\artist{Simon and Garfunkel}.
\cdtitle{Old Friends: Live on Stage}.
Warner Brothers, 2004 \cdnum[2]{2-48954}.

\cd\relax
\artist{Simon and Garfunkel}.
\cdtitle{Parsely, Sage, Rosemary and Thyme}.
Columbia, November 1966 \cdnum{CK 9363}.

\cd\relax
\artist{Simon and Garfunkel}.
\cdtitle{Sounds of Silence}.
Columbia, January 1966 \cdnum{CK 9269}.

\cd\relax
\artist{Simon and Garfunkel}.
\cdtitle{Wednesday Morning, 3AM}.
Columbia, 1964 \cdnum{CK 9049}.

\cd\relax
\artist{Simon, Carly}.
\cdtitle{No Secrets}.
Elektra/Asylum Records, 1972 \cdnum{75049-2}.

\cd\relax
\artist{Simon, Paul}.
\cdtitle{Paul Simon}.
Warner Brothers, 1972 \cdnum{25588-2}.

\cd\relax
\artist{Simon, Paul}.
\cdtitle{The Rhythm of the Saints}.
Warner Brothers, 1990 \cdnum{9 26098-2}.

\cd\relax
\artist{Simpson, Robert}.
\cdtitle{\track Canzona for Brass \(1958\) \; \track Media morte in vita
  sumus \(1975\) \; \track Tempi \(1988\) \; \track Eppur si muove
  \(1985\)}.
Iain Quinn (organ) and corydon Singers.
Corydon Brass Ensemble.
Matthew Best, cond.
Hyperion Records, 1998 \cdnum{CDA67016}.

\cd\relax
\artist{Simpson, Robert}.
\cdtitle{\track Quintet for clarinet and strings \; \track String
  Quartet No~13 \; \track String Quintet No~2}.
Galin Solodchin (violin), John Trusler (violin), John Underwood (viola),
  Johnathan Williams (cello), Christopher van Kampen (cello) and Thea
  King (clarinet).
Hyperion, 1997 \cdnum{CDA66905}.

\cd\relax
\artist{Simpson, Robert}.
\cdtitle{\track Sonata for violin and piano, 1984 \; \track Trio for
  violin, cello and piano, 1988/9}.
Pauline Lowbury (violin), Christopher Green-Armytage (piano), Ursula
  Smith (cello) and Elizabeth Burley (piano).
Hyperion Records, 1995 \cdnum{CDA66737}.

\cd\relax
\artist{Simpson, Robert}.
\cdtitle{\track String Quartet No~14 \; \track Quintet for clarinet,
  bass clarinet and string trio \; \track String Quartet No~15}.
Gregory Ellis (violin), Elizabeth Charleson (violin), Simon Aspell
  (viola), Christopher Marwood (cello), Joy Farrall (clarinet) and Fiona
  Cross (bass clarinet).
Hyperion, 1993 \cdnum{CDA66626}.

\cd\relax
\artist{Simpson, Robert}.
\cdtitle{Symphony No~10 \(1988\)}.
Royal Liverpool Philharmonic Orchestra.
Vernon Handley, cond.
Hyperion, 1991 \cdnum{CDA66510}.

\cd\relax
\artist{Simpson, Robert}.
\cdtitle{\track Symphony No~3 \(1962\) \; \track Symphony No~5
  \(1972\)}.
Royal Philharmonic Orchestra.
Vernon Handley, cond.
Hyperion, 1994 \cdnum{CDA66728}.

\cd\relax
\artist{Simpsons, The}.
\cdtitle{The Yellow Album}.
Geffen Records, 1998 \cdnum{GEFD-24480}.

\cd*\relax
\artist{Sinding, Christian}.
\cdtitle{Presto \from Suite im alten Stil, Op.~10}.
\see{1315}.

\cd*\relax
\artist{Singel\'ee, Jean-Baptiste}.
\cdtitle{Duo concertant, Op.~55}.
\see{1334}.

\cd*\relax
\artist{Singel\'ee, Jean-Baptiste}.
\cdtitle{Premier Quatuor, Op.~53 \(1857\)}.
\see{1147}.

\cd\relax
\artist{Skovhus, Bo}.
\cdtitle{Arias}.
English National Opera Orchestra.
James Conlon, cond.
Sony, 1998 \cdnum{SK~60035}.

\cd\relax
\artist{Slipknot}.
\cdtitle{Slip into Somewhere}.
SlipKnot, 1997.

\cd*\relax
\artist{Sluka, Lubos}.
\cdtitle{Sonata}.
\see{293}.

\cd\relax
\artist{Smetana, Bed\v{r}ich}.
\cdtitle{Dalibor}.
Leo Marian Vodi\v{c}ka, Eva Urbanov\'a and Ivan Kusnjer.
Prague National Theatre Chorus and Orchestra.
Zden\v{e}k Ko\v{s}ler, cond.
Supraphon, 1995 \cdnum[2]{SU 0077-2 632}.

\cd*\relax
\artist{Smetana, Bedrich}.
\cdtitle{II.~The Moldau}.
\see{526}.

\cd\relax
\artist{Smetana, Bed\v{r}ich}.
\cdtitle{M\'a Vlast}.
Czech Philharmonic Orchestra.
Rafael Kubel{\'\i}k, cond.
Supraphon, 1990 \cdnum{11 1208-2}.

\cd\relax
\artist{Smokin' Joe Kubek Band}.
\cdtitle{Got My Mind Back}.
Rounder Records, 1996 \cdnum{Bullseye Blues CD BB~9578}.

\cd\relax
\artist{Sock}.
\cdtitle{Sock}.
Sock, 1998 \cdnum{SOC.001}.

\cd\relax
\artist{Sofronitsky, Vladimir}.
\cdtitle{Chopin/Scriabin \: \track \C{Fr\'ed\'eric Chopin} Polonaise in
  C~sharp minor, Op.~26, No.~1 \and Waltz in A~flat, Op.~69, No.~1
  ``Farewell'' \and Waltz in F~minor/A~flat, Op.~70, No.~2 \and Waltz in
  D~flat, Op.~70, No.~3 \and Impromptu No.~3 in G~flat, Op.~51 \and
  Barcarolle in F~sharp, Op.~60 \and Nocturne in C~sharp minor, Op.~27,
  No.~1 \and Nocturne in D~flat, Op.~27, No.~2 \and Mazurka in C~sharp
  minor, Op.~41, No.~1 \and Mazurka in E~minor, Op.~41, No.~2 \and
  Mazurka in F~minor, Op.~63, No.~2 \and Mazurka in~C, Op.~33, No.~3
  \and Mazurka in B~minor, Op.~33, No.~4 \and Mazurka in F~minor,
  Op.~68, No.~4 \and Mazurka in B~minor, Op.~30, No.~2 \and Mazurka in
  D~flat, Op.~30, No.~3 \and Mazurka in C~sharp minor, Op.~30, No.~4
  \and Mazurka in C~sharp minor, Op.~50, No.~3 \; \track \C{Alexander
  Scriabin} Piano Sonata No.~3 in F~sharp minor, Op.~23 \and Piano
  Sonata No.~9, Op.~68 ``Messe noire'' \and Andante from Piano Sonata
  No.~2 in G~sharp minor, Op.~19 ``Sonata Fantasy'' \and Vers la flamme,
  Op.~72 \and Deux Danses, Op.~73 \and Prelude in B~flat minor, Op.~22,
  No.~16 \and Prelude in B~flat, Op.~35, No.~2 \and Prelude in B~flat,
  Op.~37, No.~1 \and Deux Po\`emes, Op.~32 \and Etude in F~sharp minor,
  Op.~42, No.~3 \and Piano Sonata No.~4 in F~sharp, Op.~30}.
Volume~91 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 970-2}.

\cd*\relax
\artist{Soler, Antonio}.
\cdtitle{Piano Sonata in C~sharp minor \and Piano Sonata in~F \and Piano
  Sonata in~D}.
\see{477}.

\cd*\relax
\artist{S\"oll, Burkhardt}.
\cdtitle{Lumen}.
\see{293}.

\cd\relax
\artist{Solomon}.
\cdtitle{Beethoven/Brahms/Chopin/Liszt/Mozart \: \track \C{Johann
  Sebastian Bach and Franz Liszt} Prelude and Fugue in A~minor, BWV~543
  \; \track \C{Wolfgang Amadeus Mozart} Piano Sonata in B~flat, KV~333
  \; \track \C{Ludwig van Beethoven} Piano Sonata in B~flat, Op.~106
  ``Hammerklavier'' \; \track \C{Fr\'ed\'eric Chopin} Berceuse in
  D~flat, Op.~57 \and Ballade No.~4 in F~minor, Op.~52 \and Fantaise in
  F~minor, Op.~49 \and Polonaise in A~flat, Op.~53 ``Heroic'' \; \track
  \C{Franz Liszt} La leggierezza \and Au bord d'une source \; \track
  \C{Johannes Brahms} Variations and Fugue on a Theme by Handel, Op.~24
  \and Intermezzo in B~flat minor, Op.~117 No.~2}.
Volume~92 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 973-2}.

\cd\relax
\artist{Sorabji, Kaikhosru Shapurji}.
\cdtitle{Gulist\=an}.
Charles Hopkins (piano).
Altarus Records, 1995 \cdnum{AIR-CD-9036}.

\cd*\relax
\artist{Sorabji, Kaikhosru Shapurji}.
\cdtitle{Pastiche on the Hindu Merchant's Song from ``Sadko'' by
  Rimsky-Korsakov}.
\see{726}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{Born in the U.S.A.}
Columbia, 1984 \cdnum{CK 38653}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{Born to Run}.
Columbia, 1975 \cdnum{CK 33795}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{Darkness on the Edge of Town}.
Columbia, 1978 \cdnum{CK 35318}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{Devils and Dust}.
Columbia, 2005 \cdnum{CN 93900}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{Greetings from Asbury Park, N.J.}
Columbia, 1973 \cdnum{CK 31903}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{Human Touch}.
Columbia, 1992 \cdnum{CK~53000}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{In Concert}.
Columbia, 1992 \cdnum{CK 68730}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{Lucky Town}.
Columbia, 1992 \cdnum{CK 53001}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{Nebraska}.
Columbia, 1982 \cdnum{CK 38358}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{The Ghost of Tom Joad}.
Columbia, 1995 \cdnum{CK~67484}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{The Rising}.
Columbia, 2002 \cdnum{CK~86600}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{The River}.
Columbia, 1980 \cdnum[2]{C2K 36854}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{The Wild, the Innocent and the E~Street Shuffle}.
Columbia, 1973 \cdnum{CK 32432}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{Tracks}.
Columbia, 1998 \cdnum[4]{CXK~69475}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{Tunnel of Love}.
Columbia, 1987 \cdnum{CK 40999}.

\cd\relax
\artist{Springsteen, Bruce}.
\cdtitle{We Shall Overcome: The Seeger Sessions}.
Columbia, 2006 \cdnum{82876 82867~2}.

\cd\relax
\artist{Springsteen, Bruce and the E Street Band}.
\cdtitle{Live 1975--85}.
Columbia, 1997 \cdnum{C3K 65328}.

\cd\relax
\artist{Sproule, D\'aith{\'\i}}.
\cdtitle{A Heart Made of Glass}.
Green Linnet, 1993 \cdnum{GLCD 1123}.

\cd\relax
\artist{Squirrel Nut Zippers}.
\cdtitle{Hot}.
Mammoth Records, 1996 \cdnum{MR0137-2}.

\cd\relax
\artist{Squirrel Nut Zippers}.
\cdtitle{Roasted Right}.
Merge Records, 1993 \cdnum{MRG~057}.

\cd\relax
\artist{Squirrel Nut Zippers}.
\cdtitle{Sold Out}.
Mammoth Records, 1997 \cdnum{MR0177-2}.

\cd\relax
\artist{Squirrel Nut Zippers}.
\cdtitle{The Inevitable}.
Mammoth Records, 1995 \cdnum{MR0105-2}.

\cd\relax
\artist{Stamitz, Carl}.
\cdtitle{Cello Concertos \: \track Concerto No.~1 in G~Major \; \track
  Concerto No.~2 in A~Major \; \track Concerto No.~3 in C~Major}.
Christian Benda (cello).
Prague Chamber Orchestra.
Naxos, 1993 \cdnum{8.550865}.

\cd*\relax
\artist{Stamitz, Carl Phillip}.
\cdtitle{Concerto in F~Major}.
\see{1162}.

\cd*\relax
\artist{Stanford, Charles Villiers}.
\cdtitle{Sonata for clarinet and piano Op~129}.
\see{894}.

\cd*\relax
\artist{Stanford, Charles Villiers}.
\cdtitle{Sonata No.~2 for Cello and Piano, Op.~39}.
\see{984}.

\cd*\relax
\artist{Starer, Robert}.
\cdtitle{Five Preludes}.
\see{719}.

\cd\relax
\artist{Starker, Janos}.
\cdtitle{\track \C{Robert Schumann} Cello Concerto in A~minor, Op.~129
  \; \track \C{Edouard Lalo} Cello Concerto in D~minor \; \track
  \C{Camille Saint-Sa\"ens} Cello Concerto in A~minor, Op.~33}.
The London Symphony Orchestra.
Stanislaw Skrowaczewski and Antal Dorati, cond.
Mercury, 1991 \cdnum{432 010-2}.

\cd\relax
\artist{Starker, Janos}.
\cdtitle{The Road to Cello Playing: Traditional Etudes and Modern
  Concert Pieces}.
Parnassus Records, 1997 \cdnum{PACD 97-008}.

\cd\relax
\artist{Starker, Janos}.
\cdtitle{Virtuoso Music for Cello}.
Nippon Columbia, 1992 \cdnum{DC-8118}.

\cd*\relax
\artist{Staude, Christoph}.
\cdtitle{Obduktion}.
\see{578}.

\cd*\relax
\artist{Stein, Herman}.
\cdtitle{Sour Suite}.
\see{1687}.

\cd*\relax
\artist{Sternberg, Erich Walter}.
\cdtitle{Etude No.~3 in C~minor, Op.~120}.
\see{775}.

\cd\relax
\artist{Steve Miller Band, The}.
\cdtitle{Greatest Hits 1974--78}.
Capitol Records, 1978 \cdnum{CDP~7 46101~2}.

\cd\relax
\artist{Stewart, Andy M.}
\cdtitle{By the Hush}.
Green Linnet, 1983 \cdnum{GLCD 3030}.

\cd\relax
\artist{Stewart, Andy M.}
\cdtitle{Donegal Rain}.
Green Linnet, 1997 \cdnum{GLCD 1183}.

\cd\relax
\artist{Stewart, Andy M.}
\cdtitle{Man in the Moon}.
Green Linnet, 1994 \cdnum{GLCD 1140}.

\cd\relax
\artist{Stewart, Andy M.}
\cdtitle{Songs of Robert Burns}.
Green Linnet, 1991 \cdnum{GLCD 3059}.

\cd\relax
\artist{Stewart, Andy M., Phil Cunningham and Manus Lunny}.
\cdtitle{Fire in the Glen}.
Shanachie Records, 1989 \cdnum{79062}.

\cd\relax
\artist{Stewart, Andy M. and M\'anus Lunny}.
\cdtitle{At It Again}.
Green Linnet, 1990 \cdnum{GLCD 1107}.

\cd\relax
\artist{Stewart, Andy M. and Manus Lunny}.
\cdtitle{Dublin Lady}.
Green Linnet, 1987 \cdnum{GLCD 1083}.

\cd\relax
\artist{Stewart, Rod}.
\cdtitle{Every Picture Tells a Story}.
PolyGram Records, 1971 \cdnum{822 385-2}.

\cd*\relax
\artist{Still, William Grant}.
\cdtitle{Romance \(1966\)}.
\see{1601}.

\cd\relax
\artist{Stock, Jeffrey}.
\cdtitle{Lulie the Iceberg}.
Sam Waterston (narrator), Pamela Frank (violin), Yo-Yo Ma (cello) and
  Paul Winter (soprano saxophone).
Sony Classical, 1999 \cdnum{SK~61665}.

\cd*\relax
\artist{Stockhausen, Karlheinz}.
\cdtitle{In Freundschaft f\"ur Solo-Posaune, Werke~46$12\over13$}.
\see{964}.

\cd*\relax
\artist{Stockhausen, Karlheinz}.
\cdtitle{Tierkreis}.
\see{1524}.

\cd\relax
\artist{Stockhausen, Markus}.
\cdtitle{New Colours of Piccolo Trumpet \: \track \C{Johann Friedrich
  Fasch} Konzert D-dur f\"ur Trompete, 2 Oboen, Streicher und Basso
  continuo \; \track \C{Bernhard Krol} Magnificat-Variationen f\"ur
  Trompete und Streichorchester, op.~40 \; \track \C{Leopold Mozart}
  Konzert d-dur f\"ur Trompete, H\"orner und Streicher \; \track
  \C{Johann Sebastian Bach} Brandenburgisches Konzert Nr.~2 F-dur
  BWV~1047 f\"ur Trompete, Fl\"ote, Oboe, Violine, Streicher und Basso
  continuo}.
Detmolder Kammerorchester.
Christoph Poppen, cond.
EMI Classics, 1993 \cdnum{7243 5 55022 2~3}.

\cd\relax
\artist{Stockhausen, Markus and Margareta H\"urholz}.
\cdtitle{New Colours of Trumpet and Organ \: \track \C{Heinz Martin
  Lonquich} Preisungen \; \track \C{Andr\'e Jolivet} Arioso barocco \;
  \track \C{Karlheinz Stockhausen} Tierkreis}.
EMI Classics, 1993 \cdnum{7243 5 55023 2~2}.

\cd*\relax
\artist{Straus, Richard}.
\cdtitle{Don Juan, Symphonic Poem for Orchestra, op.~20 \and Till
  Eulenspiegels lustige Streiche, op.~28}.
\see{628}.

\cd*\relax
\artist{Strauss, Johann}.
\cdtitle{Arabesques on ``An der sch\"onen, blauen Donau''}.
\see{844}.

\cd*\relax
\artist{Strauss, Johann}.
\cdtitle{Arabesques on ``An der sch\"onen, blauen Donau''}.
\see{952}.

\cd*\relax
\artist{Strauss, Johann}.
\cdtitle{Arabesques on ``An der sch\"onen, blauen Donau'' \and Wein,
  Weib und Gesang, Op.~333}.
\see{418}.

\cd*\relax
\artist{Strauss, Johann}.
\cdtitle{Man lebt nur einmal \(Valse caprice, Op.~167 No.~2\)}.
\see{1233}.

\cd*\relax
\artist{Strauss, Johann}.
\cdtitle{Symphonic Metamorphosis on Themes from ``Die Fledermaus''}.
\see{623}.

\cd*\relax
\artist{Strauss, Richard}.
\cdtitle{An einsamer Quelle \from Stimmungsbilder, Op.~9 \and Don
  Quixote, Op.~35}.
\see{1315}.

\cd*\relax
\artist{Strauss, Richard}.
\cdtitle{Burleske}.
\see{716}.

\cd\relax
\artist{Strauss, Richard}.
\cdtitle{\track Don Quixote, Op.~35 \; \track Die Liebe der Danae,
  Op.~83}.
Yo-Yo Ma (cello) and Burton Fine (viola).
Boston Symphony Orchestra.
Seiji Ozawa, cond.
CBS Records, 1990 \cdnum{MDK~45804}.

\cd\relax
\artist{Strauss, Richard}.
\cdtitle{Ein Heldenleben, op.~40 \and Also Sprach Zarathustra, op.~30
  \and Don Juan, op.~20 \and Till Eulenspiegel, op.~28 \and Eine
  Alpensinfonie, op.~64}.
Sir Georg Solti, cond.
The Decca Record Company, 1994 \cdnum[2]{440 618-2}.

\cd*\relax
\artist{Strauss, Richard}.
\cdtitle{Five Piano Pieces, Op.~3}.
\see{658}.

\cd\relax
\artist{Strauss, Richard}.
\cdtitle{Lieder}.
Dietrich Fischer-Dieskau (bariton) and Wolfgang Sawallisch (piano).
Deutsche Grammophon, 1984 \cdnum[2]{447 512-2}.

\cd\relax
\artist{Strauss, Richard}.
\cdtitle{Lieder}.
Dietrich Fischer-Dieskau and Gerald Moore.
EMI Records, 1991 \cdnum[6]{CMS~7 63995~2}.

\cd\relax
\artist{Strauss, Richard}.
\cdtitle{Music for Wind Ensemble \(complete\) \: \track Serenade for
  Wind Instruments, Op.~7 \; \track Suite in B~flat for 13 Wind
  Instruments, Op.~4 \; \track Sonatine No.~1 in~F for Wind Instruments
  \(``From an Invalid's Workshop''\) \; \track Symphony for Wind
  Instruments \(``The Happy Workshop''\) \; \track Oboe Concerto in~D}.
Heinz Holliger (oboe).
Netherlands Wind Ensemble/New Philharmonia Orchestra.
Edo de Waart, cond.
The Decca Record Company, 1993 \cdnum[2]{438 733-2}.

\cd*\relax
\artist{Strauss, Richard}.
\cdtitle{St\"andchen}.
\see{623}.

\cd\relax
\artist{Strauss, Richard}.
\cdtitle{Vier Letzte Lieder \and Orchesterlieder}.
Jessye Norman (soprano).
Gewandhausorchester Leipzig.
Kurt Masur, cond.
Philips, 1983 \cdnum{411 052-2}.

\cd*\relax
\artist{Stravinsky, Igor}.
\cdtitle{3 Movements from ``Petrouchka''}.
\see{644}.

\cd*\relax
\artist{Stravinsky, Igor}.
\cdtitle{3 Movements from ``Pretrouchka''}.
\see{1683}.

\cd*\relax
\artist{Stravinsky, Igor}.
\cdtitle{Concerto for Piano and Wind Instruments}.
\see{930}.

\cd*\relax
\artist{Stravinsky, Igor}.
\cdtitle{Danse Russe \emph{from} P\'etrouchka}.
\see{929}.

\cd*\relax
\artist{Stravinsky, Igor}.
\cdtitle{Duo Concertant}.
\see{875}.

\cd\relax
\artist{Stravinsky, Igor}.
\cdtitle{Fireworks, Fantasy for Orchestra \and The Firebird \and Tango
  \and Scherzo \`a la Russe \and The Song of the Nightingale}.
The London Symphony Orchestra.
Antal Dorati, cond.
Mercury, 1991 \cdnum{432 012-2}.

\cd\relax
\artist{Stravinsky, Igor}.
\cdtitle{P\'etrouchka \and Le Sacre du printemps}.
New York Philharmonic and the Cleveland Orchestra.
Pierre Boulez, cond.
Sony, 1994 \cdnum{SMK~64 109}.

\cd*\relax
\artist{Stravinsky, Igor}.
\cdtitle{Petrouchka \(Three movements\)}.
\see{1207}.

\cd*\relax
\artist{Stravinsky, Igor}.
\cdtitle{Russian Song \(Parasha's Aria\) \from Mavra \and Pas de deux
  \from Le baiser de la f\'ee}.
\see{1315}.

\cd\relax
\artist{Stravinsky, Igor}.
\cdtitle{Symphonies and Concertos \: \track Symphony in~C \; \track
  Symphony in Three Movements \; \track Symphonies for Wind Instruments
  \; \track Violin Concerto in~D \; \track Ebony Concerto \; \track
  Symphonie de Psaumes}.
Philips Classics, 1994 \cdnum[2]{442 583-2}.

\cd\relax
\artist{Stravinsky, Igor}.
\cdtitle{The Firebird \(L'oiseau de feu\) \and \C{Alexander Scriabin}
  Prometheus---the Poem of Fire}.
Alexander Toradze (piano).
Kirov Orchestra.
Valery Gergiev, cond.
Philips, 1998 \cdnum{289 446 715-2}.

\cd\relax
\artist{Stravinsky, Igor}.
\cdtitle{The Rake's Progress}.
Deborah York, Ian Bostridge, Bryn Terfel and Anne Sofie von Otter.
The Monteverdi Choir and the London Symphony Orchestra.
John Eliot Gardiner, cond.
Deutsche Grammophon, 1999 \cdnum[2]{289 459 648-2}.

\cd*\relax
\artist{Stravinsky, Igor}.
\cdtitle{Three Pieces for Clarinet Solo}.
\see{439}.

\cd*\relax
\artist{Stravinsky, Igor}.
\cdtitle{Violin Concerto in D~major}.
\see{433}.

\cd\relax
\artist{Stravinsky, Igor and Charles-Ferdinand Ramuz}.
\cdtitle{\track The Soldier's Tale \; \track Concerto in E~flat
  \(Dumbarton Oaks\)}.
Northen Chamber Orchestra.
Nicholas Ward, cond.
Naxos, 1998 \cdnum{8.553662}.
English version by Michael Flanders and Kitty Black.

\cd*\relax
\artist{Suber, Stephen}.
\cdtitle{Angels}.
\see{719}.

\cd\relax
\artist{Suk, Josef}.
\cdtitle{\track A Summer's Tale \; \track A Winter's Tale}.
Slovak Radio Symphony Orchestra.
Andrew Mogrelia, cond.
Naxos, 1999 \cdnum{8.553703}.

\cd\relax
\artist{Sweet Honey in the Rock}.
\cdtitle{Still on the Journey}.
Earthbeat! Records, 1993 \cdnum{9 42536-2}.

\cd\relax
\artist{Syrewicz, Stanislas}.
\cdtitle{Russia's War: Blood upon the Snow}.
Dmitri Hvorostovsky.
State Symphonic Orchestra of Cinematography, Cantus Dei Choir of Moscow,
  and the Red Army Choir.
Sergei Skripka, cond.
Philips Classics, 1996 \cdnum{454 181-2}.

\cd\relax
\artist{Szeryng, Henryk}.
\cdtitle{\track \C{Ludwig van Beethoven} Sonata in D~major, Op.~12 No.~1
  \; \track \C{Johannes Brahms} Sonata in G~major, Op.~78 \; \track
  \C{Johann Sebastian Bach} Partita BWV~1004 \(with ``Ciaccona''\)}.
Eugenio Bagnoli (piano).
Aura \cdnum{AUR 203-2 ADD}.

\cd*\relax
\artist{Tabakov, Emil}.
\cdtitle{Motivy for Double Bass Solo}.
\see{619}.

\cd\relax
\artist{Tahitian Choir, The}.
\cdtitle{Rapa Iti}.
Soulitude Records, 1999/2004 \cdnum{TC S-1204-2}.

\cd\relax
\artist{Taieb, Walter}.
\cdtitle{The Alchemist's Symphony}.
BMG Entertainment, 1998 \cdnum{09026-63157-2}.

\cd*\relax
\artist{Ta{\"\i}ra, Yoshihisa}.
\cdtitle{P\'enombres~VI}.
\see{483}.

\cd*\relax
\artist{Takemitsu, T\=oru}.
\cdtitle{Distance}.
\see{483}.

\cd*\relax
\artist{Takemitsu, T\=oru}.
\cdtitle{Distance de F\'ee}.
\see{875}.

\cd\relax
\artist{Tallis Scholars, The}.
\cdtitle{Silver: The Best of the Tallis Scholars}.
Gimell, 1998 \cdnum[2]{289 454 990-2}.

\cd\relax
\artist{Tan Dun}.
\cdtitle{Crouching Tiger, Hidden Dragon}.
Yo-Yo Ma (cello) and CoCo Lee (vocals).
Sony Classical, 2000 \cdnum{SK~89347}.

\cd\relax
\artist{Tan Dun}.
\cdtitle{Hero}.
Itzhak Perlman (violin).
Sony Classical, 2004 \cdnum{SK~87726}.

\cd\relax
\artist{Tan Dun}.
\cdtitle{Marco Polo: An Opera within an Opera}.
Thomas Young, Alexandra Montano, Dong-Jian Gong, Susan Botti, Shi-Zheng
  Chen, Nina Warren and Stephen Bryant.
The Netherlands Radio Kamerorkest and the Cappella Amsterdam.
Tan Dun, cond.
Sony, 1997 \cdnum[2]{S2K~62912}.

\cd\relax
\artist{Tan Dun}.
\cdtitle{Water Passion}.
Elizabeth Keusch (soprano), Stephen Bryant (bass), Mark O'Connor
  (violin), Maya Beiser (cello), David Cossin (percussion), Martin
  Homann (percussion), Adam Weisman (percussion) and Sarah Ioannides
  (choir director).
RIAS-Kammerchor Berlin.
Tan Dun, cond.
Sony Classical, 2002 \cdnum[2]{S2K~89927}.

\cd*\relax
\artist{Tanada, Fuminori}.
\cdtitle{Mysterious Morning~III}.
\see{483}.

\cd*\relax
\artist{Tanaka, Karen}.
\cdtitle{Night Bird}.
\see{483}.

\cd\relax
\artist{Tan~Dun}.
\cdtitle{Bitter Love}.
Ying Huang (soprano).
New York Virtuoso Singers and NChiCa-Orchestra.
Tan~Dun, cond.
Sony Classical, 1999 \cdnum{SK~61658}.

\cd\relax
\artist{Tan~Dun}.
\cdtitle{Ghost Opera}.
Kronos Quartet and Wu Man.
Nonesuch Records, 1997 \cdnum{79445-2}.

\cd\relax
\artist{Tan~Dun}.
\cdtitle{\track On Taoism \; \track Orchestral Theatre~I \; \track Death
  and Fire---Dialogue with Paul Klee}.
BBC Scottish Symphony Orchestra.
Tan~Dun, cond.
Koch/Schwann, 1993 \cdnum{3-1298-2}.

\cd\relax
\artist{Tan~Dun}.
\cdtitle{\track Out of Peking Opera for solo violin and orchestra \;
  \track Death and Fire: Dialogue with Paul Klee \; \track Orchestral
  Theatre~II: Re for divided orchestra, bass voice and audience with two
  conductors}.
Cho-Liang Lin (violin) and Kalevi Olli (bass).
Helsinki Philharmonic Orchestra.
Muhai Tang and Kari Kropsu, cond.
Ondine, 1998 \cdnum{ODE 864-2}.

\cd\relax
\artist{Tan~Dun}.
\cdtitle{Snow in June \: \track Circle with Four Trios, Conductor and
  Audience \; \track Eight Colors for String Quartet \; \track Silk Road
  \; \track In Distance \; \track Elegy: Snow in June}.
Composers Recordings, 1993 \cdnum{CD~655}.

\cd\relax
\artist{Tan~Dun}.
\cdtitle{Symphony 1997: Heaven Earth Mankind}.
Yo-Yo Ma (cello).
Yips Children's Choir, Imperial Bells Ensemble of China, and the Hong
  Kong Philharmonia Orchestra.
Tan~Dun, cond.
Sony Classical, 1997 \cdnum{SK~63368}.

\cd*\relax
\artist{Taneiev, Sergei}.
\cdtitle{Canzona}.
\see{1315}.

\cd\relax
\artist{Tannahill Weavers, The}.
\cdtitle{Arnish Light}.
Green Linnet, 2003 \cdnum{GLCD 1226}.

\cd\relax
\artist{Tannahill Weavers, The}.
\cdtitle{Capernaum}.
Green Linnet, 1994 \cdnum{GLCD 1146}.

\cd\relax
\artist{Tannahill Weavers, The}.
\cdtitle{Cullen Bay}.
Green Linnet, 1990 \cdnum{GLCD 1108}.

\cd\relax
\artist{Tannahill Weavers, The}.
\cdtitle{Land of Light}.
Green Linnet, 1985 \cdnum{GLCD 1067}.

\cd\relax
\artist{Tannahill Weavers, The}.
\cdtitle{Passage}.
Green Linnet, 1984 \cdnum{GLCD~3031}.

\cd\relax
\artist{Tannahill Weavers, The}.
\cdtitle{The Mermaid's Song}.
Green Linnet, 1992 \cdnum{GLCD 1121}.

\cd\relax
\artist{Tara}.
\cdtitle{Boys in the Lane}.
ARC Music, 1991 \cdnum{EUCD 1019}.

\cd\relax
\artist{Tara}.
\cdtitle{Rigs of the Time}.
ARC Music \cdnum{EUCD 1006}.

\cd\relax
\artist{Tara}.
\cdtitle{Sammy's Bar}.
ARC Music, 1998 \cdnum{EUCD 1451}.

\cd*\relax
\artist{Tartini, Giuseppe}.
\cdtitle{Concerto in D~major}.
\see{1314}.

\cd\relax
\artist{Tartini, Giuseppe}.
\cdtitle{The Devil's Sonata and other works \: \track ``La Sonata del
  Diavolo'' in G~minor \; \track from ``L'arte del arco'' \; \track
  Sonata in A~minor \; \track ``Pastorale'' for violin in scordatura}.
Andrew Manze.
Harmonia Mundi, 1997 \cdnum{HMU 907213}.

\cd*\relax
\artist{Tausig, Carl}.
\cdtitle{Marche militaire}.
\see{900}.

\cd*\relax
\artist{Tausig, Carl}.
\cdtitle{Pastorale e capriccio \and Marche militaire No.~1 in~D \(\from
  D.~733\)}.
\see{775}.

\cd*\relax
\artist{Tausig, Karl}.
\cdtitle{Der Kontrabandiste}.
\see{952}.

\cd\relax
\artist{Tavener, John}.
\cdtitle{\track Eternity's Sunrise \; \track Song of the Angel \; \track
  Petra: A Ritual Dream \; \track Sappho: Lyrical Fragments \; \track
  Funeral Canticle}.
Patricia Rozario (soprano), Julia Gooding (soprano), George Mosley
  (baritone) and Andrew Manze (violin).
The Choir and Orchestra of the Academy of Ancient Music.
Paul Goodwin, cond.
Harmonia Mundi, 1999 \cdnum{HMU 907231}.

\cd\relax
\artist{Tavener, John}.
\cdtitle{The Protecting Veil \and Wake Up\dots and Die}.
Yo-Yo Ma.
Baltimore Symphony Orchestra.
David Zinman, cond.
Sony, 1998 \cdnum{SK~62821}.

\cd*\relax
\artist{Taverner, John}.
\cdtitle{Kyrie ``Le Roy'' \and Mass ``The Western Wind'' \and Dum
  transisset sabbatum \and Christe Jesu pastor bone \and Mater Christi}.
\see{389}.

\cd\relax
\artist{Tchaikovsky, Peter}.
\cdtitle{\track 1812 Overture \; \track Overture-Fantasy \; \track
  Marche Slave \; \track Romeo and Juliet}.
New York Philharmonic.
Leonard Bernstein, cond.
CBS Records, 1985 \cdnum{MYK~36723}.

\cd*\relax
\artist{Tchaikovsky, Peter}.
\cdtitle{Andante cantabile \and Variations on a Rococo Theme}.
\see{1144}.

\cd\relax
\artist{Tchaikovsky, Peter}.
\cdtitle{\track Concerto for Piano and Orchestra No.~1 in B-flat Minor,
  Op.~23 \; \track Concerto for Violin and Orchestra in D~Major,
  Op.~35}.
Emil Gilels (piano) and David Oistrakh (violin).
New York Philharmonic and The Philadelphia Orchestra.
Zubin Mehta and Eugene Ormandy, cond.
Sony Classical, 1990 \cdnum{SBK~46339}.

\cd\relax
\artist{Tchaikovsky, Peter}.
\cdtitle{\track Concerto for Violin and Orchestra in D~major, Op.~35 \;
  \track \C{Jean Sibelius} Concerto for Violin and Orchestra in D~minor,
  Op.~47}.
Isaac Stern.
Philadelphia Orchestra.
Eugene Ormandy, cond.
Sony Classical, 1959/1970/1995 \cdnum{SMK 66~829}.

\cd\relax
\artist{Tchaikovsky, Peter}.
\cdtitle{The Ultimate Nutcracker: Tchaikovsky's Greatest Hit}.
with Susan Scott and Chorus Spike Jones and his City Slickers, James
  Galway (flute) and Modern Mandolin Quartet.
Philadelphia Orchestra.
Eugene Ormandy, cond.
RCA Victor \cdnum{82876-62821-2}.

\cd*\relax
\artist{Tchaikovsky, Peter}.
\cdtitle{Violin Concerto, Op.~35}.
\see{766}.

\cd*\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Concert Suite from ``The Nutcracker'' \(arr.~Pletnev\) \and
  Romance in F~minor, Op.~5 \and Valse-Scherzo in~A, Op.~7 \and
  Capriccio in G~flat, Op.~8 \and Les saisons, Op.~37b \(The Months\)
  \and Music from ``The Sleeping Beauty'' \and Piano Concerto No.~2
  in~G, Op.~44}.
\see{1203}.

\cd\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Concerto for Violin and Orchestra in D~major, Op.~35 \:
  \C{Dmitri Shostakovich} Concerto for Violin and Orchestra No.~1 in
  A~minor, Op.~77}.
Ilya Gringolts.
Israel Philharmonic Orchestra.
Itzhak Perlman, cond.
Deutsche Grammophon, 2002 \cdnum{289 471 616-2}.

\cd\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Concerto for Violin and Orchestra in D~major, op.~35 \:
  \C{Erich Wolfgang Korngold} Concerto for Violin and Orchestra in
  D~major, op.~35}.
Anne-Sophie Mutter.
Wiener Philharmoniker and London Symphony Orchestra.
Andr\'e Previn, cond.
Deutsche Grammophon, 2004 \cdnum{B0003526-02}.

\cd*\relax
\artist{Tchaikovsky, Piotr Ilich}.
\cdtitle{Marche miniature \and Marche slave}.
\see{1137}.

\cd*\relax
\artist{Tchaikovsky, Piotr Ilich}.
\cdtitle{Nocturne, Op.~19, No.~4 in D~minor}.
\see{929}.

\cd*\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Novembre: Tro{\"\i}ka \(from ``Les saisons,'' Op.~37b\)}.
\see{1233}.

\cd*\relax
\artist{Tschaikowsky, Peter I.}
\cdtitle{Overture 1812, Op.~36}.
\see{299}.

\cd*\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Piano Concerto No.~1 in B~flat inor, Op.~23 \and Juin:
  Barcarolle \(\from ``Les Saisons,'' Op.~37b\) \and Mars: Chant de
  l'alouette \(\from ``Les saisons,'' Op.~37b\)}.
\see{435}.

\cd*\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Piano Concerto No.~1 in B~flat minor, Op.~23}.
\see{1319}.

\cd*\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Piano Concerto No.~1 in B~flat minor, Op.~23}.
\see{845}.

\cd*\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Piano Concerto No.~1 in B~flat minor, Op.~23 \and Piano
  Concerto No.~2 in~G, Op.~44}.
\see{418}.

\cd*\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Piano Concerto No.~2 in~G, Op.~44}.
\see{644}.

\cd*\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Polonaise from ``Eugene Onegin'' \arr{Franz Liszt} \and
  ``Eugene Onegin'' Paraphrase \arr{Paul Pabst} \and Grande Sonate in~G,
  Op.~37}.
\see{645}.

\cd\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Symphonies 1--6 \and ``Manfred'' Symphony \and Romeo and Juliet
  \and Francesca da Rimini}.
The London Philharmonic Orchestra.
Mstislav Rostropovich, cond.
EMI Records, 1995 \cdnum[5]{7243 5 65709 2~4}.

\cd*\relax
\artist{Tschaikowsky, Peter Iljitsch}.
\cdtitle{Symphony No.~6 in B~flat major, op.~67 Path\'etique}.
\see{626}.

\cd\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{The Best of Tchaikovsky \: \track Piano Concerto No.~1 in
  B~flat minor, Op.~23 \; \track Serenade for Strings in~C, Op.~48 \;
  \track Capriccio italien, Op.~45 \; \track The Nutcracker, Op.~71a:
  Waltz of the Flowers \; \track Valse-Scherzo, Op.~34 \; \track Swan
  Lake, Op.~20 \; \track The Sleeping Beauty, Op.~66 \; \track Violin
  Concerto in~D, Op.~35 \; \track Ouverture solennelle "1812", Op.~49}.
Philips Classics \cdnum[2]{438 386-2}.

\cd\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{\track The Nutcracker \; \track \C{Jacques Offenbach} Le
  Papillon}.
National Philharmonic Orchestra and London Symphony Orchestra.
Richard Bonynge, cond.
The Decca Record Company, 1995 \cdnum[2]{444 827-2}.

\cd*\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Th\`eme original et variations, Op.~19, No.~6}.
\see{632}.

\cd*\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Trepak}.
\see{952}.

\cd*\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{Variationen \"uber ein Rokoko-Thema f\"ur Violoncello und
  Orchester, op.~33}.
\see{511}.

\cd*\relax
\artist{Tchaikovsky, Pyotr Ilyich}.
\cdtitle{Variations on a Rococo Theme, Op.~33}.
\see{1315}.

\cd*\relax
\artist{Tchaikovsky, Pyotr Ilyich}.
\cdtitle{Violin Concerto in D major, op.~35}.
\see{246}.

\cd\relax
\artist{Tchaikovsky, Peter Ilyich}.
\cdtitle{\track Violin Concerto \(Op.~35\) \; \track \C{Johannes Brahms}
  Hungarian Dances}.
Sarah Chang.
Sir Colin Davis, cond.
EMI Records, 1993 \cdnum{CDC 54753 2~6}.

\cd\relax
\artist{Tchaikovsky, Piotr Ilich}.
\cdtitle{\track Violin Concerto in D~major, Op.~35 \; \track
  S\'er\'enade m\'elancollque, Op.~26 \; \track Waltz \(from Skerenade,
  Op.~48\) \; \track \C{Felix Mendelssohn} Violin Concerto in E~minor,
  Op.~64}.
Jascha Heifetz (violin).
Chicago Symphony Orchestra and Boston Symphony Orchestra.
Fritz Reiner and Charles Munch, cond.
BMG Classics, 1995 \cdnum{09026-61743-2}.
Recorded 1957, 1959, 1970.

\cd\relax
\artist{Tchaikovsky, Piotr Ilytch}.
\cdtitle{\track Violin Concerto in D~major, Op.~35 \; \track
  S\'er\'enade M\'elancolique, Op.~26}.
Itzhak Perlman.
The Philadelphia Orchestra.
Eugene Ormandy, cond.
EMI Records, 1979 \cdnum{CDC 7 47106~2}.

\cd\relax
\artist{Tcherepnin, Alexander}.
\cdtitle{Complete Music for Cello and Piano \: \track Cello Sonata
  No.~1, Op.~29 \; \track Cello Sonata No.~2, Op.~30 No.~1 \; \track
  Cello Sonata No.~3, Op.~30 No.~2 \; \track The Well-Tempered Cello,
  Op.~38 \; \track Songs and Dances, Op.~84 \; \track Ode}.
Chandos Records, 1999 \cdnum{CHAN~9770}.

\cd*\relax
\artist{Tcherepnin, Alexander}.
\cdtitle{Suite for Solo Cello}.
\see{1017}.

\cd\relax
\artist{Teldec Classics}.
\cdtitle{Teldec Classics---Fall~98/Spring~99}.
Teldec Classics, 1998 \cdnum{1744}.

\cd*\relax
\artist{Telemann, G. Ph.}
\cdtitle{Fantasy No.~1 in A~major for Oboe Solo \and Fantasy No.~3 in
  B~minor for Oboe Solo \and Suite in G~minor for Oboe and Basso
  Continuo from ``Der getreue Music-Meister''}.
\see{784}.

\cd\relax
\artist{Telemann, Georg Philipp}.
\cdtitle{6 Paris Quartets \: \track Quatuor No.~1 in D~major \; \track
  Quatuor No.~2 in A~minor \; \track Quatuor No.~3 in G~major \; \track
  Quatuor No.~4 in B~minor \; \track Quatuor No.~5 in A~major \; \track
  Quatuor No.~6 in E~minor}.
Wilbert Hazelzet (flauto traverso), Monica Huggett (violin), Sarah
  Cunningham (viola da gamba), Gary Cooper (harpsichord) and Mitzi
  Meyerson (harpsichord).
Veritas, 2000 \cdnum[2]{7243~5~61812~2~9}.

\cd*\relax
\artist{Telemann, Georg Philipp}.
\cdtitle{Concerto a quattro violini senza basso}.
\see{619}.

\cd*\relax
\artist{Telemann, Georg Philipp}.
\cdtitle{Concerto in C~minor}.
\see{965}.

\cd*\relax
\artist{Telemann, Georg Philipp}.
\cdtitle{Concerto in D~major \and Concerto in F~minor}.
\see{1139}.

\cd*\relax
\artist{Telemann, Georg Philipp}.
\cdtitle{Concerto in E~flat major for Oboe, Strings and Continuo \and
  Concerto in B~major for two Flutes, two Oboes, Strings and Continuo}.
\see{783}.

\cd*\relax
\artist{Telemann, Georg Philipp}.
\cdtitle{Die Hoffnung ist mein Leben}.
\see{69}.

\cd\relax
\artist{Telemann, Georg Philipp}.
\cdtitle{Six Sonatas for two flutes, Op.~2}.
Stephen Schultz and Mindy Rosenfeld (baroque flutes).
American Baroque.
Naxos, 1998 \cdnum{8.554132}.

\cd\relax
\artist{Telemann, Georg Philipp}.
\cdtitle{Trio Sonatas \: \track Partita~2 in G~major \; \track Sonata in
  G~minor \; \track Adabio from Oboe Concerto in D-Minor \; \track Suite
  in G~minor \; \track Sonata in A~minor \; \track Triosonata in E~major
  \; \track Trisonata in D~minor}.
Bart Schneemann (baroque oboe), Menno van Delft (harpsichord), Siebe
  Henstra (organ), Pieter Wispelwey (baroque cello) and Frans Robert
  Berkhout (baroque bassoon).
Channel Classics, 2000 \cdnum{CCS~14098}.

\cd\relax
\artist{Telemann, Georg Philipp}.
\cdtitle{Trios and Quartets from ``Tafelmusik''}.
Musica Antiqua K\"oln.
Reinhard Goebel, cond.
Deutsche Grammophon, 1989 \cdnum{447-296-2}.

\cd\relax
\artist{Telemann, Georg Philipp}.
\cdtitle{Twelve Fantasias for Violin Solo \and Gulliver Suite for Two
  Violins}.
Andrew Manze and Caroline Balding.
Harmonia Mundi, 1995 \cdnum{HMU 907137}.

\cd\relax
\artist{Telemann, Georg Philipp}.
\cdtitle{Twelve Fantasies for Violin Solo}.
Rachel Podger.
Channel Classics, 2002 \cdnum{CCS~18298}.

\cd\relax
\artist{Telemann, Georg Philipp and Musique de Table \(Tafelmusik\)}.
\cdtitle{\track Trio in E~flat major \; \track Solo Sonata in B~minor
  for flute and continuo \; \track Conclusion \; \track Overture
  \(Suite\) in D~major \(Tafelmusic Part~II\)}.
Volume~2.
Orchestra of the Golden Age.
Naxos, 1999 \cdnum{8.553725}.

\cd\relax
\artist{Telemann, Georg Philipp and Musique de Table \(Tafelmusik\)
  Part~III}.
\cdtitle{\track Overture \(Suite\) in B~flat major \; \track Quartet in
  E~minor \; \track Concerto in E~flat major for two horns and strings
  \; \track Trio in D~major \; \track Solo sonata in G~minor for oboe
  and continuo \; \track Conclusion in B~flat major}.
Volume~4.
Orchestra of the Golden Age.
Naxos, 1999 \cdnum{8.553732}.

\cd\relax
\artist{Telson, Bob and Lee Breuer}.
\cdtitle{The Gospel at Colonus}.
Elektra/Nonesuch, 1988 \cdnum{9~79191-2}.

\cd*\relax
\artist{Thomas, August Read}.
\cdtitle{Meditation for Trombone and Orchestra}.
\see{962}.

\cd*\relax
\artist{Thomas, David Bennett}.
\cdtitle{Rondo Capricioso for Alto Saxophone and Piano}.
\see{23}.

\cd*\relax
\artist{Thomys, Alojzy}.
\cdtitle{Ten Miniatures in different styles}.
\see{253}.

\cd\relax
\artist{Thunemann, Klaus}.
\cdtitle{Romantic Bassoon Rarities \: \track \C{Franz Berwald} Concert
  Piece in~F for bassoon and orchestra \; \track \C{Johann Wenzel
  Kalliwoda} Variatons and Rondo in B~flat for bassoon and orchestra \;
  \track \C{Conradin Kreutzer} Varations in B~flat for bassoon and
  orchestra \; \track \C{Edward Elgar} Romance, Op.~62 for bassoon and
  orchestra \; \track \C{Ferdinand David} Concertino in B~flat, Op.~12
  for bassoon and orchestra \; \track \C{Bernhard Crusell} Concertino in
  B~flat for bassoon and orchestra}.
Academy of St~Martin in the Fields.
Sir Neville Marriner, cond.
Philips Classics, 1995 \cdnum{446 096-2}.

\cd\relax
\artist{Tiersen, Yann}.
\cdtitle{Good Bye, Lenin!}
Virgin Records, 2004 \cdnum{7243 5 91609 2 4}.

\cd\relax
\artist{Tippet, Michael}.
\cdtitle{A Child of Our Time}.
Faye Robinson (soprano), Sarah Walker (mezzo soprano), Jon Garrison
  (tenor) and John Cheek (bass).
City of Birmingham Symphony Orchestra and Chorus.
Sir Michael Tippet, cond.
Collins, 1992 \cdnum{13392}.

\cd\relax
\artist{Tir Na Nog}.
\cdtitle{Tir Na Nog}.
Chrysalis Records, 1971/1992 \cdnum{BGOCD53}.

\cd*\relax
\artist{Tishchenko, Boris}.
\cdtitle{Concerto for cello, seventeen wind instruments, percussion and
  organ, Op.~23}.
\see{1315}.

\cd*\relax
\artist{Tomasi, Henri}.
\cdtitle{Concerto for Trumpet and Orchestra}.
\see{1138}.

\cd*\relax
\artist{Torke, Michael}.
\cdtitle{July}.
\see{50}.

\cd*\relax
\artist{Torke, Michael}.
\cdtitle{July \(1995\)}.
\see{1147}.

\cd*\relax
\artist{Torke, Michael}.
\cdtitle{Saxophone Concerto}.
\see{1053}.

\cd\relax
\artist{Touchstone}.
\cdtitle{Jealousy}.
Green Linnet, 1984 \cdnum{GLCD~1050}.

\cd\relax
\artist{Touchstone}.
\cdtitle{The New Land}.
Green Linnet, 1982 \cdnum{GLCD 1040}.

\cd*\relax
\artist{Toyama, Yuzo}.
\cdtitle{Cello Concerto}.
\see{1315}.

\cd\relax
\cdtitle{Toys}.
Geffen Records, 1992 \cdnum{GEFD-24505}.

\cd\relax
\cdtitle{Traditional Fiddle Music of Cape Breton, Volume~1: Mabou Coal
  Mines}.
Gregory Campbell, Alex Francis MacKay, Rannie MacLellan, Johnny MacLeod,
  Fr. Angus Morris and Gordon MacLean (piano).
Rounder Records, 2002 \cdnum{82161-7037-2}.

\cd*\relax
\artist{Traille, Gregory La}.
\cdtitle{Quintet for Oboe and String Quartet}.
\see{432}.

\cd\relax
\artist{Trenchcoats, The}.
\cdtitle{Exposed}.

\cd\relax
\artist{Trio Indiana}.
\cdtitle{Trio Indiana \: \track \C{Jean-Michele Defaye} Six Pi\`eces
  D'Audition \; \track \C{Peter Schickele} Dances for Three \; \track
  \C{Gary Kulesha} Political Implications \; \track \C{Michael Kibbe}
  Ebony Suite \; \track \C{Frederick Fox} Time Weaving}.
James Campbell, Eli Eban and Howard Klug.
Crystal Records, 1996 \cdnum{CD734}.

\cd*\relax
\artist{Troilo, Annibal}.
\cdtitle{Contrabajando}.
\see{830}.

\cd\relax
\artist{Trudel, Alain and Patrick Wedd}.
\cdtitle{The Art of the Trombone \: \track \C{Gustav Holst} Duet for
  trombone and organ \; \track \C{Ernst Schiffmann} Intermezzo, Op.~53
  \; \track \C{Otto H\"oser} Romanze \; \track \C{Alexandre Guilmant}
  Morceau symphonique \and Chorale \(Kirchenordnung Braunschweig\) \;
  \track \C{Franz Liszt} Hosannah \; \track \C{Bernhard Krol} Sinfonia
  sacra ``Jesu, meine Freude'', Op.~56 \; \track \C{Friedrich August
  Belcke} Fantasia, Op.~58 \; \track \C{Harald Genzmer} Sonata}.
Naxos, 1999 \cdnum{8.553716}.

\cd\relax
\artist{Tschaikowsky, Peter}.
\cdtitle{Concerto for Violin and Orchestra in D~major, Op.~35}.
Anne-Sophie Mutter.
Wiener Philharmoniker.
Herbert von Karajan, cond.
Deutsche Grammophon, 1988 \cdnum{419 241-2}.

\cd\relax
\artist{Tse, Kenneth}.
\cdtitle{\track \C{David DeBoor Canfield} Sonata for Alto Saxophone and
  Piano \(2000\) \; \track \C{John Cheetham} Sonata for Alto Saxophone
  and Piano \(2001\) \; \track \C{Libby Larsen} Holly roller \(1997\) \;
  \track \C{William Grant Still} Romance \(1966\) \; \track \C{Leonard
  Mark Lewis} As in Stained Light \(2002\) \; \track \C{Jay Vosk} Thaw
  \(1994\) \; \track \C{Walter Hartley} Sonata for Baritone Saxophone
  and Piano \(1976\)}.
Mami Nagai (piano) and Leonard Mark Lewis (piano).
Crystal Records, 2002 \cdnum{CD657}.

\cd\relax
\artist{Tse, Kenneth}.
\cdtitle{In Memory \: \track \C{Johann Sebastian Bach} Sonata in
  E~major, BWV~1035 \; \track \C{Joseph Canteloube} Chants d'Auvergne \;
  \track \C{Alfred Reed} Ballade \; \track \C{Karel Husa} El\'egie et
  Roundeau \; \track \C{Eug\`ene Bozza} Aria \; \track \C{J\'er\^ome
  Naulais} Frissons \; \track \C{Samuel Barber} Souvenirs}.
Hayashida Kazuyuki (soprano saxophone), Yoshiyuki Hattori (Tenor
  Saxophone), Karl Miller (piano), Mami Nagai (piano) and Mariko Hattori
  (piano).
Enharmonic, 2000 \cdnum{ENCD00-014}.

\cd\relax
\artist{Tse, Kenneth}.
\cdtitle{\track \C{Jind\u{r}ich Feld} Sonata for Alto Saxophone and
  Piano \; \track \C{Walter Kaufmann} Meditation \; \track \C{Robert
  Muczynski} Sonata Op.~29 \; \track \C{Warren Benson} Aeolian Song \;
  \track \C{Bernhard Heiden} Solo for Alto Saxophone and Piano \; \track
  \C{Victor Morosco} Blue Caprice \; \track \C{Leonard Bernstein} West
  Side Story Medley}.
Kari Miller (piano).
Crystal Records, 1998 \cdnum{CD656}.

\cd\relax
\artist{Tse, Kenneth}.
\cdtitle{Lyric Soprano \: \track \C{Antonino Pasculli} Le Api \; \track
  \C{Gabriel Faur\'e} Troi Romances sans Paroles \; \track \C{J\'er\^ome
  Naulais} Sax de Voyage \; \track \C{Isaac Alb\'eniz} Tango, Op.~165,
  No.~2 \; \track \C{Denis B\'edard} Fantaisie \; \track \C{John C.
  Worley} Six Dances \; \track \C{Astor Piazzolla} Prelude \(for Kenneth
  Tse\) \; \track \C{Leonard Mark Lewis}}.
Alan Huckleberry (piano).
Crystal Records, 2005 \cdnum{CD658}.

\cd\relax
\artist{Tse, Kenneth}.
\cdtitle{\c{S}\=ona\d{t}e \: \track \C{David Maslanka} Sonata for Alto
  Saxophone and Piano \; \track \C{Camille Saint-Saens} Sonata for Oboe
  and Piano, Op.~166 \; \track \C{Jeanine Rueff} Sonata for Alto
  Saxophone \; \track \C{John C. Worley} Sonata for Alto Saxophone and
  Piano}.
Su-Yen Chee (piano) and Daniel Michalak (piano).
RIAX, 1998 \cdnum{RICA-2002}.

\cd\relax
\artist{Tse, Kenneth (saxophone), Benjamin Coelho (bassoon) and Alan
  Huckleberry (piano)}.
\cdtitle{Pas de Trois \: \track \C{Bernard van Beurden} Pas de trois \;
  \track \C{Jindrich Feld} Trio Giocoso \; \track \C{David Froom}
  Arirang Variations \; \track \C{Perry Goldstein} Noir \; \track \C{Don
  Freund} Lounder than Words}.
Crystal Records, 2006 \cdnum{CD358}.

\cd\relax
\artist{Tureck, Rosalyn}.
\cdtitle{Bach \: \track ``Goldberg'' Variations, BWV~988 \; \track
  French Overture \(Partita\) in B~minor, BWV~831 \; \track Italian
  Concerto in~F, BWV~971 \; \track Four Duets, BWV802--805}.
Volume~94 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1999 \cdnum[2]{456 979-2}.

\cd\relax
\artist{Tureck, Rosalyn}.
\cdtitle{Bach \: \track Partita No.~1 in B~flat, BWV~825 \; \track
  Partita No.~2 in C~minor, BWV~826 \; \track Partita No.~3 in A~minor,
  BWV~827 \; \track Partita No.~4 in~D, BWV~828 \; \track Partita No.~5
  in~G, BWV~829 \; \track Partita No.~6 in E~minor, BWV~830}.
Volume~93 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 976-2}.

\cd*\relax
\artist{Tveitt, Geirr}.
\cdtitle{Fifty Folk Tunes from Hardanger, Op.~150}.
\see{28}.

\cd*\relax
\artist{Uccellini, Marco}.
\cdtitle{Sinfonia Nona a tre violini from \emph{Opus~9}}.
\see{1184}.

\cd\relax
\artist{Uccellini, Marco}.
\cdtitle{Sonatas}.
Romanesca, Andrew Manze (violin), archlute, and Baroque guitar Nigel
  North (theorbo) and John Toll (harpsichord and organ).
Harmonia Mundi, 1999 \cdnum{HMX 907196}.

\cd\relax
\artist{Uchida, Mitsuko}.
\cdtitle{Debussy/Mozart/Schoenberg \: \track \C{Wolfgang Amadeus Mozart}
  10 Variations in~G, KV~455 on ``Unser dummer P\"obel meint'' \(C. W.
  Gluck\) \and Rondo in A~minor, KV~511 \and Piano Sonata in~D, KV~576
  \and Adagio in B~minor, KV~540 \and Piano Concerto No.~9 in E~flat,
  KV~271 ``Jeunehomme'' \; \track \C{Claude Debussy} Douz Etudes pour
  piano \; \track \C{Arnold Schoenberg} Drei Klavierst\"ucke, Op.~11}.
Volume~95 of \emph{Great Pianists of the 20th Century}.
English Chamber Orchestra.
Jeffrey Tate, cond.
Philips Classics, 1998 \cdnum[2]{456 982-2}.

\cd\relax
\artist{Umebayashi, Shigeru}.
\cdtitle{House of Flying Daggers}.
Sony Classical, 2004 \cdnum{SK~93561}.

\cd\relax
\artist{Uncle Bonsai}.
\cdtitle{A Lonely Grain of Corn}.
Yellow Tail Records, 1984/2001 \cdnum{YT-10019}.

\cd\relax
\artist{Uncle Bonsai}.
\cdtitle{Apology}.
Yellow Tail Records, 2001 \cdnum{YT-10017}.

\cd\relax
\artist{Uncle Bonsai}.
\cdtitle{Boys Want Sex in the Morning}.
Freckle Records, 1986 \cdnum{FRCD1911}.

\cd\relax
\artist{Uncle Bonsai}.
\cdtitle{Doug}.
Electric Bonsai Band and Mel Cooley's.
Yellow Tail Records, 1999 \cdnum{YT-10010}.

\cd\relax
\artist{Uncle Bonsai}.
\cdtitle{Myn ynd Wymyn}.
Yellow Tail Records, 1992 \cdnum{YT-10003}.

\cd\relax
\artist{Uncle Bonsai}.
\cdtitle{Plain Brown Wrapper: Unreleased Songs 1984--1989}.
Yellow Tail Records, 1999 \cdnum{YT-10013}.

\cd\relax
\artist{Uncle Bonsai}.
\cdtitle{The Inessential Uncle Bonsai!}
Yellow Tail Records, 1992 \cdnum{YT-10002}.

\cd\relax
\artist{Universal Classics}.
\cdtitle{The Age of Elegance \: \track \C{Luigi Boccherini} Minuet
  \from\ String Quintet in E~Major, Op.~13, No.~5 \; \track \C{Roman
  Hoffstetter} Andante cantabile \from\ String Quartet in F~Major
  ``Serenade'' \; \track \C{Michael Haydn} Adagio \from\ Notturno in
  F~Major, P.~106 \; \track \C{Franz Xavier Pokorny} Quintet No.~4 for
  Guitar and Strings in D~Major, G.~448 ``Fandango'' \and Symphony No.~3
  in C~Major, Op.~12}.
Universal Classics/Phillips, 2004 \cdnum{B0002180-02}.

\cd*\relax
\artist{Ustvolskaya, Galina}.
\cdtitle{Grand Duet}.
\see{1315}.

\cd\relax
\artist{Utah Saxophone Quartet, The}.
\cdtitle{Playing Tribute: A Nod to the Paris and the Hollywood Saxophone
  Quartets}.
Tantara Records, 2005 \cdnum{TCD0205USQ}.

\cd*\relax
\artist{Vainberg, Mieczys{\l}aw}.
\cdtitle{Cello Concerto, Op.~43}.
\see{1315}.

\cd*\relax
\artist{Vainberg, Moissei}.
\cdtitle{Concerto for Trumpet and Orchestra, Op.~94}.
\see{1143}.

\cd\relax
\artist{Vajda, J\'anos}.
\cdtitle{String Quartets and Sonatas \: \track String Quartet No.~1 \;
  \track Piano Sonata \; \track Sonata for Violin and Piano \; \track
  String Quartet No.~2}.
Danubius String Quartet, M\'arta Erdei (piano), Eszter Per\'enyi
  (violin), Sarolta Hars\'anyi (piano) and New Haydn String Quartet.
Hungaroton, 1999 \cdnum{HCD 31797}.

\cd*\relax
\artist{Valen, Fartein}.
\cdtitle{Variations for piano, Op.~23}.
\see{28}.

\cd*\relax
\artist{Valitsky, Ken}.
\cdtitle{Saxomaphone \(1998\)}.
\see{1146}.

\cd*\relax
\artist{Vallier, John}.
\cdtitle{Toccatina}.
\see{724}.

\cd*\relax
\artist{Vanhal, Johann B.}
\cdtitle{Concerto in F~Major}.
\see{1164}.

\cd*\relax
\artist{Vanherenthals, Jacques}.
\cdtitle{Varium et mutabile for Four Double Basses}.
\see{619}.

\cd\relax
\artist{Vaovy}.
\cdtitle{Vamba}.
Label Bleu, 1998 \cdnum{LBLC 2537}.

\cd\relax
\artist{Various}.
\cdtitle{Festival of Irish Music}.
The Dubliners, Golden~Bough, Noel McLoughlin and Tara.
ARC Music, 1991 \cdnum{EUCD 1156}.

\cd\relax
\artist{Various}.
\cdtitle{Festival of Irish Music}.
Golden~Bough, Noel McLoughlin, Tara, Sean Talamh and Pied~Pipers.
ARC Music, 1994 \cdnum{DRC VGR 9001}.

\cd\relax
\artist{Various}.
\cdtitle{Festival of Irish Music, Volume~II}.
The Dubliners, Golden~Bough, Noel McLoughlin and Tara.
ARC Music, 1991 \cdnum{EUCD 1160}.

\cd\relax
\artist{Various}.
\cdtitle{Festival of Irish Music, Volume~III}.
Oisin, Golden~Bough, the Dubliners, Noel McLoughlin, Tara and
  Pied~Pipers.
ARC Music, 1992 \cdnum{EUCD 1212}.

\cd\relax
\artist{Various}.
\cdtitle{Festival of Irish Music, Volume~IV}.
Golden~Bough, the Dubliners, Tara, Sean Talamh, Noel McLoughlin,
  Pied~Pipers and Margie Butler.
ARC Music, 1994 \cdnum{EUCD 1278}.

\cd\relax
\artist{Various}.
\cdtitle{Folk 'n' Hell: Fiery New Music from Scotland}.
EMI Premier, 1996 \cdnum{7243 8 53344 2~9}.

\cd\relax
\artist{Various}.
\cdtitle{The Music Never Stopped: Roots of the Grateful Dead}.
Shanachie Entertainment, 1995 \cdnum{6014}.
Compiled by Henry Kaiser and David Gans.

\cd\relax
\artist{V\"arttin\"a}.
\cdtitle{Live in Helsinki}.
Northside, 2002 \cdnum{NSD6066}.

\cd\relax
\artist{Vaughan Williams, Ralph}.
\cdtitle{\track A Pastoral Symphony \(Symphony No.~3\) \; \track
  Symphony No.~4}.
London Philharmonic Orchestra.
Bernard Haitink, cond.
EMI Classics, 1998 \cdnum{7243 5 56564~2~1}.

\cd\relax
\artist{Vaughan Williams, Ralph}.
\cdtitle{\track Symphony No.~6 in E~minor \; \track In the Fen Country
  \; \track On Wenlock Edge}.
Ian Bostridge (tenor).
London Philharmonic Orchestra.
Bernard Haitink, cond.
EMI Classics, 1999 \cdnum{7243 5 56762~2~1}.

\cd\relax
\artist{Vaughan Williams, Ralph}.
\cdtitle{The Wasps \(excerpts\) \and The Lark Ascending \and Fantasia on
  a Theme by Thomas Tallis \and Fantasia on ``Greensleaves'' \and
  English Folk Song Suite}.
Jonathan Carney (solo violin).
Royal Philharmonic Orchestra.
Christopher Seaman, cond.
Platinum Entertainment, 1996 \cdnum{2836}.

\cd*\relax
\artist{Veldhuis, Jacob ter}.
\cdtitle{the Garden of Love}.
\see{1344}.

\cd\relax
\cdtitle{Veracini, Francesco Maria \: \track Sonata No.~1 from
  \emph{Sonate a violino solo e basso op.~1} \; \track Sonata No.~5 from
  \emph{Sonate a violio, o flauto solo, e basso} \; \track Sonata No.~1
  from \emph{Dissertazioni\ldots sopra l'opera quinta del Corelli} \;
  \track Sonata No.~6 from \emph{Sonate accademiche op.~2}}.
John Holloway (violin), Jaap ter Linden (violoncello) and Lars Ulrik
  Mortensen (harpsichord).
ECM Records, 2005 \cdnum{B0004233-02}.

\cd*\relax
\artist{Verbey, Theo}.
\cdtitle{Passamezzo}.
\see{51}.

\cd\relax
\artist{Verdi, Giuseppe}.
\cdtitle{Il Trovatore}.
Leontyne Price, Placido Domingo, Sherril Milnes and Fiorenza Cossotto.
New Philharmonia Orchestra and The Ambrosian Opera Chorus.
Zubin Mehta, cond.
RCA, 1970 \cdnum[2]{6194-2-RC}.

\cd\relax
\artist{Verdi, Giuseppe}.
\cdtitle{Rigoletto}.
Edita Gruberova, Brigitte Fassbaender, Neil Shicoff, Renato Bruson and
  Robert Lloyd.
Coro e Orchestra dell'Accademia Nazionale.
Giuseppe Sinopoli, cond.
Philips Classics, 1985/1998 \cdnum[2]{289 462 158-2}.

\cd*\relax
\artist{Verdi, Giuseppe}.
\cdtitle{Streichquartett e-moll \and Luisa Miller}.
\see{721}.

\cd*\relax
\artist{Veress, S\'andor}.
\cdtitle{Sonatina per violoncello e pianoforte \and Sonata per
  violoncello}.
\see{804}.

\cd\relax
\artist{Verve, The}.
\cdtitle{A Northern Soul}.
VC Records, 1995 \cdnum{7243~8 40437~2 8}.

\cd\relax
\artist{Verve, The}.
\cdtitle{Urban Hymns}.
Virgin Records, 1997 \cdnum{7243 8 44913 2~1}.

\cd*\relax
\artist{Vieuxtemps, Henri}.
\cdtitle{Cantilena, Op.~48, No.~24}.
\see{902}.

\cd\relax
\artist{Vieuxtemps, Henry}.
\cdtitle{\track Violin Concerto No.~2 in F~Sharp Minor, Op.~19 \; \track
  Violin Concerto No.~3 in A~Major, Op.~25}.
Misha Keylin (violin).
Jan\'a\v{c}ek Philharmonic Orchestra.
Dennis Burkh, cond.
Naxos, 1997 \cdnum{8.554114}.

\cd\relax
\artist{Villa-Lobos, Heitor}.
\cdtitle{\track As Tr\^es Marias \; \track A Prole do Beb\^e---Suite
  No~1 \; \track A Prole do Beb\^e---Suite No~2 \; \track Rudepo\^ema}.
Marc-Andr\'e Hamelin.
Hyperion, 2000 \cdnum{CDA67176}.
Recorded in Henry Wood Hall, London, on 27 August (\emph{Rudepo\^ema})
  and 6--7 October 1999.

\cd*\relax
\artist{Villa-Lobos, Heitor}.
\cdtitle{Bachianas brasileiras No.~5}.
\see{396}.

\cd*\relax
\artist{Villa-Lobos, Heitor}.
\cdtitle{Bachianas Brasileiras No.~6}.
\see{881}.

\cd*\relax
\artist{Villa-Lobos, Heitor}.
\cdtitle{Fantasia for soprano saxophone and chamber orchestra}.
\see{744}.

\cd\relax
\artist{Villa-Lobos, Heitor}.
\cdtitle{Instrumental and Orchestral Works}.
EMI Records, 1998 \cdnum{7243 5 72670 2~1}.

\cd*\relax
\artist{Villa-Lobos, Heitor}.
\cdtitle{Prel\'udio \(Modhina\) \from Bachianas Brasileiras No.~1 for
  eight cellos}.
\see{1315}.

\cd\relax
\artist{Villaz\'on, Rolando}.
\cdtitle{Italian Opera Arias}.
M\"unchner Rundfunkorchester.
Marcello Viotti, cond.
EMI Records, 2004 \cdnum{7243 5 45626 2~4}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Cello Concerti, Volume~1 \: \track Concerto in F~Major, RV~412
  \; \track Concerto in A~Minor, RV~419 \; \track Concerto in D~Major,
  RV~404 \; \track Concerto in C~Major, RV~399 \; \track Concerto in
  D~Minor, RV~406 \; \track Concerto in C~Major, RV~398 \; \track
  Concerto in F~Major, RV~410}.
Raphael Wallfisch (cello).
City of London Sinfonia.
Nicholas Kraemer, cond.
Naxos, 1995 \cdnum{8.550907}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Cello Concerti, Volume~2 \: \track Concerto in C~Major, RV~400
  \; \track Concerto in C~Minor, RV~401 \; \track Concerto in E~Flat
  Major, RV~408 \; \track Concerto in G~Major, RV~413 \; \track Concerto
  in A~Minor, RV~422 \; \track Concerto in G~Minor for two cellos,
  RV~531}.
Raphael Wallfisch (cello).
City of London Sinfonia.
Nicholas Kraemer, cond.
Naxos, 1995 \cdnum{8.550908}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Cello Concerti, Volume~3 \: \track Concerto in C~Minor, RV~402
  \; \track Concerto in D~Major, RV~403 \; \track Concerto in D~Minor,
  RV~407 \; \track Concerto in E~Minor, RV~409 \; \track Concerto in
  A~Minor, RV~418 \; \track Concerto in B~Flat Major, RV~423 \; \track
  Concerto in B~Minor, RV~424}.
Raphael Wallfisch (cello).
City of London Sinfonia.
Nicholas Kraemer, cond.
Naxos, 1995 \cdnum{8.550909}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Cello Concerti, Volume~4 \: \track Concerto in D~Minor, RV~405
  \; \track Concerto in F~Major, RV~411 \; \track Concerto in G~Major,
  RV~414 \; \track Concerto in G~Minor, RV~416 \; \track Concerto in
  G~Minor, RV~417 \; \track Concerto in A~Minor, RV~420 \; \track
  Concerto in A~Minor, RV~421}.
Raphael Wallfisch (cello).
City of London Sinfonia.
Nicholas Kraemer, cond.
Naxos, 1995 \cdnum{8.550910}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Concert for the Prince of Poland \: \track Sinfonia in G~major,
  RV~149 \; \track Violin Concerto in E-flat major, ``La tempesta di
  Mare,'' op.~VIII, no.~5, RV~253 \; \track Concerto in D~minor, RV~540
  \; \track Concerto in A~major, RV~552 \; \track Violin Concerto in
  C~major, ``Il piacere,'' op.~VIII, no.~6, RV~180 \; \track Concerto in
  C~major, RV~558}.
The Academy of Ancient Music.
Andrew Manze, cond.
Harmonia Mundi, 1997 \cdnum{HMU~907230}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Concerti per fagotto, archi e continuo \: \track Concerto in Mi
  bem magg., RV~483 \; \track Concerto in Fa magg., RV~485 \; \track
  Concerto in La min., RV~497 \; \track Concerto in Si bem. magg.,
  RV~501 \; \track Concerto in La min., RV~498 \; \track Concerto in Mi
  Min., RV~484 \; \track Concerto in Si bem. magg., RV~502}.
Paolo Carlini (fagotto) and Alberto Martini (1st violino).
Accademia I Filarmonici de Verona.
Tactus, 2004 \cdnum{TC 672240}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Concerti per fagotto e oboe \: \track Concerto in D~minor per
  fagotto, archi e basso continuo, RV481 \; \track Concerto in A~minor
  per oboe, archi e basso continuo, RV461 \; \track Concerto in G~major
  per oboe e fagotto, archi e basso continuo, RV545 \; \track Concerto
  in A~minor per fagotto, archi e basso continuo, RV498 \; \track
  Concerto in C~major per oboe, archi e basso continuo, RV451 \; \track
  Concerto in B~flat major per fagotto, archi e basso continuo, RV501
  ``Le Notte''}.
Volume~3 of \emph{Concerti per strumenti a fiato}.
Sergio Azzolini (fagotto) and Hans Peter Westermann (oboe).
Sonatori de la Gioiosa Marca, cond.
Opus111, 2004 \cdnum{OP~30379}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Concerti per mandolini; Concerti con molti strumenti \: \track
  Concerto RV~532 for 2 mandolins \; \track Concerto RV~558 for 2
  violini in tromba marina, 2 recorders, 2 mandolines, 2 chalumeux, 2
  theorbos and cello \; \track Concerto RV~576 for violin, 2 recorders,
  3 oboes and bassoon \; \track Concerto RV~564 for 2 violins, 2 cellos
  and strings \; \track Concerto RV~319 for solo violin, 2 oboes, basson
  and strings \; \track Concerto RV~425 for mandoline \; \track Concerto
  RV~555 for 3 violins, oboe, 2 recorders, 2 viole all'inglese,
  chalumeau, 2 cellos, 2 harpsichords and 2 violini in tromba marina}.
Europa Galante.
Fabio Bondi, cond.
Virgin/Veritas/EMI, 2002 \cdnum{7243~5 45527 2~4}.

\cd*\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Concerto in B~flat major}.
\see{1139}.

\cd*\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Concerto in C~major for two oboes, two clarinets and strings,
  RV560 \and Concerto in F~major for solo oboe, RV455 \and Concerto in
  C~major for two oboes, two clarinets and strings, RV559}.
\see{13}.

\cd*\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Concerto in D~minor, RV~406}.
\see{1314}.

\cd*\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Concerto in G~minor for Two Cellos, Strings and Basso Continuo,
  RV~531 \and Concerto in B-flat Major for Cello, Strings and Basso
  Continuo, RV~423 \and Concerto for Viola D'Amore, Lute and Orchestra,
  RV~540 \and Concerto in C~minor for Cello, Strings and Basso Continuo,
  RV~401}.
\see{1020}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Concertos for Oboe, Strings and Basso continuo \: \track
  Concerto F.~VII No.~4 in C~major, RV~451 \; \track Concerto F.~VII
  No.~5 in A~minor, RV~461 \; \track Concerto F.~VII No.~11 in C~major,
  RV~450 \; \track Concerto F.~VII No.~12 in F~major, RV~457 \; \track
  Concerto F.~VII No.~13 in AC~minor, RV~463 \; \track Concerto F.~VII
  No.~16 in F~major, RV~456}.
Hansj\"org Schellenberger (oboe).
Franz Liszt Chamber Orchestra, cond.
Sony, 1995 \cdnum{SK~66~271}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Concertos for the Emperor \: \track Concerto No.~2 in C~major,
  RV~189 \; \track Concerto No.~10 in E~major, RV~271 ``L'amoroso'' \;
  \track Concerto No.~3 in C~minor, RV~202 \; \track Concerto No.~7 in
  C~major, RV~183 \; \track Concerto No.~11 in E~minor, RV~277 ``Il
  favorito'' \; \track Concerto No.~4 in F~major, RV~286}.
Andrew Manze (solo violin and director).
The English Concert.
Harmonia Mundi, 2004 \cdnum{HMU 907332}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Flute Concertos \: \track Concerto in A minor, RV~108 \; \track
  Concert in D~Major, RV~84 \; \track Concert in G~Major, RV~102 \;
  \track Concert in D~Major, RV~89 \; \track Sonata in D~minor ``La
  Follia'', RV~63 \; \track \C{Francesco Mancini} Sonata in E~minor \and
  Sonata in D~minor \; \track \C{Francesco Barbella} Sonata in C~major}.
Gudrun Heyens (recorder), Wilbert Hazelzet (transverse flute), Reinhard
  Goebel (violin) and Hajo B\"ass (violin).
Musica Antiqua K\"oln.
Reinhard Goebel, cond.
Deutsche Grammophon, 1978/1981 \cdnum{471 729-2}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Gloria in D~major, RV~588 \and Gloria in D~major, RV~589 \and
  Magnificat in G~minor, RV~610 \and Dixit Dominus in D~major, RV~594
  \and Beatus vir in C~major, RV~597}.
The Decca Record Company, 1994 \cdnum[2]{443 455-2}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Gloria in D~major, RV~589 \and Nisi Dominus, RV~608 \and Nulla
  in mundo pax sincera, RV~630 \and Amor, hai vinto, RV~651 \and Trio
  Sonata ``La folia'', RV~63 \and All'ombra di sospetto, RV~673 \and
  Lungi dal vago volto, RV~680 \and Vengo a voi, luci adorate, RV~682}.
The Decca Record Company, 1997 \cdnum[2]{455 727-2}.

\cd*\relax
\artist{Vivaldi, Antonio}.
\cdtitle{``Inverno'' from the Four Seasons, Op.~8 No.~4}.
\see{965}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{La Stravaganza, op.~4}.
Academy of St~Martin-in-the-Fields.
Sir Neville Marriner, cond.
The Decca Record Company, 1995 \cdnum[2]{444 821-2}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{L'estro armonico---12 Concertos, op.~3 \and Concerto in F~major
  for oboe, RV~456 \and Concerto in A~minor for bassoon, RV~498 \and
  Concerto in C~minor for flute, RV~441 \and Concerto in F~major for 2
  oboes, bassoon, 2 horns and violin, RV~574}.
Academy of St~Martin-in-the-Fields.
Sir Neville Marriner, cond.
The Decca Record Company, 1994 \cdnum[2]{443 476-2}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{``Manchester'' Sonata for Violin and Continuo \(Nos.~I--VI\)}.
Romanesca, Andrew Manze (violin), Nigel North (chitarrone and chitarra
  alla spagnola) and John Toll (harpsichord and organ).
Harmonia Mundi, 1993 \cdnum{HMU 907089}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{``Manchester'' Sonata for Violin and Continuo
  \(Nos.~VII--XII\)}.
Romanesca, Andrew Manze (violin), Nigel North (chitarrone and chitarra
  alla spagnola) and John Toll (harpsichord and organ).
Harmonia Mundi, 1993 \cdnum{HMU 907090}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Six Cello Concertos \: \track Concerto in C~minor, RV~401 \;
  \track Concerto in F~major, RV~412 \; \track Concerto in G~major,
  RV~413 \; \track Concerto in G~minor, RV~416 \; \track Concerto in
  A~minor, RV~418 \; \track Concerto in B~minor, RV~424}.
Christophe Coin (cello).
The Academy of Ancient Music.
Christopher Hogwood, cond.
The Decca Record Company, 1989 \cdnum{421 732-2}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{The Four Seasons, Op.~8 \and Sinfonia ``Al Santo Sepolcro''
  \and Concerto Op.~2, No.~10}.
Jeanne Lamon.
Tafelmusik.
Jeanne Lamon, cond.
Sony, 1992 \cdnum{SK~48 251}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{The Ultimate Four Seasons: Vivaldi's Greatest Hit}.
Vladimir Spivakov (violin), James Galway (flute), Michala Petri
  (recorder), Gottfried von der Goltz (Baroque violin), Kazuhito
  Yamashita and Larry Coryell (guitars), Tracy Scott Silverman (violin),
  Ransom Wilson (flute), Amsterdam Guitar Trio and Modern Mandolin
  Quartet.
RCA Victor \cdnum{09026-64015-2}.

\cd\relax
\artist{Vivaldi, Antonio}.
\cdtitle{Violin Concertos, Op.~6 \: \track Concerto No.~1 in G~minor,
  RV~324 \; \track Concerto No.~2 in E~flat minor, RV~259 \; \track
  Concerto No.~3 in G~minor, RV~318 \; \track Concerto No.~4 in D~major,
  RV~216 \; \track Concerto No.~5 in E~minor, RV~280 \; \track Concerto
  No.~6 in D~minor, RV~329 \; \track Concerto in A~major, RV~335 ``The
  Cuckoo''}.
Andrew Manze (violin).
The Academy of Ancient Music.
Christopher Hogwood, cond.
The Decca Record Company, 2000 \cdnum{455 653-2}.

\cd*\relax
\artist{Vlasak, Brian}.
\cdtitle{La Joie de Sax \emph{for saxophone quartet}}.
\see{1429}.

\cd\relax
\artist{Vogel, Allan}.
\cdtitle{Oboe Obsession: Romantic and Virtuosic Works for Oboe \: \track
  \C{Camille Saint-Sa\"ens} Sonata for Oboe and Piano, Op. 166 \; \track
  \C{Francis Poulenc} Sonata for Oboe and Piano \; \track \C{Benjamin
  Britten} Six Metamorphoses after Ovid for Oboe Solo, Op. 49 \; \track
  \C{Robert Schumann} Three Romances for Oboe and Piano \; \track \C{W.
  F. Bach} Duet for Flute and Oboe, No.~4 in F~major \; \track \C{Makoto
  Shinohara} Obsession for Oboe and Piano}.
Janice Tipton (flute) and Bryan Pezzone (pian).
Delos International, 2000 \cdnum{DE 3235}.

\cd*\relax
\artist{Vo\v{r}{\'\i}\v{s}ek, Jan V\'aclav}.
\cdtitle{Symphony in D major}.
\see{46}.

\cd*\relax
\artist{Vosk, Jay}.
\cdtitle{Thaw \(1994\)}.
\see{1601}.

\cd*\relax
\artist{Vustin, Alexander}.
\cdtitle{Musique pour l'ange \(1995\)}.
\see{484}.

\cd*\relax
\artist{Waddle, P. Kellach}.
\cdtitle{Broken Icicle Twilight \and Severe Thunderstorm Warning}.
\see{1161}.

\cd*\relax
\artist{Wagenseil, Georg Christoph}.
\cdtitle{Concerto in E~flat major for Alto Trombone}.
\see{963}.

\cd\relax
\artist{Wagenseil, Georg Christoph}.
\cdtitle{Symphonien \: \track Symphony in C~Major, WV~361 \; \track
  Symphony in D~Major, WV~374 \; \track Symphony in E~Major, WV~393 \;
  \track Symphony in F~Major, WV~398 \; \track Symphony in A~Major,
  WV~421 \; \track Symphony in A~Major, WV~432 \; \track Celloconcerto
  in C~Major}.
Orchestra da Camera ``Salieri''.
Tam\'as P\'al, cond.
Arkadia, 1993 \cdnum{CDAK~130.1}.

\cd\relax
\artist{Wagner, Richard}.
\cdtitle{Das Rheingold}.
Kirsten Flagstad, George London, Set Svanholm and Gustav Neidlinger.
Wiener Philharmoniker.
Sir Georg Solti, cond.
The Decca Record Company, 1984 \cdnum[3]{414 101-2}.

\cd*\relax
\artist{Wagner, Richard}.
\cdtitle{Isoldens Liebestod}.
\see{158}.

\cd*\relax
\artist{Wagner, Richard}.
\cdtitle{Magic Fire Music \(\from Die Walk\"ure\)}.
\see{775}.

\cd*\relax
\artist{Wagner, Richard}.
\cdtitle{Parsifal: \emph{Prelude to the 2nd Act} and
  \emph{Karfreitagszauber} \and Tristan und Isolde: \emph{Vorspeil und
  Liebestod} \and Lohengrin: \emph{Prelude to the 1st Act} \and Die
  Meistersinger von N\"urnberg: \emph{Prelude to the 1st Act}}.
\see{627}.

\cd\relax
\artist{Wainwright III, Loudon}.
\cdtitle{History}.
Virgin Records, 1992 \cdnum{0777 7 86416 2~9}.

\cd\relax
\artist{Wainwright III, Loudon}.
\cdtitle{Therapy}.
Silvertone Records, 1989 \cdnum{1203-2-J}.

\cd\relax
\artist{Wainwright, Rufus}.
Dreamworks, 1998 \cdnum{drmd-50039}.

\cd\relax
\artist{Wainwright, Rufus}.
\cdtitle{Poses}.
Dreamworks, 2002 \cdnum{0044-50369-2}.
With bonus DVD.

\cd\relax
\artist{Wainwright, Rufus}.
\cdtitle{Want One}.
Geffen Records, 2003 \cdnum{B0000896-12}.

\cd\relax
\artist{Wainwright, Rufus}.
\cdtitle{Want Two}.
Geffen Records, 2004 \cdnum{B0003716-00}.

\cd\relax
\artist{Waits, Tom}.
\cdtitle{Blue Valentine}.
Elektra, 1978 \cdnum{162-2}.

\cd\relax
\artist{Waits, Tom}.
\cdtitle{Nighthawks at the Diner}.
Elektra/Asylum Records, 1975 \cdnum{2008-2}.

\cd\relax
\artist{Waits, Tom}.
\cdtitle{Rain Dogs}.
Island Records, 1985 \cdnum{422-826 382-2}.

\cd\relax
\artist{Waits, Tom}.
\cdtitle{Small Change}.
Elektra/Asylum Records, 1976 \cdnum{1078-2}.

\cd\relax
\artist{Waits, Tom}.
\cdtitle{Swordfishtrombones}.
Island Records, 1983 \cdnum{422-842 469-2}.

\cd\relax
\artist{Waits, Tom}.
\cdtitle{The Black Rider}.
Island Records, 1993 \cdnum{314-518 559-2}.

\cd\relax
\artist{Waits, Tom}.
\cdtitle{The Heart of Saturday Night}.
Elektra/Asylum Records, 1974 \cdnum{1015-2}.

\cd*\relax
\artist{Walker, George}.
\cdtitle{Concerto for Trombone and Orchestra \(1957\)}.
\see{961}.

\cd\relax
\artist{Walton, Sir William}.
\cdtitle{Cello Concerto \and Improvisations on an Impromptu of Benjamin
  Britten \and Passacaglia for solo cello \and Partita for Orchestra}.
Raphael Wallfisch.
The London Philharmonic.
Bryden Thomson, cond.
Chandos Records, 1991 \cdnum{CHAN~8959}.

\cd*\relax
\artist{Walton, William}.
\cdtitle{Concerto for Cello and Orchestra}.
\see{1002}.

\cd*\relax
\artist{Walton, William}.
\cdtitle{Concerto for Violin and Orchestra}.
\see{1}.

\cd\relax
\artist{Walton, William}.
\cdtitle{Fa\c{c}ade: An Entertainment: The Complete Extant Numbers \:
  \C{Constant Lambert} Suite from the incidental music to
  \emph{Salome}}.
Eleanor Bron (reciter) and Richard Stilgoe (reciter).
The Nash Ensemble.
David Lloyd-Jones, cond.
Hyperion, 2001 \cdnum{CDA66239}.

\cd\relax
\artist{Walton, William}.
\cdtitle{\track Johannesburg Festival Overture \; \track Viola Concerto
  \; \track Symphony No.~2}.
Lars Anders Tomter.
English Northern Philharmonia.
Paul Daniel, cond.
Naxos, 1996 \cdnum{8.553402}.

\cd*\relax
\artist{Walton, William}.
\cdtitle{Passacaglia for Violoncello Solo}.
\see{983}.

\cd*\relax
\artist{Ward, Robert}.
\cdtitle{Concerto for Tenor Saxophone and Orchestra}.
\see{799}.

\cd*\relax
\artist{Warren, Frank}.
\cdtitle{Music for Contrabassoon and Piano, op.~28}.
\see{1163}.

\cd\relax
\artist{Watts, Andr\'e}.
\cdtitle{Bach/Chopin/Debussy/Prokoviev/Stravinsky \: \track \C{Johann
  Sebastian Bach} Partita No.~4 in~D, BWV~828 \and Prelude and Fugue in
  A~minor, BWV~543 \and Prelude in B~minor \; \track \C{Fr\'ed\'eric
  Chopin} Nocturne in~B, Op.~62 No.~1 \and Nocturne in~E, Op.~62 No.~2
  \and \; \track \C{Carl Czerny} Variations on ``La Ricordanza'' \;
  \track \C{Claude Debussy} Estampes \; \track \C{Sergei Prokofiev}
  Piano Sonata No.~3 in A~minor, Op.~28 \and Suggestion diabolique
  \(from 4~Pieces, Op.~4\) \; \track \C{Sergei Rachmaninoff} Prelude in
  B~minor, Op.~32 No.~10 \and Piano Sonata No.~1 in D~minor, Op.~28 \;
  \track \C{Domenico Scarlatti} Sonata in A~minor, K.~109 \and Sonata
  in~F, K.~107 \and Sonata in B~minor, K.~87 \and Sonata in F~minor,
  K.~184 \; \track \C{Alexander Scriabin} Etude in B~flat minor, Op.~8
  No.~11 \and Nocturne in D~flat ``for the left hand'', Op.~9 No.~2 \;
  \track \C{Igor Stravinsky} 3 Movements from ``Pretrouchka''}.
Volume~97 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 988-2}.

\cd\relax
\artist{Watts, Andr\'e}.
\cdtitle{Gershwin/Debussy/Liszt/Rachmaninoff \: \track \C{Ludwig van
  Beethoven} 32 Variations in C~minor, WoO~80 \; \track \C{Fr\'ed\'eric
  Chopin} Etude in~C, Op.~10 No.~1 \and Etude in C~sharp minor, Op.~25
  No.~7 \and Etude in C~minor, Op.~25 No.~12 \; \track \C{Claude
  Debussy} Children's Corner \; \track \C{George Gershwin} Gershwin
  Songbook \; \track \C{Franz Liszt} Piano Concerto No.~1 in E~flat \and
  Grande \'Etude de Paganini No.~3 ``La campanella'' \and \'Etude
  d'ex\'ecution transcendante No.~10 in F~minor \and Hungarian Rhapsody
  No.~13 \and Totentanz \; \track \C{Sergei Rachmaninoff} Variations on
  a Theme by Corelli, Op.~42 \; \track \C{Franz Schubert} Fantasy in~C,
  D.~760 ``Wanderer-Fantasie''}.
Volume~96 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 985-2}.

\cd*\relax
\artist{Weber, Carl Maria von}.
\cdtitle{Aufforderung zum Tanz}.
\see{625}.

\cd\relax
\artist{Weber, Carl Maria von}.
\cdtitle{Der Freisch\"utz}.
Gundula Janowitz, Edith Mathis, Peter Schreier and Theo Adam.
Rundfunkchor Leipzig and Staatskapelle Dresden.
Carlos Kleiber, cond.
Deutsche Grammophon, 1973 \cdnum[2]{289 457 736-2}.

\cd*\relax
\artist{Weber, Carl Maria von}.
\cdtitle{Der Freisch\"utz: Overture}.
\see{628}.

\cd*\relax
\artist{Weber, Carl Maria von}.
\cdtitle{Grand Duo Concertant, Op.~48}.
\see{438}.

\cd*\relax
\artist{Weber, Carl Maria von}.
\cdtitle{Konzertst\"uck in F~minor, Op.~79}.
\see{336}.

\cd*\relax
\artist{Weber, Carl Maria von}.
\cdtitle{Konzertst\"uck in F~minor, Op.~79}.
\see{716}.

\cd*\relax
\artist{Weber, Carl Maria von}.
\cdtitle{Piano Sonata No.~2 in A~flat, Op.~39}.
\see{642}.

\cd*\relax
\artist{Weber, Carl Maria von}.
\cdtitle{Piano Sonata No.~4 in E~minor, Op.~70}.
\see{604}.

\cd*\relax
\artist{Webern, Anton}.
\cdtitle{Piano Variations, Op.~27}.
\see{1207}.

\cd*\relax
\artist{Webern, Anton}.
\cdtitle{Quartet op.~22 for violin, clarinet, tenor saxophone and
  piano}.
\see{1686}.

\cd*\relax
\artist{Weiner, Le\'o}.
\cdtitle{Romance for Cello and Piano, Op.~14}.
\see{804}.

\cd*\relax
\artist{Weisberg, Arthur}.
\cdtitle{From the Deep}.
\see{1164}.

\cd\relax
\artist{Weiss, Marcus}.
\cdtitle{Saxophone: Conquest of Melody \: \track \C{Elliott Carter}
  Inner Song \; \track \C{Stefan Wolpe} Quartet for Trumpet, Saxophone,
  Piano and Percussion \; \track \C{John Cage} Five$^4$ \; \track
  \C{Anton Webern} Quartet op.~22 for violin, clarinet, tenor saxophone
  and piano \; \track \C{Arnold Sch\"onberg} Canons arranged for
  saxophones \; \track \C{Stefan Wolpe} Conquest of Melody/Erobergun des
  Melos \; \track \C{John Cage} Four$^5$}.
Hat Hut Records, 1997 \cdnum{CD~6178}.

\cd*\relax
\artist{Westbrook, Mike}.
\cdtitle{Bean Rows and Blues Shots}.
\see{745}.

\cd\relax
\artist{Westwood Wind Quintet}.
\cdtitle{Woodwind Treasures \: \track \C{August Klughardt} Quintet,
  Op.~79 \; \track \C{Luciano Berio} Opus Number Zoo \; \track \C{George
  Heussenstamm} Seven Etudes for Oboe, Clarinet, and Bassoon \; \track
  \C{Boris Pillin} Scherzo \; \track \C{Robert Linn} Woodwin Quintet \;
  \track \C{Herman Stein} Sour Suite}.
John Barcellona (flute), Gretel Shanley (flute), Peter Christ (oboe),
  David Atkins (clarinet), Calvin Smith (horn), Robert Henderson (horn),
  Kenneth Meyer (bassoon) and Kay Brightman (bassoon).
Crystal Records, 2001 \cdnum{CD250}.

\cd\relax
\artist{White, Jim}.
\cdtitle{No Such Place}.
Luaka Bop, 2001 \cdnum{72438-49911-2-8}.

\cd\relax
\artist{Who, The}.
\cdtitle{The Ultimate Collection}.
MCA Records, 2002 \cdnum[2]{088 112 87702}.

\cd\relax
\artist{Widespread Panic}.
\cdtitle{Space Wrangler}.
Capricorn Records, 1992 \cdnum{42001-2}.

\cd\relax
\artist{Widespread Panic}.
\cdtitle{Widespread Panic}.
Capricorn Records, 1991 \cdnum{10001-2}.

\cd*\relax
\artist{Wieniawski, Henri}.
\cdtitle{Violin Concerto No.~2 in D minor, op.~22}.
\see{246}.

\cd*\relax
\artist{Wieniawski, Henry}.
\cdtitle{Th\`eme original vari\'e, op.~15 \and Scherzo-tarantelle,
  op.~16}.
\see{245}.

\cd*\relax
\artist{Wieniawski, Henryk}.
\cdtitle{Polonais brillante, Op.~21}.
\see{875}.

\cd\relax
\artist{Wild, Earl}.
\cdtitle{The Art of Transcription}.
Volume~98 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 991-2}.

\cd*\relax
\artist{Wilde, David}.
\cdtitle{The Cellist of Sarajevo}.
\see{1017}.

\cd*\relax
\artist{Williams, Ralph Vaughan}.
\cdtitle{Infant joy \and Cruelty has a human heart \and The piper \and
  Eternity \(\emph{from} Ten Blake Songs\)}.
\see{1344}.

\cd*\relax
\artist{Wilson, Ian}.
\cdtitle{I Sleep at Waking}.
\see{1053}.

\cd\relax
\artist{Wolf, Hugo}.
\cdtitle{Italienisches Liederbuch}.
Felicity Lott (sopran), Peter Schreier (tenor) and Graham Johnson
  (piano).
Hyperion, 1994 \cdnum{CDA66760S}.

\cd\relax
\artist{Wolf, Hugo}.
\cdtitle{Lieder}.
Dietrich Fischer-Dieskau (bariton) and Daniel Barenboim (piano).
Deutsche Grammophon, 1977 \cdnum[6]{447 515-2}.

\cd\relax
\artist{Wolf, Hugo}.
\cdtitle{Spanisches Liederbuch}.
Elisabeth Schwarzkopf (sopran), Dietrich Fischer-Dieskau (baritone) and
  Gerald Moore (piano).
Deutsche Grammophon, 1967 \cdnum[2]{289 457 726-2}.

\cd\relax
\artist{Wolf, Hugo}.
\cdtitle{The Hugo Wolf Society, 1931--1938: The Complete Edition}.
EMI Classics, 1998.

\cd*\relax
\artist{Wolpe, Stefan}.
\cdtitle{Quartet for Trumpet, Saxophone, Piano and Percussion \and
  Conquest of Melody/Erobergun des Melos}.
\see{1686}.

\cd*\relax
\artist{Woods, Edna Bentz}.
\cdtitle{Valse Phantastique}.
\see{724}.

\cd*\relax
\artist{Worley, John C.}
\cdtitle{Six Dances}.
\see{1604}.

\cd*\relax
\artist{Worley, John C.}
\cdtitle{Sonata for Alto Saxophone and Piano}.
\see{1605}.

\cd\relax
\artist{Wright, Robert and George Forrest}.
\cdtitle{Kismet}.
Rhino Music, 1996 \cdnum{R2~72482}.

\cd*\relax
\artist{Xenakis, Iannis}.
\cdtitle{Keren per trombone solo}.
\see{964}.

\cd*\relax
\artist{Ysaye, Eug\`ene}.
\cdtitle{Caprice d'apr\`es l'\'Etude en forme de valse de
  Saint-Sa\"ens}.
\see{247}.

\cd*\relax
\artist{Ysa\"ye, Eug\`ene}.
\cdtitle{Sonata for Cello solo Op.~28}.
\see{1258}.

\cd*\relax
\artist{Yuasa, Joji}.
\cdtitle{Not I, but the Wind\dots}.
\see{483}.

\cd\relax
\artist{Yudina, Maria}.
\cdtitle{Bach/Beethoven \: \track \C{Johann Sebastian Bach} ``Goldberg''
  Variations, BWV~988 \; \track \C{Ludwig van Beethoven} ``Diabelli''
  Variations, Op.~120 \and ``Eroica'' Variations, Op.~35}.
Volume~99 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 994-2}.

\cd*\relax
\artist{Yun, Isang}.
\cdtitle{Monologue for Basson}.
\see{847}.

\cd\relax
\artist{Zaretsky, Michael and Xak Bjerken}.
\cdtitle{Black Snow \: \track \C{Michail Ivanovich Glinka} Sonata for
  viola and piano \; \track \C{Dmitri Dmitrievich Shostakovich} Sonata
  for viola and piano \; \track \C{Jakov Jakoulov} Sonata for viola and
  piano \and Mikhail Glinka. Valse-fantaisie. Stylistic reminiscences.}
Artona, 1998.

\cd\relax
\artist{Zeuthen, Morten}.
\cdtitle{L'Homme Arm\'e: Works for Solo Cello \: \track \C{Poul Ruders}
  Bravour Studies for Solo Cello over ``L'Homme arm\'e'' \; \track
  \C{Karl Aage Rasmussen} Silhouette to a Poem by Naja Marie Aidt \;
  \track \C{Andy Pape} Siciliano Sconfortevole \; \track \C{Niels
  Rosing-Schow} Siciliana \; \track \C{Svend Nielsen} Siciliano, ``Once
  upon a Time'' \; \track \C{Per N{\o}rg{\aa}rd} Sonate Breve: Sonata
  for Solo Cello No.~3 ``What---is the word!'' \; \track \C{Hans
  Abrahamsen} Sonata for Solo Cello \; \track \C{Vagn Holmboe} Sonata
  for Solo Cello, Opus~101}.
dacapo, 2005 \cdnum{8.226007}.

\cd\relax
\artist{Zevon, Warren}.
\cdtitle{Excitable Boy}.
Elektra/Asylum Records, 1978 \cdnum{118-2}.

\cd*\relax
\artist{Zhang, Xiaofeng}.
\cdtitle{Parting of the Newly Wedded}.
\see{416}.

\cd*\relax
\artist{Zhu, Xiaogu}.
\cdtitle{Love in Spring \and Parting of the Newly Wedded}.
\see{416}.

\cd\relax
\artist{Zimerman, Krystian}.
\cdtitle{Brahms/Chopin/Debussy/Liszt \: \track \C{Johannes Brahms}
  Scherzo in E~flat minor, Op.~4 \and Piano Concerto No.~2 in B~flat,
  Op.~83 \; \track \C{Fr\'ed\'eric Chopin} Ballade No.~4 in F~minor,
  Op.~52 \and Fantaisie in F~minor, Op.~49 \; \track \C{Claude Debussy}
  Pr\'eludes, Book~1, Nos.~1, 5, 10--12 \and Pr\'eludes, Book~2, Nos.~5
  and~9 \; \track \C{Franz Liszt} Fun\'erailles \and Totentanz \(Dans
  macabre\)}.
Volume~100 of \emph{Great Pianists of the 20th Century}.
Philips Classics, 1998 \cdnum[2]{456 997-2}.

\cd*\relax
\artist{Zimmermann, Walter}.
\cdtitle{Fragmente der Liebe}.
\see{578}.

\cd\relax
\artist{Zwilich, Ellen Taaffe}.
\cdtitle{\track Chamber Symphony \(1979\) \; \track Concerto for Violin,
  Cello and Orchestra ``Double Concerto'' \(1991\) \; \track Symphony
  No.~2 ``Cello'' \(1985\)}.
Jaime Laredo (violin) and Sharon Robinson (cello).
The Louisville Orchestra.
Lawrence Leighton Smith and Albert-George Schram, cond.
First Edition Music, 2004 \cdnum{FECD-0004}.

\cd*\relax
\artist{Zwilich, Ellen Taaffe}.
\cdtitle{Concerto for Trombone and Orchestra \(1988\)}.
\see{961}.

\end{enumerate}
