\documentclass[twocolumn]{article}

\setcounter{secnumdepth}{-1}

% The Towers of Trebizond
% by Rose Macaulay, Jan Morris (Introduction)

\usepackage{fullpage}

{\catcode`\^^M=\active % these lines must end with %
\gdef\C#1^^M{\par\bigskip\noindent\textbf{#1}\par\nobreak}%
\gdef\T#1^^M{\par\emph{#1}\par}%
\gdef\R#1^^M{\par\enskip-- {\small #1}\par}%
}

\renewcommand{\a}[1]{\textsc{#1}}
\renewcommand{\t}[1]{\textsl{#1}}

\def\A{\hfill\break\noindent\llap{\hbox to 10pt{\hfill--\hfill}}}

\begin{document}

\begin{center}
Classical Good CD Guide 1999 \\
Suggested Basic Library
\end{center}

\frenchspacing

\small

\begin{obeylines}

%%  \C Berg
%%  \T  Violin Concerto
%%      \R Ozawa/Perlman, DG 2894474452, 23(2):215

\C Berlioz
\T   Grand messe des morts
    \R Naxos 8.554494-95, Edison, cond. 23(3):208
    \R BBC Music BBCL 4011-2.  Beecham.  23(2):216

\C Bernstein
\T   West Side Story

\C Bizet
\T  L'Arlesienne---Concert Suites Nos. 1 and 2
    \R Robert Haydon Clark.  Collins.  23(2):219
\T  Symphony in C major

\C Britten
\T  Les illuminations
\T  War Requiem
\T  The Young Person's Guide to the Orchestra
    \R Decca/London.  Britten.  23(2):224
    \R RCA.  Slatkin.  23(2):224

\C Chabrier
\T  Espana

\C Delius
\T  Brigg Fair
\T  In a summer garden
\T  On hearing the first cuckoo in Spring
\T  Sea Drift
\T  A Village Romeo and Juliet---Walk to the Paradise Garden
    \R Beecham, EMI 5~675532

\C Donizetti
\T  L'elisir d'amore

\C Dvo\v{r}\'ak
\T  Piano Quintet
    \R Richter on Revelation.  23(3):243

\C Elgar
\T  The Dream of Gerontius
\T  Introduction and Allegro for Strings
\T  Variations on an Original Theme, ``Enigma''
    \R Sony SK 60789.  Barenboim.
    \R Telarc.  Zinman.  Baltimore SO.
    \R Argo. Mackerras.  Royal Phil.
    \R 23(2):248

\C Falla
\T  Noches en los jardines de Espana
\T  El sombrero de tres picos

\C Franck
\T  Symphony in D minor

\C Gershwin
%%  \T  Piano Concerto
\T  Porgy and Bess
    \R Rattle EMI CDCC 56220

%%  \C Lalo
%%  \T  Symphonie espagnole

\C Lehar
\T  Die Lustige Witwe

\C Mahler
%%  \T  Kindertotenlieder
%%      \R EMI 5 66996 2.  Janet Baker.  23(3):280
\T  Symphony No. 1
    \R DG 289 459 610-2, Boulez.  23(1):272

\C Mascagni
\T  Cavalleria Rusticana

\C Massenet
\T  Werther
    \R Nagano.  Erato(?).  21(4), 22(3).
    \R EMI 7243 5 5682024.  Pappano, cond.  London SO

\C Mendelssohn
\T  A Midsummer Night's Dream---incidental music
\T  Octet
\T  Symphony No. 3, ``Scottish''
\T  Symphony No. 4, ``Italian''
\T  Symphony No. 5, ``Reformation''

\C Mozart
\T  Sinfonia concertante for violin and viola
\T  Symphony No. 36, ``Linz''
\T  Symphony No. 39
    \R Mackerras/Prague Chamber Orchestra/Teldec (symphonies)

\C Paganini
\T  Violin Concerto No. 1

\C Prokofiev
\T  Romeo and Juliet
    \R Ozawa
\T  Symphony No. 5
    \R Koussevitsky
    \R Martinon/Box CDX 5001, 5054

\C Puccini
%%  \T  La boheme
%%      \R EMI Callas/Di Stefano. 23(3):314
%%      \R Decca 289 466 070-2.  Chailly, cond.
%%  \T  Madama Butterfly
%%      \R Barbirolli or Leinsdorf 1.  23(1):322
\T  Tosca

\C Rossini
\T  La Cenerentola
    \R Bartoli on London.  23(1):337
\T  Stabat mater
    \R DG.  Chung.  23(3):324

\C Shostakovich
\T  Symphony No. 10
    \R BIS CD-973/974.  Wigglesworth.  BBC Nat. O. of Wales

\C J. Strauss II
\T  Die Fledermaus
\T  Various Waltzes, Polkas and Overtures
    \R Eloquence 289 476 413 2

\C R. Strauss
\T  Metamorphosen
    \R EMI.  Karajan.  Vienna Phil.  1947
\T  Der Rosenkavalier

\C Tchaikovsky
\T  Sleeping Beauty---ballet suite
\T  Swan Lake

\C Tippett
\T  Piano Concerto
\T  Symphony No. 2

\C Vaughan Williams, Ralph
\T  Serenade to Music
\T  Symphony No. 2
    \R Haitink/London PO/EMI

\C Verdi
\T  Aida
    \R Solti, Karajan~1, Levine
    \R Muti EMI 67617
\T  Falstaff
    \R Abbado DG 471194
\T  Otello
\T  Requiem
\T  La traviata

\C Wagner
\T  Parsifal
\T  The Ring---Die Walkure
\T  Siegfried Idyll

\C Walton
\T  Belshazzar's Feast

\end{obeylines}

\bigskip

\noindent
(c) 1998 Gramophone Publications Limited

\bigskip

\newpage

\subsection{Miscellaneous CDs}

\leavevmode

\begingroup

\leftskip10pt

\parindent-10pt

\parskip 9pt

Bethany and Rufus, \emph{900 Miles}.

Marty Ehrlich. \emph{News on the Rail}.

Las Rubias del Norte

``Radar Love''

Brautigam, Ronald.  Mozart and Beethoven on BIS (or Decca?)

%%* Scarlatti, Domenico.  \emph{60 Sonatas}.  Carlo Grant.  Dante PSG
%%* 9642/44.

Schubert. \emph{String Quartets} (complete). Leipzig Str Qr. MDG 307
0601-09 (9 separate CDs).

%%  Bach, Various Composers.
%%  \emph{Pathways of Baroque Music---Cathedrals and Chapels}.
%%  The Academy of Ancient Music and others.
%%  HMX 2908006.0E.

%%  Gorecki
%%  \emph{Symphony No. 3}
%%  Kozlowska/Kord/Philips 442 411-2

%%  VIVE LA FRANCE: Patrimoine Series. Works by TOURNEMIRE, KOECHLIN,
%%  D'INDY, LE FLEM, HOLM\`ES, SCHMITT, BRUNEAU, et al. (NAXOS; twenty
%%  titles to date)
%%*
%%* \a{Milhaud}.
%%* \t{Saudades do Brazil. La Muse m\'enag\`ere. L'Album de Madame Bovary}.
%%* %%  Tharaud, M. Milhaud.
%%* (NAXOS 8.5534430)
%%*
%%* \a{Szymowski}.
%%* \t{Stabat Mater. Veni Creator. Litania do Marii Panny. Demeter. Penthesilea}.
%%* %%  Stryja/Gadulanka, Szostek-Radkowa, Hiolski, Zag\'orzanka,
%%* %%  Malewicz-Madej, Owsinka/ Polish St PO & Ch
%%* NAXOS 8.553687
%%*
%%* \a{Machaut}.
%%* \t{Messe de Notre Dame. Le Voir Dit}.
%%* %%  Summerly/Oxford Camerata
%%* NAXOS 8.553833

%%* \a{Bach}.
%%* \t{Motets}.
%%* NAXOS 8.553823.

%%* Brian Terfel.  Opera Arias.  DG 445 866-2

Vellones.  Glazunov.  Keuris.  The New Sax Project.  AC 95003.
23(3):359

Kurt Weil/Berthold Brecht song.

Zwilich, Ellen Taaffe.  \emph{Peanuts Gallery for Piano and
  Orchestra}.  (No recording yet as of May 2004)

%%  We hear and discuss classical music that has been inspired by -- or
%%  created in response to -- war. PLAYLIST: Edward Elgar: Cello Concerto,
%%  3rd movement, Benjamin Britten: War Requiem, Lacrimosa/ "Move Him into
%%  the Sun," Dmitri Shostakovich: Symphony No. 8 in c-minor, 1st
%%  movement, Kurt Weill: "Zu Potsdam" from "Ute Lemper sings Kurt Weill,"
%%  Olivier Messiaen: Quartet for the End of Time

%%  BRAHMS
%%  Complete Piano Music. The 2 Piano Concertos. SCHUMANN
%%  Introduction and Allegro appassionato. Introduction and Allegro.
%%  Biret/Wit/Polish Natl RSO. NAXOS 8.501201 (12 CDs priced as 9)

%%  NAXOS HISTORICAL SERIES: Arturo Toscanini conducting the NBC Symphony
%%  Orchestra. NAXOS 8.110801-07 and 8.110809-12 (11 separate CDs)

\endgroup

\subsubsection{Cowboy Junkies}

\begin{itemize}

\item\emph{In the Time before Llamas} (2003)

\end{itemize}

\subsubsection{Greg Brown}

\begin{itemize}

\item\emph{Hacklebarney} (1974) (with Dick Pinney) (LP only)
\item\emph{Solid Heart} (1999) (benefit CD)

\end{itemize}

\subsubsection{Bob Dylan}

\begin{itemize}

% \item Bob Dylan (1962)
% \item The Freewheelin' Bob Dylan (1963)
% \item The Times They Are a-Changin' (1964)
% \item Another Side of Bob Dylan (1964)
% \item Bringing It All Back Home (1965)
% \item Highway 61 Revisited (1965)
% \item Blonde on Blonde (1966)
% \item John Wesley Harding (1967)
% \item Nashville Skyline (1969)
\item Self Portrait (1970)
% \item New Morning (1970)
% \item Pat Garrett \& Billy the Kid (1973)
\item Dylan (1973)
\item Before the Flood (1974)
% \item Planet Waves (1974)
% \item Blood on the Tracks (1975)
% \item The Basement Tapes (1975)
% \item Desire (1976)
% \item Hard Rain (1976)
% \item Street Legal (1978)
% \item Slow Train Coming (1979)
\item Bob Dylan at Budokan (1979)
% \item Saved (1980)
% \item Shot of Love (1981)
% \item Infidels (1983)
% \item Real Live (1984)
% \item Empire Burlesque (1985)
% \item Knocked Out Loaded (1986)
% \item Down in the Groove (1988)
% \item Dylan and the Dead (1989)
% \item Oh Mercy (1989)
% \item Under the Red Sky (1990)
% \item Good as I Been to You (1992)
% \item World Gone Wrong (1993)
\item MTV Unplugged (1995)
% \item Time Out of Mind (1997)
\item Live 1961--2000: Thirty-Nine Years of Great Concert Performances
\item "Love and Theft" (2001)
\item Live at the Gaslight 1962 (2005)
\item Live at Carnegie Hall 1963 (2005)
\item Modern Times (2006)
\item Live Classics (a.k.a. Classics Live) (2007)
\item Together Through Life (2009)
\item Christmas in the Heart (2009)
\item In Concert---Brandeis University 1963 (2010)
\item Tempest (2012)
\item Shadows in the Night (2015)
\item The Real Royal Albert Hall 1966 Concert (2016)
\item Live in Sydney 1966 (2016)
\item Fallen Angels (2016)
\item Triplicate (2017)
\item Live 1962--1966: Rare Performances from the Copyright Collections (2018)
% \item More Blood, More Tracks (2018)
% \item The Rolling Thunder Revue: The 1975 Live Recordings (2019)
% \item Rough and Rowdy Ways (2020)

\end{itemize}

\subsubsection{Se\'an Keane}

\begin{itemize}

\item\emph{The Man That I Am} (2000)
% \item\emph{Seansongs} (2002)
\item\emph{Portrait---The Best of Seane Keane} (2003)
% \item\emph{You Got Gold} (2006)
\item\emph{An Irish Scattering} (2008)
\item\emph{Valley of the Heart} (2009)
\item\emph{Never Alone} (2013)
\item\emph{Christmas by the Hearth} (2014)

\item\emph{The Irish Scattering} (DVD) (2008).
\item\emph{Se\'an Keane} (DVD) (2016).

\end{itemize}

\begin{itemize}

\item\emph{Hacklebarney} (1974) (with Dick Pinney) (LP only)
\item\emph{Solid Heart} (1999) (benefit CD)

\end{itemize}

\newpage

\subsection{Books}

\begin{itemize}

\item Asimov, Isaac:
\begin{itemize}
%%  \item \emph{The Currents of Space} (1952)
\item 6. \emph{Prelude to Foundation} (1988)
\item 7. \emph{Forward the Foundation} (1993)
\end{itemize}

\item Benson, E. F.:
\begin{enumerate}
\item[1.] \emph{Queen Lucia}, 1920.
\item[2.] \emph{Miss Mapp}, 1922.
\item[3.] \emph{Lucia in London}, 1927.
\item[4.] \emph{Mapp and Lucia}, 1931.
\item[5.] \emph{Lucia's Progress}, 1935 (aka \emph{The Worshipful Lucia})
\item[6.] \emph{Trouble for Lucia}, 1939.
\end{enumerate}

\item
Pynchon, Thomas.  \emph{Against the Day}.

\end{itemize}

\subsubsection{Rex Stout (Nero Wolfe)}

\begin{itemize}

\item \emph{The Red Box}, 1937
\item \emph{Too Many Cooks}, 1938
\item \emph{Where There's a Will}, 1940
\item \emph{Too Many Women}, 1947

\bigskip

\item \emph{Trouble in Triplicate}, 1949
\item \emph{Three Doors to Death}, 1950
\item \emph{In the Best Families} (\emph{Even in the Best Families}), 1950
\item \emph{Curtains for Three}, 1951
\item \emph{Murder by the Book}, 1951
\item \emph{Triple Jeopardy}, 1952
\item \emph{Three Men Out}, 1954
\item \emph{The Black Mountain}, 1954
\item \emph{Before Midnight}, 1955
\item \emph{Three Witnesses}, 1956
\item \emph{Might As Well Be Dead}, 1956
\item \emph{If Death Ever Slept}, 1957
\item \emph{Plot It Yourself} (\emph{Murder in Style}), 1959
\item \emph{Too Many Clients}, 1960
\item \emph{The Final Deduction}, 1961
\item \emph{Homicide Trinity}, 1962
\item \emph{Gambit}, 1962
\item \emph{The Mother Hunt}, 1963
\item \emph{Trio for Blunt Instruments}, 1964
\item \emph{Death of a Doxy}, 1966
\item \emph{The Father Hunt}, 1968
\item \emph{Death of a Dude}, 1969
\item \emph{Please Pass the Guilt}, 1973
\item \emph{A Family Affair}, 1975
\item \emph{Death Times Three}, 1985

\end{itemize}

\subsubsection{Companions to Greek and Roman Tragedy}

% \paragraph{Aeschylus}

% \begin{itemize}

% \item Aeschylus: Agamemnon, by Barbara Goward
% \item Aeschylus: Eumenides, by Robin Mitchell-Boyask
% \item Aeschylus: Libation Bearers, by C. W. Marshall
% \item Aeschylus: Persians, by David Rosenbloom
% \item Aeschylus: Prometheus Bound, by Ian Ruffell
% \item Aeschylus: Seven against Thebes, by Isabelle Torrance
% \item Aeschylus: Suppliants, by Thalia Papadopoulou

% \end{itemize}

\paragraph{Euripides}

\begin{itemize}

% \item Euripides: Alcestis, by Niall W. Slater
% \item Euripides: Bacchae, by Sophie Mills
\item Euripides: Children of Heracles, by Florence Yoon
% \item Euripides: Cyclops, by Carl A. Shaw
\item Euripides: Electra, by Rush Rehm, 2020
% \item Euripides: Hecuba, by Helene P. Foley
% \item Euripides: Heracles, by Emma Griffiths
% \item Euripides: Hippolytus, by Sophie Mills
% \item Euripides: Ion, by Laura Swift
\item Euripides: Iphigenia among the Taurians, by Isabelle Torrance
% \item Euripides: Iphigenia at Aulis, by Pantelis Michelakis
% \item Euripides: Medea, by William Allan
\item Euripides: Orestes, by Matthew Wright
\item Euripides: Phoenician Women, by Thalia Papadopolou
\item Euripides: Suppliant Women, by Ian C. Storey
\item Euripides: Trojan Women, by Barbara Goff

\medskip

\item Euripides: Andromache, TBD
\item Euripides: Helen, TBD
\item Euripides: Rhesus, TBD

\end{itemize}

\paragraph{Sophocles}

\begin{itemize}

% \item Sophocles: Ajax, by John Hesk
% \item Sophocles: Antigone, by Douglas Cairns
% \item Sophocles: Electra, by Michael Lloyd
% \item Sophocles: Oedipus at Colonus, by Adrian Kelly
% \item Sophocles: Philoctetes, by Hanna M. Roisman
% \item Sophocles: Women of Trachis, by Brad Levett

\item Sophocles: Oedipus Rex, TBD

\end{itemize}

\paragraph{Seneca}

\begin{itemize}

\item Seneca: Hercules Furens, by Neil Bernstein
\item Seneca: Medea, by Helen Slaney
\item Seneca: Oedipus, by Susanna Braund
\item Seneca: Phaedra, by Roland Mayer
\item Seneca: Thyestes, by P. J. Davis

\end{itemize}

\subsubsection{Blackwell History of the Ancient World}

\begin{itemize}

\item * A History of Ancient Egypt (2ed)
\item * A History of Ancient Persia
\item * A History of the Ancient Near East (2ed) [3ed]
\item * A History of the Archaic Greek World
\item * A History of Babylon
\item * A History of Byzantium
\item * A History of the Classical Greek World
\item * A History of Greece
\item * A History of the Hellenistic World
\item * A History of the Later Roman Empire (2ed)

\bigskip

\item A History of the Roman Republic [in preparation]
\item A History of the Roman Empire [in preparation]

\end{itemize}

\newpage

\subsubsection{Movies}

\begin{itemize}

\item Futuro Beach
\item The Circle
\item Tiger Orange
\item I Am Happiness on Earth
\item Jamie Marks Is Dead
\item The Way He Looks
\item North Sea Texas

\end{itemize}

\subsubsection{Rentals}

\begin{itemize}

\item Head On

\end{itemize}

\end{document}

5, 47, 540, 1256, 1269, 404, 815, 816, 353

Straus:
    Don Quixote

===========================================================================

 --- Moody Blues's [forgot the name, "Nights in white satin", "Breathe
   deep the evening gloom ..."] album.

Hendrix: Purple Haze, Wind Cries Mary

White Room (Jack Bruce/Pete Brown)

===========================================================================

Recommendations from Marsalis on ``Talk of the Nation'', 9 Sep 2008

Art Tatum solo piano

Thelonious Monk plays Duke Ellington
